### 2017-02-07 Moltres.tex
Pare down tex file to only the Model Description.

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage[export]{adjustbox}
\graphicspath{{./figures/}}
% hyperref usually has to go last
\usepackage[hidelinks]{hyperref}
% but glossaries behaves best if after hyperref
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
% cleveref only behaves if after hyperref & glossaries
\usepackage{cleveref}

\let\Oldsection\section
\renewcommand{\section}{\FloatBarrier\Oldsection}

\let\Oldsubsection\subsection
\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}

\let\Oldsubsubsection\subsubsection
\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}

\newcommand{\code}[1]{\texttt{#1}}

\title{Introduction to Moltres: an Application for Simulation of Molten Salt Reactors}
\author{Alexander Lindsay, Kathryn Huff}

\begin{document}
\maketitle

\section{Model Description}

Neutrons are described with time-dependent multi-group diffusion theory as shown
in \cref{eq:neutrons}:

\begin{equation}
\frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
+ \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
\nu \Sigma_{g'}^f \phi_{g'}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'} + \sum_i^I \lambda_i \chi_g^{d,i} C_i
\label{eq:neutrons}
\end{equation}

\textbf{Note that at present we do not have the neutron source term from decay
  of delayed neutron precursors. Currently coupling with precursors is only one
  way, e.g. precursors are a function of temperature and neutron flux and not
  the other way around. This reverse coupling should be added before publication.}

Delayed neutron precursors are described by \cref{eq:precursors}:

\begin{equation}
\frac{\partial C_i}{\partial t} = \sum_{g'= 1}^G \beta_i \nu \Sigma_{g'}^f
\phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u C_i
\label{eq:precursors}
\end{equation}

with the last term representing the effect of fuel advection.

\FloatBarrier
\clearpage
\printglossary[type=\acronymtype]
%% \bibliographystyle{unsrt}
%% \bibliography{Moltres}
\end{document}

### 2017-02-07 acros.tex
Pare down tex file to only the Model Description.

%\newacronym{<++>}{<++>}{<++>}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{API}{API}{application programming interface}
\newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
\newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
\newacronym{BDBE}{BDBE}{Beyond Design Basis Event}
\newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
\newacronym{CI}{CI}{continuous integration}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{CTAH}{CTAHs}{Coiled Tube Air Heaters}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{DBE}{DBE}{Design Basis Event}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{DRACS}{DRACS}{Direct Reactor Auxiliary Cooling System}
\newacronym{DRE}{DRE}{dynamic resource exchange}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{EP}{EP}{Engineering Physics}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{FHR}{FHR}{Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
\newacronym{gpm}{gpm}{gallons per minute}
\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
\newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}
\newacronym{HTGR}{HTGR}{High Temperature Gas-Cooled Reactor}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{LMFBR}{LMFBR}{Liquid-Metal-cooled Fast Breeder Reactor}
\newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
\newacronym{LOHS}{LOHS}{Loss of Heat Sink}
\newacronym{LOLA}{LOLA}{Loss of Large Area}
\newacronym{LP}{LP}{linear program}
\newacronym{MA}{MA}{minor actinide}
\newacronym{MCNP}{MCNP}{Monte Carlo N-Particle code}
\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{MOAB}{MOAB}{Mesh-Oriented datABase}
\newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
\newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{MSR}{MSR}{Molten Salt Reactor}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NSSC}{NSSC}{Nuclear Science and Security Consortium}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{ORION}{ORION}{ORION}
\newacronym{ORNL}{ORNL}{Oak Ridge National Laboratory}
\newacronym{PARCS}{PARCS}{Purdue Advanced Reactor Core Simulator}
\newacronym{PBAHTR}{PB-AHTR}{Pebble Bed Advanced High Temperature Reactor}
\newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{PH}{PRONGHORN}{PRONGHORN}
\newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
\newacronym{PSPG}{PSPG}{Pressure-Stabilizing/Petrov-Galerkin}
\newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
\newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
\newacronym{PyRK}{PyRK}{Python for Reactor Kinetics}
\newacronym{QA}{QA}{quality assurance}
\newacronym{RDD}{RD\&D}{Research Development and Demonstration}
\newacronym{RD}{R\&D}{Research and Development}
\newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
\newacronym{RIA}{RIA}{Reactivity Insertion Accident}
\newacronym{RIF}{RIF}{Region-Institution-Facility}
\newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{SKB}{SKB}{Svensk K\"{a}rnbr\"{a}nslehantering AB}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{STC}{STC}{specific temperature change}
\newacronym{SUPG}{SUPG}{Streamline-Upwind/Petrov-Galerkin}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{SWU}{SWU}{Separative Work Unit}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
\newacronym{ThOX}{ThOX}{thorium oxide}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{UML}{UML}{Unified Modeling Language}
\newacronym{UOX}{UOX}{uranium oxide}
\newacronym{UQ}{UQ}{uncertainty quantification}
\newacronym{US}{US}{United States}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{VV}{V\&V}{verification and validation}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}

### 2017-02-07 Moltres.tex
Update on moltres results.

@@
 \usepackage[margin=1in]{geometry}
+\renewcommand{\topfraction}{0.9}
+\renewcommand{\bottomfraction}{0.8}
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\textfraction}{0.07}
+\renewcommand{\floatpagefraction}{0.7}
 \usepackage{graphicx}
@@
 
-with the last term representing the effect of fuel advection.
+with the last term representing the effect of fuel advection. The governing
+equation for the temperature is given by:
+
+\begin{equation}
+  \rho_fc_{p,f}\frac{\partial T_f}{\partial t} + \nabla\cdot\left(\rho_f c_{p,f}
+  \vec{u}\cdot T_f -k_f\nabla T_f\right) =  Q_f
+  \label{eq:fuel_temp}
+\end{equation}
+
+in the fuel and by:
+
+\begin{equation}
+  \rho_gc_{p,g}\frac{\partial T_g}{\partial t} + \nabla\cdot\left(-k_g\nabla T_g\right) =  Q_g
+  \label{eq:moderator_temp}
+\end{equation}
+
+in the moderator. $Q_f$ is defined by:
+
+\begin{equation}
+  Q_f = \sum_{g=1}^G \epsilon_{f,g}\Sigma_{f,g}\phi_g
+  \label{eq:fuel_source}
+\end{equation}
+
+and $Q_g$ is equal to $\gamma Q_f$, representing heat dissipation by gamma and
+neutron irradiation in the moderator.
+
+\section{Results \& Discussion}
+
+\subsection{Continuous Galerkin for Temperature with Isotropic Stabilization}
+
+\Cref{fig:cg_group1,fig:cg_group2} show expected cosinusoidal shapes for the
+fast and thermal group fluxes with respect to the axial coordinate. Fast group neutrons
+show a slight preference for the fuel region, while the thermal group slightly
+prefers the moderator as we would intuitively expect.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{nt_group_1.png}
+  \caption{Fast group neutron flux for Continuous Galerkin discretization}
+  \label{fig:cg_group1}
+\end{figure}
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{nt_group_2.png}
+  \caption{Thermal group neutron flux for Continuous Galerkin discretization}
+  \label{fig:cg_group2}
+\end{figure}
+
+In \cref{fig:cg_temperature} we see that the reactor outlet temperature is
+around 992 K, which is within the realm of physical possiblity. The temperature
+monotonically increases with increasing axial coordinate in the direction of
+flow; radial profiles are uniform.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{temperature.png}
+  \caption{Temperature for Continuous Galerkin discretization}
+  \label{fig:cg_temperature}
+\end{figure}
+
+\Cref{fig:cg_longest_precursor,fig:cg_shortest_precursor} show the profiles of
+the longest and shortest lived precursors respectively. The longest lived
+precursor concentration peaks at the reactor outlet, while the shortest lived
+precursor shows a maximum concentration at approximately z = 85 cm. The use of
+constant monomial basis functions for the precursor solution approximation is
+evident in the elemental visualizations.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{longest_lived_precursor.png}
+  \caption{Longest lived precursor for Continuous Galerkin discretization}
+  \label{fig:cg_longest_precursor}
+\end{figure}
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{shortest_lived_precursor.png}
+  \caption{Shortest lived precursor for Continuous Galerkin discretization}
+  \label{fig:cg_shortest_precursor}
+\end{figure}
+
+\FloatBarrier
+
+\subsection{Discontinuous Galerkin for Temperature}
+
+Moving to a discontinuous Galerkin discretization and removing isotropic
+stabilization yields a dramatically different temperature profile, as shown in
+\cref{fig:dg_temperature}. With dramatically reduced heat flux due to removal of
+artificial conduction, the outlet temperature of the reactor is now 1119 K,
+about 130 K higher than the \gls{CG} case shown in \cref{fig:cg_temperature}.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_temperature.png}
+  \caption{Temperature for Discontinuous Galerkin discretization}
+  \label{fig:dg_temperature}
+\end{figure}
+
+As shown in \cref{fig:dg_group1,fig:dg_group2}, the shapes of the neutron flux
+distributions do not change with the move to \gls{DG}. The magnitudes of the
+fluxes do increase by about 35\%.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_group1.png}
+  \caption{Fast group neutron flux for Discontinuous Galerkin discretization}
+  \label{fig:dg_group1}
+\end{figure}
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_group2.png}
+  \caption{Thermal group neutron flux for Discontinuous Galerkin discretization}
+  \label{fig:dg_group2}
+\end{figure}
+
+\FloatBarrier
+
+\subsection{DG Temperature with Moderator Heat Source}
+
+The \gls{MSR} model can be modified by adding a heat source in the moderator
+corresponding to gamma heating and neutron irradiation \cite{robertson_conceptual_1971}.
+
+Introduction of the moderator heat source further modifies the reactor
+temperature profile as shown in
+\cref{fig:dg_mod_source_temperature,fig:dg_mod_source_temperature_outlet}. Without
+the moderator heat source, the maximum temperature in the reactor for \gls{CG}
+and \gls{DG} discretizations is 992 and 1119 K respectively. These maxima both
+occur at the reactor outlet and are more or less uniform over the radial
+coordinate. However, with the addition of the moderator heat source, the reactor
+temperature maximum rises to a somewhat absurd 1615 K (this is only 88 K below
+the boiling point of \gls{FLiBe}). The location of the maximum is in the top right
+corner of the simulation domain, corresponding to the middle of the graphite
+moderator in a periodic lattice arrangement.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_mod_source_temperature_full_domain.png}
+  \caption{Temperature for Discontinuous Galerkin discretization with moderator
+    heat source}
+  \label{fig:dg_mod_source_temperature}
+\end{figure}
+
+The temperature profile at the top of the reactor is no longer uniform with
+respect to the radial coordinate as shown in
+\cref{fig:dg_mod_source_temperature_outlet}. From the right edge of the
+simulation domain (r = R$_2$), the graphite temperature decreases from its
+maximum value of 1615 K to a value of about 1200 K at the fuel/graphite
+interface. At the interface, perhaps due to the \gls{DG} discretization and the
+order of magnitude difference in diffusion coefficients, there is a shock and
+temperature oscillations in the fuel. After the oscillations are damped, the
+fuel outlet temperature is uniform between r = 0 and 1.2 cm at a value of
+approximately 990 K. This corresponds fairly closely to the outlet temperature
+calculated in the isotropically stabilized \gls{CG} simulation, but the
+correspondence is believed to be purely coincidental.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_mod_source_temperature_outlet.png}
+  \caption{Fuel outlet temperature profile for Discontinuous Galerkin
+    discretization with moderator heat source}
+  \label{fig:dg_mod_source_temperature_outlet}
+\end{figure}
+
+\Cref{fig:dg_mod_source_group1,fig:dg_mod_source_group2} show the neutron fluxes
+for the moderator heat source simulation case. Spatial shapes are the same as
+the previous two simulation cases; howevever, the flux magnitudes are
+less. A comparison of maximum flux magnitudes between the three simulation cases
+is shown in \cref{tab:max_fluxes}.
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_mod_source_group1.png}
+  \caption{Fast group neutron flux for Discontinuous Galerkin discretization
+    with moderator heat source}
+  \label{fig:dg_mod_source_group1}
+\end{figure}
+
+%% \begin{figure}[H]
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=.5\textwidth]{dg_mod_source_group2.png}
+  \caption{Thermal group neutron flux for Discontinuous Galerkin discretization
+    with moderator heat source}
+  \label{fig:dg_mod_source_group2}
+\end{figure}
+
+\begin{table}[htpb]
+    \begin{center}
+      \begin{tabular}{l|c|c}
+        Simulation Case & Maximum Fast Flux ($10^{15}\frac{\#}{cm^2s}$) & Maximum Thermal
+        Flux ($10^{15}\frac{\#}{cm^2s}$)\\
+        \hline \hline
+        \gls{CG} & 3.488 & 1.785 \\
+        \gls{DG} & 4.700 & 2.465 \\
+        \gls{DG} with moderator source & 2.751 & 1.408 \\
+      \end{tabular}
+    \end{center}
+    \caption{Maximum fluxes for different simulation cases}
+    \label{tab:max_fluxes}
+\end{table}
 
@@
 \printglossary[type=\acronymtype]
-%% \bibliographystyle{unsrt}
-%% \bibliography{Moltres}
+\bibliographystyle{unsrt}
+\bibliography{Moltres}
 \end{document}

### 2017-02-23 bw-prop.tex
adds BW prop and pagecounting

\documentclass[11pt]{article}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
% Color Information from - http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/latex_advanced/node13.html

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
  \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\newcommand\bb[1]{\mbox{\em #1}}
\def\baselinestretch{1.1}
%\pagestyle{empty}
\newcommand{\hsp}{\hspace*{\parindent}}
\definecolor{gray}{rgb}{0.4,0.4,0.4}

\newcommand{\authorname}{Kathryn~D.~Huff }
\newcommand{\authoremail}{katyhuff@gmail.com}
\newcommand{\authorsite}{katyhuff.github.com}

\begin{document}

\pagestyle{fancy}
%\pagenumbering{gobble}
%\fancyhead[location]{text}
% Leave Left and Right Header empty.
%\lhead{}
%\rhead{}
\lhead{\textcolor{gray}{\it \authorname}}
\rhead{\textcolor{gray}{\thepage}}
%\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

\paragraph{Research Goal}

The Advanced Reactors and Fuel Cycles (ARFC) group pursues improved safety and
sustainability of nuclear power. To do so, we model and
simulate the design, safety, and performance of advanced nuclear reactors.
Such reactors  involve tight coupling between physics such as thermal-hydraulic
phenomena, neutron transport, and fuel performance.

The current state of the art in advanced nuclear reactor simulation (e.g. the
CASL DOE innovation hub) is focused on traditional light water reactors.
The ARFC group seeks to extend that state of the art by enabling similarly high fidelity simulation of more advanced reactor designs through development of models and tools for representing unique materials, geometries, and physical phenomena. Current work includes extension
of the MOOSE framework to appropriately model coupled thermal-hydraulics and
neutronics of promising molten salt fuelled reactor designs.
ARFC develops physics kernel extensions and runs simulations using the highly
scalable, fully implicit, Multiphysics Object-Oriented Simulation Environment
(MOOSE) framework from Idaho National Laboratory.

\paragraph{Role of Blue Waters}
Simulations which faithfully capture this coupling at realistic spatial and
temporal resolution are only possible with the aid of high performance
computing resources.  To solve these large systems of partial differential
equations on a finite element mesh in a fully-coupled, implicit way, the MOOSE
framework was designed to take advantage of high performance computing
capability.  The framework conducts fully implicit physics coupling with a
Jacobian Free Newton Krylov (JFNK) solver method and sophisticated automatic
adaptive meshing.  These simulations are memory intensive, so the exceptional
memory capability of the Blue Waters resource will be essential to performant
simulation times. It is also important to note that rendering visualizations of
the results can be computationally intensive was well.

\paragraph{Progress}

While the allocation needs will vary according to the particular simulations, Dr. Huff’s research group will conduct many 2-dimensional and 3-dimensional finite element simulations per year using the MOOSE framework and modules. Such simulations commonly occupy tens of thousands of CPU cores at a time and vary in completion time. The MOOSE framework is shown to scale very well up to 10,000 cores. Transient and multi-scale simulations, which require greater capability per simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those larger simulations are likely to be run per year.

\paragraph{Potential Impact}
Detailed spatially and temporally resolved neutron flux and
temperature distributions can improve designs, help characterize
performance, inform reactor safety margins, and enable validation of numerical
modeling techniques for unique physics.
Future work may include similarly challenging materials and geometries such as
those in sodium cooled, gas cooled, and very high temperature reactor designs
which also boast improved safety and sustainability.

Simulations on the reactor core scale require substantial
computing resources to enable interrogation of
physical phenomena in the complex environments inside a nuclear reactor.

\end{document}

### 2017-02-23 bw-prop.tex
tentative draft, needs alex input

@@
 
-While the allocation needs will vary according to the particular simulations, Dr.
-Huff’s research group will conduct many 2-dimensional and 3-dimensional finite element simulations per year using the MOOSE framework and modules.
-Such simulations commonly occupy tens of thousands of CPU cores at a time and vary in completion time.
-The MOOSE framework is shown to scale very well up to 10,000 cores.
-Transient and multi-scale simulations, which require greater capability per simulation, may occupy up to 100,000 CPU cores at a time.
-Only a few of those larger simulations are likely to be run per year.
+Initial simulations of the MSRE have been conducted both locally on the desktop 
+computer scale and on Blue Wates. These have been steady state simulations and 
+have occupied up to hundreds of nodes simultaneously. Coupling between 
+neutronics and thermal hydraulics ahve been established in the Moltres tool, 
+though validation and verification efforts are ongoing. In the near term, these 
+steady state calculations will provide the initial conditions for full core 
+reactor transient simulations. Such simulations commonly occupy tens of 
+thousands of CPU cores at a time and vary in completion time. The MOOSE 
+framework is shown to scale very well up to 10,000 cores. Transient and 
+multi-scale simulations, which require greater capability per simulation, may 
+occupy up to 100,000 CPU cores at a time. Only a few of those larger 
+simulations are likely to be run this year..
 
@@
 
-Simulations on the reactor core scale require substantial
-computing resources to enable interrogation of
-physical phenomena in the complex environments inside a nuclear reactor.
-
 \end{document}

### 2017-02-23 bw-prop.tex
get heading right
phrasing

@@
 \newcommand{\authoremail}{katyhuff@gmail.com}
-\newcommand{\authorsite}{katyhuff.github.com}
+\newcommand{\authorsite}{arfc.npre.illinois.edu}
 
@@
 %\rhead{}
-\lhead{\textcolor{gray}{\it \authorname}}
-\rhead{\textcolor{gray}{\thepage}}
+\lhead{\textcolor{gray}{Investigator: Prof. \authorname\\Presenter: Dr. Alexander Lindsay}}
+\rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles\\}}
 %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
@@
 computer scale and on Blue Wates. These have been steady state simulations and 
-have occupied up to hundreds of nodes simultaneously. Coupling between 
-neutronics and thermal hydraulics ahve been established in the Moltres tool, 
-though validation and verification efforts are ongoing. In the near term, these 
-steady state calculations will provide the initial conditions for full core 
-reactor transient simulations. Such simulations commonly occupy tens of 
-thousands of CPU cores at a time and vary in completion time. The MOOSE 
-framework is shown to scale very well up to 10,000 cores. Transient and 
-multi-scale simulations, which require greater capability per simulation, may 
-occupy up to 100,000 CPU cores at a time. Only a few of those larger 
-simulations are likely to be run this year..
+have occupied up to many hundreds of nodes simultaneously. This talk will 
+describe how coupling between neutronics and thermal hydraulics ahve been 
+established in the Moltres tool as well as the validation and verification 
+efforts which are ongoing.
+
+In the near term, these steady state calculations will provide the initial 
+conditions for full core reactor transient simulations. Such simulations 
+commonly occupy tens of thousands of CPU cores at a time and vary in completion 
+time. The MOOSE framework is shown to scale very well up to 10,000 cores. 
+Transient and multi-scale simulations, which require greater capability per 
+simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those 
+larger simulations are likely to be run this year..
 

### 2017-02-23 bw-prop.tex
adds BDBA concept
Change JFNK to Newton-Krylov since that incorporates both traditional and matrix-free methods.

@@
 framework was designed to take advantage of high performance computing
-capability.  The framework conducts fully implicit physics coupling with a
-Jacobian Free Newton Krylov (JFNK) solver method and sophisticated automatic
+capability.  The framework conducts fully implicit physics coupling with
+Newton-Krylov based solver methods and sophisticated automatic
 adaptive meshing.  These simulations are memory intensive, so the exceptional
@@
 have occupied up to many hundreds of nodes simultaneously. This talk will
-describe how coupling between neutronics and thermal hydraulics ahve been 
+describe how coupling between neutronics and thermal hydraulics have been
 established in the Moltres tool as well as the validation and verification
@@
 Transient and multi-scale simulations, which require greater capability per
-simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those 
-larger simulations are likely to be run this year..
+simulation, may occupy up to 100,000 CPU cores at a time. Such transient
+simulations will evaluate the safety performance of advanced reactors in severe
+(beyond design basis) accidents.
 

### 2017-02-24 zjui-prop.tex
final matchmaking doc?

\documentclass[11pt]{article}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
% Color Information from - http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/latex_advanced/node13.html

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
  \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\newcommand\bb[1]{\mbox{\em #1}}
\def\baselinestretch{1.1}
%\pagestyle{empty}
\newcommand{\hsp}{\hspace*{\parindent}}
\definecolor{gray}{rgb}{0.4,0.4,0.4}

\newcommand{\authorname}{Kathryn~D.~Huff }
\newcommand{\authoremail}{katyhuff@gmail.com}
\newcommand{\authorsite}{arfc.npre.illinois.edu}

\begin{document}

\pagestyle{fancy}
%\pagenumbering{gobble}
%\fancyhead[location]{text}
% Leave Left and Right Header empty.
%\lhead{}
%\rhead{}
\lhead{\textcolor{gray}{Investigator: Prof. \authorname}}
\rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles}}
%\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

\paragraph{The \gls{ARFC} group} pursues improved 
safety and sustainability of nuclear power. To do so, we model and simulate novel reactor designs
boasting inherent safety features (i.e. accident tolerant fuels or non-voiding 
coolants) and sustainable fuel cycles (i.e. high fuel utilization, online 
reprocessing strategies). These analyses rely on developing computational 
methods that navigate trade-offs between accuracy and compute time, with 
special treatment of coupled feedbacks among thermal-hydraulic phenomena, 
neutron transport, and fuel performance.
Simulations which faithfully capture this coupling at realistic spatial and
temporal resolution are only possible with the aid of high performance
computing resources such as the Blue Waters supercomputing facility which this 
group relies on.

\paragraph{The state of the art} in advanced nuclear reactor simulation (e.g. the 
CASL DOE innovation hub) is focused on traditional light water reactors.  The 
\gls{ARFC} group seeks to extend that state of the art by enabling similarly high 
fidelity simulation of more advanced reactor designs through development of 
models and tools applicable to their unique materials, geometries, and physics.

\paragraph{Our current work} models the transient, three-dimensional, multi-scale physics
of promising molten salt reactors such as the \gls{MSRE}, \gls{MSBR}, and \gls{FHR} designs.  
This work is well underway with our development of the Moltres application 
\cite{lindsay_moltres_2017}, which relies on the \gls{MOOSE} framework \cite{gaston_moose:_2009}. 
Initial steady state simulations of the \gls{MSRE} have leveraged the Blue Waters 
supercomputer to establish successful coupling between neutronics and thermal 
hydraulics using the \gls{ARFC}-developed Moltres tool. Validation and 
verification efforts are ongoing and upcoming transient simulations seek to explore 
parameters that might increase \gls{LOFC}, \gls{LOHS}, and \gls{RIA} 
survivability in novel reactors.

\paragraph{Potential areas of future collaboration include:}
\begin{itemize}
        \item validation collaborations between \gls{ARFC} and materials scientists, especially 
                experimentalists interested in high flux, high heat performance of 
                molten fluoride salts, liquid metals, graphites, silicon 
                carbides, and uranium nitrides
        \item verification benchmarking collaborations between \gls{ARFC} and computationalists 
                interested in comparing methods for coupled neutronics and 
                thermal hydraulics in fluid fuelled reactors
        \item modeling collaborations between \gls{ARFC} and neutron transport 
                or thermal hydraulics theorists 
        \item algorithmic and data science collaborations on accelerating monte 
                carlo neutron transport calculations with machine learning or 
                information theoretic technicques
\end{itemize}

\paragraph{Our future work} will approach similarly challenging materials and geometries such as those in sodium cooled, gas cooled, and very high temperature reactor designs which also boast improved safety and sustainability.

\bibliographystyle{unsrt}
\bibliography{2017-zjui-prop}

\end{document}

### 2017-02-27 2017-inl-ldrd.tex
inl ldrd draft

--- 2017-02-24 zjui-prop.tex
@@
 \paragraph{Our current work} models the transient, three-dimensional, multi-scale physics
-of promising molten salt reactors such as the \gls{MSRE}, \gls{MSBR}, and \gls{FHR} designs.  
+of promising molten salt reactors such as the \gls{MSRE}, \gls{MSBR}.
 This work is well underway with our development of the Moltres application 
-\cite{lindsay_moltres_2017}, which relies on the \gls{MOOSE} framework \cite{gaston_moose:_2009}. 
+\cite{lindsay_moltres_2017}. Moltres relies on the \gls{MOOSE} framework 
+\cite{gaston_moose:_2009} as well as its Navier-Stokes capabilities. These 
+existing tools are extended with multi-group diffusion neutronics, . 
 Initial steady state simulations of the \gls{MSRE} have leveraged the Blue Waters 

### 2017-02-27 2017-inl-ldrd.tex
adds bib

@@
 temporal resolution are only possible with the aid of high performance
-computing resources such as the Blue Waters supercomputing facility which this 
-group relies on.
+computing resources such as the Blue Waters supercomputing facility at the 
+University of Illinois in Urbana-Champaign.
 
@@
 \paragraph{Our current work} models the transient, three-dimensional, multi-scale physics
-of promising molten salt reactors such as the \gls{MSRE}, \gls{MSBR}.
+of promising molten salt reactors such as the \gls{MSRE} and \gls{MSBR}.
 This work is well underway with our development of the Moltres application 
@@
 \cite{gaston_moose:_2009} as well as its Navier-Stokes capabilities. These 
-existing tools are extended with multi-group diffusion neutronics, . 
+existing tools are extended with multi-group diffusion neutronics incorporating 
+delayed neutron kinetics. We additionally support these calculations with few group 
+constants which we have generated with Serpent 
+\cite{leppanen_serpent_2012,leppanen_study_2015} and verfied using 
+SCALE-NEWT \cite{nuclear_regulatory_commission_scale:_1997}.
+
 Initial steady state simulations of the \gls{MSRE} have leveraged the Blue Waters 
 supercomputer to establish successful coupling between neutronics and thermal 
-hydraulics using the \gls{ARFC}-developed Moltres tool. Validation and 
-verification efforts are ongoing and upcoming transient simulations seek to explore 
+hydraulics using the \gls{ARFC}-developed Moltres tool. 
+These have initially been steady state simulations and have occupied up to many hundreds of nodes
+simultaneously. Three dimensional coupling between neutronics and thermal hydraulics have been
+established in the Moltres tool, but validation and verification efforts are
+ongoing.
+
+In the near term, these steady state calculations will provide the initial
+conditions for full core reactor transient simulations. Such simulations
+commonly occupy tens of thousands of CPU cores at a time and vary in completion
+time. The MOOSE framework is shown to scale very well up to 10,000 cores 
+\cite{gaston_moose:_2009}.
+Transient and multi-scale simulations, which require greater capability per
+simulation, may occupy up to 100,000 CPU cores at a time. Such transient
+simulations will evaluate the safety performance of advanced reactors in severe
+(beyond design basis) accidents in these reactors. These will seek to explore 
 parameters that might increase \gls{LOFC}, \gls{LOHS}, and \gls{RIA} 
@@
 
-\paragraph{Potential areas of future collaboration include:}
+\paragraph{The Blue Waters Supercomputer} (notably, the fastest supercomputer 
+on a university campus \cite{ncsa_about_2017}).  is therefore essential to our 
+efforts. The PI, Kathryn Huff, has been awarded a named Blue Waters Assistant 
+Professorship in affiliation with the \gls{NCSA}, and has been accordingly 
+allocated 100,000 node hours annually to support her work.  To solve these 
+large systems of partial differential equations on a finite element mesh in a 
+fully-coupled, implicit way, the MOOSE framework was designed to take advantage 
+of exactly this kind of high performance computing capability.  The framework 
+conducts fully implicit physics coupling with Newton-Krylov based solver 
+methods and sophisticated automatic adaptive meshing.  These simulations are 
+memory intensive, so the exceptional memory capability of the 
+supercomputer is essential to performant simulation times.
+
+It is also important to note that rendering visualizations of the results can 
+be computationally intensive was well. Accordingly, the \gls{ARFC} group has 
+established a collaboration with the Data Exploration Laboratory 
+\cite{turk_data_2017} in order to 
+take advantage of HPC visualization capabilities of the yt software package 
+when visualizing simulation results \cite{turk_yt:_2011}.
+
+\paragraph{The potential impact} of this work lies in the possibility of 
+simultaneously detailed spatially and temporally resolved neutron flux and
+temperature distributions. Such simulations can improve designs, help characterize
+performance, inform reactor safety margins, and enable validation of numerical
+modeling techniques for unique physics.
+
+\paragraph{Our future work} will approach similarly challenging materials and
+geometries such as those in sodium cooled, gas cooled, and very high
+temperature reactor designs which also boast improved safety and
+sustainability. Accordingly, potential areas of future collaboration include:
+
 \begin{itemize}
@@
 
-\paragraph{Our future work} will approach similarly challenging materials and geometries such as those in sodium cooled, gas cooled, and very high temperature reactor designs which also boast improved safety and sustainability.
-
 \bibliographystyle{unsrt}
-\bibliography{2017-zjui-prop}
+\bibliography{2017-inl-ldrd}
 

### 2017-02-27 acros.tex
Update on moltres results.
adds bib

@@
 \newacronym{ABM}{ABM}{agent-based modeling}
+\newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
 \newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
@@
 \newacronym{API}{API}{application programming interface}
+\newacronym{ARCH}{ARCH}{autoregressive conditional heteroskedastic}
 \newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
 \newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
+\newacronym{ARMA}{ARMA}{autoregressive moving average}
 \newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
@@
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
+\newacronym{CASL}{CASL}{Consortium for Advanced Simulation of Light Water Reactors}
+\newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
 \newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
 \newacronym{CI}{CI}{continuous integration}
+\newacronym{CNEN}{CNEN}{Comiss\~{a}o Nacional de Energia Nuclear}
 \newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
@@
 \newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
+\newacronym{CURIE}{CURIE}{Centralized Used Fuel Resource for Information Exchange}
 \newacronym{DAG}{DAG}{directed acyclic graph}
@@
 \newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
+\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
 \newacronym{EPA}{EPA}{Environmental Protection Agency}
@@
 \newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
-\newacronym{gpm}{gpm}{gallons per minute}
+\newacronym{GCAM}{GCAM}{Global Change Assessment Model}
 \newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
@@
 \newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
+\newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
 \newacronym{INL}{INL}{Idaho National Laboratory}
+\newacronym{IPRR1}{IRP-R1}{Instituto de Pesquisas Radioativas Reator 1}
+\newacronym{IRP}{IRP}{Integrated Research Project}
+\newacronym{ISFSI}{ISFSI}{Independent Spent Fuel Storage Installation}
+\newacronym{ISRG}{ISRG}{Independent Student Research Group}
 \newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
@@
 \newacronym{LP}{LP}{linear program}
+\newacronym{MARKAL}{MARKAL}{MARKet and ALlocation}
 \newacronym{MA}{MA}{minor actinide}
@@
 \newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
+\newacronym{NCSA}{NCSA}{National Center for Supercomputing Applications}
 \newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
@@
 \newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
+\newacronym{NFC}{NFC}{Nuclear Fuel Cycle}
 \newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
+\newacronym{NMWPC}{NMWPC}{Nuclear MW Per Capita}
 \newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
+\newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
 \newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
@@
 \newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
+\newacronym{NWF}{NWF}{Nuclear Waste Fund}
 \newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
@@
 \newacronym{SWU}{SWU}{Separative Work Unit}
+\newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
 \newacronym{TRISO}{TRISO}{Tristructural Isotropic}
@@
 \newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
-\newacronym{ThOX}{ThOX}{thorium oxide}
 \newacronym{UFD}{UFD}{Used Fuel Disposition}

### 2017-02-27 siip.tex
siip draft

%        File: siip.tex
%     Created: Mon Feb 27 08:00 AM 2017 C
% Last Change: Mon Feb 27 08:00 AM 2017 C
%
\documentclass[11pt]{article}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
          \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
          }

          \usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
          \newcommand\bb[1]{\mbox{\em #1}}
          \def\baselinestretch{1.1}
          %\pagestyle{empty}
          \newcommand{\hsp}{\hspace*{\parindent}}
          \definecolor{gray}{rgb}{0.4,0.4,0.4}

          \newcommand{\authorname}{Kathryn~D.~Huff }
          \newcommand{\authoremail}{katyhuff@illinois.edu}
          \newcommand{\authorsite}{arfc.npre.illinois.edu}

          \begin{document}

          \pagestyle{fancy}
          %\pagenumbering{gobble}
          %\fancyhead[location]{text}
          % Leave Left and Right Header empty.
          %\lhead{}
          %\rhead{}
          \lhead{\textcolor{gray}{Investigator: Prof. \authorname\\\authoremail}}
          \rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles\\Dept. of Nuclear, 
          Plasma, and Radiological Engineering}}
          %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

          \section{The Problem}
          As you read this, thousands of professors in the United States are 
          simultaneously preparing lessons on solving a conduction equation. They are doing so largely 
          without recieving feedback from one another or directly building on 
          one another's experience \cite{wilson_software_2014}.  It's distressing but 
          true that professors spend 10-40\% of 
          their time each year repeating curriculum development efforts already 
          tackled by numerous colleagues within their disciplines. What's worse 
          is that these efforts are rarely, if ever, reviewed by, shared with, 
          or extended upon by others.

          \section{The Proposed Solution}
          We propose a proof-of-concept for collaborative, open source, 
          curriculum development that will break down barriers between 
          classrooms and improve the transfer of lessons learned across universities.

          The goal will be to explore whether curriculum development can 
          operate like open source software development does, drawing on a 
          community of experts toward creating a shared core resource. In open 
          source software, developers share code revisions in online 
          repositories. In a typical project, the main 'fork' holds the 
          official copy of the software package. Developers each have their own 
          forks, copies of the repository, where they are able to make changes 
          on their own.

          This initiative already involves a 
          few peer professors -- faculty in Nuclear Engineering from UC 
          Berkeley, U. Wisconsin at Madison, Kansas State, U. South Carolina, 
          and U. Tennessee-Knoxville. We all use GitHub \cite{github} to store, 
          revise, and collaborate on research, especially source code. A few 
          of us have already started to host our course curricula online as 
          well, but these are typically single author repositories \cite{}.

          The participants will collaborate on a master set of learning 
          modules} for a common upper-division course in nuclear engineering : 
          The Nuclear Fuel Cycle.  The curriculum will be hosted on GitHub, 
          used by all of us, and improved continually as we learn and grow as 
          instructors.

          \paragraph{Each learning module} may include active in-class exercises, 
          presentation notes, homework problems, project descriptions, and 
          evaluation tools.

          However, curriculum is not the same as source code, because each 
          instructor wants and deserves to impart their own style of teaching 
          (and corny jokes) on their instruction. This challenge has been 
          encountered by collaborative instruction organizations such as 
          Software Carpentry, in which forks of the original material diverge 
          without any strong incentive for contribution back to the master 
          material \cite{wilson_software_2014}.

          This proposal suggests that fine-grained modularity and a clear 
          dependency graph may assist in overcoming this goal. Further, a small 
          and devoted group of like-minded nuclear engineering professors 
          should be able to compromise on a cohesive set of modular materials 
          that can be mixed and matched according to individual preference. 
          This work could provide an important proof of concept for groups of 
          instructors willing to collaborate on open source curriculum for:

          - core courses with many sections in a single university
          - niche courses taught by a select group of professors across 
          universities
          - fundamental courses in small fields (like nuclear engineering)

          Why do educators not diff, patch, and merge one another's . 
          Collaboratively construct and improve lesson materials.

          Scientists are more than happy to build upon one another's work, form 
          collaborations with others in their field. But, 
          when it comes to educating, where is the sharing of lessons learned 
          and collaboration?

          \section{The Potential Impact}
          \cite{wilson_software_2014}.

          Doing code review at the end of the work isn't useful. What works is 
          incremental code review. This proposal suspects that the same is true 
          for curriculum review. 
          \cite{wilson_software_2014}.

          Education is an inherently distributed system, but this need not be a 
          hinderance to collaboration.

          \bibliographystyle{katyunsrt}
          \bibliography{bibliography}

          \end{document}

### 2017-03-01 siip.tex
siip draft, so messy

@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
           As you read this, thousands of professors in the United States are 
-          simultaneously preparing lessons on solving a conduction equation. They are doing so largely 
-          without recieving feedback from one another or directly building on 
-          one another's experience \cite{wilson_software_2014}.  It's distressing but 
-          true that professors spend 10-40\% of 
-          their time each year repeating curriculum development efforts already 
-          tackled by numerous colleagues within their disciplines. What's worse 
-          is that these efforts are rarely, if ever, reviewed by, shared with, 
-          or extended upon by others.
+          simultaneously preparing lessons on solving a conduction equation. 
+          They are doing so largely without recieving feedback from one another 
+          or directly building on one another's experience 
+          \cite{wilson_software_2014}.  It's distressing but true that 
+          professors spend 10-40\% of their time each year repeating curriculum 
+          development efforts already tackled by numerous colleagues within 
+          their disciplines. What's worse is that these efforts are rarely, if 
+          ever, reviewed by, shared with, or extended upon by others.
 
@@
           source software, developers share code revisions in online 
-          repositories. In a typical project, the main 'fork' holds the 
+          repositories. In a typical project, the main ``fork'' holds the 
           official copy of the software package. Developers each have their own 
-          forks, copies of the repository, where they are able to make changes 
-          on their own.
+          forks, copies of the repository, where they can work on features and 
+          bug fixes. When those features and bug fixes are ready for prime 
+          time, the developer makes a ``pull request'' to the main fork, it is 
+          reviewed by their collaborators, and it is eventually merged into the 
+          main fork where it can be used by all.
 
-          This initiative already involves a 
-          few peer professors -- faculty in Nuclear Engineering from UC 
-          Berkeley, U. Wisconsin at Madison, Kansas State, U. South Carolina, 
-          and U. Tennessee-Knoxville. We all use GitHub \cite{github} to store, 
-          revise, and collaborate on research, especially source code. A few 
-          of us have already started to host our course curricula online as 
-          well, but these are typically single author repositories \cite{}.
+          \begin{figure}
+                  \centering
+                  \begin{subfigure}{.4\textwidth}
+                            \centering
+                              \includegraphics[width=.8\linewidth]{git-flow}
+        \caption{This figure, from \cite{scopatz_effective_2016}, captures a process, often called Git Flow, through which a new feature or bug fix enters a piece of open source software \cite{scopatz_effective_2016}.}
+                                  \label{fig:sub1}
+                  \end{subfigure}\hfill%
+                  \begin{subfigure}{.4\textwidth}
+                            \centering
+                              \includegraphics[width=.8\linewidth]{siip-flow}
+  \caption{This adaptation imagines the process in the context of learning module development, using the same git version control system and GitHub repository hosting framework.}
+                                  \label{fig:sub2}
+                  \end{subfigure}
+                  \caption{A figure with two subfigures}
+                  \label{fig:test}
+          \end{figure}
+
+          This initiative already involves a few peer professors. Six faculty 
+          in Nuclear Engineering from UC Berkeley, the University of Wisconsin 
+          at Madison, Kansas State, U. South Carolina, and U. 
+          Tennessee-Knoxville are involved. We all use GitHub \cite{github} to 
+          store, revise, and collaborate on research, especially source code. A 
+          few of us have already started to host our course curricula online as 
+          well, but these are typically single author repositories 
+          \cite{skutnik,wilson,slaybaugh,scopatz,borelli,roberts}.
 
           The participants will collaborate on a master set of learning 
-          modules} for a common upper-division course in nuclear engineering : 
+          modules for an upper-division course in nuclear engineering : 
           The Nuclear Fuel Cycle.  The curriculum will be hosted on GitHub, 
@@
 
+          \section{Departmental Support}
+          The Department of Nuclear, Plasma, and Radiological Engineering will 
+          support this work with relese time through startup funds. 
+          Additionally, NPRE will support workshop activities through 
+          administrative effort and by providing space.
           \end{document}

### 2017-03-01 siip.tex
more draft

@@
           %\rhead{}
-          \lhead{\textcolor{gray}{Investigator: Prof. \authorname\\\authoremail}}
-          \rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles\\Dept. of Nuclear, 
+          \lhead{\textcolor{gray}{Investigator: Prof. \authorname 
+          <\authoremail>}}
+          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\Dept. of Nuclear, 
           Plasma, and Radiological Engineering}}
@@
           As you read this, thousands of professors in the United States are 
-          simultaneously preparing lessons on solving a conduction equation. 
+          simultaneously preparing lessons on transposing a matrix.
           They are doing so largely without recieving feedback from one another 
           or directly building on one another's experience 
-          \cite{wilson_software_2014}.  It's distressing but true that 
-          professors spend 10-40\% of their time each year repeating curriculum 
-          development efforts already tackled by numerous colleagues within 
-          their disciplines. What's worse is that these efforts are rarely, if 
-          ever, reviewed by, shared with, or extended upon by others.
+          \cite{wilson_software_2014}. In this way, professors spend an enormous amount of time 
+          duplicating curriculum development efforts already tackled 
+          by colleagues. What's worse is that these efforts are 
+          rarely, if ever, reviewed by, shared with, or extended upon by 
+          peers.
+
+          Wikipedia and open source software development provide excellent 
+          examples of distributed expert collaboration and dynamic peer review 
+          on a master product. So, why aren't professors sharing their lesson 
+          materials online, collaborating on canonical lesson sets, 
+          diffing and merging similar lessons, and reviewing one another's 
+          work? \emph{Our goal is to explore the possibility that curriculum development for 
+          university courses can operate like open source software development 
+          does.}
 
@@
           We propose a proof-of-concept for collaborative, open source, 
-          curriculum development that will break down barriers between 
-          classrooms and improve the transfer of lessons learned across universities.
+          curriculum development to improve the transfer of lessons learned 
+          between instructors of the same course (either at a single university or 
+          among different campuses). This small-scale prototype collaboration 
+          will provide a framework which could be adopted for collaboration among faculty 
+          teaching courses with an inherently larger scale (e.g. CS101).
 
-          The goal will be to explore whether curriculum development can 
-          operate like open source software development does, drawing on a 
-          community of experts toward creating a shared core resource. In open 
-          source software, developers share code revisions in online 
-          repositories. In a typical project, the main ``fork'' holds the 
-          official copy of the software package. Developers each have their own 
-          forks, copies of the repository, where they can work on features and 
-          bug fixes. When those features and bug fixes are ready for prime 
-          time, the developer makes a ``pull request'' to the main fork, it is 
+          This initiative already involves a few peer professors. Six faculty 
+          in Nuclear Engineering from UC Berkeley, the University of Wisconsin 
+          at Madison, Kansas State, U. South Carolina, and U. 
+          Tennessee-Knoxville are involved. We all use GitHub \cite{github} to 
+          store, revise, and collaborate on research, especially source code. A 
+          few of us have already started to host our course curricula online as 
+          well, but these are typically single author repositories 
+          \cite{skutnik,wilson,slaybaugh,scopatz,borelli,roberts}.
+
+          \paragraph{In a typical open source project,} a main copy of the 
+          repository (or ``fork'') holds the 
+          official copy of the software package. Individual developers each have their own 
+          forks where they can work on features and 
+          bug fixes. When the developer makes changes that are ready for prime 
+          time, they make a ``pull request'' to the main fork, it is 
           reviewed by their collaborators, and it is eventually merged into the 
-          main fork where it can be used by all.
+          main fork where it can be used by all. Figures 
+          \ref{fig:sub1} and \ref{fig:sub2} show how the workflow used for many 
+          open source projects can be leveraged toward course development.
 
@@
                   \end{subfigure}
-                  \caption{A figure with two subfigures}
                   \label{fig:test}
@@
 
-          This initiative already involves a few peer professors. Six faculty 
-          in Nuclear Engineering from UC Berkeley, the University of Wisconsin 
-          at Madison, Kansas State, U. South Carolina, and U. 
-          Tennessee-Knoxville are involved. We all use GitHub \cite{github} to 
-          store, revise, and collaborate on research, especially source code. A 
-          few of us have already started to host our course curricula online as 
-          well, but these are typically single author repositories 
-          \cite{skutnik,wilson,slaybaugh,scopatz,borelli,roberts}.
+          Such projects occur drawing on a community of experts toward 
+          creating a robust shared resource. In open source software, 
+          developers share code revisions in online repositories, review one 
+          anothers work, and contribute back their own improvements to the main 
+          project.
 
-          The participants will collaborate on a master set of learning 
+          \paragraph{The participants will collaborate} on a master set of learning 
           modules for an upper-division course in nuclear engineering : 
-          The Nuclear Fuel Cycle.  The curriculum will be hosted on GitHub, 
-          used by all of us, and improved continually as we learn and grow as 
+          The Nuclear Fuel Cycle. In the near term, we will develop fine 
+          grained learning modules which may be mixed and matched to meet the 
+          learning . The curriculum will be hosted on GitHub, 
+          test by all of us, and improved continually as we learn and grow as 
           instructors.
@@
 
-          However, curriculum is not the same as source code, because each 
-          instructor wants and deserves to impart their own style of teaching 
-          (and corny jokes) on their instruction. This challenge has been 
-          encountered by collaborative instruction organizations such as 
-          Software Carpentry, in which forks of the original material diverge 
+          \paragraph{This challenge has been encountered} by collaborative 
+          instruction organizations already. Most notable among these is 
+          Software Carpentry, in which experience shows 
+          \cite{wilson_lessons_2014} forks of the original material tend to diverge 
           without any strong incentive for contribution back to the master 
           material \cite{wilson_software_2014}.
-
-          This proposal suggests that fine-grained modularity and a clear 
-          dependency graph may assist in overcoming this goal. Further, a small 
-          and devoted group of like-minded nuclear engineering professors 
-          should be able to compromise on a cohesive set of modular materials 
-          that can be mixed and matched according to individual preference. 
-          This work could provide an important proof of concept for groups of 
-          instructors willing to collaborate on open source curriculum for:
-
-          - core courses with many sections in a single university
-          - niche courses taught by a select group of professors across 
-          universities
-          - fundamental courses in small fields (like nuclear engineering)
-
-          Why do educators not diff, patch, and merge one another's . 
-          Collaboratively construct and improve lesson materials.
-
-          Scientists are more than happy to build upon one another's work, form 
-          collaborations with others in their field. But, 
-          when it comes to educating, where is the sharing of lessons learned 
-          and collaboration?
 
@@
 
+          \paragraph{We expect that} fine-grained modularity of lesson components and a clear dependency graph of prerequisite modules for each lesson may assist in overcoming this goal.
+Further, a small
+          and devoted group of like-minded nuclear engineering professors 
+          should be able to compromise on a cohesive set of modular materials 
+          that can be mixed and matched according to individual preference.
+
+          This work will provide an important proof of concept for groups of 
+          instructors willing to collaborate on open source curriculum for:
+          \begin{itemize}
+                  \item core courses with many sections in a single university
+                  \item niche courses taught by a select group of professors across 
+          universities
+                  \item fundamental courses in small fields (e.g. nuclear engineering)
+          \end{itemize}
+
+          Through exploration of the option space, we will arrive at a raw 
+          curriculum format for each type of learning module.
+
+          Scientists are more than happy to build upon one another's work, form 
+          collaborations with others in their field. But, 
+          when it comes to educating, where is the sharing of lessons learned 
+          and collaboration?
+
           \bibliographystyle{katyunsrt}

### 2017-03-01 siip.tex
adds refs

@@
 \usepackage{subcaption}
+\usepackage[hidelinks]{hyperref}
 
@@
           %\rhead{}
-          \lhead{\textcolor{gray}{Investigator: Prof. \authorname 
-          <\authoremail>}}
-          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\Dept. of Nuclear, 
-          Plasma, and Radiological Engineering}}
+          \lhead{\textcolor{gray}{PI: \authorname (NPRE)\\\authoremail}}
+          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\}}
           %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
@@
 
-          \section{The Problem}
-          As you read this, thousands of professors in the United States are 
+          \subsection*{Problem}
+          At this very moment, hundreds of professors in the United States are 
           simultaneously preparing lessons on transposing a matrix.
-          They are doing so largely without recieving feedback from one another 
+          They are doing so largely without receiving feedback from one another 
           or directly building on one another's experience 
-          \cite{wilson_software_2014}. In this way, professors spend an enormous amount of time 
-          duplicating curriculum development efforts already tackled 
-          by colleagues. What's worse is that these efforts are 
-          rarely, if ever, reviewed by, shared with, or extended upon by 
-          peers.
+          \cite{green_building_2014}. In this way, 
+          professors spend an enormous amount of time duplicating curriculum 
+          development efforts already tackled by colleagues. What's worse is 
+          that these efforts are rarely, if ever, reviewed by, shared with, or 
+          extended upon by peers.
 
-          Wikipedia and open source software development provide excellent 
-          examples of distributed expert collaboration and dynamic peer review 
-          on a master product. So, why aren't professors sharing their lesson 
-          materials online, collaborating on canonical lesson sets, 
-          diffing and merging similar lessons, and reviewing one another's 
-          work? \emph{Our goal is to explore the possibility that curriculum development for 
+          Open source software development provides an excellent 
+          example of a possible solution.
+          These communities have mastered distributed expert collaboration, 
+          dynamic peer review, and de-duplication of effort. In open source 
+          software, developers share code revisions in online repositories, 
+          review one another's work in small chunks \cite{wilson_best_2014}, 
+          and contribute back their own improvements to the main project.
+
+          So, why aren't professors sharing their lesson materials online, 
+          collaborating on canonical lesson sets, diffing and merging similar 
+          lessons, and reviewing one another's learning materials? \textbf{Our 
+          goal is to explore the possibility that curriculum development for 
           university courses can operate like open source software development 
@@
 
-          \section{The Proposed Solution}
-          We propose a proof-of-concept for collaborative, open source, 
-          curriculum development to improve the transfer of lessons learned 
-          between instructors of the same course (either at a single university or 
-          among different campuses). This small-scale prototype collaboration 
-          will provide a framework which could be adopted for collaboration among faculty 
-          teaching courses with an inherently larger scale (e.g. CS101).
+          Attempts at this have been made before. Most notable among 
+          these is Software Carpentry (which with the PI is quite involved). 
+          Unfortunately, our experience showed that 
+          forks of the original material tend to diverge without any strong 
+          incentive for contribution back to the master material 
+          \cite{wilson_software_2014,wilson_software_2014-1}. We expect that fine-grained modularity 
+          of lesson components and a clear dependency graph of prerequisite 
+          modules for each lesson may assist in overcoming the challenges 
+          encountered by Software Carpentry and others.
 
-          This initiative already involves a few peer professors. Six faculty 
-          in Nuclear Engineering from UC Berkeley, the University of Wisconsin 
-          at Madison, Kansas State, U. South Carolina, and U. 
-          Tennessee-Knoxville are involved. We all use GitHub \cite{github} to 
-          store, revise, and collaborate on research, especially source code. A 
-          few of us have already started to host our course curricula online as 
-          well, but these are typically single author repositories 
-          \cite{skutnik,wilson,slaybaugh,scopatz,borelli,roberts}.
+          \subsection*{Proposed Solution}
+          We propose a small-scale proof-of-concept for collaborative, open 
+          source, curriculum development to improve the transfer of lessons 
+          learned between instructors of the same course (either at a single 
+          university or among different campuses). This prototype collaboration 
+          will provide a template which could be adopted for collaboration 
+          among faculty teaching courses with an inherently larger scale (e.g. 
+          CS101).
+
+          Faculty in Nuclear Engineering from four institutions\footnote{P.  
+          Wilson at (UW Madison),Steven Skutnik (UT Knoxville), J. Roberts 
+          (Kansas State University), Anthony Scopatz (University of South 
+          Carolina)} have agreed to be participants in 
+          this prototyping effort. We all currently use 
+          \href{https://github.com}{GitHub} to store, 
+          revise, and collaborate on research, especially source code. 
+          Additionally, this select group already started to host our course 
+          curricula online as well, but these are typically single author 
+          repositories (e.g. \cite{huff_npre412_2017}).
+
+          The participants will collaborate on a master set of learning 
+          modules for an upper-division course in nuclear engineering : 
+          The Nuclear Fuel Cycle. In the near term, we will develop fine 
+          grained lessons which may be mixed and matched to meet the 
+          learning objectives. The curriculum will be hosted on GitHub, 
+          tested by all of us, and improved continually.
+
+          \paragraph{A two-day kick-off workshop (\$15K)} at UIUC will allow the 
+          participants to sketch the initial framework of 
+          the collaboration and coordinate logistics. The workshop will 
+          deliver:
+
+          \begin{itemize} 
+                  \item learning objectives\cite{bloom_bloom_1984} and a concept 
+                          map\cite{novak_concept_1990} for the course
+                  \item a list of fine-grained lesson topics
+                  \item a directed acyclic graph describing dependencies among 
+                          lessons
+                  \item individual assignments for curriculum development
+                  \item decisions to adopt specific raw formats for lesson content
+                        (markdown vs. \LaTeX, Jupyter vs MATLAB, etc.)
+                  \item a repository structure for organizing the lesson 
+                          material (at this stage, compatibility with 
+                          frameworks like RELATE 
+                          \cite{kloeckner_relate_2017,kloeckner_relate_2017} 
+                          and tools like PrarieLearn 
+                          \cite{west_prairielearn:_2015} will be considered)
+          \end{itemize}
+
+          \paragraph{Between Workshops} work will commence on developing 
+          lessons. These lessons will be submitted by pull request to the main 
+          repository and each lesson will include:
+          \begin{itemize} 
+                  \item associated learning objectives (identified previously)
+                \item content (e.g. speaking notes, presentation material, 
+                        derivations, worked examples, active learning  
+                          exercises, external readings, videos, images)
+                  \item learning assessments (e.g. project descriptions, exam questions) 
+          \end{itemize}
+
+          Interactions will commence primarily via issues, pull requests, and 
+          reviews on GitHub during this time. Meanwhile, monthly video 
+          conferences will help to spur high-level conversation onward.
+
+          \paragraph{A two-day retrospective workshop (\$15K)} at UIUC will wrap up the 
+          project. Discussion concerning the process will allow reflection as 
+          well as a collection of lessons learned.
+          Experiences live testing the developed course material (for example 
+          in NPRE412 at UIUC in Fall 2017) will be shared and suggested 
+          improvements will be captures as feature requests on GitHub.  The 
+          successful parts of the process will be captured a template 
+          repository and collaboration instruction manual, intended for use by 
+          other groups of faculty seeking to collaborate in a similar way.
+
+          \subsection*{Potential Impact}
+
+          This work will provide an important proof of concept for groups of 
+          instructors willing to collaborate on open source curriculum for:
+          \begin{itemize}
+                  \item core courses with many subsections in a single university
+                  \item niche courses taught by a select group of professors across 
+          universities
+                  \item fundamental courses in small fields (e.g. nuclear engineering)
+          \end{itemize}
+
+          \subsection*{Departmental Support}
+          The Department of Nuclear, Plasma, and Radiological Engineering will 
+          support this work in kind with release time for Kathryn Huff through 
+          her Start-Up funds.  Additionally, NPRE will support workshop activities 
+          with administrative effort and by providing space. Finally, 
+          collaborating external participants will contribute in kind with 
+          summer time hours.
+
+          \bibliographystyle{katyunsrt}
+          \bibliography{2017-siip}
+
+          \end{document}
+
+\iffalse
+          New features are described in 
+          tickets and discussed before implementation. Small, atomic changes 
+          are reviewed before merging. Communities of practice are nurtured.
+
+          Doing code review at the end of the work isn't useful. What works is 
+          incremental code review. This proposal suspects that the same is true 
+          for curriculum review. 
+          \cite{wilson_software_2014}.
+
+          Education is an inherently distributed system, but this need not be a 
+          hinderance to collaboration.
+
+          Scientists are more than happy to build upon one another's work, form 
+          collaborations with others in their field. But, 
+          when it comes to educating, where is the sharing of lessons learned 
+          and collaboration?
 
@@
 
-          Such projects occur drawing on a community of experts toward 
-          creating a robust shared resource. In open source software, 
-          developers share code revisions in online repositories, review one 
-          anothers work, and contribute back their own improvements to the main 
-          project.
-
-          \paragraph{The participants will collaborate} on a master set of learning 
-          modules for an upper-division course in nuclear engineering : 
-          The Nuclear Fuel Cycle. In the near term, we will develop fine 
-          grained learning modules which may be mixed and matched to meet the 
-          learning . The curriculum will be hosted on GitHub, 
-          test by all of us, and improved continually as we learn and grow as 
-          instructors.
-
-          \paragraph{Each learning module} may include active in-class exercises, 
-          presentation notes, homework problems, project descriptions, and 
-          evaluation tools.
-
-          \paragraph{This challenge has been encountered} by collaborative 
-          instruction organizations already. Most notable among these is 
-          Software Carpentry, in which experience shows 
-          \cite{wilson_lessons_2014} forks of the original material tend to diverge 
-          without any strong incentive for contribution back to the master 
-          material \cite{wilson_software_2014}.
-
-          \section{The Potential Impact}
-          \cite{wilson_software_2014}.
-
-          Doing code review at the end of the work isn't useful. What works is 
-          incremental code review. This proposal suspects that the same is true 
-          for curriculum review. 
-          \cite{wilson_software_2014}.
-
-          Education is an inherently distributed system, but this need not be a 
-          hinderance to collaboration.
-
-          \paragraph{We expect that} fine-grained modularity of lesson components and a clear dependency graph of prerequisite modules for each lesson may assist in overcoming this goal.
-Further, a small
-          and devoted group of like-minded nuclear engineering professors 
-          should be able to compromise on a cohesive set of modular materials 
-          that can be mixed and matched according to individual preference.
-
-          This work will provide an important proof of concept for groups of 
-          instructors willing to collaborate on open source curriculum for:
-          \begin{itemize}
-                  \item core courses with many sections in a single university
-                  \item niche courses taught by a select group of professors across 
-          universities
-                  \item fundamental courses in small fields (e.g. nuclear engineering)
-          \end{itemize}
-
-          Through exploration of the option space, we will arrive at a raw 
-          curriculum format for each type of learning module.
-
-          Scientists are more than happy to build upon one another's work, form 
-          collaborations with others in their field. But, 
-          when it comes to educating, where is the sharing of lessons learned 
-          and collaboration?
-
-          \bibliographystyle{katyunsrt}
-          \bibliography{bibliography}
-
-          \section{Departmental Support}
-          The Department of Nuclear, Plasma, and Radiological Engineering will 
-          support this work with relese time through startup funds. 
-          Additionally, NPRE will support workshop activities through 
-          administrative effort and by providing space.
-          \end{document}
+\fi

### 2017-03-02 siip.tex
siip submitted

@@
           in NPRE412 at UIUC in Fall 2017) will be shared and suggested 
-          improvements will be captures as feature requests on GitHub.  The 
-          successful parts of the process will be captured a template 
-          repository and collaboration instruction manual, intended for use by 
-          other groups of faculty seeking to collaborate in a similar way.
+          improvements will be captured as feature requests on GitHub.  
+          The process will be captured in a template repository 
+          and a collaboration instruction manual will be produced
+          for use by other groups of faculty seeking to collaborate in a 
+          similar way.
 

### 2017-03-02 2017-03-02-ae3.tex
final draft

%        File: 2017-03-02-ae3.tex
%     Created: Thu Mar 02 09:00 AM 2017 C
% Last Change: Thu Mar 02 09:00 AM 2017 C
%
\documentclass[11pt]{article}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
          \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
          }

          \usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
          \newcommand\bb[1]{\mbox{\em #1}}
          \def\baselinestretch{1.1}
          %\pagestyle{empty}
          \newcommand{\hsp}{\hspace*{\parindent}}
          \definecolor{gray}{rgb}{0.4,0.4,0.4}

          \newcommand{\authorname}{Kathryn~D.~Huff }
          \newcommand{\authoremail}{katyhuff@illinois.edu}
          \newcommand{\authorsite}{arfc.npre.illinois.edu}

          \begin{document}
\pagestyle{fancy}
          %\pagenumbering{gobble}
          %\fancyhead[location]{text}
          % Leave Left and Right Header empty.
          %\lhead{}
          %\rhead{}
          \lhead{\textcolor{gray}{Prof. \authorname\\\authoremail}}
          \rhead{\textcolor{gray}{Academy for Excellence in Engineering 
          Education}}
          %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

          \begin{itemize}
                  \item Hello everyone. ``What's the cube root of eight?''
                  \item ``Anyone? Yes, you, please what's the cube root of eight?'' 
                  \item Yes, it's 2. Thank you. 
          \end{itemize}

          \paragraph{Now what just happened?}

          All of you knew the answer, but not all of you raised your hands.
          \paragraph{Some of you did,} because you felt comfortable, confident, 
          and engaged. 
          \paragraph{Some of you didn't.} Perhaps you were checking your email 
          and I caught you offguard.
          \paragraph{According to research on stereotype threat} some of you 
          may have resisted raising your hands because you were under threat of 
          confirming a negative stereotype about your social or demographic group. 
          In the case of academics during a talk, perhaps the fear is that you 
          would appear to be an attention-seeking know-it-all. Of course, in 
          the case of an engineering classroom, there are much more sinister 
          stereotypes which threaten the comfort of underrepresented minority 
          and female students in particular.

          \paragraph{Ok, fine, not everyone raised their hands.} But then what 
          happened?

          \paragraph{I picked that guy. But why?} Maybe because I'm right 
          handed. In the case of a classroom after many sessions with the same 
          students, perhaps I'll choose him because he reliably gives 
          the correct answer.
          I \emph{could} conciously try to avoid that implicit bias by  
          explicitly choosing someone who didn't their hand. However, 
          that solution isn't fair either and can feel like punishment.

          \paragraph{Ok that was a fun experiment which I think 
          demonstrates a problem that is already very well understood by anyone 
          who has ever been in a classroom.}

          I've tried to level the playing field in my class when I ask a 
          question, by randomizing the name that I call on.

          While it's initially uncomfortable, it does help me learn everyone's 
          names, it keeps folks on their toes, it acts as a spot check on 
          attendance.  I'll sample from the presenter's names as an example.

          \begin{itemize}
                  \item What's the square root of nine?
          \end{itemize} 
          It also has the added benefit of showing that even the really smart kid doesn't always know the answer.
          \begin{itemize}
                  \item What's the prompt energy of a fission neutron?
          \end{itemize}

          \bibliographystyle{unsrt}
          \bibliography{bibliography}

          \end{document}

### 2017-03-31 Moltres.tex
Having now added delayed neutron production, we can remove the warning block.

@@
 \begin{equation}
+%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
+%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
+%% \nu \Sigma_{g'}^f \phi_{g'}
 \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
 + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
-\nu \Sigma_{g'}^f \phi_{g'}
-%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
-%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
-%% \nu \Sigma_{g'}^f \phi_{g'} + \sum_i^I \lambda_i \chi_g^{d,i} C_i
+\nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
 \label{eq:neutrons}
 \end{equation}
-
-\textbf{Note that at present we do not have the neutron source term from decay
-  of delayed neutron precursors. Currently coupling with precursors is only one
-  way, e.g. precursors are a function of temperature and neutron flux and not
-  the other way around. This reverse coupling should be added before publication.}
 

### 2017-04-10 Moltres.tex
Add passage describing how group constants are generated.
Remove single channel results. May restore later perhaps.

--- 2017-02-07 Moltres.tex
@@
 
-\section{Model Description}
+\section{Governing Equations}
 
@@
 
-with the last term representing the effect of fuel advection.
+with the last term representing the effect of fuel advection. The governing
+equation for the temperature is given by:
+
+\begin{equation}
+  \rho_fc_{p,f}\frac{\partial T_f}{\partial t} + \nabla\cdot\left(\rho_f c_{p,f}
+  \vec{u}\cdot T_f -k_f\nabla T_f\right) =  Q_f
+  \label{eq:fuel_temp}
+\end{equation}
+
+in the fuel and by:
+
+\begin{equation}
+  \rho_gc_{p,g}\frac{\partial T_g}{\partial t} + \nabla\cdot\left(-k_g\nabla T_g\right) =  Q_g
+  \label{eq:moderator_temp}
+\end{equation}
+
+in the moderator. $Q_f$ is defined by:
+
+\begin{equation}
+  Q_f = \sum_{g=1}^G \epsilon_{f,g}\Sigma_{f,g}\phi_g
+  \label{eq:fuel_source}
+\end{equation}
+
+and $Q_g$ is equal to $\gamma Q_f$, representing heat dissipation by gamma and
+neutron irradiation in the moderator.
+
+Group constants are generated with either Serpent \cite{leppanen_serpent_2015}
+or Scale \cite{dehart_reactor_2011}. Temperature vs group constant interpolation
+tables are constructed separately for fuel and moderator regions.
+
+\section{Results \& Discussion}
 

### 2017-04-11 Moltres.tex
Add most recent 2D-axi figures. Begin outline of moltres and 2D-axi model.

@@
 
-\section{Governing Equations}
+\section{Model Description}
 
-Neutrons are described with time-dependent multi-group diffusion theory as shown
+As a proof of concept and to ease resolution of strong transient gradients in
+temperature between fuel and moderator, the physical three dimensional problem
+is reduced to a two dimensional axisymmetric model. The model molten salt
+reactor is based on the \gls{MSRE}. To approximately simulate the lattice
+structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
+fuel-moderator regions, as shown in \cref{fig:geom}. The fuel and moderator
+radii are chosen such that the resulting area/volume fraction of fuel is .225 as
+for the \gls{MSRE}.
+
+\begin{figure}
+  \centering
+  \includegraphics{geometry.eps}
+  \label{fig:geom}
+  \caption{A sketch of the \gls{MSR} model geometry}
+\end{figure}
+
+The model is implemented using the MOOSE \cite{gaston_physics-based_2015} application code
+Moltres. \cite{lindsayad_arfc/moltres_nodate} Building on the massively
+parallelizable MOOSE framework allows Moltres to be run on super-computing
+platforms like \gls{NCSA}'s Blue Waters. For some three-dimensional simulations
+(results not discussed here), the number of elements in the mesh and total
+number of degrees of freedom exceed one million and ten million respectively. To
+handle problems of this size, Moltres has been run on up to 608 cores. However,
+reducing the problem dimension from three to two and using a structured mesh
+that can be much more coarse in the axial direction allows problem solution to
+be carried out on a single core in under five minutes.
+
+The Moltres code-base currently includes kernels and boundary conditions for
+solving for neutron fluxes, temperature, and precursor concentrations. In MOOSE
+jargon, kernels are C++ classes that contain methods for computing residual and
+Jacobian contributions corresponding to individual piecies of governing
+equations. Developing the code-base in this way allows very modular construction
+of equation systems; e.g. the same kernel that is used to represent heat
+conduction can also be used to represent generic chemical diffusion. Moltres
+also features neutron and precursor ``actions.'' These actions enable automatic
+construction of the systems of equations for an arbitrary number of neutron and
+precursor groups. This means that as long as group constants are provided in an appropriate
+tabular form, a user only has to modify a couple of lines in a Moltres input
+file to change from say two to fourty-four neutron groups.
+
+In Moltres, neutrons are described with time-dependent multi-group diffusion theory as shown
 in \cref{eq:neutrons}:
@@
 
-Group constants are generated with either Serpent \cite{leppanen_serpent_2015}
-or Scale \cite{dehart_reactor_2011}. Temperature vs group constant interpolation
-tables are constructed separately for fuel and moderator regions.
+Reactor composition is based on the enriched uranium design for the \gls{MSRE}
+and is given in \cref{table:comp}. \cite{robertson_msre_1965} Group constants
+are generated with either Serpent \cite{leppanen_serpent_2015} or Scale
+\cite{dehart_reactor_2011}. Temperature vs group constant interpolation tables
+are constructed separately for fuel and moderator regions.
+
+\begin{table}[htpb]
+  \begin{center}
+    \begin{tabular}{l | r}
+      Component & Mass Fraction\\\hline\hline
+      Li-7 & .1090\\
+      Li-6 & 5$\cdot$10$^{-6}$\\
+      F-19 & .6680\\
+      Be-9 & .0627\\
+      U-235 & .0167\\
+      U-238 & .0344\\
+    \end{tabular}
+  \end{center}
+  \caption{Fuel salt composition based on enriched Uranium \gls{MSRE} design \cite{robertson_msre_1965}
+  \label{table:comp}
+\end{table}
 
 \section{Results \& Discussion}
+
+Group fluxes are shown in \cref{fig:group1,fig:group2}. The effect of the vacuum
+boundary conditions is shown clearly in the cosinusoidal shapes in radial and
+axial directions. Striations are observed in both fast and thermal fluxes, with
+the fast group preferring the fuel and the thermal group preferring the moderator.
+
+\begin{figure}
+  \centering
+  \includegraphics{auto_diff_rho_group1.eps}
+  \caption{Group 1 flux}
+  \label{fig:group1}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics{auto_diff_rho_group2.eps}
+  \caption{Group 2 flux}
+  \label{fig:group2}
+\end{figure}
+
+The effect of the advecting fuel is seen in {fig:temp} where the temperature
+rises steadily with increasing z-coordinate. As one might expect, the temperature
+gradient is negative in the radial direction.
+
+\begin{figure}
+  \centering
+  \includegraphics{auto_diff_rho_temp.eps}
+  \caption{Temperature}
+  \label{fig:temp}
+\end{figure}
+
+\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
+reactor. Not surprisingly, the channel concentrations are higher in fuel channels
+with higher neutron fluxes and consequently a higher number of fission
+events. Because of the small decay constant of the precursor, the maximum
+concentration in any given channel occurs at the core outlet.
+
+% Fix me! Precursor concentrations have goofy scaling
+\begin{figure}
+  \centering
+  \includegraphics{auto_diff_rho_pre1.eps}
+  \caption{Longest lived precursor concentration}
+  \label{fig:pre1}
+\end{figure}
+
+With its much larger decay constant, the sixth and last precursor has its
+maximum concentration around the center-plane of the reactor as shown in
+\cref{fig:pre6}. As for all other precursors, its concentration decreases with
+increasing radius and decreasing neutron flux.
+
+% Fix me! Precursor concentrations have goofy scaling
+\begin{figure}
+  \centering
+  \includegraphics{auto_diff_rho_pre6.eps}
+  \caption{Shortest lived precursor concentration}
+  \label{fig:pre6}
+\end{figure}
 

### 2017-04-11 Moltres.tex
Three meaty paragraphs in introduction.

@@
 \usepackage{cleveref}
+\usepackage{minted}
 
@@
 \maketitle
+
+\section{Introduction}
+
+Molten salt reactors are a reactor concept that received considerable interest
+in the 1950s and 60s with development of the Aircraft Reactor Experiment and
+later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the
+Generation-IV reactor designs, the reactor concept has gained renewed research
+interest in the past decade. Some of the advantages offered by the \gls{MSR}
+include lower fissile inventories, no radiation damage constraint on attainable
+fuel burn-up, no spent nuclear fuel, no requirement to fabricate and handle
+solid fuel, and a homogeneous isotopic composition of fuel in the
+reactor. \cite{noauthor_gen_2008} These characteristics give the \gls{MSR} a
+potentially unique capability for actinide burning and extension of fuel
+resources.
+
+\gls{MSR} modeling efforts are focused on description of steady-state and
+transient behavior. Krepel et. al. extended the in-house light-water reactor
+diffusion code DYN3D to consider drift of delayed neutron precursors alongside
+the reactor temperature profile, re-casting the extended code as
+DYN3D-MSR. \cite{krepel_dyn3d-msr_2007} DYN3D-MSR was compared against
+experimental \gls{MSRE} data and was then used to simulate local fuel channel
+blockages as well as local temperature perturbations. In a similar vein, Kophazi
+et. al. used iterative coupling between in-house three dimensional neutronic and
+one-dimensional heat conduction models DALTON and THERM to analyze the normal
+operational state of the \gls{MSRE} and some channel-blocking-incident
+transients. \cite{kophazi_development_2009} Additions in the Kophazi model
+included entrance effects of heat transfer coefficients as well as thermal
+coupling between fuel channels through moderator heat conduction. More recently,
+Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
+\gls{MSBR} using the commercial finite element package COMSOL
+Multiphysics. \cite{cammi_multi-physics_2011} Advances in this work included
+solution of the fuel salt velocity field, use of heterogeneous group constants
+in fuel and moderator regions, and employment of a software package (COMSOL)
+intrinsically designed for coupled multi-physics simulation.
+
+This work does not introduce new science relative to the current literature so
+much as it introduces a new open tool, Moltres
+\cite{lindsayad_arfc/moltres_nodate}, for \gls{MSR} simulation. Moltres is an
+open source code licensed under LGPL2 terms that aims to be a tool that can be
+freely used, studied, critiqued, and developed by the \gls{MSR}
+community. Though Moltres is devoted to an accurate description of \gls{MSR}
+physics, its openness is its defining characteristic and one that actually
+promotes the former quality through transparency and easy peer review. In the
+era of github and global development, open and modern software practices must be
+employed in order for nuclear engineering simulation capability to keep pace
+with that of fields like astronomy whose multitude of open simulation tools
+(Enzo, Gadget, Flash, Gizmo, Ramses, Mesa) allows them to be the darlings of
+scientific visualization and documentaries. In that vein Moltres uses
+\mintinline{latex}{git} for version control, integration testing to protect
+developed physics capabilities, and a C++ object-oriented design to allow easy
+class extensibility and minimal code duplication. Moreover, Moltres is built on
+top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another LGPL
+code that itself leans on LibMesh \cite{kirk2006libmesh}, a LGPL finite element
+library, and PetSc \cite{petsc-user-ref}, a BSD toolkit for solving nonlinear
+equations stemming from discretization of PDEs. MOOSE and LibMesh handle
+translation of application (Moltres) defined weak PDE forms into residual and
+Jacobian functions that are the inputs into PetSc Newton-Raphson solution
+routines. All codes use MPI for parallel communication and are easily deployed
+on massively-parallel cluster-computing platforms. MOOSE applications by default
+use monolithic and implicit methods that are ideal for closely-coupled and
+multi-scale physics. These methods are ideal for the model problem described in
+this work. However, it should be noted that Moltres can also use explicit
+time-stepping routines as well as segregated solution methods, making it more
+extensible to future problems.
 

### 2017-04-11 Moltres.tex
Add conclusion section.

@@
 much as it introduces a new open tool, Moltres
-\cite{lindsayad_arfc/moltres_nodate}, for \gls{MSR} simulation. Moltres is an
-open source code licensed under LGPL2 terms that aims to be a tool that can be
+\cite{lindsay_arfc/moltres_nodate}, for \gls{MSR} simulation. Moltres is an
+open source code licensed under \gls{LGPL} terms that aims to be a tool that can be
 freely used, studied, critiqued, and developed by the \gls{MSR}
@@
 class extensibility and minimal code duplication. Moreover, Moltres is built on
-top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another LGPL
-code that itself leans on LibMesh \cite{kirk2006libmesh}, a LGPL finite element
-library, and PetSc \cite{petsc-user-ref}, a BSD toolkit for solving nonlinear
-equations stemming from discretization of PDEs. MOOSE and LibMesh handle
+top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another \gls{LGPL}
+code that itself leans on LibMesh \cite{kirk2006libmesh}, a \gls{LGPL} finite element
+library, and PetSc \cite{petsc-user-ref}, a \gls{BSD}-licensed toolkit for solving nonlinear
+equations stemming from discretization of PDEs. \gls{MOOSE} and LibMesh handle
 translation of application (Moltres) defined weak PDE forms into residual and
@@
 routines. All codes use MPI for parallel communication and are easily deployed
-on massively-parallel cluster-computing platforms. MOOSE applications by default
+on massively-parallel cluster-computing platforms. \gls{MOOSE} applications by default
 use monolithic and implicit methods that are ideal for closely-coupled and
@@
 
-The model is implemented using the MOOSE \cite{gaston_physics-based_2015} application code
-Moltres. \cite{lindsayad_arfc/moltres_nodate} Building on the massively
-parallelizable MOOSE framework allows Moltres to be run on super-computing
+The model is implemented using the \gls{MOOSE} \cite{gaston_physics-based_2015} application code
+Moltres. \cite{lindsay_arfc/moltres_nodate} Building on the massively
+parallelizable \gls{MOOSE} framework allows Moltres to be run on super-computing
 platforms like \gls{NCSA}'s Blue Waters. For some three-dimensional simulations
@@
 The Moltres code-base currently includes kernels and boundary conditions for
-solving for neutron fluxes, temperature, and precursor concentrations. In MOOSE
+solving for neutron fluxes, temperature, and precursor concentrations. In \gls{MOOSE}
 jargon, kernels are C++ classes that contain methods for computing residual and
@@
   \end{center}
-  \caption{Fuel salt composition based on enriched Uranium \gls{MSRE} design \cite{robertson_msre_1965}
+  \caption{Fuel salt composition based on enriched Uranium \gls{MSRE} design \cite{robertson_msre_1965}}
   \label{table:comp}
@@
 
-The effect of the advecting fuel is seen in {fig:temp} where the temperature
+The effect of the advecting fuel is seen in \cref{fig:temp} where the temperature
 rises steadily with increasing z-coordinate. As one might expect, the temperature
@@
 
+\section{Conclusion}
+
+This work introduces the open source \gls{MSR} simulation code Moltres. Moltres
+solves arbitrary-group neutron diffusion, temperature, and precursor governing
+equations in anywhere from one to three dimensions and can be deployed on an
+arbitrary number of processing units. The model problem presented here has a
+2D-axisymmetric geometry with heterogeneous group constants for fuel and
+moderator regions. Fuel volume fraction and fuel salt composition are based on
+the \gls{MSRE}. Neutron fluxes show expected cosinusoidal shapes in radial and
+axial directions with visible striations between fuel and moderator regions. The
+fast group flux is enhanced in fuel regions while the thermal group flux in
+enhanced in moderator regions. Due to advection the temperature profile
+increases monotonically in the direction of salt flow. The role of advection is
+also seen in precursor concentrations. Long lived precursors exhibit maximum
+concentrations at the core outlet. As the decay constant increases across
+precursor groups the maximum concentrations moves towards the reactor center
+where the precursor production rate is maximum. Future Moltres work includes
+generating a high-fidelity 3D model as well as investigating various transient
+accident scenarios.
+
 \FloatBarrier

### 2017-04-11 acros.tex
Add conclusion section.

--- 2017-02-07 acros.tex
@@
 \newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
+\newacronym{BSD}{BSD}{Berkeley Software Distribution}
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
-\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
+\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies
+Alternatives}
+\newacronym{CG}{CG}{Continuous Galerkin}
 \newacronym{CI}{CI}{continuous integration}
@@
 \newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
+\newacronym{DG}{DG}{Discontinuous Galerkin}
 \newacronym{DHS}{DHS}{Department of Homeland Security}
@@
 \newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
+\newacronym{LGPL}{LGPL}{Lesser GNU Public License}
 \newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
@@
 \newacronym{PEI}{PEI}{Peak Environmental Impact}
+\newacronym{PetSc}{PetSc}{Portable, Extensible Toolkit for Scientific Computation}
 \newacronym{PH}{PRONGHORN}{PRONGHORN}

### 2017-04-17 siip.tex
siip comments uncommented

@@
 \usepackage{subcaption}
+\usepackage{placeins}
 \usepackage[hidelinks]{hyperref}
@@
           \begin{document}
+          \title{Open Source, Collaborative Curriculum}
+          \author{PI: Kathryn Huff\\Co-PI: Neal Davis}
+          \maketitle
 
@@
           \lhead{\textcolor{gray}{PI: \authorname (NPRE)\\\authoremail}}
-          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\}}
+          \rhead{\textcolor{gray}{Collaborative Open Source Curriculum Development\\}}
           %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
@@
 
-          \subsection*{Departmental Support}
-          The Department of Nuclear, Plasma, and Radiological Engineering will 
-          support this work in kind with release time for Kathryn Huff through 
-          her Start-Up funds.  Additionally, NPRE will support workshop activities 
-          with administrative effort and by providing space. Finally, 
-          collaborating external participants will contribute in kind with 
-          summer time hours.
+          Development of this proof-of-concept curriculum will be undertaken 
+          similarly to an open source software project.
 
-          \bibliographystyle{katyunsrt}
-          \bibliography{2017-siip}
-
-          \end{document}
-
-\iffalse
-          New features are described in 
-          tickets and discussed before implementation. Small, atomic changes 
-          are reviewed before merging. Communities of practice are nurtured.
+          Some features of open source development that will be emulated 
+          include those that cultivate collaboration. In open source, 
+          for example, new code features are described in tickets and discussed 
+          before implementation. Small, atomic changes are reviewed before 
+          merging. Through these discussions and incremental reviews, communities of practice are nurtured.
 
@@
           \end{figure}
+          \FloatBarrier
 
-\fi
+          \subsection*{Departmental Support}
+          The Department of Nuclear, Plasma, and Radiological Engineering will 
+          support this work in kind with release time for Kathryn Huff through 
+          her Start-Up funds.  Additionally, NPRE will support workshop activities 
+          with administrative effort and by providing space. Finally, 
+          collaborating external participants will contribute in kind with 
+          summer time hours.
+
+          \bibliographystyle{katyunsrt}
+          \bibliography{2017-siip}
+
+          \end{document}

### 2017-04-17 siip.tex
adds ecip citation

@@
 
-          \subsection*{Problem}
+          \section*{Problem}
           At this very moment, hundreds of professors in the United States are 
@@
 
-          \subsection*{Proposed Solution}
+          \section*{Proposed Solution}
           We propose a small-scale proof-of-concept for collaborative, open 
@@
           among faculty teaching courses with an inherently larger scale (e.g. 
-          CS101).
+          CS101)
 
-          Faculty in Nuclear Engineering from four institutions\footnote{P.  
-          Wilson at (UW Madison),Steven Skutnik (UT Knoxville), J. Roberts 
+          Faculty in Nuclear Engineering from four institutions\footnote{Paul 
+          Wilson at (UW Madison), Steven Skutnik (UT Knoxville), Jeremy Roberts 
           (Kansas State University), Anthony Scopatz (University of South 
@@
 
+          \paragraph{In a typical open source project,} a main copy of the 
+          repository (or ``fork'') holds the 
+          official copy of the software package. Individual developers each have their own 
+          forks where they can work on features and 
+          bug fixes. When the developer makes changes that are ready for prime 
+          time, they make a ``pull request'' to the main fork, it is 
+          reviewed by their collaborators, and it is eventually merged into the 
+          main fork where it can be used by all. Figures 
+          \ref{fig:sub1} and \ref{fig:sub2} show how the workflow used for many 
+          open source projects can be leveraged toward course development.
+
+          Development of this proof-of-concept curriculum will be undertaken 
+          similarly to an open source software project.
+
+          Some features of open source development that will be emulated 
+          include those that cultivate collaboration. In open source, 
+          for example, new code features are described in tickets and discussed 
+          before implementation. Small, atomic changes are reviewed before 
+          merging. These discussions and incremental reviews nurture 
+          communities of practice.
+
+          \begin{figure}
+                  \centering
+                  \begin{subfigure}{.4\textwidth}
+                            \centering
+                              \includegraphics[width=.8\linewidth]{git-flow}
+        \caption{This figure, from \cite{scopatz_effective_2015}, captures a 
+                          process, often called Git Flow, through which a new 
+                          feature or bug fix enters a piece of open source 
+                          software.}
+                                  \label{fig:sub1}
+                  \end{subfigure}\hfill%
+                  \begin{subfigure}{.4\textwidth}
+                            \centering
+                              \includegraphics[width=.8\linewidth]{siip-flow}
+  \caption{This adaptation imagines the process in the context of learning module development, using the same git version control system and GitHub repository hosting framework.}
+                                  \label{fig:sub2}
+                  \end{subfigure}
+                  \label{fig:test}
+          \end{figure}
+          \FloatBarrier
+
+\iffalse
+          Doing code review at the end of the work isn't useful. What works is 
+          incremental code review. This proposal suspects that the same is true 
+          for curriculum review.  \cite{wilson_software_2014}.
+
+          Education is an inherently distributed system, but this need not be a hinderance to collaboration.
+
+          Scientists are more than happy to build upon one another's work, form 
+          collaborations with others in their field. But, 
+          when it comes to educating, where is the sharing of lessons learned 
+          and collaboration? 
+\fi
+
           \paragraph{A two-day kick-off workshop (\$15K)} at UIUC will allow the 
@@
           \begin{itemize} 
-                  \item learning objectives\cite{bloom_bloom_1984} and a concept 
-                          map\cite{novak_concept_1990} for the course
+                  \item learning objectives\cite{bloom_bloom_1984} for the 
+                          course
+                  \item a concept map\cite{novak_concept_1990} for the course
                   \item a list of fine-grained lesson topics
@@
                           \cite{west_prairielearn:_2015} will be considered)
+          \end{itemize}
+
+          Invited participants in the first workshop will include:
+          \begin{itemize}
+                  \item UIUC PI Huff and UIUC Co-PI Davis
+                  \item external collaborating Professors Wilson, Roberts, 
+                          Skutnik, and Scopatz
+                  \item up to 5 UIUC professors who may be likely to extend 
+                          this work in the future for their own courses.
           \end{itemize}
@@
           conferences will help to spur high-level conversation onward.
+          Co-PI Davis will be invited to engage in these video conference as 
+          part of action research toward the final 
+          As progress is made, lessons learned will be recorded by all 
+          participants in a draft instruction manual.
 
@@
           improvements will be captured as feature requests on GitHub.  
-          The process will be captured in a template repository 
-          and a collaboration instruction manual will be produced
-          for use by other groups of faculty seeking to collaborate in a 
-          similar way.
+          The lessons learned from the year-long process will be captured:
 
-          \subsection*{Potential Impact}
+          \begin{itemize}
+                  \item in a template repository 
+                  \item and in a collaboration instruction manual 
+          \end{itemize}
+
+          These products will be produced for use by other groups of faculty 
+          seeking to collaborate in a similar way.
+
+          Invited participants in the retrospective workshop will include:
+
+          \begin{itemize}
+                  \item UIUC PI Huff and UIUC Co-PI Davis
+                  \item external collaborating Professors Wilson, Roberts, 
+                          Skutnik, and Scopatz
+                  \item up to 20 UIUC professors interested in extending this 
+                          work in the future for their own courses.
+          \end{itemize}
+
+          \section*{Potential Impact}
+          This work will have immediate student and faculty outcomes at UIUC, 
+          USC, KSU, UT Knoxville, and UW Madison. It will additionally have long term 
+          student and faculty outcomes at UIUC. Beyond this, it may have 
+          institutional outcomes at UIUC.
 
@@
           \begin{itemize}
-                  \item core courses with many subsections in a single university
+                  \item core courses with many sections in a single university
                   \item niche courses taught by a select group of professors across 
@@
 
-          Development of this proof-of-concept curriculum will be undertaken 
-          similarly to an open source software project.
+          \paragraph{Student Outcomes}
+          Students enrolled in NPRE412 at UIUC and peer courses at partner 
+          institutions (USC, UT-Knoxville, Kansas State University, and 
+          UW-Madison) will have an improved experience. Their 
+          curriculum will be bolstered by the comprehensive concept mapping 
+          process as well as exercises and assessment tools reviewed by and 
+          improved by the expertise of professors at peer institutions.
 
-          Some features of open source development that will be emulated 
-          include those that cultivate collaboration. In open source, 
-          for example, new code features are described in tickets and discussed 
-          before implementation. Small, atomic changes are reviewed before 
-          merging. Through these discussions and incremental reviews, communities of practice are nurtured.
+          \paragraph{UIUC Faculty Outcomes}
+          The effort of developing curriculum in this way may be labor 
+          intensive initially. However, if the experience is similar to that of 
+          open source software, the maintenance effort will reduce 
+          substantially. Minor improvements and updates to the curriculum 
+          contributed by colleagues will be effectively 'free' in the long 
+          term.
 
-          Doing code review at the end of the work isn't useful. What works is 
-          incremental code review. This proposal suspects that the same is true 
-          for curriculum review. 
-          \cite{wilson_software_2014}.
+          \paragraph{UIUC Institutional Outcomes}
 
-          Education is an inherently distributed system, but this need not be a 
-          hinderance to collaboration.
+          Fame, glory.
 
-          Scientists are more than happy to build upon one another's work, form 
-          collaborations with others in their field. But, 
-          when it comes to educating, where is the sharing of lessons learned 
-          and collaboration?
-
-\paragraph{In a typical open source project,} a main copy of the 
-          repository (or ``fork'') holds the 
-          official copy of the software package. Individual developers each have their own 
-          forks where they can work on features and 
-          bug fixes. When the developer makes changes that are ready for prime 
-          time, they make a ``pull request'' to the main fork, it is 
-          reviewed by their collaborators, and it is eventually merged into the 
-          main fork where it can be used by all. Figures 
-          \ref{fig:sub1} and \ref{fig:sub2} show how the workflow used for many 
-          open source projects can be leveraged toward course development.
-
-          \begin{figure}
-                  \centering
-                  \begin{subfigure}{.4\textwidth}
-                            \centering
-                              \includegraphics[width=.8\linewidth]{git-flow}
-        \caption{This figure, from \cite{scopatz_effective_2016}, captures a process, often called Git Flow, through which a new feature or bug fix enters a piece of open source software \cite{scopatz_effective_2016}.}
-                                  \label{fig:sub1}
-                  \end{subfigure}\hfill%
-                  \begin{subfigure}{.4\textwidth}
-                            \centering
-                              \includegraphics[width=.8\linewidth]{siip-flow}
-  \caption{This adaptation imagines the process in the context of learning module development, using the same git version control system and GitHub repository hosting framework.}
-                                  \label{fig:sub2}
-                  \end{subfigure}
-                  \label{fig:test}
-          \end{figure}
-          \FloatBarrier
-
-          \subsection*{Departmental Support}
+          \section*{Departmental Support}
           The Department of Nuclear, Plasma, and Radiological Engineering will 
@@
 
+          \section*{Timeline and Deliverables}
+
+          \begin{itemize}
+                  \item[July 2017] 1st Workshop
+                  \item[.] 
+                  \item[.] 
+                  \item[.] 
+                  \item[July 2018] Retrospective Workshop
+          \end{itemize}
+
+          \section*{Budget Justification}
+          Explain travel for external collaborators, meals, meeting space, etc. 
+          Host it in the Union?
+
           \bibliographystyle{katyunsrt}

### 2017-04-17 Moltres.tex
moves periods after citations

@@
 solid fuel, and a homogeneous isotopic composition of fuel in the
-reactor. \cite{noauthor_gen_2008} These characteristics give the \gls{MSR} a
+reactor \cite{noauthor_gen_2008}. These characteristics give the \gls{MSR} a
 potentially unique capability for actinide burning and extension of fuel
@@
 the reactor temperature profile, re-casting the extended code as
-DYN3D-MSR. \cite{krepel_dyn3d-msr_2007} DYN3D-MSR was compared against
+DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
 experimental \gls{MSRE} data and was then used to simulate local fuel channel
@@
 operational state of the \gls{MSRE} and some channel-blocking-incident
-transients. \cite{kophazi_development_2009} Additions in the Kophazi model
+transients \cite{kophazi_development_2009}. Additions in the Kophazi model
 included entrance effects of heat transfer coefficients as well as thermal
@@
 \gls{MSBR} using the commercial finite element package COMSOL
-Multiphysics. \cite{cammi_multi-physics_2011} Advances in this work included
+Multiphysics \cite{cammi_multi-physics_2011}. Advances in this work included
 solution of the fuel salt velocity field, use of heterogeneous group constants
@@
 The model is implemented using the \gls{MOOSE} \cite{gaston_physics-based_2015} application code
-Moltres. \cite{lindsay_arfc/moltres_nodate} Building on the massively
+Moltres \cite{lindsay_arfc/moltres_nodate}. Building on the massively
 parallelizable \gls{MOOSE} framework allows Moltres to be run on super-computing
@@
 Reactor composition is based on the enriched uranium design for the \gls{MSRE}
-and is given in \cref{table:comp}. \cite{robertson_msre_1965} Group constants
+and is given in \cref{table:comp} \cite{robertson_msre_1965}. Group constants
 are generated with either Serpent \cite{leppanen_serpent_2015} or Scale

### 2017-04-17 Moltres.tex
adds ARE acronym

@@
 Molten salt reactors are a reactor concept that received considerable interest
-in the 1950s and 60s with development of the Aircraft Reactor Experiment and
+in the 1950s and 60s with development of the \gls{ARE} and
 later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the

### 2017-04-17 Moltres.tex
deleting words for brevity

@@
 
-Molten salt reactors are a reactor concept that received considerable interest
+Molten salt reactor concepts received considerable interest
 in the 1950s and 60s with development of the \gls{ARE} and

### 2017-04-19 Moltres.tex
adds abstract

@@
 \maketitle
+
+\begin{abstract}
+        This work introduces Moltres, a new physics application for multiphysics modeling of 
+        fluid-fuelled molten salt reactors. The neutronics model, thermal 
+        hydraulics model, and their coupling in the MOOSE framework are 
+        described. Validation against other coupled models as well as experimental 
+        results from the Molten Salt Reactor Experiment are demonstrated.
+\end{abstract}
 

### 2017-04-19 Moltres.tex
Add abstract

--- 2017-04-17 Moltres.tex
@@
 
+\begin{abstract}
+
+This work introduces Moltres, a new physics application for multiphysics
+modeling of fluid-fuelled molten salt reactors. The neutronics model, thermal
+hydraulics model, and their coupling in the MOOSE framework are
+described. Neutron and precursor equations are implemented using an Action
+system that allows use of an arbitrary number of groups with no change in the
+input card. Results for many-channel configurations in 2D-axisymmetric and 3D
+coordinates are presented. These are compared against other coupled models as
+well as the Molten Salt Reactor Experiment.
+
+\end{abstract}
+
 \section{Introduction}
 
-Molten salt reactor concepts received considerable interest
-in the 1950s and 60s with development of the \gls{ARE} and
+Molten salt reactors are a reactor concept that received considerable interest
+in the 1950s and 60s with development of the Aircraft Reactor Experiment and
 later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the
@@
 solid fuel, and a homogeneous isotopic composition of fuel in the
-reactor \cite{noauthor_gen_2008}. These characteristics give the \gls{MSR} a
+reactor. \cite{noauthor_gen_2008} These characteristics give the \gls{MSR} a
 potentially unique capability for actinide burning and extension of fuel
@@
 the reactor temperature profile, re-casting the extended code as
-DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
+DYN3D-MSR. \cite{krepel_dyn3d-msr_2007} DYN3D-MSR was compared against
 experimental \gls{MSRE} data and was then used to simulate local fuel channel
@@
 operational state of the \gls{MSRE} and some channel-blocking-incident
-transients \cite{kophazi_development_2009}. Additions in the Kophazi model
+transients. \cite{kophazi_development_2009} Additions in the Kophazi model
 included entrance effects of heat transfer coefficients as well as thermal
@@
 \gls{MSBR} using the commercial finite element package COMSOL
-Multiphysics \cite{cammi_multi-physics_2011}. Advances in this work included
+Multiphysics. \cite{cammi_multi-physics_2011} Advances in this work included
 solution of the fuel salt velocity field, use of heterogeneous group constants
@@
 The model is implemented using the \gls{MOOSE} \cite{gaston_physics-based_2015} application code
-Moltres \cite{lindsay_arfc/moltres_nodate}. Building on the massively
+Moltres. \cite{lindsay_arfc/moltres_nodate} Building on the massively
 parallelizable \gls{MOOSE} framework allows Moltres to be run on super-computing
@@
 Reactor composition is based on the enriched uranium design for the \gls{MSRE}
-and is given in \cref{table:comp} \cite{robertson_msre_1965}. Group constants
+and is given in \cref{table:comp}. \cite{robertson_msre_1965} Group constants
 are generated with either Serpent \cite{leppanen_serpent_2015} or Scale

### 2017-04-25 Moltres.tex
among

--- 2017-04-17 Moltres.tex
@@
 in the 1950s and 60s with development of the \gls{ARE} and
-later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the
+later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} among the
 Generation-IV reactor designs, the reactor concept has gained renewed research

### 2017-04-27 siip.tex
external outcomes

@@
           UW-Madison) will have an improved experience. Their 
-          curriculum will be bolstered by the comprehensive concept mapping 
-          process as well as exercises and assessment tools reviewed by and 
-          improved by the expertise of professors at peer institutions.
+          curriculum will be bolstered by the comprehensive concept maps 
+          underlying their coursework\cite{concept_maps}, as well as exercises 
+          and assessment tools reviewed and improved by expert professors at 
+          peer institutions.
 
@@
 
-          \section*{Departmental Support}
-          The Department of Nuclear, Plasma, and Radiological Engineering will 
-          support this work in kind with release time for Kathryn Huff through 
-          her Start-Up funds.  Additionally, NPRE will support workshop activities 
-          with administrative effort and by providing space. Finally, 
-          collaborating external participants will contribute in kind with 
-          summer time hours.
+          \paragraph{External Outcomes}
+
+          Of perhaps most relevance in the context of this work is the 
+          potential impact externally. This effort should spawn an 
+          instruction-centric community of 
+          practice among colleagues previously primarily connected by research 
+          in their specific technical subdomain.
 
@@
           \section*{Budget Justification}
+          The two workshops will 
           Explain travel for external collaborators, meals, meeting space, etc. 
           Host it in the Union?
+
+          \section*{Departmental Support}
+          The Department of Nuclear, Plasma, and Radiological Engineering will 
+          support this work in kind with release time for Kathryn Huff through 
+          her Start-Up funds.  Additionally, NPRE will support workshop activities 
+          with administrative effort and by providing space. Finally, 
+          collaborating external participants will contribute in kind with 
+          summer time hours.
 

### 2017-04-27 siip.tex
subsections rather than paragraphs

@@
           \newcommand{\authorname}{Kathryn~D.~Huff }
-          \newcommand{\authoremail}{katyhuff@illinois.edu}
+          \newcommand{\authoremail}{kdhuff@illinois.edu}
           \newcommand{\authorsite}{arfc.npre.illinois.edu}
@@
           \renewcommand{\footrulewidth}{0pt}
-          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}
+          %\fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}
 
-          \section*{Problem}
+          \section{Problem}
           At this very moment, hundreds of professors in the United States are 
@@
 
-          \section*{Proposed Solution}
+          \section{Proposed Solution}
           We propose a small-scale proof-of-concept for collaborative, open 
@@
           (Kansas State University), Anthony Scopatz (University of South 
-          Carolina)} have agreed to be participants in 
+          Carolina), and Robert Borrelli (University of Idaho)} have agreed to be participants in 
           this prototyping effort. We all currently use 
@@
 
-          \paragraph{In a typical open source project,} a main copy of the 
-          repository (or ``fork'') holds the 
-          official copy of the software package. Individual developers each have their own 
-          forks where they can work on features and 
-          bug fixes. When the developer makes changes that are ready for prime 
-          time, they make a ``pull request'' to the main fork, it is 
-          reviewed by their collaborators, and it is eventually merged into the 
-          main fork where it can be used by all. Figures 
-          \ref{fig:sub1} and \ref{fig:sub2} show how the workflow used for many 
-          open source projects can be leveraged toward course development.
-
+          \subsection{Open Source Workflow}
           Development of this proof-of-concept curriculum will be undertaken 
           similarly to an open source software project. 
+          In particular, this work will emulate features of open source software development 
+          that cultivate distributed collaboration. In open source, for 
+          example, new code features are described in \emph{issues} or 
+          \emph{tickets} and discussed before implementation. Small, atomic 
+          changes are reviewed before they are merged into the 
+          \emph{repository}. These discussions and incremental reviews nurture 
+          communities of practice.
 
-          Some features of open source development that will be emulated 
-          include those that cultivate collaboration. In open source, 
-          for example, new code features are described in tickets and discussed 
-          before implementation. Small, atomic changes are reviewed before 
-          merging. These discussions and incremental reviews nurture 
-          communities of practice.
+          In a typical open source project, a main copy of the 
+          repository (or main \emph{fork}) holds the 
+          official copy of the software package. Individual developers each have their own 
+          \emph{forks} where they can work on features and 
+          bug fixes. When the developer makes changes that are ready for prime 
+          time, they make a ``pull request'' to the main \emph{fork}. That 
+          \emph{pull request} is 
+          reviewed by their collaborators, and it is eventually merged into the 
+          main \emph{fork} where it can be used by all. Figures 
+          \ref{fig:sub1} and \ref{fig:sub2} show how this open source software 
+          development workflow
+          can be leveraged toward course development.
 
@@
 
-          \paragraph{A two-day kick-off workshop (\$15K)} at UIUC will allow the 
+          \subsection{Kick-Off Workshop}
+          A two-day kick-off workshop (\$15K) at UIUC will allow the 
           participants to sketch the initial framework of 
@@
                   \item external collaborating Professors Wilson, Roberts, 
-                          Skutnik, and Scopatz
+                          Borrelli, Skutnik, and Scopatz
                   \item up to 5 UIUC professors who may be likely to extend 
@@
 
-          \paragraph{Between Workshops} work will commence on developing 
+          \subsection{Interim Period}
+          Between Workshops, work will commence on developing 
           lessons. These lessons will be submitted by pull request to the main 
@@
 
-          \paragraph{A two-day retrospective workshop (\$15K)} at UIUC will wrap up the 
+          \subsection{Retrospective Workshop}
+          A two-day retrospective workshop (\$15K) at UIUC will wrap up the 
           project. Discussion concerning the process will allow reflection as 
@@
 
-          \section*{Potential Impact}
+          \section{Potential Impact}
           This work will have immediate student and faculty outcomes at UIUC, 
@@
 
-          \section*{Timeline and Deliverables}
+          \section{Timeline and Deliverables}
 
@@
 
-          \section*{Budget Justification}
+          \section{Budget Justification}
           The two workshops will 
@@
 
-          \section*{Departmental Support}
+          \section{Departmental Support}
           The Department of Nuclear, Plasma, and Radiological Engineering will 

### 2017-04-28 siip.tex
budget table

@@
           Attempts at this have been made before. Most notable among 
-          these is Software Carpentry (which with the PI is quite involved). 
-          Unfortunately, our experience showed that 
+          these is Software Carpentry (with which the PI and Co-PI are quite involved). 
+          Software Carpentry teaches computational skills for scientists using 
+          a shared curriculum hosted on GitHub. Unfortunately, our experience showed that 
           forks of the original material tend to diverge without any strong 
@@
 
-          \section{Budget Justification}
-          The two workshops will 
-          Explain travel for external collaborators, meals, meeting space, etc. 
-          Host it in the Union?
+          \section{Budget}
+          The two workshops will be hosted at the Illini Union, where a meeting 
+          room will be reserved. Visiting 
+          invited workshop participants will be flown to Urbana-Champaign and 
+          lodged at the Illini Union Hotel.
+
+\begin{tabular}[htb]{|l|c|c|c|}
+        \hline
+        \textbf{Item} & \textbf{Cost} & \textbf{Units} & \textbf{Notes} \\ 
+        \hline
+        \textbf{Lodging} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \textbf{<++>} & <++> & <++> & <++> \\ 
+        \hline
+\end{tabular}
 

### 2017-04-29 siip.tex
table budget

@@
 \usepackage[hidelinks]{hyperref}
+\usepackage{tabularx}
 
@@
           \section{Timeline and Deliverables}
+          \subsection{Timeline}
+          The timeline will be bookended by two workshops, a kickoff workshop 
+          and a retrospective workshop. In the intervening time, consistent 
+          communication through GitHub's collaboration framework, a Slack 
+          channel, an email listhost, a shared Google Drive folder, and
 
@@
 
+          \subsection{Deliverables}
+
+          \subsubsection{Learning Objectives List}
+          \subsubsection{Concept Map}
+          \subsubsection{Learning Dependency Graph}
+\begin{figure}[htb!]
+        \begin{center}
+                \includegraphics[height=0.5\textheight]{rosalind.png}
+        \end{center}
+        \caption{Rosalind.info has a graph of exercises and their dependencies.}
+        \label{fig:rosalind}
+\end{figure}
+          \subsubsection{Lesson Materials}
+
           \section{Budget}
@@
 
-\begin{tabular}[htb]{|l|c|c|c|}
+\begin{table}[htb]
+        \begin{tabularx}{\textwidth}{| X |c|c|c|c|c|}
         \hline
-        \textbf{Item} & \textbf{Cost} & \textbf{Units} & \textbf{Notes} \\ 
+        \textbf{Event} & \textbf{Item} & \textbf{Cost} & \textbf{Units} & \textbf{\$} & \textbf{Notes}\\ 
         \hline
-        \textbf{Lodging} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
-        \textbf{<++>} & <++> & <++> & <++> \\ 
+Kick-off Workshop&Meeting Room&744&2&1488&Allerton, all day package\\
+&Lodging&150&24&3600&Allerton guest rooms\\
+&Flights&800&6&4800&Estimated\\
+&Taxi&20&12&240&\\
+&Incidentals&100&6&600&\\
+&Continental breakfast&8.5&24&204&Working breakfasts, Allerton\\
+&Dinner&30&24&720&In Champaign-Urbana\\
 \hline
-\end{tabular}
+Retrospective Workshop&Meeting Room&50&2&100&Illini Union\\
+&Projector&300&4&1200&Illini Union\\
+&Lodging&150&24&3600&Illini Union Hotel\\
+&Flights&800&6&4800&Estimated\\
+&Taxi&20&12&240&\\
+&Incidentals&100&6&600&\\
+&Continental breakfast&8.5&24&204&University Catering\\
+&Coffee Service&32.5&4&130&\\
+&Lunch&15&24&360&University Catering\\
+&Dinner&30&24&720&In Champaign-Urbana\\
+        \hline
+        &\textbf{Total}&&&\textbf{23606}&\\
+        \hline
+\end{tabularx}
+\end{table}
 

### 2017-04-29 siip.tex
lots of edits toward final version

@@
           \title{Open Source, Collaborative Curriculum}
-          \author{PI: Kathryn Huff\\Co-PI: Neal Davis}
+          \author{\textbf{PI: Kathryn Huff}\\%
+%          \textbf{Co-PI: Neal Davis}\\%
+                  University of Illinois Urbana-Champaign
+                  \and
+\textbf{Co-PI: Neal Davis}\\University of Illinois Urbana-Champaign
+\and
+Paul Wilson\\University of Wisconsin - Madison 
+\and
+          Steven Skutnik\\University of Tennessee - Knoxville
+\and
+          Anthony Scopatz\\University of South Carolina 
+\and
+          Jeremy Roberts\\Kansas State University 
+\and
+          Robert Borrelli\\University of Idaho at Idaho Falls
+}
           \maketitle
@@
 
-          Attempts at this have been made before. Most notable among 
-          these is Software Carpentry (with which the PI and Co-PI are quite involved). 
-          Software Carpentry teaches computational skills for scientists using 
-          a shared curriculum hosted on GitHub. Unfortunately, our experience showed that 
-          forks of the original material tend to diverge without any strong 
-          incentive for contribution back to the master material 
-          \cite{wilson_software_2014,wilson_software_2014-1}. We expect that fine-grained modularity 
-          of lesson components and a clear dependency graph of prerequisite 
-          modules for each lesson may assist in overcoming the challenges 
-          encountered by Software Carpentry and others.
+          Previous attempts at collaborative curriculum development have met with 
+          challenges. Most notable among these is Software Carpentry (with 
+          which the PI and Co-PI are quite involved) 
+          \cite{wilson_software_2014}.  Software Carpentry teaches 
+          computational skills for scientists using a shared curriculum hosted 
+          on GitHub. Instructors can use and remix the curriculum, but our 
+          experience showed that instructors improved on the original material, 
+          but lacked a  strong incentive for contribution back to the master 
+          material. Thus, versions of the original material tended to diverge 
+          rather than converge 
+          \cite{wilson_software_2014,wilson_software_2014-1}.
+
+          We expect that 
+          fine-grained modularity of lesson components and a clear dependency 
+          graph of prerequisite modules for each lesson may assist in 
+          overcoming the challenges encountered by Software Carpentry and 
+          others.
 
@@
           among faculty teaching courses with an inherently larger scale (e.g. 
-          CS101)
+          CS101).
 
-          Faculty in Nuclear Engineering from four institutions\footnote{Paul 
-          Wilson at (UW Madison), Steven Skutnik (UT Knoxville), Jeremy Roberts 
-          (Kansas State University), Anthony Scopatz (University of South 
-          Carolina), and Robert Borrelli (University of Idaho)} have agreed to be participants in 
+          Faculty in Nuclear Engineering from five institutions\footnote{
+          Paul Wilson at (UW Madison), 
+          Steven Skutnik (UT Knoxville), 
+          Anthony Scopatz (University of South Carolina), 
+          Jeremy Roberts (Kansas State University), 
+          and Robert Borrelli (University of Idaho)
+          } have agreed to be participants in 
           this prototyping effort. We all currently use 
@@
           modules for an upper-division course in nuclear engineering : 
-          The Nuclear Fuel Cycle. In the near term, we will develop fine 
-          grained lessons which may be mixed and matched to meet the 
-          learning objectives. The curriculum will be hosted on GitHub, 
-          tested by all of us, and improved continually.
+          on The Nuclear Fuel Cycle. In the near term, we will develop 
+          fine-grained lessons and assessments which may be mixed and matched 
+          to meet the learning objectives. The curriculum will be hosted on 
+          GitHub, tested by all of us, and improved continually.
+
+          Prof. Neal Davis, Co-PI of this proposal, has contemplated a 
+          Collaborative Computational Curriculum for some time 
+          \cite{davis_ui-ccc_2016}. Since he 
+          teaches large-scale 
+          computational curriculum at UIUC 
+          he is an ideal person to potentially scale-up this work in the 
+          future. Additionally, he has the nuclear engineering background to 
+          understand the context of this prototyping effort. Prof. Davis' role 
+          in this effort will be to conduct \emph{action research}, observing 
+          our process and teasing out potential avenues for future 
+          extensions and applications of the process.
 
@@
 
-          Education is an inherently distributed system, but this need not be a hinderance to collaboration.
+          Education is an inherently distributed system, but this need not be a hindrance to collaboration.
 
@@
           \subsection{Kick-Off Workshop}
-          A two-day kick-off workshop (\$15K) at UIUC will allow the 
+          A two-day kick-off workshop hosted at the University of Illinois at 
+          Urbana-Champaign will allow the 
           participants to sketch the initial framework of 
-          the collaboration and coordinate logistics. The workshop will 
-          deliver:
+          the collaboration and coordinate logistics. Through brainstorming and 
+          discussion activities, the workshop will deliver a number of 
+          products. These products will be published in an online repository 
+          and associated website, both hosted by GitHub.
 
-          \begin{itemize} 
-                  \item learning objectives\cite{bloom_bloom_1984} for the 
-                          course
-                  \item a concept map\cite{novak_concept_1990} for the course
-                  \item a list of fine-grained lesson topics
-                  \item a directed acyclic graph describing dependencies among 
-                          lessons
-                  \item individual assignments for curriculum development
-                  \item decisions to adopt specific raw formats for lesson content
-                        (markdown vs. \LaTeX, Jupyter vs MATLAB, etc.)
-                  \item a repository structure for organizing the lesson 
-                          material (at this stage, compatibility with 
-                          frameworks like RELATE 
-                          \cite{kloeckner_relate_2017,kloeckner_relate_2017} 
-                          and tools like PrarieLearn 
-                          \cite{west_prairielearn:_2015} will be considered)
-          \end{itemize}
+          Invited participants in the first workshop will include UIUC PI Huff 
+          and UIUC Co-PI Davis, excternal collaborating professors Wilson, 
+          Skutnik, Roberts, Scopatz, and Borrelli, and up to 2 UIUC professors 
+          who may be likely to extend this work in the future for their own 
+          courses.
 
-          Invited participants in the first workshop will include:
-          \begin{itemize}
-                  \item UIUC PI Huff and UIUC Co-PI Davis
-                  \item external collaborating Professors Wilson, Roberts, 
-                          Borrelli, Skutnik, and Scopatz
-                  \item up to 5 UIUC professors who may be likely to extend 
-                          this work in the future for their own courses.
-          \end{itemize}
+          As indicated in Table \ref{tab:kickoff}, products to be developed in the first workshop include learning 
+          objectives\cite{bloom_bloom_1984}, a concept 
+          map\cite{novak_concept_1990}, a list of fine-grained lesson topics, a 
+          directed acyclic graph describing dependencies among lessons. Additionally, concrete logistics 
+          for completion will be established, including individual curriculum 
+          development assignments, decisions to adopt specific raw formats 
+          for lesson content (markdown vs. \LaTeX, Jupyter vs MATLAB, etc.), 
+          and a repository structure for organizing the lesson material. At 
+          this workshop, interest and compatibility with frameworks like RELATE 
+          \cite{kloeckner_relate_2017,kloeckner_relate_2017} and tools like 
+          PrarieLearn \cite{west_prairielearn:_2015} will be considered.
+
+          \begin{table}[h!]
+                  \centering
+          \begin{tabularx}{\textwidth}{r|l|l|X}
+                                  \multicolumn{4}{c}{\textbf{Day 1}}\\
+                                  \hline
+                          \textbf{Time}& \textbf{Activity}& \textbf{Lead}& \textbf{Deliverable}\\
+                                  \hline
+8:00& Welcome and Breakfast& Huff \& Davis& \\
+9:00& Vision Lightning Talk& Wilson& Idea Collection\\
+9:15& Vision Lightning Talk& Skutnik& \\
+9:30& Vision Lightning Talk& Scopatz& \\
+9:45& Vision Lightning Talk& Roberts& \\
+10:00& Vision Lightning Talk& Borrelli& \\
+10:15& Vision Lightning Talk& Huff& \\
+10:30& Break&&  \\
+10:45& Concept Mapping Exercise& All& Curriculum Concept Map\\
+12:00& Lunch& All& \\
+13:00& Brainstorm Learning Objectives& All& Learning Objectives List\\
+15:00& Break&&  \\
+15:15& Refine Lesson Topics& All& Lesson Topics List\\
+16:00& Discussion of Formats for Content& All&  \\
+17:00& Break&&  \\
+19:00& Dinner&&  \\
+\hline
+                                  \multicolumn{4}{c}{}\\
+                                  \multicolumn{4}{c}{\textbf{Day 2}}\\
+                                  \hline
+                          \textbf{Time}& \textbf{Activity}& \textbf{Lead}& \textbf{Deliverable}\\
+                                  \hline
+8:00& Review and Breakfast& Huff \& Davis& \\
+9:00& Lesson Dependency Exercise& All& Lesson Dependency Graph\\
+10:30& Break&&  \\
+10:45& Lesson Dependency Exercise& All& \\
+12:00& Lunch& All& \\
+13:00& Repository Initialization&&  Template Workspace\\
+14:00& Determination of Milestones& All& Work Plan\\
+15:00& Break&&  \\
+15:15& Assigment of Responsibilities& All&  \\
+16:00& Review and Wrap-up& All&  \\
+17:00& Break&&  \\
+19:00& Dinner&&  \\
+\hline
+                  \end{tabularx}
+                  \caption{Preliminary schedule for the Kick-off Workshop}
+                  \label{tab:kickoff}
+          \end{table}
 
@@
           communication through GitHub's collaboration framework, a Slack 
-          channel, an email listhost, a shared Google Drive folder, and
+          channel, an email listhost, a shared Google Drive folder, and monthly 
+          Google Hangouts will drive this work.
 
           \begin{itemize}
-                  \item[July 2017] 1st Workshop
-                  \item[.] 
-                  \item[.] 
-                  \item[.] 
-                  \item[July 2018] Retrospective Workshop
+                  \item[Jul 2017] 1st Workshop
+                  \item[Aug 2017 - Jun 2018] Monthly Video Conferences 
+                  \item[Jul 2018] Retrospective Workshop
           \end{itemize}
@@
           \subsubsection{Learning Dependency Graph}
-\begin{figure}[htb!]
+\begin{figure}[ht!]
         \begin{center}
@@
         \end{center}
-        \caption{Rosalind.info has a graph of exercises and their dependencies.}
+        \caption{Rosalind.info, an educational bioinformatics resource, 
+        organizes exercises based on their dependencies.}
         \label{fig:rosalind}
@@
           \section{Budget}
-          The two workshops will be hosted at the Illini Union, where a meeting 
-          room will be reserved. Visiting 
+          The first workshop will be hosted at the Allerton Retreat Center, 
+          where a small meeting room will be reserved. Visiting 
           invited workshop participants will be flown to Urbana-Champaign and 
@@
 
-\begin{table}[htb]
+\begin{table}[h!]
         \begin{tabularx}{\textwidth}{| X |c|c|c|c|c|}
@@
 \end{tabularx}
+\caption{All expenses will support travel for visitors and workshop 
+necessities.}
 \end{table}

### 2017-04-29 siip.tex
adds note about insitutional outcomes

@@
 \usepackage{placeins}
+%\usepackage{chronology}
+\usepackage{tabularx}
 \usepackage[hidelinks]{hyperref}
-\usepackage{tabularx}
 
-% Trying to bold my name in the bib
+% Trying to bold PI names in the bib
 \usepackage{xstring}
 \def\FormatName#1{%
-          \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
+          \IfSubStr{#1}{Huff}{\textbf{#1}}{\IfSubStr{#1}{Neal Davis}{\textbf{#1}}{#1}}%
           }
@@
           computational skills for scientists using a shared curriculum hosted 
-          on GitHub. Instructors can use and remix the curriculum, but our 
-          experience showed that instructors improved on the original material, 
-          but lacked a  strong incentive for contribution back to the master 
-          material. Thus, versions of the original material tended to diverge 
-          rather than converge 
+          on GitHub. Hundreds of instructors accross the planet use and remix 
+          the curriculum, but our experience showed that while these 
+          instructors used and improved on the original material, they rarely 
+          contributed their changes back to the master material. Thus, versions 
+          of the original material tend to diverge rather than converge 
           \cite{wilson_software_2014,wilson_software_2014-1}.
@@
           modules for an upper-division course in nuclear engineering : 
-          on The Nuclear Fuel Cycle. In the near term, we will develop 
+          The Nuclear Fuel Cycle. In the near term, we will develop 
           fine-grained lessons and assessments which may be mixed and matched 
@@
           Collaborative Computational Curriculum for some time 
-          \cite{davis_ui-ccc_2016}. Since he 
+          \cite{davis_university_2016}. Since he 
           teaches large-scale 
@@
 
-          \paragraph{UIUC Institutional Outcomes}
-
-          Fame, glory.
+          \paragraph{UIUC Institutional Outcomes} Openness and collaboration 
+          both increase visibility. The leadership of UIUC College of 
+          Engineering faculty in this effort, if successful, will be exemplary 
+          of the forward-thinking nature of the college and the university at 
+          large. Furthermore, extensions to this work may be competitive for  
+          support from educational grant-making agencies such as the National 
+          Science Foundation and even private foundations such as Moore and 
+          Sloan.
 
@@
 
+          %\input{timeline}
           \begin{itemize}

### 2017-05-10 Moltres.tex

--- 2017-04-25 Moltres.tex
@@
 \maketitle
+
+\begin{abstract}
+
+This work introduces Moltres, a new physics application for multiphysics
+modeling of fluid-fuelled molten salt reactors. The neutronics model, thermal
+hydraulics model, and their coupling in the MOOSE framework are
+described. Neutron and precursor equations are implemented using an Action
+system that allows use of an arbitrary number of groups with no change in the
+input card. Results for many-channel configurations in 2D-axisymmetric and 3D
+coordinates are presented. These are compared against other coupled models as
+well as the Molten Salt Reactor Experiment.
+
+\end{abstract}
 

### 2017-05-10 Moltres.tex
corrections of some stretched truths in the intro

@@
 
-Molten salt reactor concepts received considerable interest
-in the 1950s and 60s with development of the \gls{ARE} and
-later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} among the
-Generation-IV reactor designs, the reactor concept has gained renewed research
-interest in the past decade. Some of the advantages offered by the \gls{MSR}
-include lower fissile inventories, no radiation damage constraint on attainable
-fuel burn-up, no spent nuclear fuel, no requirement to fabricate and handle
-solid fuel, and a homogeneous isotopic composition of fuel in the
-reactor \cite{noauthor_gen_2008}. These characteristics give the \gls{MSR} a
-potentially unique capability for actinide burning and extension of fuel
-resources.
+Molten salt reactor concepts garnered considerable interest in the 1950s and 
+60s with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}. 
+With the inclusion of the \gls{MSR} among the Generation-IV reactor designs 
+\cite{gen_IV}, this reactor concept has gained renewed research interest in the 
+past decade, with many new nuclear companies proposing both fluid-fuelled and 
+solid-fuelled commerical \gls{MSR} designs 
+\cite{terrapower,terrestrial,elysium,thorcon,kairos}. Two key advantages 
+offered by the fluid-fuelled \gls{MSR} are improved fuel utilization and no 
+radiation damage constraint on attainable fuel burn-up. Together, these 
+attributes result in significantly reduced core fissile inventories and spent 
+nuclear fuel mass \cite{noauthor_gen_2008}.  These characteristics give the 
+\gls{MSR} a potentially unique capability for actinide burning and extension of 
+fuel resources.
 
 \gls{MSR} modeling efforts are focused on description of steady-state and
-transient behavior. Krepel et. al. extended the in-house light-water reactor
+transient behavior. Krepel et. al. extended the in-house \gls{LWR}
 diffusion code DYN3D to consider drift of delayed neutron precursors alongside
@@
 blockages as well as local temperature perturbations. In a similar vein, Kophazi
-et. al. used iterative coupling between in-house three dimensional neutronic and
+et. al. used iterative coupling between in-house three-dimensional neutronic and
 one-dimensional heat conduction models DALTON and THERM to analyze the normal

### 2017-05-10 Moltres.tex
avoid some

@@
 one-dimensional heat conduction models DALTON and THERM to analyze the normal
-operational state of the \gls{MSRE} and some channel-blocking-incident
+operational state of the \gls{MSRE} as well as channel-blocking-incident
 transients \cite{kophazi_development_2009}. Additions in the Kophazi model

### 2017-05-10 Moltres.tex
some rephrasings to put the spotlight on capability and scientific discovery

@@
 \gls{MSBR} using the commercial finite element package COMSOL
-Multiphysics \cite{cammi_multi-physics_2011}. Advances in this work included
+Multiphysics \cite{cammi_multi-physics_2011}. Advances in that work included
 solution of the fuel salt velocity field, use of heterogeneous group constants
@@
 
-This work does not introduce new science relative to the current literature so
-much as it introduces a new open tool, Moltres
-\cite{lindsay_arfc/moltres_nodate}, for \gls{MSR} simulation. Moltres is an
-open source code licensed under \gls{LGPL} terms that aims to be a tool that can be
-freely used, studied, critiqued, and developed by the \gls{MSR}
-community. Though Moltres is devoted to an accurate description of \gls{MSR}
-physics, its openness is its defining characteristic and one that actually
-promotes the former quality through transparency and easy peer review. In the
-era of github and global development, open and modern software practices must be
-employed in order for nuclear engineering simulation capability to keep pace
-with that of fields like astronomy whose multitude of open simulation tools
+The present work introduces the open source simulation tool, Moltres 
+\cite{lindsay_arfc/moltres_nodate}, for \gls{MSR} simulation.  By implementing 
+deterministic neutronics and thermal hydraulics in the context of the 
+\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group 
+neutron diffusion, temperature, and precursor governing equations in anywhere 
+from one to three dimensions and can be deployed on an arbitrary number of 
+processing units. Moltres is devoted to previously unmatched 
+fidelity in coupled neutronics and thermal hydraulics \gls{MSR} simulation.
+
+Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a tool that can be
+freely used, studied, interrogated, and improved by the \gls{MSR}
+community.  Its openness is a defining characteristic and 
+promotes unmatched quality through transparency and ease of peer review. In the
+era of GitHub\cite{github} and international scientific collaboration, open and modern software practices must be
+employed in order for nuclear engineering simulation capability to enable 
+discovery and support the regulatory needs presented by new reactor designs. 
+Furthermore, to openness is necessary to keep pace with scientific computing 
+advances in fields like astronomy whose multitude of open simulation tools
 (Enzo, Gadget, Flash, Gizmo, Ramses, Mesa) allows them to be the darlings of
-scientific visualization and documentaries. In that vein Moltres uses
+scientific visualization and public interest. In that vein Moltres uses
 \mintinline{latex}{git} for version control, integration testing to protect

### 2017-05-10 Moltres.tex
updates acros"

@@
 advances in fields like astronomy whose multitude of open simulation tools
-(Enzo, Gadget, Flash, Gizmo, Ramses, Mesa) allows them to be the darlings of
-scientific visualization and public interest. In that vein Moltres uses
+(Enzo\cite{enzo}, Gadget\cite{gadget}, Flash\cite{flash}, Gizmo\cite{gizmo}, 
+Ramses\cite{ramses}, Mesa\cite{mesa}) allows them to be the darlings of
+scientific visualization and public interest.
+
+In that vein, Moltres uses
 \mintinline{latex}{git} for version control, integration testing to protect
@@
 this work. However, it should be noted that Moltres can also use explicit
-time-stepping routines as well as segregated solution methods, making it more
-extensible to future problems.
+time-stepping routines as well as segregated solution methods, making it very 
+extensible to myriad future modeling challenges.
 
-\section{Model Description}
-
-As a proof of concept and to ease resolution of strong transient gradients in
-temperature between fuel and moderator, the physical three dimensional problem
-is reduced to a two dimensional axisymmetric model. The model molten salt
-reactor is based on the \gls{MSRE}. To approximately simulate the lattice
-structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
-fuel-moderator regions, as shown in \cref{fig:geom}. The fuel and moderator
-radii are chosen such that the resulting area/volume fraction of fuel is .225 as
-for the \gls{MSRE}.
-
-\begin{figure}
-  \centering
-  \includegraphics{geometry.eps}
-  \label{fig:geom}
-  \caption{A sketch of the \gls{MSR} model geometry}
-\end{figure}
+\section{Methods}
 
@@
 
-\begin{equation}
+\begin{align}
 %% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
@@
 %% \nu \Sigma_{g'}^f \phi_{g'}
-\frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
-+ \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
-\nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
+        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g 
+        \nabla \phi_g + \Sigma_g^r \phi_g &= \sum_{g \ne g'}^G 
+        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
+        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
 \label{eq:neutrons}
-\end{equation}
+        \intertext{where}
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>].
+\end{align}
 
@@
 
-\begin{equation}
-\frac{\partial C_i}{\partial t} = \sum_{g'= 1}^G \beta_i \nu \Sigma_{g'}^f
-\phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u C_i
-\label{eq:precursors}
-\end{equation}
+\begin{align}
+        \frac{\partial C_i}{\partial t} &= \sum_{g'= 1}^G \beta_i \nu 
+        \Sigma_{g'}^f \phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u 
+        C_i \label{eq:precursors}
+        \intertext{where}
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+\end{align}
 
@@
 
-Reactor composition is based on the enriched uranium design for the \gls{MSRE}
-and is given in \cref{table:comp} \cite{robertson_msre_1965}. Group constants
+Group constants
 are generated with either Serpent \cite{leppanen_serpent_2015} or Scale
@@
 are constructed separately for fuel and moderator regions.
+
+\section{Model Description}
+
+As a proof of concept and to ease resolution of strong transient gradients in
+temperature between fuel and moderator, the physical three dimensional problem
+is reduced to a two dimensional axisymmetric model. The model molten salt
+reactor is based on the \gls{MSRE}. To approximately simulate the lattice
+structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
+fuel-moderator regions, as shown in \cref{fig:geom}. The fuel and moderator
+radii are chosen such that the resulting area/volume fraction of fuel is .225 as
+for the \gls{MSRE}.
+
+\begin{figure}
+  \centering
+  \includegraphics{geometry.eps}
+  \label{fig:geom}
+  \caption{A sketch of the \gls{MSR} model geometry}
+\end{figure}
+
+The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
+and is given in \cref{table:comp} \cite{robertson_msre_1965}.
 

### 2017-05-10 Moltres.tex
tries to do some rearranging into Methods vs. Model

@@
 
-The model is implemented using the \gls{MOOSE} \cite{gaston_physics-based_2015} application code
-Moltres \cite{lindsay_arfc/moltres_nodate}. Building on the massively
-parallelizable \gls{MOOSE} framework allows Moltres to be run on super-computing
-platforms like \gls{NCSA}'s Blue Waters. For some three-dimensional simulations
-(results not discussed here), the number of elements in the mesh and total
-number of degrees of freedom exceed one million and ten million respectively. To
-handle problems of this size, Moltres has been run on up to 608 cores. However,
-reducing the problem dimension from three to two and using a structured mesh
-that can be much more coarse in the axial direction allows problem solution to
-be carried out on a single core in under five minutes.
+Moltres \cite{lindsay_arfc/moltres_nodate} is implemented as an application for 
+use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework.
 
@@
 
-Group constants
-are generated with either Serpent \cite{leppanen_serpent_2015} or Scale
-\cite{dehart_reactor_2011}. Temperature vs group constant interpolation tables
-are constructed separately for fuel and moderator regions.
+Group constants are generated with either Serpent \cite{leppanen_serpent_2015} 
+or Scale \cite{dehart_reactor_2011}. Temperature vs group constant 
+interpolation tables are constructed separately for fuel and moderator regions.
+
+\subsection{Performance}
+
+Building on the massively parallelizable \gls{MOOSE} framework allows Moltres 
+to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some 
+three-dimensional simulations (results not discussed here), the number of 
+elements in the mesh and total number of degrees of freedom exceed one million 
+and ten million respectively. To handle problems of this size, Moltres has been 
+run on up to 608 cores. However, reducing the problem dimension from three to 
+two and using a structured mesh that can be much more coarse in the axial 
+direction allows problem solution to be carried out on a single core in under 
+five minutes.
 
@@
 
-\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
+\cref{fig:pre1} shows the concentration of the longest lived precursor in the
 reactor. Not surprisingly, the channel concentrations are higher in fuel channels

### 2017-05-10 Moltres.tex
I prefer capitalized Fig, Table, etc.

@@
 In Moltres, neutrons are described with time-dependent multi-group diffusion theory as shown
-in \cref{eq:neutrons}:
+in \Cref{eq:neutrons}:
 
@@
 
-Delayed neutron precursors are described by \cref{eq:precursors}:
+Delayed neutron precursors are described by \Cref{eq:precursors}:
 
@@
 structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
-fuel-moderator regions, as shown in \cref{fig:geom}. The fuel and moderator
+fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
 radii are chosen such that the resulting area/volume fraction of fuel is .225 as
@@
 The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
-and is given in \cref{table:comp} \cite{robertson_msre_1965}.
+and is given in \Cref{table:comp} \cite{robertson_msre_1965}.
 
@@
 
-Group fluxes are shown in \cref{fig:group1,fig:group2}. The effect of the vacuum
+Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
 boundary conditions is shown clearly in the cosinusoidal shapes in radial and
@@
 
-The effect of the advecting fuel is seen in \cref{fig:temp} where the temperature
+The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
 rises steadily with increasing z-coordinate. As one might expect, the temperature
@@
 
-\cref{fig:pre1} shows the concentration of the longest lived precursor in the
+\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
 reactor. Not surprisingly, the channel concentrations are higher in fuel channels
@@
 maximum concentration around the center-plane of the reactor as shown in
-\cref{fig:pre6}. As for all other precursors, its concentration decreases with
+\Cref{fig:pre6}. As for all other precursors, its concentration decreases with
 increasing radius and decreasing neutron flux.

### 2017-05-10 Moltres.tex
adds definitions for variable in diffusion eqn

@@
 use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework. 
-
-The Moltres code-base currently includes kernels and boundary conditions for
+Accordingly, Moltres includes physics kernels and boundary conditions for
 solving for neutron fluxes, temperature, and precursor concentrations. In \gls{MOOSE}
@@
 %% \nu \Sigma_{g'}^f \phi_{g'}
-        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g 
-        \nabla \phi_g + \Sigma_g^r \phi_g &= \sum_{g \ne g'}^G 
+        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} &- \nabla \cdot D_g 
+        \nabla \phi_g + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G 
         \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
@@
         \intertext{where}
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>].
+        v_g &= \mbox{speed of neutrons in group g } [<+units+>]\\ 
+        \phi_g &= \mbox{flux of neutrons in group g } [<+units+>]\\ 
+        t &= \mbox{time } [<+units+>]\\ 
+        D_g &= \mbox{Diffusion coefficient for neutrons in group g } [<+units+>]\\ 
+        \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons 
+        from group g } [<+units+>]\\ 
+        \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
+        scattering from g' to g } [<+units+>]\\ 
+        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g } [<+units+>]\\ 
+        G &= \mbox{number of discrete groups, g } [<+units+>]\\ 
+        \nu &= \mbox{number of neutrons produced per fission } [<+units+>]\\ 
+        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g } [<+units+>]\\ 
+        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g } [<+units+>]\\ 
+        I &= \mbox{number of delayed neutron precursor groups } [<+units+>]\\ 
+        \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
+        in precursor group i } [<+units+>]\\ 
+        C_i &= \mbox{concentration of delayed neutron precursors in precursor 
+        group i } [<+units+>]. 
 \end{align}
@@
         \intertext{where}
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
-        <+var+> &= \mbox{<++>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
+        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
 \end{align}

### 2017-05-10 Moltres.tex
who needs units anyway

@@
         \intertext{where}
-        v_g &= \mbox{speed of neutrons in group g } [<+units+>]\\ 
-        \phi_g &= \mbox{flux of neutrons in group g } [<+units+>]\\ 
-        t &= \mbox{time } [<+units+>]\\ 
-        D_g &= \mbox{Diffusion coefficient for neutrons in group g } [<+units+>]\\ 
+        v_g &= \mbox{speed of neutrons in group g} \\ 
+        \phi_g &= \mbox{flux of neutrons in group g} \\ 
+        t &= \mbox{time} \\ 
+        D_g &= \mbox{Diffusion coefficient for neutrons in group g} \\ 
         \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons 
-        from group g } [<+units+>]\\ 
+        from group g} \\ 
         \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
-        scattering from g' to g } [<+units+>]\\ 
-        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g } [<+units+>]\\ 
-        G &= \mbox{number of discrete groups, g } [<+units+>]\\ 
-        \nu &= \mbox{number of neutrons produced per fission } [<+units+>]\\ 
-        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g } [<+units+>]\\ 
-        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g } [<+units+>]\\ 
-        I &= \mbox{number of delayed neutron precursor groups } [<+units+>]\\ 
+        scattering from g' to g} \\ 
+        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g} \\ 
+        G &= \mbox{number of discrete groups, g} \\ 
+        \nu &= \mbox{number of neutrons produced per fission} \\ 
+        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g} \\ 
+        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g} \\ 
+        I &= \mbox{number of delayed neutron precursor groups} \\ 
         \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
-        in precursor group i } [<+units+>]\\ 
+        in precursor group i} \\ 
         C_i &= \mbox{concentration of delayed neutron precursors in precursor 
-        group i } [<+units+>]. 
+        group i} . 
 \end{align}

### 2017-05-10 Moltres.tex
all vars in delayed neutron equation have been previously handled

@@
         I &= \mbox{number of delayed neutron precursor groups} \\ 
+        \beta &= \mbox{delayed neutron fraction}\\
         \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
@@
         C_i \label{eq:precursors}
-        \intertext{where}
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
-        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
 \end{align}

### 2017-05-10 Moltres.tex
defines fuel and mod temp eqn vars.

@@
 
-\begin{equation}
-  \rho_fc_{p,f}\frac{\partial T_f}{\partial t} + \nabla\cdot\left(\rho_f c_{p,f}
-  \vec{u}\cdot T_f -k_f\nabla T_f\right) =  Q_f
+\begin{align}
+        \rho_fc_{p,f}\frac{\partial T_f}{\partial t} &+ \nabla\cdot\left(\rho_f 
+        c_{p,f} \vec{u}\cdot T_f -k_f\nabla T_f\right) =  Q_f
   \label{eq:fuel_temp}
-\end{equation}
+  \intertext{where}
+  \rho_f &= \mbox{density of fuel salt}\\
+  c_{p,f} &= \mbox{specific heat capacity of fuel salt}\\
+  T_f &= \mbox{temperature of fuel salt}\\
+  \vec{u} &= \mbox{velocity of fuel salt}\\
+  k_f &= \mbox{thermal conductivity of fuel salt}\\
+  Q_f &= \mbox{source term}\\
+\end{align}
 
@@
 
-\begin{equation}
-  \rho_gc_{p,g}\frac{\partial T_g}{\partial t} + \nabla\cdot\left(-k_g\nabla T_g\right) =  Q_g
+\begin{align}
+        \rho_gc_{p,g}\frac{\partial T_g}{\partial t} &+ 
+        \nabla\cdot\left(-k_g\nabla T_g\right) =  Q_g
   \label{eq:moderator_temp}
-\end{equation}
+  \intertext{where}
+  \rho_g &= \mbox{density of graphite moderator}\\
+  c_{p,g} &= \mbox{specific heat capacity of graphite moderator}\\
+  T_g &= \mbox{temperature of graphite moderator}\\
+  k_g &= \mbox{thermal conductivity of graphite moderator}\\
+  Q_g &= \mbox{source term in graphite moderator}\\
+\end{align}
 

### 2017-05-10 Moltres.tex
moved fuel source term def and rephrased interpolation explanation.

@@
 
-in the fuel and by:
+in the fuel, where the source term $Q_f$ is defined by:
+
+\begin{equation}
+  Q_f = \sum_{g=1}^G \epsilon_{f,g}\Sigma_{f,g}\phi_g
+  \label{eq:fuel_source}
+\end{equation}
+
+In the moderator, the governing equation for temperature is given by:
 
@@
 
-in the moderator. $Q_f$ is defined by:
+in the moderator.
 
-\begin{equation}
-  Q_f = \sum_{g=1}^G \epsilon_{f,g}\Sigma_{f,g}\phi_g
-  \label{eq:fuel_source}
-\end{equation}
-
-and $Q_g$ is equal to $\gamma Q_f$, representing heat dissipation by gamma and
-neutron irradiation in the moderator.
+and $Q_g$ is equal to $\gamma Q_f$, where $\gamma$ is a factor representing 
+heat dissipation by gamma and neutron irradiation in the moderator.
 
 Group constants are generated with either Serpent \cite{leppanen_serpent_2015} 
-or Scale \cite{dehart_reactor_2011}. Temperature vs group constant 
-interpolation tables are constructed separately for fuel and moderator regions.
+or Scale \cite{dehart_reactor_2011} by the modeler. Group constant temperature 
+dependence is implmented via interpolation tables, which must be constructed 
+separately for fuel and moderator regions.
 

### 2017-05-10 Moltres.tex
adds image sent by alex via email on May 9, 2017.

@@
   \end{center}
-  \caption{Fuel salt composition based on enriched Uranium \gls{MSRE} design \cite{robertson_msre_1965}}
+        \caption{Fuel salt composition is based on the \gls{BOL} enriched 
+        uranium composition in the \gls{MSRE} design 
+        \cite{robertson_msre_1965}.}
   \label{table:comp}
@@
   \includegraphics{auto_diff_rho_group1.eps}
-  \caption{Group 1 flux}
+        \caption{The group 1 flux in this 2-D cylindrical axisymmetric model 
+        has the anticipated magnitude and canonical cosine shape ($r=1$ is center of core). }
   \label{fig:group1}
@@
   \includegraphics{auto_diff_rho_group2.eps}
-  \caption{Group 2 flux}
+        \caption{The group 2 flux in this 2-D cylindrical axisymmetric model 
+        has the anticipated magnitude and canonical cosine shape ($r=1$ is center of core). }
   \label{fig:group2}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics{radial_group_comparison.eps}
+        \caption{The thermal and fast flux profiles are compared at the 
+        core center in this 2-D cylindrical axisymmetric model ($r=1$ is center of core). }
+\end{figure}
+
 The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
-rises steadily with increasing z-coordinate. As one might expect, the temperature
+rises steadily with increasing z-coordinate. As is accordingly expected, the temperature
 gradient is negative in the radial direction.
@@
   \includegraphics{auto_diff_rho_temp.eps}
-  \caption{Temperature}
+        \caption{The reactor core temperature peaks near the reactor outlet 
+        in this 2-D axisymmetric model ($r=1$ is center of core).}
   \label{fig:temp}
@@
   \includegraphics{auto_diff_rho_pre1.eps}
-  \caption{Longest lived precursor concentration}
+        \caption{The concentration of the group of longest lived precursors 
+        ($\lambda = ?$) peaks near the reactor outlet
+        in this 2-D axisymmetric model ($r=1$ is center of core).}
   \label{fig:pre1}
@@
   \includegraphics{auto_diff_rho_pre6.eps}
-  \caption{Shortest lived precursor concentration}
+        \caption{The concentration of the group of shortest lived precursors 
+        ($\lambda = ?$) peaks near the reactor center
+        in this 2-D axisymmetric model ($r=1$ is center of core).}
   \label{fig:pre6}

### 2017-05-11 Moltres.tex
Some small fixes and add passage describing radial plot of fluxes.

--- 2017-05-10 Moltres.tex
@@
         from group g} \\
-        \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
+        \Sigma_{g'\rightarrow g}^s &= \mbox{macroscopic cross-section of
         scattering from g' to g} \\
@@
 
-in the moderator.
+In this work $Q_g$ is set equal to $\gamma Q_f$, where $\gamma$ is a factor
+representing heat dissipation by gamma and neutron irradiation in the moderator.
 
-and $Q_g$ is equal to $\gamma Q_f$, where $\gamma$ is a factor representing 
-heat dissipation by gamma and neutron irradiation in the moderator.
-
-Group constants are generated with either Serpent \cite{leppanen_serpent_2015} 
-or Scale \cite{dehart_reactor_2011} by the modeler. Group constant temperature 
-dependence is implmented via interpolation tables, which must be constructed 
-separately for fuel and moderator regions.
+Group constants are generated by the modeler with either Serpent
+\cite{leppanen_serpent_2015} or Scale \cite{dehart_reactor_2011}. Group constant
+temperature dependence is implemented via interpolation tables, which must be
+constructed separately for fuel and moderator regions.
 
@@
   \end{center}
-  \caption{Fuel salt composition based on enriched Uranium \gls{MSRE} design \cite{robertson_msre_1965}}
+        \caption{Fuel salt composition is based on the \gls{BOL} enriched
+        uranium composition in the \gls{MSRE} design
+        \cite{robertson_msre_1965}.}
   \label{table:comp}
@@
   \includegraphics{auto_diff_rho_group1.eps}
-  \caption{Group 1 flux}
+        \caption{The group 1 flux in this 2-D cylindrical axisymmetric model
+        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
   \label{fig:group1}
@@
   \includegraphics{auto_diff_rho_group2.eps}
-  \caption{Group 2 flux}
+        \caption{The group 2 flux in this 2-D cylindrical axisymmetric model
+        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
   \label{fig:group2}
@@
 
+\Cref{fig:flux_comparison} compares the fast and thermal neutron fluxes at the
+reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
+moderator regions and visa versa in fuel regions are even more apparent. The
+larger fast flux magnitude is attributable to using \gls{BOL} fuel
+composition. As the fuel salt reaches an equilibrium composition, the thermal
+flux is expected to exceed that of the fast group.
+
+\begin{figure}
+  \centering
+  \includegraphics{radial_group_comparison.eps}
+  \caption{The thermal and fast flux profiles are compared at the core mid-plane
+    ($z=H/2$) in this 2-D cylindrical axisymmetric model ($r=0$ is radial center
+    of core). }
+  \label{fig:flux_comparison}
+\end{figure}
+
 The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
-rises steadily with increasing z-coordinate. As one might expect, the temperature
+rises steadily with increasing z-coordinate. As is expected, the temperature
 gradient is negative in the radial direction.
@@
   \includegraphics{auto_diff_rho_temp.eps}
-  \caption{Temperature}
+        \caption{The reactor core temperature peaks near the reactor outlet in
+          this 2-D axisymmetric model because of fuel advection ($r=0$ is center
+          of core).}
   \label{fig:temp}
@@
 events. Because of the small decay constant of the precursor, the maximum
-concentration in any given channel occurs at the core outlet.
+concentration in any given channel occurs at the core outlet due to advection.
 
@@
   \includegraphics{auto_diff_rho_pre1.eps}
-  \caption{Longest lived precursor concentration}
+        \caption{The concentration of the group of longest lived precursors
+        ($\lambda = 1.24\cdot 10^{-2} s^{-1}$) peaks near the reactor outlet
+        in this 2-D axisymmetric model ($r=0$ is center of core).}
   \label{fig:pre1}
@@
   \includegraphics{auto_diff_rho_pre6.eps}
-  \caption{Shortest lived precursor concentration}
+        \caption{The concentration of the group of shortest lived precursors
+        ($\lambda = 3.07 s^{-1}$) peaks near the reactor center
+        in this 2-D axisymmetric model ($r=0$ is center of core).}
   \label{fig:pre6}

### 2017-05-11 Moltres.tex

@@
 
-Molten salt reactor concepts garnered considerable interest in the 1950s and
-60s with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.
-With the inclusion of the \gls{MSR} among the Generation-IV reactor designs
-\cite{gen_IV}, this reactor concept has gained renewed research interest in the
-past decade, with many new nuclear companies proposing both fluid-fuelled and
-solid-fuelled commerical \gls{MSR} designs
-\cite{terrapower,terrestrial,elysium,thorcon,kairos}. Two key advantages
-offered by the fluid-fuelled \gls{MSR} are improved fuel utilization and no
-radiation damage constraint on attainable fuel burn-up. Together, these
-attributes result in significantly reduced core fissile inventories and spent
-nuclear fuel mass \cite{noauthor_gen_2008}.  These characteristics give the
-\gls{MSR} a potentially unique capability for actinide burning and extension of
-fuel resources.
+Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
+with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
+the inclusion of the \gls{MSR} among the Generation-IV reactor designs
+\cite{noauthor_gif_2015}, this reactor concept has gained renewed research
+interest in the past decade, with many new nuclear companies proposing both
+fluid-fuelled and solid-fuelled commerical \gls{MSR} designs
+\cite{hyde_liquid_2015,leblanc_integral_2015,noauthor_-able_2017,scarlat_design_2014,noauthor_neutronics_2016}. Two
+key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
+utilization and no radiation damage constraint on attainable fuel
+burn-up. Together, these attributes result in significantly reduced core fissile
+inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  These
+characteristics give the \gls{MSR} a potentially unique capability for actinide
+burning and extension of fuel resources.
 
@@
 from one to three dimensions and can be deployed on an arbitrary number of
-processing units. Moltres is devoted to previously unmatched
-fidelity in coupled neutronics and thermal hydraulics \gls{MSR} simulation.
+processing units. Through its computing power, Moltres is devoted to previously
+unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
+simulation.
 
-Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a tool that can be
-freely used, studied, interrogated, and improved by the \gls{MSR}
-community.  Its openness is a defining characteristic and
-promotes unmatched quality through transparency and ease of peer review. In the
-era of GitHub\cite{github} and international scientific collaboration, open and modern software practices must be
-employed in order for nuclear engineering simulation capability to enable
-discovery and support the regulatory needs presented by new reactor designs.
-Furthermore, to openness is necessary to keep pace with scientific computing
-advances in fields like astronomy whose multitude of open simulation tools
-(Enzo\cite{enzo}, Gadget\cite{gadget}, Flash\cite{flash}, Gizmo\cite{gizmo},
-Ramses\cite{ramses}, Mesa\cite{mesa}) allows them to be the darlings of
-scientific visualization and public interest.
-
-In that vein, Moltres uses
+Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a
+tool that can be freely used, studied, interrogated, and improved by the
+\gls{MSR} community.  Its openness is a defining characteristic and promotes
+quality through transparency and ease of peer review. In the era of
+GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
+open and modern software practices must be employed in order for nuclear
+engineering simulation capability to enable discovery and support the regulatory
+needs presented by new reactor designs. In that vein, Moltres uses
 \mintinline{latex}{git} for version control, integration testing to protect
@@
 class extensibility and minimal code duplication. Moreover, Moltres is built on
-top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another \gls{LGPL}
-code that itself leans on LibMesh \cite{kirk2006libmesh}, a \gls{LGPL} finite element
-library, and PetSc \cite{petsc-user-ref}, a \gls{BSD}-licensed toolkit for solving nonlinear
-equations stemming from discretization of PDEs. \gls{MOOSE} and LibMesh handle
-translation of application (Moltres) defined weak PDE forms into residual and
-Jacobian functions that are the inputs into PetSc Newton-Raphson solution
-routines. All codes use MPI for parallel communication and are easily deployed
-on massively-parallel cluster-computing platforms. \gls{MOOSE} applications by default
-use monolithic and implicit methods that are ideal for closely-coupled and
-multi-scale physics. These methods are ideal for the model problem described in
-this work. However, it should be noted that Moltres can also use explicit
+top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another
+\gls{LGPL} code that itself leans on LibMesh \cite{kirk_libmesh:_2006}, a
+\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
+\gls{BSD}-licensed toolkit for solving nonlinear equations stemming from
+discretization of PDEs. \gls{MOOSE} and LibMesh handle translation of
+application (Moltres) defined weak PDE forms into residual and Jacobian
+functions that are the inputs into PetSc Newton-Raphson solution routines. All
+codes use MPI for parallel communication and are easily deployed on
+massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
+default use monolithic and implicit methods that are ideal for closely-coupled
+and multi-scale physics. These methods are ideal for the model problem described
+in this work. However, it should be noted that Moltres can also use explicit
 time-stepping routines as well as segregated solution methods, making it very

### 2017-05-11 Moltres.tex
Add parameter table (#2)

@@
 
+Other simulation inputs are outlined in \Cref{table:params}. It should be noted
+that the reactor simulation height of 151.75 cm was chosen to produce an
+approximately critical reactor configuration corresponding to \gls{BOL}
+\gls{MSRE} composition. It is about 10 cm shorter than the actual \gls{MSRE}
+height of 162.56 cm.
+
+\begin{table}[htpb]
+  \begin{center}
+    \begin{tabular}{l|c|c|c}
+      Parameter & Value & Units & Source\\\hline\hline
+      Inlet temp. & 922 & $K$ & \gls{MSRE} nominal \cite{robertson_msre_1965}\\
+      Wall temp. & 922 & $K$ & \gls{MSRE} nominal \cite{robertson_msre_1965}\\
+      Neutron groups & 2 & 1 & User\\
+      Precursor groups & 6 & 1 & User\\
+      Reactor radius & 72.5 & $cm$ & $\approx$\gls{MSRE} radius (70.2 cm) \cite{robertson_msre_1965}\\
+      Reactor height & 151.75 & $cm$ & User\\
+      $k{_f}$ & .0553 & $W cm^{-1} K^{-1}$ & \cite{robertson_msre_1965}\\
+      $c_{p,f}$ & 1967 & $J K^{-1} kg^{-1}$ & \cite{robertson_msre_1965}\\
+      $\rho_f$ & $2.146\cdot 10^{-3} e^{-\alpha_f (T_f - 922)}$ & $kg\ cm^{-3}$ & \cite{robertson_msre_1965}\\
+      $\alpha_f$ & $2.12\cdot 10^{-4}$ & $K^{-1}$ &
+      \cite{haubenreich_experience_1970}\\
+      $k_g$ & .312 & $W cm^{-1} K^{-1}$ & \cite{cammi_multi-physics_2011}\\
+      $c_{p,g}$ & 1760 & $J K^{-1} kg^{-1}$ & \cite{cammi_multi-physics_2011}\\
+      $\rho_g$ & $1.86\cdot 10^{-3} e^{-\alpha_g (T_g - 922)}$ & $kg\ m^{-3}$ &
+      \cite{robertson_msre_1965}\\
+      $\alpha_g$ & $1.8\cdot 10^{-5}$ & $K^{-1}$ &
+      \cite{haubenreich_experience_1970}\\
+    \end{tabular}
+  \end{center}
+  \caption{Simulation input parameters}
+  \label{table:params}
+\end{table}
+
 \section{Results \& Discussion}

### 2017-05-14 Moltres.tex
use times rather than cdot for scientific notation

@@
       Li-7 & .1090\\
-      Li-6 & 5$\cdot$10$^{-6}$\\
+      Li-6 & 5$\times$10$^{-6}$\\
       F-19 & .6680\\

### 2017-06-01 full-core_msbr_model.tex
Name of file changed. Title and authors added

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Full-core analysis of thorium-fueled molten salt breader reactor using the SERPENT-2 Monte Carlo code}

\author{Andrei Rykhlevskii, Kathryn Huff, Alexander Lindsay}

\institute{
Department of Nuclear, Plasma, and Radiological Engineering, University of Illinois at Urbana-Champaign
Urbana, IL
}

\email{andreir2@illinois.edu}

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF

\newcommand{\SN}{S$_N$}
\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
\newcommand{\grad}{\vec{\nabla}} % gradient
\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The molten salt reactor (MSR) is advanced type of reactor which was  developed in Oak Ridge National Laboratory for a military aircraft nuclear propulsion project. In the MSR flourides of fissile and/or ferile materials (i.e. $UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form liquid fuel. 
combining two functions: heat transportation from the energy generation region  to heat exchanger and

Microsoft Word can be a finicky beastie. \LaTeX\ abstracts content from
formatting, allowing the user to let a style file such as this take care of
uppercasing the section headings, spacing the paragraphs, and shuffle around
the figures.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis
nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu
fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum.

The \SN\ equations were developed by Carlson \cite{Car1953}. Another
paper is cited here \cite{Lar2008}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Theory}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur faucibus
erat sed nisi aliquet molestie. Etiam malesuada, sapien at lobortis lacinia,
justo ante volutpat nunc, gravida commodo justo purus ut quam. Proin tincidunt
sem quis dui condimentum rhoncus. Nulla ut libero est, ut sollicitudin ligula.
Curabitur quam orci, aliquet dignissim feugiat eu, porta ac leo. Aenean in
ipsum arcu. Duis tempus porttitor turpis, eu volutpat odio fringilla sit amet.
Donec malesuada, arcu id porttitor mattis, arcu est molestie arcu, quis
dignissim tellus justo nec sapien. Praesent pretium interdum odio ac varius.
Suspendisse dui mauris, posuere in varius a, semper id dui. Suspendisse
placerat, quam quis luctus aliquam, metus justo hendrerit massa, vel tempus
ligula sem et purus.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur faucibus
erat sed nisi aliquet molestie.

Equations look exceedingly pretty. Here is a 3-D, monoenergetic, steady-state
transport equation with isotropic scattering and an isotropic extraneous source:
\begin{subequations} \label{eqs:fullTransport}
\begin{multline} \label{eq:fullTransportVol}
  \vec{\Omega}\vd \grad \psi(\vec{x}, \vec{\Omega})
  + \sigma(\vec{x}) \psi (\vec{x}, \vec{\Omega})
\\ =
  \frac{\sigma_s(\vec{x})}{4\pi} \int_{4\pi} \psi(\vec{x},\vec{\Omega}')
  \ud\Omega' + \frac{q(\vec{x})}{4\pi}
  \equiv \frac{1}{4\pi} Q(\vec{x}) \,,
\end{multline}
inside $\vec{x} \in V$, $\vec{\Omega} \in 4\pi$, with an incident boundary
condition
\begin{equation} \label{eq:fullTransportBndy}
  \psi(\vec{x}, \vec{\Omega}) = \psi^b(\vec{x}, \vec{\Omega}) \,,
 \quad \vec{x} \in \partial V, \ \vec{\Omega} \vd \vec{n} < 0\,.
\end{equation}
\end{subequations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Analysis}
The results were interesting, so interesting in fact that we have decided to
present them here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection Goes Here}
The user must manually capitalize initial letters of a subsection heading.

For those who like equations in their papers, \LaTeX\ is a good choice. Here is
an equation for the Marshak diffusion boundary condition:
\begin{equation} \label{eq:marshak}
  4 J^- = \phi + 2 D \vec{n} \vd \grad \phi \,.
\end{equation}
If we so choose, we can effortlessly reference the equation later.

Another paragraph starts with Eq.~\eqref{eq:marshak} and sets $J^-$ to zero, a
vacuum boundary condition:
\begin{equation*}
  0 = \phi + \frac{2}{3} \frac{1}{\sigma} \vec{n} \vd \grad \phi \,.
\end{equation*}
The extrapolation distance is $2/3$. A more detailed asymptotic analysis yields
an extrapolation distance of about $0.71045$.

Figure~\ref{fig:voltage} shows how a plot might conceivably look in your
document. Always place figures after they are referenced so as not to throw
off the reader. You can use symbols and different line styles to help
differentiate your results, especially if they are printed in black and white.
Note how Fig.~\ref{fig:voltage} uses dashed lines \verb|--| for the exact
solution, solid lines \verb|-| for the new method's solutions, and dotted lines
\verb|:| for existing inaccurate methods.
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics{example_figure}
  \caption{Captions are flush with the left.}
  \label{fig:voltage}
\end{figure}

Later on, we can include a table, even one that spans two columns such as
Table~\ref{tab:widetable}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htb]
  \centering
\begin{tabular}{llllllllll}\toprule
      & $\phi_T(0)$      & $\phi_T(10)$      & $\phi_T(20)$      &
      $\phi_D(0)$      & $\phi_D(10)$      & $\phi_D(20)$      & $\rho$      &
      $\varepsilon$      & $N_\text{it}$
\\ \midrule
$c=0.999$  & 0.9038 & 20.63 & 31.24 & 0.9087 & 20.63 & 31.23 & 0.2192 & $10^{-7}$ & 15
\\
$c=0.990$  & 0.3675 & 13.04 & 24.7 & 0.3696 & 13.04 & 24.69 & 0.2184 & $10^{-7}$ & 15
\\
$c=0.900$  & 0.009909 & 4.776 & 17.64 & 0.009984 & 4.786 & 17.63 & 0.2118 & $10^{-7}$ & 14
\\
$c=0.500$  & $6.069\times 10^{-5}$ & 2.212 & 15.53 & 6.213$\times 10^{-5}$ & 2.239 & 15.53 & 0.2068 & $10^{-7}$ & 13
\\
\bottomrule
\end{tabular}
  \caption{This is an example of a really wide table which might not normally
  fit in the document.}
  \label{tab:widetable}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Notice how the table reference uses a Roman numeral
for its numbering scheme, whereas the figure reference uses an Arabic numeral.
For one-column tables, use the \verb|table| environment; two-column tables use
\verb|table*|. The same applies to figures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Another Subsection}
Excessive sectioning in a three-page document is discouraged, but here are more
subsections to demonstrate compliance with the ANS formatting guidelines.

\subsubsection{Third-level Heading}
This subsubsection shows compliance with the ANS-specified standard. This level
of heading should be used rarely.

\subsubsection{Another Such Heading}
And, if you really think you need a third-level heading, you should make sure
that your subsection needs at least two of them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

The included ANS style file and this clear example file are a panacea for
the hours of headache that invariably results from formatting a document in
Microsoft Word.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Appendix}

Numbering in the appendix is different:
\begin{equation} \label{eq:appendix}
  2 + 2 = 5\,.
\end{equation}
and another equation:
\begin{equation} \label{eq:appendix2}
  a + b = c\,.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
This material is based upon work supported a Department of Energy Nuclear
Energy University Programs Graduate Fellowship.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ans}
\bibliography{bibliography}
\end{document}

### 2017-06-05 full-core_msbr_model.tex
Introduction and part of MSBR describing added. Whole views figures added

@@
 \usepackage{graphicx} % allows inclusion of graphics
+\usepackage{caption}  % allows center figures caption
 \usepackage{booktabs} % nice rules (thick lines) for tables
 \usepackage{microtype} % improves typography for PDF
+\graphicspath{{figures/}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-The molten salt reactor (MSR) is advanced type of reactor which was  developed in Oak Ridge National Laboratory for a military aircraft nuclear propulsion project.
-In the MSR flourides of fissile and/or ferile materials (i.e.
-$UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form liquid fuel.
-combining two functions: heat transportation from the energy generation region  to heat exchanger and
+\section{1. Introduction}
+The molten salt reactor (MSR) is advanced type of reactor which was  developed at Oak Ridge National Laboratory for a military aircraft nuclear propulsion project.
+In the MSR fluorides of fissile and/or fertile materials (i.e.
+$UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form a liquid fuel which circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
+This conception leads to immediate advantages over traditional reactors with a solid fuel, such as near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
 
-Microsoft Word can be a finicky beastie. \LaTeX\ abstracts content from
-formatting, allowing the user to let a style file such as this take care of
-uppercasing the section headings, spacing the paragraphs, and shuffle around
-the figures.
+Thermal spectrum Molten Salt Breeder Reactor (MSBR) designed specifically to realize promising thorium fuel cycle which allows use natural thorium instead of enriched uranium as the fertile element to breed the fissile $^{233}U$ and avoid uranium enrichment.
+The mixtures of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ (72-16-12-0.232-0.0006 mole \%) has a melting point $499^\circ$C, good flow and heat transfer properties \cite{robertson_conceptual_1971}.
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
-incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis
-nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu
-fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
-culpa qui officia deserunt mollit anim id est laborum.
+For the development of MSBR research, this paper demonstrates advanced whole-core three-dimensional model developed using a continuous-energy Monte Carlo reactor physics calculation code Serpent 2 and cross-verification with existing MCNP6 results \cite{park_whole_2015,leppanen_serpent_2012}.
+The neutronics model could be useful for optimization fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation, and for depletion calculations using built-in Serpent burnup module.
+Moreover, this model in the future will be employed to generate problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017} as well as for routine applications.
 
-The \SN\ equations were developed by Carlson \cite{Car1953}. Another
-paper is cited here \cite{Lar2008}.
+All the calculations presented in this paper were performed using the Serpent 2 code version 2.1.28.
+Comparing with Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
+Before burnup calculations can be undertaken MSBR model should be validated.
+In Section 2 a brief description of the MSBR geometry model is given.
+There is no approximations were applied for this core simulation despite aspects of MSBR geometry are difficult to model \cite{park_whole_2015}.
+In Section 3 the results are presented and discussed.
+Section 4 reflected conclusions and plans for the future research.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Theory}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur faucibus
-erat sed nisi aliquet molestie. Etiam malesuada, sapien at lobortis lacinia,
-justo ante volutpat nunc, gravida commodo justo purus ut quam. Proin tincidunt
-sem quis dui condimentum rhoncus. Nulla ut libero est, ut sollicitudin ligula.
-Curabitur quam orci, aliquet dignissim feugiat eu, porta ac leo. Aenean in
-ipsum arcu. Duis tempus porttitor turpis, eu volutpat odio fringilla sit amet.
-Donec malesuada, arcu id porttitor mattis, arcu est molestie arcu, quis
-dignissim tellus justo nec sapien. Praesent pretium interdum odio ac varius.
-Suspendisse dui mauris, posuere in varius a, semper id dui. Suspendisse
-placerat, quam quis luctus aliquam, metus justo hendrerit massa, vel tempus
-ligula sem et purus.
+\section{2. Molten salt breeder reactor description}
+MSBR vessel has diameter 680 cm and high 610 cm and contains molten fluoride fuel-salt mixture which performs to functions: generate heat in the moderated region and transport heat energy from the core to primary heat exchanger using primary salt pump.
+The vessel also contains graphite blocks for neutron moderation and reflection.
+The reactor core has a central zone, Zone I, in which 13\% of the volume is fuel salt and 87\% - graphite.
+The first zone is composed of 1320 graphite cells, 2 graphite control rods and 2 safety rods consisting of boron carbide clad.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur faucibus
-erat sed nisi aliquet molestie.
+The undermoderated zone, Zone II, with 37\% fuel salt, or radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
+This zone is formed of two kinds of elements: elements like those for Zone I except for a larger hole size (Zone II-A), and radially spread 42.72cm-thick graphite slats (Zone II-B).
+At the outer of the core there are 70cm-thick graphite reflector and 5cm-thick vessel wall.
+Betweeen the core and the reflector blocks located 5.08cm-wide annulus which is 100\% salt needed to provide possibility removing and inserting a core graphite assembly.
+
+Figure~\ref{fig:plan} shows plan view of the whole core configuration at the expected reactor operational level when all control rods are fully withdrawn from the core.
+Figure~\ref{fig:elevation} shows longitudinal section of the reactor.
+The violet color represents bare graphite, and the yellow represents fuel salt.
+The blue color shows Hastelloy-N, material used for the plenum and vessel wall, and the black color is a void space.
+All figures of the core in this work generated using built-in Serpent plotter.
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \captionsetup{justification=centering}
+  \includegraphics[width=1\linewidth]{figure_2_1.png}
+  \caption{Plan view of molten salt breeder reactor (MSBR) core.}
+  \label{fig:plan}
+\end{figure}
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \captionsetup{justification=centering}
+  \includegraphics[width=1\linewidth]{figure_2_2.png}
+  \caption{Elevation view of MSBR.}
+  \label{fig:elevation}
+\end{figure}
+
+\subsection{2.1. Zone I and II-A}
+The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements, as shown in Fig.2.2. The elements
+
+\subsection{2.2. Zone II-B}
 
@@
 
-Figure~\ref{fig:voltage} shows how a plot might conceivably look in your
+shows how a plot might conceivably look in your
 document. Always place figures after they are referenced so as not to throw

### 2017-06-06 full-core_msbr_model.tex
Section 2 finished

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Full-core analysis of thorium-fueled molten salt breader reactor using the SERPENT-2 Monte Carlo code}
+\title{Full-core analysis of thorium-fueled molten salt breeder reactor using the SERPENT-2 Monte Carlo code}
 
@@
 \institute{
-Department of Nuclear, Plasma, and Radiological Engineering, University of Illinois at Urbana-Champaign
+Department of Nuclear, Plasma, and Radiological Engineering, University of Illinois at Urbana-Champaign \break
 Urbana, IL
@@
 In Section 2 a brief description of the MSBR geometry model is given.
-There is no approximations were applied for this core simulation despite aspects of MSBR geometry are difficult to model \cite{park_whole_2015}.
 In Section 3 the results are presented and discussed.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{2. Molten salt breeder reactor description}
+\section{2. MSBR design description}
 MSBR vessel has diameter 680 cm and high 610 cm and contains molten fluoride fuel-salt mixture which performs to functions: generate heat in the moderated region and transport heat energy from the core to primary heat exchanger using primary salt pump.
@@
 The undermoderated zone, Zone II, with 37\% fuel salt, or radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
-This zone is formed of two kinds of elements: elements like those for Zone I except for a larger hole size (Zone II-A), and radially spread 42.72cm-thick graphite slats (Zone II-B).
+This zone is formed of two kinds of elements: elements like those for Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
 At the outer of the core there are 70cm-thick graphite reflector and 5cm-thick vessel wall.
@@
   \centering
-  \captionsetup{justification=centering}
-  \includegraphics[width=1\linewidth]{figure_2_1.png}
+  \includegraphics[width=\linewidth]{figure_2_1.png}
   \caption{Plan view of molten salt breeder reactor (MSBR) core.}
@@
   \centering
-  \captionsetup{justification=centering}
-  \includegraphics[width=1\linewidth]{figure_2_2.png}
-  \caption{Elevation view of MSBR.}
+  \includegraphics[width=\linewidth]{figure_2_2.png}
+  \caption{Elevation view of molten salt breeder reactor (MSBR).}
   \label{fig:elevation}
@@
 \subsection{2.1. Zone I and II-A}
-The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements, as shown in Fig.2.2. The elements
+The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements.
+The fuel salt to graphite volume ratio of Zone 1 is 13.2\% which possible with a central hole diameter about $3.42cm$.
+Zone II having 37\% salt and central hole diameter about $6.604cm$.
+Both types of elements mostly have rectangular shape with a part of cylinder sticking out at each corner to form salt flow between tje griphite channels.
+Different sizes of elements neccesarily to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
+Figure~\ref{fig:zone12A} demonstrates the reconstructed graphite element utilized for Serpent model.
+
+\begin{figure}[h] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.95\linewidth]{figure_2_4.png}
+  \caption{Zone I (left) and Zone II-A (right) elements.}
+  \label{fig:zone12A}
+\end{figure}
 
 \subsection{2.2. Zone II-B}
-
-Equations look exceedingly pretty. Here is a 3-D, monoenergetic, steady-state
-transport equation with isotropic scattering and an isotropic extraneous source:
-\begin{subequations} \label{eqs:fullTransport}
-\begin{multline} \label{eq:fullTransportVol}
-  \vec{\Omega}\vd \grad \psi(\vec{x}, \vec{\Omega})
-  + \sigma(\vec{x}) \psi (\vec{x}, \vec{\Omega})
-\\ =
-  \frac{\sigma_s(\vec{x})}{4\pi} \int_{4\pi} \psi(\vec{x},\vec{\Omega}')
-  \ud\Omega' + \frac{q(\vec{x})}{4\pi}
-  \equiv \frac{1}{4\pi} Q(\vec{x}) \,,
-\end{multline}
-inside $\vec{x} \in V$, $\vec{\Omega} \in 4\pi$, with an incident boundary
-condition
-\begin{equation} \label{eq:fullTransportBndy}
-  \psi(\vec{x}, \vec{\Omega}) = \psi^b(\vec{x}, \vec{\Omega}) \,,
- \quad \vec{x} \in \partial V, \ \vec{\Omega} \vd \vec{n} < 0\,.
-\end{equation}
-\end{subequations}
+Second core zone is divided into two different zones: Zone II-A and Zone II-B.
+The graphite elements for zone II-A are prismatic and form first reflecting layer surrounding the core zone I.
+The elements for zone II-B made ip in the foru of rectangular slats spaced far enough apart to achieve 0.37 fuel salt volume fraction.
+Figure~\ref{fig:zone2B} shows Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
+The annulus contains 100\% fuel salt and serves to reduce the damage flux for internal surface of the graphite reflector blocks.
+From the ORNL report suggested model for Zone II-B has 8 graphite elements every $45^\circ$ with special shape and have holes for the flow of salt and were simplified into a uniformly sized chopped fan shape with the central hole.
+All other graphite $5.08cm$-thick slats and various length in width (average width is about $26.67cm$ are reconstructed as is in the model without any approximation.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and Analysis}
+\section{3. Results and Analysis}
 The results were interesting, so interesting in fact that we have decided to
 present them here.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=\linewidth]{figure_2_5.png}
+  \caption{Plan view of Zone II-B.}
+  \label{fig:zone2B}
+\end{figure}
 
@@
 an equation for the Marshak diffusion boundary condition:
-\begin{equation} \label{eq:marshak}
-  4 J^- = \phi + 2 D \vec{n} \vd \grad \phi \,.
-\end{equation}
-If we so choose, we can effortlessly reference the equation later.
-
-Another paragraph starts with Eq.~\eqref{eq:marshak} and sets $J^-$ to zero, a
-vacuum boundary condition:
-\begin{equation*}
-  0 = \phi + \frac{2}{3} \frac{1}{\sigma} \vec{n} \vd \grad \phi \,.
-\end{equation*}
-The extrapolation distance is $2/3$. A more detailed asymptotic analysis yields
-an extrapolation distance of about $0.71045$.
 

### 2017-06-14 full-core_msbr_model.tex
First draft of MSBR model summary added

@@
 \section{1. Introduction}
-The molten salt reactor (MSR) is advanced type of reactor which was  developed at Oak Ridge National Laboratory for a military aircraft nuclear propulsion project.
+The molten salt reactor (MSR) is an advanced type of reactor which was developed at Oak Ridge National Laboratory (ORNL) in the 1950s for a military aircraft nuclear propulsion project.
 In the MSR fluorides of fissile and/or fertile materials (i.e.
@@
 Thermal spectrum Molten Salt Breeder Reactor (MSBR) designed specifically to realize promising thorium fuel cycle which allows use natural thorium instead of enriched uranium as the fertile element to breed the fissile $^{233}U$ and avoid uranium enrichment.
-The mixtures of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ (72-16-12-0.232-0.0006 mole \%) has a melting point $499^\circ$C, good flow and heat transfer properties \cite{robertson_conceptual_1971}.
+The mixtures of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ has a melting point $499^\circ$C, good flow and heat transfer properties \cite{robertson_conceptual_1971}.
 
@@
 \section{2. MSBR design description}
-MSBR vessel has diameter 680 cm and high 610 cm and contains molten fluoride fuel-salt mixture which performs to functions: generate heat in the moderated region and transport heat energy from the core to primary heat exchanger using primary salt pump.
+MSBR vessel has diameter 680 cm and high 610 cm and contains molten fluoride fuel-salt mixture which performs to functions: generate heat in the moderated region and transport heat energy from the core to primary heat exchanger using the primary salt pump.
 The vessel also contains graphite blocks for neutron moderation and reflection.
@@
 This zone is formed of two kinds of elements: elements like those for Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
-At the outer of the core there are 70cm-thick graphite reflector and 5cm-thick vessel wall.
-Betweeen the core and the reflector blocks located 5.08cm-wide annulus which is 100\% salt needed to provide possibility removing and inserting a core graphite assembly.
+At the outer of the core there are 70cm-thick graphite reflector and the 5cm-thick vessel wall.
+Between the core and the reflector blocks located 5.08cm-wide annulus which is 100\% salt needed to provide possibility removing and inserting a core graphite assembly.
 
-Figure~\ref{fig:plan} shows plan view of the whole core configuration at the expected reactor operational level when all control rods are fully withdrawn from the core.
-Figure~\ref{fig:elevation} shows longitudinal section of the reactor.
+Figure~\ref{fig:plan} shows the plan view of the whole-core configuration at the expected reactor operational level when all control rods are fully withdrawn from the core.
+Figure~\ref{fig:elevation} shows the longitudinal section of the reactor.
 The violet color represents bare graphite, and the yellow represents fuel salt.
-The blue color shows Hastelloy-N, material used for the plenum and vessel wall, and the black color is a void space.
+The blue color shows Hastelloy-N, a material used for the plenum and vessel wall, and the black color is a void space.
 All figures of the core in this work generated using built-in Serpent plotter.
@@
 
-\subsection{2.1. Zone I and II-A}
+\subsection{2.1. Core zone I and II-A}
 The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements.
@@
 Zone II having 37\% salt and central hole diameter about $6.604cm$.
-Both types of elements mostly have rectangular shape with a part of cylinder sticking out at each corner to form salt flow between tje griphite channels.
-Different sizes of elements neccesarily to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
+Both types of elements mostly have a rectangular shape with a part of cylinder sticking out at each corner to form salt flow between the graphite channels.
+Different sizes of elements necessarily to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
 Figure~\ref{fig:zone12A} demonstrates the reconstructed graphite element utilized for Serpent model.
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{figure_2_4.png}
+  \includegraphics[width=0.96\linewidth]{figure_2_4.png}
   \caption{Zone I (left) and Zone II-A (right) elements.}
@@
 
-\subsection{2.2. Zone II-B}
+\subsection{2.2. Core zone II-B}
 Second core zone is divided into two different zones: Zone II-A and Zone II-B.
 The graphite elements for zone II-A are prismatic and form first reflecting layer surrounding the core zone I.
-The elements for zone II-B made ip in the foru of rectangular slats spaced far enough apart to achieve 0.37 fuel salt volume fraction.
+The elements for zone II-B made up in the form of rectangular slats spaced far enough apart to achieve 0.37 fuel salt volume fraction.
 Figure~\ref{fig:zone2B} shows Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{3. Results and Analysis}
-The results were interesting, so interesting in fact that we have decided to
-present them here.
+\subsection{2.3. Material composition}
+The fuel salt, the reactor graphite, and the modified Hastelloy N are exclusive MSBR materials which have been created at ORNL for a program which have been started over 15 years ago.
+The isotope composition of each material at the initial state was detailed described in the MSBR conceptual design study \cite{robertson_conceptual_1971} and have been applied to Serpent model without any modification.
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
   \centering
-  \includegraphics[width=\linewidth]{figure_2_5.png}
+  \includegraphics[width=0.93\linewidth]{figure_2_5.png}
   \caption{Plan view of Zone II-B.}
@@
 
+Initial fuel salt loading composition is $LiF-BeF_2-ThF_4-^{233}UF_4-^{239}PuF_3$ (72-16-12-0.232-0.0006 mole \%).
+The lithium is enriched to 99.995\% $^{7}Li$ because $^{6}Li$ is a very strong neutron poison and becomes tritium.
+In this study, 0.005\% atomic fraction of $^{6}Li$ have been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on effective multiplication factor.
+For cross section data generation ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
+%Specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when Serpent generate problem-oriented nuclear data library.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Subsection Goes Here}
-The user must manually capitalize initial letters of a subsection heading.
+\section{3. Results and Analysis}
+The reactor physics calculation was carried out using the methods described earlier.
+This section presenting calculation results, such as the effective multiplication factor for whole core, neutron flux spectrum, and temperature reactivity coefficients.
+The normalized neutron flux distribution is calculated for the whole core using continuous-energy nuclear data which allows to obtaining very smooth distribution.
+The temperature coefficients for both fuel salt solution and reactor graphite are computed by comparing effective multiplication factors for two temperatures in the working range.
 
-For those who like equations in their papers, \LaTeX\ is a good choice. Here is
-an equation for the Marshak diffusion boundary condition:
+The MSBR criticality simulations were performed on one Intel Xeon E3-1225 3.3GHz processor wich has four physical cores, each simulation takes 23 minutes or 92 minutes per one core.
+Similar whole-core MSBR simulation using MCNP6 required approximately 890 minutes per core \cite{park_whole_2015}, consequently, Serpent 2 can provide tremendous computer costs savings for heavy depletion computations.
 
-shows how a plot might conceivably look in your
-document. Always place figures after they are referenced so as not to throw
-off the reader. You can use symbols and different line styles to help
-differentiate your results, especially if they are printed in black and white.
-Note how Fig.~\ref{fig:voltage} uses dashed lines \verb|--| for the exact
-solution, solid lines \verb|-| for the new method's solutions, and dotted lines
-\verb|:| for existing inaccurate methods.
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\subsection{3.1. Neutron spectrum}
+Figure~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for the whole core in the energy range from $10^{-10}$ to $100 MeV$.
+The results shows close fit with the MCNP simulation \cite{park_whole_2015}, especially in thermal energy range.
+\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
   \centering
-  \includegraphics{example_figure}
-  \caption{Captions are flush with the left.}
-  \label{fig:voltage}
+  \includegraphics[width=\linewidth]{figure_3_1.png}
+  \caption{Neutron flux spectrum of MSBR for MCNP6 and Serpent2 model.}
+  \label{fig:spectrum}
 \end{figure}
+There is important to obtain epithermal or thermal spectrum to produce $^{233}U$ from $^{232}Th$ because radiative capture cross section of thorium monotonically decreasing from $10^{-10} MeV$ to $10^{-5} MeV$.
+Hardening the spectrim tends to significantly increasing resonance absorbtion in thorium and decreasing the absorptions in fissile and construction materials thus large amount of fissile material will be needed to make the reactor critical.
 
-Later on, we can include a table, even one that spans two columns such as
-Table~\ref{tab:widetable}.
+\subsection{3.2. Effective multiplication factor}
+Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 and Serpent2 whole core models.
+The coefficient obtained using Serpent2 is about 4.37\% higher than MCNP6 one.
+The discrepancy was ocurred most likely because Park and his colleagues didn't take into account $^{239}PuF_3$, contained in the fuel salt solution.
+Plutonium-239 has very high fission cross section in thermal energy range and produce more neutrons per fission than $^{233}U$, consequently, multiplication factor for this case is higher.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}[htb]
-  \centering
-\begin{tabular}{llllllllll}\toprule
-      & $\phi_T(0)$      & $\phi_T(10)$      & $\phi_T(20)$      &
-      $\phi_D(0)$      & $\phi_D(10)$      & $\phi_D(20)$      & $\rho$      &
-      $\varepsilon$      & $N_\text{it}$
+\captionsetup[table]{
+  labelsep = newline,
+  name = TABLE, 
+  justification=justified,
+  singlelinecheck=false,%%%%%%% a single line is centered by default
+  labelsep=colon,%%%%%%
+  skip = \medskipamount}
+\begin{table}[h!]
+%\centering
+\begin{tabular}{p{0.15\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
+      & Serpent2      & MCNP6 \cite{park_whole_2015}          
 \\ \midrule
-$c=0.999$  & 0.9038 & 20.63 & 31.24 & 0.9087 & 20.63 & 31.23 & 0.2192 & $10^{-7}$ & 15
-\\
-$c=0.990$  & 0.3675 & 13.04 & 24.7 & 0.3696 & 13.04 & 24.69 & 0.2184 & $10^{-7}$ & 15
-\\
-$c=0.900$  & 0.009909 & 4.776 & 17.64 & 0.009984 & 4.786 & 17.63 & 0.2118 & $10^{-7}$ & 14
-\\
-$c=0.500$  & $6.069\times 10^{-5}$ & 2.212 & 15.53 & 6.213$\times 10^{-5}$ & 2.239 & 15.53 & 0.2068 & $10^{-7}$ & 13
+$K_{eff}$  & $1.05134\pm0.00116$ & $1.00736$
 \\
@@
 \end{tabular}
-  \caption{This is an example of a really wide table which might not normally
-  fit in the document.}
-  \label{tab:widetable}
-\end{table*}
+  \caption{Effective multiplication factor of whole core model.}
+  \label{tab:keff}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{3.3. Temperature effect of reactivity}
+Table~\ref{tab:tcoef} represents the quantitive analysis of temperature effects on reactivity.
+Uncertainty for each temperature coefficient also was calculated and shown in Table~\ref{tab:tcoef}.
+Main physical principle underlies the reactor temperature feedback is expanding of a matter when it is heated.
+When fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is defined by the space for fuel in the graphite.
+When the reactor graphite temperature growing, the density of graphite declines which also free up space for fuel salt.
+To determine temperature coefficients three cases were considered:
+\begin{enumerate}  
+\item Temperature of fuel salt growing from 900K to 1200K.
+\item Temperature of graphite increasing from 900K to 1200K. 
+\item Whole reactor temperature rising from 900K to 1200K.
+\end{enumerate}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Notice how the table reference uses a Roman numeral
-for its numbering scheme, whereas the figure reference uses an Arabic numeral.
-For one-column tables, use the \verb|table| environment; two-column tables use
-\verb|table*|. The same applies to figures.
+\captionsetup[table]{
+  labelsep = newline,
+  name = TABLE, 
+  justification=justified,
+  singlelinecheck=false,%%%%%%% a single line is centered by default
+  labelsep=colon,%%%%%%
+  skip = \medskipamount}
+\begin{table}[h!]
+%\centering
+\begin{tabular}{p{0.22\linewidth} p{0.22\linewidth} p{0.21\linewidth} p{0.15\linewidth}} \toprule
+   Reactivity coefficient [pcm/K]  & Serpent2      & MCNP6 \cite{park_whole_2015}   & Reference \cite{robertson_conceptual_1971}      
+\\ \midrule
+Fuel salt        & $-3.93\pm0.005$ & $-3.20\pm0.05$ & $-3.22$ 
+\\ \midrule
+Moderator        & $+2.44\pm0.013$ & $-0.11\pm0.05$ & $+2.35$ 
+\\ \midrule
+Total            & $-1.74\pm0.030$ & $-3.21\pm0.04$ & $-0.87$ 
+\\
+\bottomrule
+\end{tabular}
+  \caption{Temperature coefficient of reactivity.}
+  \label{tab:tcoef}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+On the one hand, changes in fuel temperature cause only density variation, geometry keeps the same because fuel is in the form of liquid.
+On the other hand, when moderator heats up both the density and the geometry changes due to thermal expansion of the graphite blocks and the reflector.
+New graphite density was calculated using linear temperature expansion coefficient of reactor graphite which is $1.3\times10^{-6}1/K$ \cite{robertson_conceptual_1971}.
+Based on this information new geometry input, which takes into account graphite expansion, was created.
 
+The fuel temperature coefficient (FTC) is positive due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with early research \cite{robertson_conceptual_1971,park_whole_2015}.
+The moderator temperature coefficient is negative due to changing density, and would increasing when reactor operating because of spectrum hardening along the fuel depletion \cite{park_whole_2015}.
+Finally, the total temperature coefficient of reactivity is relatively large negative, despite graphite component, and affords adequate reactor stability and controllability.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Another Subsection}
-Excessive sectioning in a three-page document is discouraged, but here are more
-subsections to demonstrate compliance with the ANS formatting guidelines.
+\section{4. Conclusions}
+The MSBR full-core analysis was performed using Monte Carlo code Serpent2.
+The complex geometry of the reactor is reconstructed in three-dimensional space without any major approximations.
+Accurate material data was employed to calculate reactor key design parameters.
+Effective multiplication factor for initial fuel composition is slightly higher than 1 (1.05) which allows reactor operates from startup to first online reprocessing cycle.
+The neutron flux energy spectrum was calculated for the whole core and represents the epithermal spectrum of the MSBR.
+The total temperature coefficient is negative, consequently, the MSBR has negative temperature feedback, but MTC is negative which is do not affect on safety because most of the energy releasing in the fuel salt.
 
-\subsubsection{Third-level Heading}
-This subsubsection shows compliance with the ANS-specified standard. This level
-of heading should be used rarely.
-
-\subsubsection{Another Such Heading}
-And, if you really think you need a third-level heading, you should make sure
-that your subsection needs at least two of them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-The included ANS style file and this clear example file are a panacea for
-the hours of headache that invariably results from formatting a document in
-Microsoft Word.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Appendix}
-
-Numbering in the appendix is different:
-\begin{equation} \label{eq:appendix}
-  2 + 2 = 5\,.
-\end{equation}
-and another equation:
-\begin{equation} \label{eq:appendix2}
-  a + b = c\,.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgments}
-This material is based upon work supported a Department of Energy Nuclear
-Energy University Programs Graduate Fellowship.
+The high-fidelity full-core model will be employed for a number of future works.
+First of all, depletion simulation will be performed using built-in Serpent 2 to find equilibrium state of the MSBR, optimal fuel salt composition, reprocessing characteristics (i.e.
+rates of removing fission products, the rate of adding thorium) and fuel utilization.
+Secondly, the model needed to generating problem-oriented nuclear data libraries for multi-physics models of MSRs developed in MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
+Finally, transient accident simulations for safety investigation of the reactor core will be performed to studying the dynamic behavior of Molten Salt Breeder Reactor.
 

### 2017-06-19 full-core_msbr_model.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Full-core analysis of thorium-fueled molten salt breeder reactor using the SERPENT-2 Monte Carlo code}
+\title{Full-core analysis of thorium-fueled molten salt breeder reactor using the SERPENT 2 Monte Carlo code}
 
-\author{Andrei Rykhlevskii, Kathryn Huff, Alexander Lindsay}
+\author{Andrei Rykhlevskii, Alexander Lindsay, Kathryn Huff}
 
@@
 \usepackage{microtype} % improves typography for PDF
+\usepackage[section]{placeins}
 \graphicspath{{figures/}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{1. Introduction}
-The molten salt reactor (MSR) is an advanced type of reactor which was developed at Oak Ridge National Laboratory (ORNL) in the 1950s for a military aircraft nuclear propulsion project.
-In the MSR fluorides of fissile and/or fertile materials (i.e.
-$UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form a liquid fuel which circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
-This conception leads to immediate advantages over traditional reactors with a solid fuel, such as near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
+\section{Introduction}
+The molten salt reactor (MSR) is an advanced type of reactor which was developed at Oak Ridge National Laboratory (ORNL) in the 1950s and was operated in the 1960s.
+In the MSR, fluorides of fissile and/or fertile materials (i.e.
+$UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
+This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
+These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
 
-Thermal spectrum Molten Salt Breeder Reactor (MSBR) designed specifically to realize promising thorium fuel cycle which allows use natural thorium instead of enriched uranium as the fertile element to breed the fissile $^{233}U$ and avoid uranium enrichment.
-The mixtures of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ has a melting point $499^\circ$C, good flow and heat transfer properties \cite{robertson_conceptual_1971}.
+The thermal spectrum Molten Salt Breeder Reactor (MSBR) was designed specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
+Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment.
+The mixture of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
+The MSBR geometry is difficult to describe in computer code input and usually require major approximations to proceed \cite{park_whole_2015}.
 
-For the development of MSBR research, this paper demonstrates advanced whole-core three-dimensional model developed using a continuous-energy Monte Carlo reactor physics calculation code Serpent 2 and cross-verification with existing MCNP6 results \cite{park_whole_2015,leppanen_serpent_2012}.
-The neutronics model could be useful for optimization fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation, and for depletion calculations using built-in Serpent burnup module.
-Moreover, this model in the future will be employed to generate problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017} as well as for routine applications.
+For the development of MSBR research, this paper demonstrates an advanced whole-core three-dimensional model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code and cross-verification with existing MCNP6 results \cite{park_whole_2015,leppanen_serpent_2012}.
+This neutronics model is of sufficient fidelity to inform optimization of fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation, and for depletion calculations using built-in Serpent burnup module.
+Moreover, this model in the future will be employed to generate problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}, and for routine applications.
 
-All the calculations presented in this paper were performed using the Serpent 2 code version 2.1.28.
-Comparing with Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
-Before burnup calculations can be undertaken MSBR model should be validated.
-In Section 2 a brief description of the MSBR geometry model is given.
+All calculations presented in this paper were performed using the Serpent 2 code version 2.1.28.
+Compared with Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
+Before burnup calculations could be undertaken, MSBR model was verified.
+In Section 2, a brief description of the MSBR geometry model is given.
 In Section 3 the results are presented and discussed.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{2. MSBR design description}
-MSBR vessel has diameter 680 cm and high 610 cm and contains molten fluoride fuel-salt mixture which performs to functions: generate heat in the moderated region and transport heat energy from the core to primary heat exchanger using the primary salt pump.
+\section{MSBR design description}
+The MSBR vessel has diameter of 680 cm and a height of 610 cm.
+It contains molten fluoride fuel-salt mixture which performs two functions: to generate heat in the moderated region and to transport heat energy from the core to primary heat exchanger using the primary salt pump.
 The vessel also contains graphite blocks for neutron moderation and reflection.
-The reactor core has a central zone, Zone I, in which 13\% of the volume is fuel salt and 87\% - graphite.
-The first zone is composed of 1320 graphite cells, 2 graphite control rods and 2 safety rods consisting of boron carbide clad.
-
-The undermoderated zone, Zone II, with 37\% fuel salt, or radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
-This zone is formed of two kinds of elements: elements like those for Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
-At the outer of the core there are 70cm-thick graphite reflector and the 5cm-thick vessel wall.
-Between the core and the reflector blocks located 5.08cm-wide annulus which is 100\% salt needed to provide possibility removing and inserting a core graphite assembly.
+The reactor core has a central zone, Zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
+The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 2 safety rods consisting of boron carbide clad.
+The undermoderated zone, Zone II, with 37\% fuel salt, and radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
+This zone is formed of two kinds of elements: elements like those in Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
+At the outer of the core there are graphite reflector and vessel wall.
+Between the core and the reflector blocks located annulus which is 100\% salt needed to provide possibility removing and inserting a graphite assembly.
 
@@
 All figures of the core in this work generated using built-in Serpent plotter.
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[!htb] % replace 't' with 'b' to force it to be on the bottom
   \centering
-  \includegraphics[width=\linewidth]{figure_2_1.png}
-  \caption{Plan view of molten salt breeder reactor (MSBR) core.}
+  \vspace{-0.6em}
+  \includegraphics[width=0.93\linewidth]{figure_2_1.png}
+  \caption{Plan view of MSBR core.}
   \label{fig:plan}
@@
   \includegraphics[width=\linewidth]{figure_2_2.png}
-  \caption{Elevation view of molten salt breeder reactor (MSBR).}
+  \caption{Elevation view of MSBR core.}
   \label{fig:elevation}
@@
 
-\subsection{2.1. Core zone I and II-A}
+\subsection{Core Zone I and II-A}
 The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements.
-The fuel salt to graphite volume ratio of Zone 1 is 13.2\% which possible with a central hole diameter about $3.42cm$.
-Zone II having 37\% salt and central hole diameter about $6.604cm$.
+The fuel salt to graphite volume ratio of Zone I is 13.2\%, and the central hole has a diameter of $3.42cm$.
+Zone II has 37\% salt and central hole diameter of $6.604cm$.
 Both types of elements mostly have a rectangular shape with a part of cylinder sticking out at each corner to form salt flow between the graphite channels.
-Different sizes of elements necessarily to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
-Figure~\ref{fig:zone12A} demonstrates the reconstructed graphite element utilized for Serpent model.
+Different sizes of elements are necessary to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
+Figure~\ref{fig:zone12A} demonstrates the reconstructed graphite element utilized for this Monte Carlo model.
 
@@
 
-\subsection{2.2. Core zone II-B}
-Second core zone is divided into two different zones: Zone II-A and Zone II-B.
-The graphite elements for zone II-A are prismatic and form first reflecting layer surrounding the core zone I.
+\subsection{Core Zone II-B}
+The second core zone is divided into two different zones: Zone II-A and Zone II-B.
+The graphite elements for Zone II-A are prismatic and form the first reflecting layer surrounding the core zone I.
 The elements for zone II-B made up in the form of rectangular slats spaced far enough apart to achieve 0.37 fuel salt volume fraction.
-Figure~\ref{fig:zone2B} shows Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
-The annulus contains 100\% fuel salt and serves to reduce the damage flux for internal surface of the graphite reflector blocks.
-From the ORNL report suggested model for Zone II-B has 8 graphite elements every $45^\circ$ with special shape and have holes for the flow of salt and were simplified into a uniformly sized chopped fan shape with the central hole.
-All other graphite $5.08cm$-thick slats and various length in width (average width is about $26.67cm$ are reconstructed as is in the model without any approximation.
+Figure~\ref{fig:zone2B} shows the outer Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
+The annulus contains 100\% fuel salt and serves to reduce the damage flux at the internal surface of the graphite reflector blocks.
+The reactor Zone II-B graphite $5.08cm$-thick slats and various length in width (average width is about $26.67cm$) are reconstructed as is in the model without any approximation.
+From the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 graphite elements every $45^\circ$ with irregular shape as well as holes for the flow of salt and were simplified into a right circular hollow cylinder sector shape with the central hole.
+This is only simplification for this Monte Carlo model.
 
-\subsection{2.3. Material composition}
-The fuel salt, the reactor graphite, and the modified Hastelloy N are exclusive MSBR materials which have been created at ORNL for a program which have been started over 15 years ago.
-The isotope composition of each material at the initial state was detailed described in the MSBR conceptual design study \cite{robertson_conceptual_1971} and have been applied to Serpent model without any modification.
+\subsection{Material composition}
+The fuel salt, the reactor graphite, and the modified Hastelloy N are exclusive MSBR materials which were created at ORNL.
+The isotope composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to Serpent model without any modification.
 
@@
 
-Initial fuel salt loading composition is $LiF-BeF_2-ThF_4-^{233}UF_4-^{239}PuF_3$ (72-16-12-0.232-0.0006 mole \%).
-The lithium is enriched to 99.995\% $^{7}Li$ because $^{6}Li$ is a very strong neutron poison and becomes tritium.
-In this study, 0.005\% atomic fraction of $^{6}Li$ have been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on effective multiplication factor.
+The initial fuel salt loading composition is $LiF-BeF_2-ThF_4-^{233}UF_4-^{239}PuF_3$ (72-16-12-0.232-0.0006 mole \%).
+The lithium is enriched to 99.995\% $^{7}Li$ because $^{6}Li$ is a very strong neutron poison and becomes tritium upon neutron bombardment.
+In this study, the 0.005\% atomic fraction of $^{6}Li$ has been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on effective multiplication factor.
 For cross section data generation ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{3. Results and Analysis}
+\section{Results and Analysis}
 The reactor physics calculation was carried out using the methods described earlier.
-This section presenting calculation results, such as the effective multiplication factor for whole core, neutron flux spectrum, and temperature reactivity coefficients.
+This section presents calculation results, such as the effective multiplication factor for whole core, neutron flux spectrum, and temperature reactivity coefficients.
 The normalized neutron flux distribution is calculated for the whole core using continuous-energy nuclear data which allows to obtaining very smooth distribution.
@@
 
-The MSBR criticality simulations were performed on one Intel Xeon E3-1225 3.3GHz processor wich has four physical cores, each simulation takes 23 minutes or 92 minutes per one core.
-Similar whole-core MSBR simulation using MCNP6 required approximately 890 minutes per core \cite{park_whole_2015}, consequently, Serpent 2 can provide tremendous computer costs savings for heavy depletion computations.
+The MSBR criticality simulations were performed on one Intel Xeon E3-1225 3.3GHz processor wich has four physical cores.
+Each simulation took 23 minutes or 92 minutes per one core.
+A similar whole-core MSBR simulation using MCNP6 required approximately 890 minutes per core \cite{park_whole_2015}, consequently, Serpent 2 can provide tremendous computer costs savings for compute-heavy depletion calculations.
 
-\subsection{3.1. Neutron spectrum}
+\subsection{Neutron spectrum}
 Figure~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for the whole core in the energy range from $10^{-10}$ to $100 MeV$.
-The results shows close fit with the MCNP simulation \cite{park_whole_2015}, especially in thermal energy range.
+The results show close fit with the MCNP simulation \cite{park_whole_2015}, especially in thermal energy range.
 \begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
@@
   \includegraphics[width=\linewidth]{figure_3_1.png} 
-  \caption{Neutron flux spectrum of MSBR for MCNP6 and Serpent2 model.}
+  \caption{Neutron flux spectrum of MSBR for MCNP6 and Serpent 2 model.}
   \label{fig:spectrum}
 \end{figure}
-There is important to obtain epithermal or thermal spectrum to produce $^{233}U$ from $^{232}Th$ because radiative capture cross section of thorium monotonically decreasing from $10^{-10} MeV$ to $10^{-5} MeV$.
+It is important to obtain the epithermal and thermal spectrum to produce $^{233}U$ from $^{232}Th$ because radiative capture cross section of thorium monotonically decreasing from $10^{-10} MeV$ to $10^{-5} MeV$.
 Hardening the spectrim tends to significantly increasing resonance absorbtion in thorium and decreasing the absorptions in fissile and construction materials thus large amount of fissile material will be needed to make the reactor critical.
 
-\subsection{3.2. Effective multiplication factor}
-Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 and Serpent2 whole core models.
-The coefficient obtained using Serpent2 is about 4.37\% higher than MCNP6 one.
-The discrepancy was ocurred most likely because Park and his colleagues didn't take into account $^{239}PuF_3$, contained in the fuel salt solution.
+\subsection{Effective multiplication factor}
+Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 and Serpent 2 whole core models.
+The coefficient obtained using Serpent 2 is about 4.37\% higher than MCNP6 one.
+The discrepancy was ocurred most likely because the model used in Park et al.
+didn't take into account $^{239}PuF_3$, contained in the fuel salt solution.
 Plutonium-239 has very high fission cross section in thermal energy range and produce more neutrons per fission than $^{233}U$, consequently, multiplication factor for this case is higher.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{3.3. Temperature effect of reactivity}
+\subsection{Temperature effect of reactivity}
 Table~\ref{tab:tcoef} represents the quantitive analysis of temperature effects on reactivity.
 Uncertainty for each temperature coefficient also was calculated and shown in Table~\ref{tab:tcoef}.
-Main physical principle underlies the reactor temperature feedback is expanding of a matter when it is heated.
-When fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is defined by the space for fuel in the graphite.
-When the reactor graphite temperature growing, the density of graphite declines which also free up space for fuel salt.
-To determine temperature coefficients three cases were considered:
+The main physical principle underlying the reactor temperature feedback is expandsion of matter when it is heated.
+When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is defined by the space for fuel bounded by the graphite.
+When the reactor graphite temperature grows, the density of graphite declines which also frees up space for fuel salt.
+To determine temperature coefficients, three cases were considered:
 \begin{enumerate}  
-\item Temperature of fuel salt growing from 900K to 1200K.
-\item Temperature of graphite increasing from 900K to 1200K. 
+\item Temperature of fuel salt rising from 900K to 1200K.
+\item Temperature of graphite rising from 900K to 1200K. 
 \item Whole reactor temperature rising from 900K to 1200K.
@@
 \end{tabular}
-  \caption{Temperature coefficient of reactivity.}
+  \caption{Temperature coefficients of reactivity.}
   \label{tab:tcoef}
@@
 The fuel temperature coefficient (FTC) is positive due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with early research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient is negative due to changing density, and would increasing when reactor operating because of spectrum hardening along the fuel depletion \cite{park_whole_2015}.
-Finally, the total temperature coefficient of reactivity is relatively large negative, despite graphite component, and affords adequate reactor stability and controllability.
+The moderator temperature coefficient is negative due to changing density, and would increases during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
+Finally, the total temperature coefficient of reactivity is relatively large and negative, despite graphite components, and affords excellent reactor stability and controllability.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{4. Conclusions}
-The MSBR full-core analysis was performed using Monte Carlo code Serpent2.
+\section{Conclusions}
+The MSBR full-core analysis was performed using the Serpent 2 Monte Carlo code.
 The complex geometry of the reactor is reconstructed in three-dimensional space without any major approximations.
 Accurate material data was employed to calculate reactor key design parameters.
-Effective multiplication factor for initial fuel composition is slightly higher than 1 (1.05) which allows reactor operates from startup to first online reprocessing cycle.
+The effective multiplication factor for initial fuel composition is slightly higher than 1 (1.05) which allows reactor operation from startup to first online reprocessing cycle.
 The neutron flux energy spectrum was calculated for the whole core and represents the epithermal spectrum of the MSBR.
-The total temperature coefficient is negative, consequently, the MSBR has negative temperature feedback, but MTC is negative which is do not affect on safety because most of the energy releasing in the fuel salt.
+The total temperature coefficient is negative, consequently, the MSBR has negative temperature feedback, but MTC is negative which has a negligible effect on safety because it is outweighed by the strong, negative FTC.
 
-The high-fidelity full-core model will be employed for a number of future works.
-First of all, depletion simulation will be performed using built-in Serpent 2 to find equilibrium state of the MSBR, optimal fuel salt composition, reprocessing characteristics (i.e.
-rates of removing fission products, the rate of adding thorium) and fuel utilization.
-Secondly, the model needed to generating problem-oriented nuclear data libraries for multi-physics models of MSRs developed in MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
-Finally, transient accident simulations for safety investigation of the reactor core will be performed to studying the dynamic behavior of Molten Salt Breeder Reactor.
+This high-fidelity full-core model will be employed for a number of future efforts.
+First, depletion simulation will be performed using built-in Serpent 2 depletion capabilities to find the equilibrium state of the MSBR, its optimal fuel salt composition, reprocessing characteristics (i.e.
+rates of removing fission products, the rate of adding thorium), and fuel utilization.
+Secondly, the model will be used to generate problem-oriented nuclear data libraries for multi-physics models of MSRs developed in the MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
+Finally, transient accident simulations for safety investigation of the reactor core will be performed to study the dynamic behavior of Molten Salt Breeder Reactor.
 

### 2017-06-24 introduction.tex
removed unnecessary call to tex files

\section{Abstract}
The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
\cite{cne2_noauthor_2015} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{SNF}from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{SNF} mass
and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
the transition into \glspl{SFR}. The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{SNF} from other EU nations.

\section{Introduction}
This paper uses \Cyclus, the agent-based simulator \cite{huff_fundamental_2016} to analyze
the future nuclear inventory in the European Union. This paper focuses on the spent fuel
inventory in \gls{EU} member states in 2050, and analyzes various potential strategies of spent fuel
management.
A major focus of this paper is to determine the extent to which France has an incentive
to receive all the \gls{SNF} from \gls{EU} nations to create \gls{MOX}.
The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
and may allow France to avoid building additional \glspl{LWR}.

Past research, which focuses mostly on France, has made the assumptions that additional \glspl{LWR},
namely \glspl{EPR} are constructed in order to supply \gls{SNF} required
for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2007, freynet_multiobjective_2016}.
There has been little attention in reprocessing legacy \gls{SNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

A \Cyclus simulation is run to calculate
how much spent fuel is created from \gls{EU} nations from 1970 to 2050, as well as the amount
of \gls{MOX} that can be created with the \gls{SNF} inventory.
The paper assumes a once-through cycle for all 
\gls{EU} nations with the exception of France. France can reprocess spent \gls{UOX} and \gls{MOX} to
produce \gls{MOX} from reprocessed plutonium and depleted uranium (tails).
The simulation assumes \gls{MOX} is reprocessed infinitely. 
After obtaining the \gls{SNF} inventory of all \gls{EU} in 2050, a separate
simulation is run where the \gls{SNF} inventory is reprocessed and
used as fuel for the newly deployed \gls{SFR} reactors.
\gls{SFR} reactors in this paper models after the ASTRID reactor,
and use \gls{MOX} fuel created from 9\% reprocessed plutonium
and 91\% tailings to a burnup
of approximately 100 GWdth/t. The high burnup allows enough production of plutonium
for an equivalent mass of \gls{MOX}, if mixed with tailings.  Eventually,
the used \gls{UOX} inventory will be exhausted, and the \glspl{SFR} must be
fueled by \gls{MOX} created from recycled \gls{MOX}.
It is assumed that \glspl{SFR} are available for deployment
from 2040.

\section{Methodology}
The work relies on \Cyclus, an agent-based simulator, to simulate the nuclear fuel cycle
and track material flows in \gls{EU} nations. The \gls{PRIS} open-source 
database from \gls{IAEA} was used to populate the simulation with deployment 
information. That database is imported as a csv file, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
the output file is analyzed by another python script.

First, a simulation is run from 1970 to 2050 to calculate the mass of 
\gls{SNF} and depleted uranium (tails) \gls{EU} accumulates before 2050. 
The second simulation only looks at France, where France
uses the entire \gls{SNF} inventory from the previous
simulation to fuel
the newly deployed \glspl{SFR}. French \gls{SFR}s are deployed
to make up for the decommissioned capacity of \gls{LWR}s, to
remain a constant installed capacity of 60,000 MWe.

\subsection{Assumptions}
This paper makes the following assumptions:
\begin{itemize}
        \item \gls{SFR} technology available in 2040
        \item Decay has no effect on reprocessing viability
        \item Reactor construction is always completed on time 
        \item Unused separated uranium is stockpiled
        \item Nuclear power plants have a lifetime of 60 years, unless stated otherwise (early shutdown)
        \item (Only for SFR Case) French nuclear capacity remains constant at 60,000 MWe
        \item (Only for SFR Case) Infinite reprocessing and fabrication capacity
\end{itemize}

\subsection{Deployment Timeline}
Projections of future reactor deployment in this simulation were
assessed based on analysis from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
and the World Nuclear Association and two other papers for future plans in EU nations
\cite{world_nuclear_association_nuclear_2017, joskow_future_2012, hatch_politics_2015}.
The projections extend to 2050 at the latest. This allows the simulation to take place from
1970 to 2050, the latest foreseeable future. The specific plans for each \gls{EU} nation are explained
in detail in later sections.

It is also assumed that all reactors that are 
currently operating have a lifetime of 60 years, unless their government plans
early shutdown. This will approximate when and how much \glspl{SFR} need to be built
to make up for the shutdown of \glspl{LWR}.

\subsection{French \gls{SFR} Deployment Schedule}

From 2040, when \gls{SFR}s become available,
600-MWe \gls{SFR}s are deployed to make up for the 
decommissioned \gls{LWR} capacities.

Initially in 2040, 22 \gls{SFR}s
are deployed for the previously decommissioned
\gls{LWR}s. From then, \glspl{SFR} are deployed to
make up for the decommissioned \gls{LWR} capacity.
This results in an installed capacity of 60,000 MWe
of \gls{SFR} by 2076.

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[scale=0.7]{./images/french-transition/power_plot.png}
        \end{center}
        \caption{Timeseries of installed capacity of \gls{SFR}s}
        \label{fig:sfr_cap}
\end{figure}
\FloatBarrier

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[scale=0.7]{./images/french-transition/number_plot.png}
        \end{center}
        \caption{Timeseries of number of \gls{SFR}s}
        \label{fig:sfr_num}
\end{figure}
\FloatBarrier

\Cref{fig:sfr_cap} and \cref{fig:sfr_num} display
the \gls{SFR} number and capacity over time.
The sharp increase from 2035 to 2060 is due mainly to
French aggressive growth from 1975 to 2000.

\subsection{Depletion Calculations}
Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
and spent fuel recipe is used for each reactor type. To capture varying reactor 
capacity, a linear burnup model was assumed and extrapolated from the 
appropriate recipe. For example, a PWR of
1,000 MWe capacity has 193 assemblies of 3.2\% enriched
uranium fuel, with each assembly with a mass of 523.4 kg.
The core has a 18 month cycle, where one-third of the 
core (64 assemblies) are discharged per refueling. The refueling
is assumed to take 2 months to complete, during which the reactor
is shut down. For the \gls{SFR}, a model design is adopted from
Marsault–Marie-Sophie et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}.

For the compositions of the fuel, a reference depletion calculation
from ORIGEN is used (see appendix). The recipe has also been used for
\cite{wilson_adoption_2009}.

\subsection{Scenario Descriptions}
The simulation follows the model fuel cycle, where a `source'
provides natural uranium, which is enriched by an 'enrichment'
facility to \gls{UOX}, while disposing enrichment waste (tailings)
to the 'sink' facility. The enriched \gls{UOX} is used
in the \gls{LWR}s and \gls{UOX} waste is produced. The spent fuel
is then reprocessed to separate plutonium and uranium.
The plutonium is mixed with depleted uranium (tails) to \gls{MOX}.
The reprocessed uranium is stockpiled. \gls{SNF} decay is assumed
to have no effect on reprocessing viability.

The second scenario estimates the \gls{SNF} inventory in \gls{EU} at 2050,
and reprocesses the \gls{SNF} to separate plutonium. The separated
plutonium is mixed with the depleted uranium inventory from 2050
to create \gls{MOX}, which is used in the \gls{SFR}s. The used
\gls{MOX} is also reprocessed to extract plutonium, which also
is mixed with depleted uranium to produce \gls{MOX}.

\subsection{Reprocessed Uranium}
Reprocessed uranium contains a range of uranium isotopes, from $^{232}U$ to $^{238}U$.
This brings complications in reusing reprocessed uranium as a fuel source \cite{IAEA_management_2007}.
The presence of neutron-absorbing isotopes $^{234}U$ and $^{236}U$ requires reprocessed uranium
to require a higher enrichment of $^{235}U$. There is trace amounts (2 ppb) of fissile istope $^{233}U$,
which provides little benefit.  
Also, $^{232}U$ has a decay chain of short-lived
daughter products that undergo intense beta and gamma radiation.
The French nuclear program utilizes a fraction (1/3) of reprocessed uranium as fuel \cite{IAEA_management_2007}.
However for this simulation the reprocessed uranium is simply stockpiled.

### 2017-06-24 results.tex
resized figures

\section{Results}

\subsection{Historical Operation of \gls{EU} Reactors}

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category [unit] & Value & Specifics \\ \hline
			Total UOX Usage [t] & 188,196  &  \\ \hline
			Total MOX Usage [t] & 118 & \\ \hline
			Total Spent UOX [t] & 183,807 & \\ \hline
			Total Spent MOX [t] & 0 & All is Reprocessed. \\ \hline
			Total Tailings [t] & 1,125,798 & \\ \hline
		\end{tabular}}
		\caption{Simulation Results}
		\label{tab:sim_result}
		\end {table}

\Cref{tab:sim_result} lists the important metrics
obtained from the first simulation. The following
values are the \gls{EU} inventory and history at year 2050.

Tables \ref{tab:eu_num} and \ref{tab:eu_pow} display the
timeseries of number of reactors and installed capacity in \gls{EU}.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/number_plot.png}
	\end{center}
	\caption{Timeseries of number of reactors in \gls{EU}.}
	\label{fig:eu_num}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
	\end{center}
	\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
	\label{fig:eu_pow}
\end{figure}

Figures \ref{fig:eu_tail} and \ref{fig:snf} show the 
timeseries of mass of tailings and spent fuel accumulation in \gls{EU}.

Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

Note that the MOX usage is so little that it is invisible in the
plot.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/tailings.png}
	\end{center}
	\caption{Timeseries of Tailings in the \gls{EU}.}
	\label{fig:eu_tail}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/total_fuel.png}
	\end{center}
	\caption{Timeseries of total fuel usage in \gls{EU}.}
	\label{fig:eu_fuel}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
			\includegraphics[width=\columnwidth]{./images/eu_future/snf.png}
	\end{center}
	\caption{Timeseries of Spent Nuclear Fuel in Sink.}
	\label{fig:eu_snf}
\end{figure}

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Isotope & Mass Fraction in Spent Fuel [\%] & Quantity [t] \\ \hline
		Total & .9358 & 1,720 \\ \hline
		Pu238 & .0111 & 20.40 \\ \hline
		Pu239 & .518 & 952.12 \\ \hline
		Pu240 & .232 & 426.43 \\ \hline
		Pu241 & .126 & 231.59 \\ \hline
		Pu242 & .0487 & 89.51 \\ \hline
	\end{tabular}
	\caption{Plutonium From Spent Fuel}
	\label{tab:pu}
\end{table}

To create \gls{MOX}, 10\% Pu and 90\% depleted uranium is used.
Thus $1,720$ tons of plutonium yields $17,200$ tons of
\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
and quantity of plutonium that can be obtained from the 2050 \gls{SNF} inventory.

\subsection{French \gls{SFR} Transition Scenario}

From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
ASTRID-type \gls{SFR} of capacity $600 MWe$ needs $1.225$ tons of
plutonium a year, with an initial plutonium loading of $4.9$ tons.
Thus, it can be assumed that the ASTRID reactor takes in $49$ tons of 
\gls{MOX}, and refuels a quarter of its fuel every year. Simply,
an ASTRID reactor needs $12.25$ tons of \gls{MOX} per year.

The number of SFR-years worth of fuel that can be created with
the \gls{SNF} from 2050 is $\frac{17,611.3 t}{12.25} = 1,437.65 $,
assuming infinite reprocessing and \gls{MOX} fabrication capacity.

However, assuming that \gls{MOX} can be recycled indefinitely,
spent \gls{MOX} from an ASTRID reactor
contains enough plutonium to produce a \gls{MOX} fuel with
the same mass, if mixed with depleted uranium. For example,
spent \gls{MOX} from an ASTRID reactor is 38\% plutonium,
whereas a fresh \gls{MOX} is 10\% plutonium.
The compositions are in \cref{tab:comp}.
Separating plutonium from spent \gls{MOX} from
an ASTRID reactor can create \gls{MOX} more than
three times the mass of spent \gls{MOX}.

The second scenario, with the tails and spent \gls{UOX}
inventory, evaluates if the French can transition into \gls{SFR}
without constructing additional \gls{LWR}s. This simulation
assumed infinite reprocessing and fabrication capacity.

\Cref{fig:fuel} shows the mass of \gls{MOX} used in the 
\gls{SFR}s separated by how they are made, over time.
Note that the mass of \gls{MOX} from the spent \gls{UOX}
stops increasing around 2050, which means that the spent
\gls{MOX} is enough to create the \gls{MOX} for the
\gls{SFR} fleet.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/where_fuel.png}
	\end{center}
	\caption{Timeseries of fuel used in the \gls{SFR}s [tons]}
	\label{fig:fuel}
\end{figure}

\Cref{fig:mox_fab} shows the progression of mox created from
the fabrication plant over time. \Cref{fig:mox_fab} shows
the separated plutonium demand from spent \gls{MOX} to fuel the 
ASTRID reactors.

\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
(any content from spent fuel other than U, Pu) over time. Note that 
the amount of reprocessing waste is much greater when reprocessing
spent \gls{MOX} from ASTRID reactors, since there is little uranium
or plutonium left due to a high burnup.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/mox_from_mixer.png}
	\end{center}
	\caption{Timeseries of MOX produced from Fabrications}
	\label{fig:mox_fab}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/pu_demand.png}
	\end{center}
	\caption{Separated Plutonium demand from Spent MOX}
	\label{fig:pu_demand_mox}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
	\end{center}
	\caption{Reprocessing Waste for French Transition Scenario.}
	\label{fig:reprocess_waste}
\end{figure}

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category [unit] & Value & Specifics \\ \hline
			Total MOX used [t] & 164,141 & \\ \hline
			Total MOX from UOX Waste [t] & 2,347.2  &  \\ \hline
			Total MOX from MOX Waste [t] & 161,793.8 & \\ \hline
		\end{tabular}}
		\caption {\gls{SFR} Simulation Results}
		\label{tab:sfr_sim_result}
\end {table}

### 2017-06-24 introduction.tex
resized figures

@@
         \begin{center}
-                \includegraphics[scale=0.7]{./images/french-transition/power_plot.png}
+                \includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
         \end{center}
@@
         \begin{center}
-                \includegraphics[scale=0.7]{./images/french-transition/number_plot.png}
+                \includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
         \end{center}
@@
 is mixed with depleted uranium to produce \gls{MOX}.
-
-\subsection{Reprocessed Uranium}
-Reprocessed uranium contains a range of uranium isotopes, from $^{232}U$ to $^{238}U$.
-This brings complications in reusing reprocessed uranium as a fuel source \cite{IAEA_management_2007}.
-The presence of neutron-absorbing isotopes $^{234}U$ and $^{236}U$ requires reprocessed uranium
-to require a higher enrichment of $^{235}U$. There is trace amounts (2 ppb) of fissile istope $^{233}U$,
-which provides little benefit.  
-Also, $^{232}U$ has a decay chain of short-lived
-daughter products that undergo intense beta and gamma radiation.
-The French nuclear program utilizes a fraction (1/3) of reprocessed uranium as fuel \cite{IAEA_management_2007}.
-However for this simulation the reprocessed uranium is simply stockpiled.

### 2017-06-26 msbr_reproc.tex
initial commit

--- 2017-06-19 full-core_msbr_model.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Full-core analysis of thorium-fueled molten salt breeder reactor using the SERPENT 2 Monte Carlo code}
+\title{Online reprocessing simulation for thorium-fueled molten salt breeder reactor}
 
@@
 \usepackage[section]{placeins}
+
+\usepackage[acronym,toc]{glossaries}  % acronyms inclusion
+\include{acros}
+
+\makeglossaries
+
 \graphicspath{{figures/}}
@@
 \section{Introduction}
-The molten salt reactor (MSR) is an advanced type of reactor which was developed at Oak Ridge National Laboratory (ORNL) in the 1950s and was operated in the 1960s.
-In the MSR, fluorides of fissile and/or fertile materials (i.e.
-$UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
-This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
-These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
+The thermal spectrum \gls{MSR} is an advanced type of reactor consist of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator.
+This fuel form leads to immediate advantages over traditional, solid-fueled, reactors.
+The molten-salt carrier salt with dissolved in it fissile and/or fertile material allows to use online refuelling and reprocessing, which means \gls{MSR}s can operate years without shutdown, achieve maximum fuel utilization, and outstanding neutron economy \cite{leblanc_molten_2010}.
+Moreover, this type of fuel does not need fabrication and could be transported from enrichment plant to \gls{NPP} in form of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with regards to economics.
+Additionally, it has high level of inherent safety due to strong negative temeperature coefficient of reactivity, near-atmospheric pressure in the primary loop, stable coolant, passive decay heat cooling, and small excess reactivity \cite{elsheikh_safety_2013}.
 
-The thermal spectrum Molten Salt Breeder Reactor (MSBR) was designed specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
-Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment.
-The mixture of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
-The MSBR geometry is difficult to describe in computer code input and usually require major approximations to proceed \cite{park_whole_2015}.
+The thorium fueled Molten Salt Breeder Reactor (MSBR) was developed in early 1970s specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
+Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment \cite{robertson_conceptual_1971}.
+In the matter of nuclear fuel cycle, the thorium cycle produces much less amount of plutonium and minor actinides (MAs) comparing to the traditional uranium fuel cycle, consequently, it might significantly increase prolifiration resistance when \gls{MSR} operates in the breeder regime.
+The \gls{MSR}s also could be employed as converter reactor for transmutation spent fuel from \gls{LWR} or others.
 
-For the development of MSBR research, this paper demonstrates an advanced whole-core three-dimensional model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code and cross-verification with existing MCNP6 results \cite{park_whole_2015,leppanen_serpent_2012}.
-This neutronics model is of sufficient fidelity to inform optimization of fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation, and for depletion calculations using built-in Serpent burnup module.
-Moreover, this model in the future will be employed to generate problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}, and for routine applications.
+Nowadays, interest to \gls{MSR} coming back after long-term break because of its unique characteristics and features of this type of reactor, such as online reprocessing and refueling.
+For the development of \gls{MSR} conception special computational analysis methods and codes needed due to completely different physics of liquid-fueled nuclear reactor comparing with traditional, solid-fueled, reactors.
+Most of the contemporary nuclear reactor physics codes do not able to perform depletion calculations in the online reprocessing regime.
+J.J.
+Powers (\gls{ORNL}) has suggested a novel method to conducting depletion simulation for \gls{MSR} with taking into account the online reprocessing and refueling based on the deterministic computer code NEWT in SCALE \cite{powers_new_2013}.
+This approach was later used by Jeong et al.
+to find equilibrium state for MSBR and validate it with MCNP6/CINDER90 model \cite{jeong_equilibrium_2016}.
+For the development of MSBR research, this paper presents the MSBR single-cell model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code that was employed to find equilibrium core state, and several calculation results including the depletion calculation of the single-cell unit.
 
-All calculations presented in this paper were performed using the Serpent 2 code version 2.1.28.
+All calculations presented in this paper were performed using the Serpent 2 code version 2.1.29 with ENDF/B-VII
+nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}.
 Compared with Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
-Before burnup calculations could be undertaken, MSBR model was verified.
-In Section 2, a brief description of the MSBR geometry model is given.
-In Section 3 the results are presented and discussed.
-Section 4 reflected conclusions and plans for the future research.
+This paper use build-in Serpent 2 depletion capabilities with online reprocessing subroutine.
+Another feature, circulating
+liquid fuel, which causes delayed neutron precursor drift is not treated here.
 
@@
 From the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 graphite elements every $45^\circ$ with irregular shape as well as holes for the flow of salt and were simplified into a right circular hollow cylinder sector shape with the central hole.
-This is only simplification for this Monte Carlo model.
+This is only simplification for this model.
 

### 2017-06-29 acros.tex
finalizing paper

--- 2017-02-27 acros.tex
@@
 \newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
+\newacronym{ADS}{ADS}{Accelerator Driven System}
 \newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
@@
 \newacronym{ANL}{ANL}{Argonne National Laboratory}
+\newacronym{ANS}{ANS}{American Nuclear Society}
 \newacronym{API}{API}{application programming interface}
-\newacronym{ARCH}{ARCH}{autoregressive conditional heteroskedastic}
 \newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
 \newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
-\newacronym{ARMA}{ARMA}{autoregressive moving average}
 \newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
@@
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
-\newacronym{CASL}{CASL}{Consortium for Advanced Simulation of Light Water Reactors}
 \newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
@@
 \newacronym{EBS}{EBS}{Engineered Barrier System}
+\newacronym{EDF}{EDF}{Électricité de France}
 \newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
@@
 \newacronym{EPA}{EPA}{Environmental Protection Agency}
+\newacronym{EPR}{EPR}{European Pressurized Reactors}
 \newacronym{EP}{EP}{Engineering Physics}
+\newacronym{EU}{EU}{European Union}
 \newacronym{FCO}{FCO}{Fuel Cycle Options}
@@
 \newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
-\newacronym{GCAM}{GCAM}{Global Change Assessment Model}
+\newacronym{FP}{FP}{Fission Products}
 \newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
@@
 \newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
+\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
 \newacronym{INL}{INL}{Idaho National Laboratory}
@@
 \newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
-\newacronym{LMFBR}{LMFBR}{Liquid-Metal-cooled Fast Breeder Reactor}
+\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}
 \newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
@@
 \newacronym{LP}{LP}{linear program}
-\newacronym{MARKAL}{MARKAL}{MARKet and ALlocation}
+\newacronym{LWR}{LWR}{Light Water Reactor}
+\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
 \newacronym{MA}{MA}{minor actinide}
@@
 \newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
-\newacronym{NCSA}{NCSA}{National Center for Supercomputing Applications}
 \newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
@@
 \newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
-\newacronym{NFC}{NFC}{Nuclear Fuel Cycle}
 \newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
@@
 \newacronym{PH}{PRONGHORN}{PRONGHORN}
+\newacronym{PRIS}{PRIS}{Power Reactor Information System}
 \newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
@@
 \newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
+\newacronym{PWR}{PWR}{Pressurized Water Reactor}
 \newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
@@
 \newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
+\newacronym{ThOX}{ThOX}{thorium oxide}
 \newacronym{UFD}{UFD}{Used Fuel Disposition}
@@
 \newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
+\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
 \newacronym{VV}{V\&V}{verification and validation}

### 2017-06-29 discussion.tex
finalizing paper

\section{Discussion}
This work demonstrated that, given infinite
reprocessing and \gls{MOX} fabrication capacities,
France can transition into a fully \gls{SFR} fleet
with installed capacity of 60,000 MWe by 2076.
The initial fuel demand is filled by \gls{MOX} from
reprocessed \gls{SNF}, which later on
is met by \gls{MOX} created from recycled \gls{MOX}.

Since most \gls{EU} nations do not have an operating \gls{SNF}
repository or a management plan, they have a strong incentive
to send all their \gls{SNF} to France. France has a financial
incentive (compensation from other nations) to take this fuel,
and since reuse of spent fuel from
other nations will allow France to meet their MOX demand
without new construction of \glspl{LWR}.

Though complex political and economic factors have not been
addressed, and various assumptions were made for this scenario,
this option may hold value for the \gls{EU} as a nuclear community,
and for France to advance into a closed fuel cycle.

### 2017-06-29 introduction.tex
deleted number plot for SFR deployment
finalizing paper

@@
 The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
-\cite{cne2_noauthor_2015} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
+\cite{noauthor_cne2_nodate} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
 This paper uses \Cyclus to explore the feasibility of using \gls{SNF}from other EU nations
@@
 namely \glspl{EPR} are constructed in order to supply \gls{SNF} required
-for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2007, freynet_multiobjective_2016}.
-There has been little attention in reprocessing legacy \gls{SNF} from other
+for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
+There also are studies on regional (European) transmutation and partitioning with fast reactors
+and \gls{ADS} to reduce disposal burden \cite{fazio_study_2013, martinez-val_pateros_2009}.
+There has been little attention in utilizing legacy \gls{SNF} from other
 EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
@@
 \end{figure}
-\FloatBarrier
 
-\begin{figure}[htbp!]
-        \begin{center}
-                \includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
-        \end{center}
-        \caption{Timeseries of number of \gls{SFR}s}
-        \label{fig:sfr_num}
-\end{figure}
-\FloatBarrier
-
-\Cref{fig:sfr_cap} and \cref{fig:sfr_num} display
+\Cref{fig:sfr_cap} display
 the \gls{SFR} number and capacity over time.
@@
 
-The second scenario estimates the \gls{SNF} inventory in \gls{EU} at 2050,
+The second scenario utilizes the obtained \gls{SNF} inventory in \gls{EU} at 2050,
 and reprocesses the \gls{SNF} to separate plutonium. The separated
@@
 \gls{MOX} is also reprocessed to extract plutonium, which also
-is mixed with depleted uranium to produce \gls{MOX}.
+is mixed with depleted uranium to produce \gls{MOX}. Note that the plutonium
+from both spent fuel types are of 'good quality' (~70\% fissile, ~25\% Pu240),
+and the \gls{MOX} fuel is fabricated in the simulation to have an appropriate
+neutronic property \cite{huff_fundamental_2016}.

### 2017-06-29 results.tex
finalizing paper

@@
 			\hline
-			Category [unit] & Value & Specifics \\ \hline
-			Total UOX Usage [t] & 188,196  &  \\ \hline
-			Total MOX Usage [t] & 118 & \\ \hline
-			Total Spent UOX [t] & 183,807 & \\ \hline
-			Total Spent MOX [t] & 0 & All is Reprocessed. \\ \hline
-			Total Tailings [t] & 1,125,798 & \\ \hline
+			Category  & Value [t] & Specifics \\ \hline
+			Total Natural U & 1,314,003 & \\ \hline
+			Total UOX Usage  & 188,196  &  \\ \hline
+			Total MOX Usage  & 118 & \\ \hline
+			Total Spent UOX  & 183,992 & \\ \hline
+			Total Spent MOX  & 0 & All is Reprocessed. \\ \hline
+			Total Tailings  & 1,125,798 & \\ \hline
 		\end{tabular}}
@@
 values are the \gls{EU} inventory and history at year 2050.
-
-Tables \ref{tab:eu_num} and \ref{tab:eu_pow} display the
-timeseries of number of reactors and installed capacity in \gls{EU}.
 
@@
 
-Figures \ref{fig:eu_tail} and \ref{fig:snf} show the 
+Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
+timeseries of number of reactors and installed capacity in \gls{EU}.
+
+Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
 timeseries of mass of tailings and spent fuel accumulation in \gls{EU}.
-
-Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.
-
-Note that the MOX usage is so little that it is invisible in the
-plot.
 
@@
 	\label{fig:eu_tail}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\begin{center}
-		\includegraphics[width=\columnwidth]{./images/eu_future/total_fuel.png}
-	\end{center}
-	\caption{Timeseries of total fuel usage in \gls{EU}.}
-	\label{fig:eu_fuel}
 \end{figure}
@@
 		Isotope & Mass Fraction in Spent Fuel [\%] & Quantity [t] \\ \hline
-		Total & .9358 & 1,720 \\ \hline
-		Pu238 & .0111 & 20.40 \\ \hline
-		Pu239 & .518 & 952.12 \\ \hline
-		Pu240 & .232 & 426.43 \\ \hline
-		Pu241 & .126 & 231.59 \\ \hline
-		Pu242 & .0487 & 89.51 \\ \hline
+		Total & .9358 & 1,721.79 \\ \hline
+		Pu238 & .0111 & 20.42 \\ \hline
+		Pu239 & .518 & 953.07 \\ \hline
+		Pu240 & .232 & 426.86 \\ \hline
+		Pu241 & .126 & 231.82 \\ \hline
+		Pu242 & .0487 & 89.6 \\ \hline
 	\end{tabular}
@@
 
-To create \gls{MOX}, 10\% Pu and 90\% depleted uranium is used.
-Thus $1,720$ tons of plutonium yields $17,200$ tons of
+To create \gls{MOX}, ~9\% Pu and ~91\% depleted uranium is used.
+Thus $1,721$ tons of plutonium yields $19,122$ tons of
 \gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
@@
 
-From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
+From Varaine et al., a French
 ASTRID-type \gls{SFR} of capacity $600 MWe$ needs $1.225$ tons of
-plutonium a year, with an initial plutonium loading of $4.9$ tons.
+plutonium a year, with an initial plutonium loading of $4.9$ tons
+\cite{marsaultmarie-sophie_pre-conceptual_2012}.
 Thus, it can be assumed that the ASTRID reactor takes in $49$ tons of 
@@
 The number of SFR-years worth of fuel that can be created with
-the \gls{SNF} from 2050 is $\frac{17,611.3 t}{12.25} = 1,437.65 $,
+the \gls{SNF} from 2050 is $\frac{19,122t}{12.25} = 1,560 $,
 assuming infinite reprocessing and \gls{MOX} fabrication capacity.
@@
 contains enough plutonium to produce a \gls{MOX} fuel with
-the same mass, if mixed with depleted uranium. For example,
-spent \gls{MOX} from an ASTRID reactor is 38\% plutonium,
-whereas a fresh \gls{MOX} is 10\% plutonium.
-The compositions are in \cref{tab:comp}.
+the same mass, if mixed with depleted uranium. 
 Separating plutonium from spent \gls{MOX} from
-an ASTRID reactor can create \gls{MOX} more than
-three times the mass of spent \gls{MOX}.
+an ASTRID reactor can create \gls{MOX} 
+the mass of spent \gls{MOX}, given sufficient tailings supply.
 
@@
 
-\Cref{fig:mox_fab} shows the progression of mox created from
-the fabrication plant over time. \Cref{fig:mox_fab} shows
-the separated plutonium demand from spent \gls{MOX} to fuel the 
-ASTRID reactors.
-
-\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
-(any content from spent fuel other than U, Pu) over time. Note that 
-the amount of reprocessing waste is much greater when reprocessing
-spent \gls{MOX} from ASTRID reactors, since there is little uranium
-or plutonium left due to a high burnup.
+\Cref{fig:pu_demand} shows the separated plutonium demand
+for \gls{MOX} production to fuel the ASTRID reactors given the deployment schedule.
 
@@
 	\begin{center}
-		\includegraphics[width=\columnwidth]{./images/french-transition/mox_from_mixer.png}
+		\includegraphics[width=\columnwidth]{./images/french-transition/pu_total_demand.png}
 	\end{center}
-	\caption{Timeseries of MOX produced from Fabrications}
-	\label{fig:mox_fab}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\begin{center}
-		\includegraphics[width=\columnwidth]{./images/french-transition/pu_demand.png}
-	\end{center}
-	\caption{Separated Plutonium demand from Spent MOX}
-	\label{fig:pu_demand_mox}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\begin{center}
-		\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
-	\end{center}
-	\caption{Reprocessing Waste for French Transition Scenario.}
-	\label{fig:reprocess_waste}
+	\caption{Separated Plutonium demand for \gls{MOX} production}
+	\label{fig:pu_demand}
 \end{figure}
@@
 			Total MOX used [t] & 164,141 & \\ \hline
-			Total MOX from UOX Waste [t] & 2,347.2  &  \\ \hline
-			Total MOX from MOX Waste [t] & 161,793.8 & \\ \hline
+			Total MOX from UOX Waste [t] & 19,136.2  &   \\ \hline
+			Total MOX from MOX Waste [t] & 145,004.8 & \\ \hline
+			Total Tailings used [t] & 149,368.3 & \\ \hline
+			Total legacy SNF reprocessed [t] & 183,992 & \\ \hline
 		\end{tabular}}

### 2017-07-03 msbr_reproc.tex
Introduction finished, description of actual work almost finished

@@
 
-The thorium fueled Molten Salt Breeder Reactor (MSBR) was developed in early 1970s specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
+The thorium fueled \gls{MSBR} was developed in early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
 Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment \cite{robertson_conceptual_1971}.
@@
 This approach was later used by Jeong et al.
-to find equilibrium state for MSBR and validate it with MCNP6/CINDER90 model \cite{jeong_equilibrium_2016}.
-For the development of MSBR research, this paper presents the MSBR single-cell model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code that was employed to find equilibrium core state, and several calculation results including the depletion calculation of the single-cell unit.
+to find equilibrium state for \gls{MSBR} and validate it with \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.
+For the development of \gls{MSBR} research, this paper presents the single-cell model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code that was employed to find equilibrium core state, and several calculation results including the depletion calculation of the single-cell unit.
 
@@
 nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}.
-Compared with Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
+Compared to Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
 This paper use build-in Serpent 2 depletion capabilities with online reprocessing subroutine.
-Another feature, circulating
+Another feature of \gls{MSBR}, circulating
 liquid fuel, which causes delayed neutron precursor drift is not treated here.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{MSBR design description}
-The MSBR vessel has diameter of 680 cm and a height of 610 cm.
-It contains molten fluoride fuel-salt mixture which performs two functions: to generate heat in the moderated region and to transport heat energy from the core to primary heat exchanger using the primary salt pump.
+\section{Description of the actual work}
+The \gls{MSBR} is thermal spectrum reactor.
+The reactor vessel has diameter of 680 cm and a height of 610 cm and contains molten fluoride fuel-salt mixture which performs two functions: to generate heat in the moderated region and to transport heat energy from the core to primary heat exchanger using the primary salt pump.
 The vessel also contains graphite blocks for neutron moderation and reflection.
-The reactor core has a central zone, Zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
-The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 2 safety rods consisting of boron carbide clad.
-The undermoderated zone, Zone II, with 37\% fuel salt, and radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
-This zone is formed of two kinds of elements: elements like those in Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
-At the outer of the core there are graphite reflector and vessel wall.
-Between the core and the reflector blocks located annulus which is 100\% salt needed to provide possibility removing and inserting a graphite assembly.
+The lithium in the fuel-salt solution is enriched to 99.995\% $^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon neutron bombardment.
+In this study, the 0.005\% atomic fraction of $^6$Li has been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on neutron flux energy distribution and, consequently, on depletion calculation results.
+Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters \cite{robertson_conceptual_1971}.
 
-Figure~\ref{fig:plan} shows the plan view of the whole-core configuration at the expected reactor operational level when all control rods are fully withdrawn from the core.
-Figure~\ref{fig:elevation} shows the longitudinal section of the reactor.
-The violet color represents bare graphite, and the yellow represents fuel salt.
-The blue color shows Hastelloy-N, a material used for the plenum and vessel wall, and the black color is a void space.
-All figures of the core in this work generated using built-in Serpent plotter.
-\begin{figure}[!htb] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \vspace{-0.6em}
-  \includegraphics[width=0.93\linewidth]{figure_2_1.png}
-  \caption{Plan view of MSBR core.}
-  \label{fig:plan}
-\end{figure}
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=\linewidth]{figure_2_2.png}
-  \caption{Elevation view of MSBR core.}
-  \label{fig:elevation}
-\end{figure}
-
-\subsection{Core Zone I and II-A}
-The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements.
-The fuel salt to graphite volume ratio of Zone I is 13.2\%, and the central hole has a diameter of $3.42cm$.
-Zone II has 37\% salt and central hole diameter of $6.604cm$.
-Both types of elements mostly have a rectangular shape with a part of cylinder sticking out at each corner to form salt flow between the graphite channels.
-Different sizes of elements are necessary to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
-Figure~\ref{fig:zone12A} demonstrates the reconstructed graphite element utilized for this Monte Carlo model.
-
-\begin{figure}[h] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.96\linewidth]{figure_2_4.png}
-  \caption{Zone I (left) and Zone II-A (right) elements.}
-  \label{fig:zone12A}
-\end{figure}
-
-\subsection{Core Zone II-B}
-The second core zone is divided into two different zones: Zone II-A and Zone II-B.
-The graphite elements for Zone II-A are prismatic and form the first reflecting layer surrounding the core zone I.
-The elements for zone II-B made up in the form of rectangular slats spaced far enough apart to achieve 0.37 fuel salt volume fraction.
-Figure~\ref{fig:zone2B} shows the outer Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
-The annulus contains 100\% fuel salt and serves to reduce the damage flux at the internal surface of the graphite reflector blocks.
-The reactor Zone II-B graphite $5.08cm$-thick slats and various length in width (average width is about $26.67cm$) are reconstructed as is in the model without any approximation.
-From the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 graphite elements every $45^\circ$ with irregular shape as well as holes for the flow of salt and were simplified into a right circular hollow cylinder sector shape with the central hole.
-This is only simplification for this model.
-
-\subsection{Material composition}
-The fuel salt, the reactor graphite, and the modified Hastelloy N are exclusive MSBR materials which were created at ORNL.
-The isotope composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to Serpent model without any modification.
-
-\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.93\linewidth]{figure_2_5.png}
-  \caption{Plan view of Zone II-B.}
-  \label{fig:zone2B}
-\end{figure}
-
-The initial fuel salt loading composition is $LiF-BeF_2-ThF_4-^{233}UF_4-^{239}PuF_3$ (72-16-12-0.232-0.0006 mole \%).
-The lithium is enriched to 99.995\% $^{7}Li$ because $^{6}Li$ is a very strong neutron poison and becomes tritium upon neutron bombardment.
-In this study, the 0.005\% atomic fraction of $^{6}Li$ has been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on effective multiplication factor.
-For cross section data generation ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
-%Specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when Serpent generate problem-oriented nuclear data library.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and Analysis}
-The reactor physics calculation was carried out using the methods described earlier.
-This section presents calculation results, such as the effective multiplication factor for whole core, neutron flux spectrum, and temperature reactivity coefficients.
-The normalized neutron flux distribution is calculated for the whole core using continuous-energy nuclear data which allows to obtaining very smooth distribution.
-The temperature coefficients for both fuel salt solution and reactor graphite are computed by comparing effective multiplication factors for two temperatures in the working range.
-
-The MSBR criticality simulations were performed on one Intel Xeon E3-1225 3.3GHz processor wich has four physical cores.
-Each simulation took 23 minutes or 92 minutes per one core.
-A similar whole-core MSBR simulation using MCNP6 required approximately 890 minutes per core \cite{park_whole_2015}, consequently, Serpent 2 can provide tremendous computer costs savings for compute-heavy depletion calculations.
-
-\subsection{Neutron spectrum}
-Figure~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for the whole core in the energy range from $10^{-10}$ to $100 MeV$.
-The results show close fit with the MCNP simulation \cite{park_whole_2015}, especially in thermal energy range.
-\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=\linewidth]{figure_3_1.png} 
-  \caption{Neutron flux spectrum of MSBR for MCNP6 and Serpent 2 model.}
-  \label{fig:spectrum}
-\end{figure}
-It is important to obtain the epithermal and thermal spectrum to produce $^{233}U$ from $^{232}Th$ because radiative capture cross section of thorium monotonically decreasing from $10^{-10} MeV$ to $10^{-5} MeV$.
-Hardening the spectrim tends to significantly increasing resonance absorbtion in thorium and decreasing the absorptions in fissile and construction materials thus large amount of fissile material will be needed to make the reactor critical.
-
-\subsection{Effective multiplication factor}
-Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 and Serpent 2 whole core models.
-The coefficient obtained using Serpent 2 is about 4.37\% higher than MCNP6 one.
-The discrepancy was ocurred most likely because the model used in Park et al.
-didn't take into account $^{239}PuF_3$, contained in the fuel salt solution.
-Plutonium-239 has very high fission cross section in thermal energy range and produce more neutrons per fission than $^{233}U$, consequently, multiplication factor for this case is higher.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\centering
-\begin{tabular}{p{0.15\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
-      & Serpent2      & MCNP6 \cite{park_whole_2015}          
+\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
+Thermal capacity of reactor           & 2250 MW(t)
 \\ \midrule
-$K_{eff}$  & $1.05134\pm0.00116$ & $1.00736$
+%Net electrical output                 & 1000 MW(e) 
+%\\ \midrule
+%Net thermal efficiency        & 44.4\%
+%\\ \midrule
+Volume fraction of salt in central core zone     & 0.132
+\\ \midrule
+Volume fraction of salt in outer core zone       & 0.37
+\\ \midrule
+Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
+\\ \midrule
+Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
+\\ \midrule
+Fuel salt components                  & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	
+\\ \midrule
+Fuel salt composition                 & 71.767-16-12-0.232-0.0006 mole\%
 \\
@@
 \end{tabular}
-  \caption{Effective multiplication factor of whole core model.}
-  \label{tab:keff}
+  \caption{Summary of principal data for MSBR.}
+  \label{tab:data}
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The \gls{MSBR} core consist of two different zones with one flow.
+The central zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite.
+The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 2 safety rods consisting of boron carbide clad.
+The undermoderated zone, Zone II, with 37\% fuel salt, and radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
+In this work, only Zone I element with the hole diameter of 3.42138 cm, and the molten-salt fuel volume fraction is 0.132 was considered.
+Figure~\ref{fig:zoneI} shows the geometry of unit cell model.
+The boundary condition of the unit cell is periodic.
+The density of fuel salt is 3.3304 g/cm$^3$ and graphite one is 1.843 g/cm$^3$.
+The temperature of fuel and graphite is fixed for the whole reprocessing cycle at 908K \cite{robertson_conceptual_1971}.
+
+\begin{figure}[h] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.6em}
+  \includegraphics[width=0.99\linewidth]{zone_I_mesh.png}
+  \caption{MSBR unit cell of Zone I geometry.}
+  \label{fig:zoneI}
+\end{figure}
+\subsection{Online reprocessing method}
+
+Currently, researchers usually using supporting tools and scripts to simulate online reprocessing and refueling.
+Most researchers investigating the \gls{MSR}s have utilised for reprocessing calculations stochastic (i.e.
+\gls{MCNP}) or deterministic (i.e.
+SCALE) code with originally-developed scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}.
+The Serpent 2 is the first code supporting continuous material reprocessing, and allows create needed number of material flows into the fuel and/or out from the fuel.
+
+The \gls{MSBR} has the capability to remove every 20 seconds all poisons (e.g.
+$^{135}$Xe), noble metals and gases (e.g.
+$^{75}$Se, $^{85}$Kr) which also have relatively high absorption cross section.
+The thorium-232 absorbs thermal neutrons and produce $^{233}$Pa which then decay into the fissile $^{233}$U.
+The problem of protactinium is a large absorption cross section in the thermal energy spectrum, therefore $^{233}$Pa continuously removing from fuel salt into protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without reactor poisoning.
+The reactor reprocessing system designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, held it to produce $^{233}$U and return it back to the primary loop.
+This feature allows to keep the neutrons losses to protactinium and fission products to a very low level, and increses the efficency of $^{233}$U breeding \cite{robertson_conceptual_1971}.
+
+A major problem with the reprocessing method is that different nuclides have specific removal rates.
+On the one hand, if the depletion time intervals are very short it means specific isotope beign instantly removed, and it is hard to obtain equilibrium composition because enormous large number of depletion steps.
+On the other hand, if the depletion calculation time interval is too long the results would not truly represents \gls{MSBR} conceptual design.
+Following this idea, the time interval for depletion calculations was selected 3 days that correlate with the removal interval of $^{233}$Pa which is the major isotope for producing $^{233}$U.
+Thorium is continuously adding to maintain the initial mass fraction of $^{232}$ThF$_4$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results and Analysis}
+
+Using the methodology described previously, the \gls{MSBR} unit cell depletion analysis was performed to find equilibrium core conditions.
+In this section, the calculation results including multiplication factor, neutron flux energy spectrum, atomic density of major isotopes are summarised.
+
 \subsection{Temperature effect of reactivity}

### 2017-07-06 msbr_reproc.tex
Finish paper, ready to review

@@
 
-All calculations presented in this paper were performed using the Serpent 2 code version 2.1.29 with ENDF/B-VII
+All calculations presented in this paper were performed using the Serpent 2 code version 2.1.29 with ENDF/B-VII.0
 nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}.
@@
   \vspace{-0.6em}
-  \includegraphics[width=0.99\linewidth]{zone_I_mesh.png}
+  \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
   \caption{MSBR unit cell of Zone I geometry.}
@@
 \end{figure}
+
 \subsection{Online reprocessing method}
@@
 
-\subsection{Temperature effect of reactivity}
-Table~\ref{tab:tcoef} represents the quantitive analysis of temperature effects on reactivity.
-Uncertainty for each temperature coefficient also was calculated and shown in Table~\ref{tab:tcoef}.
-The main physical principle underlying the reactor temperature feedback is expandsion of matter when it is heated.
-When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is defined by the space for fuel bounded by the graphite.
-When the reactor graphite temperature grows, the density of graphite declines which also frees up space for fuel salt.
-To determine temperature coefficients, three cases were considered:
-\begin{enumerate}  
-\item Temperature of fuel salt rising from 900K to 1200K.
-\item Temperature of graphite rising from 900K to 1200K. 
-\item Whole reactor temperature rising from 900K to 1200K.
-\end{enumerate}
+\subsection{Equilibrium state analysis}
 
+The method approximate a single representative unit cell for the whole \gls{MSBR} core, consequently, it does not take into consideration different fuel-moderator volume ratio for Zone I, Zone II, annulus, and reflector.
+The initial multiplication factor during depletion calculation is selected for state with fully withdrawn control and poison rods position which gaves high excess reactivity in the beginning of the cycle (approximately 5000 pcm).
+Standart deviation is about 100 pcm.
+
+\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.8em}
+  \includegraphics[width=1.03\linewidth]{keff.png}
+  \caption{Infinite multiplication factor during 4 years depletion simulation.}
+    \vspace{-0.8em}
+  \label{fig:keff}
+\end{figure}
+
+Figure~\ref{fig:keff} shows the infinite muliplication factor for 4-year reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data.
+The high standard deviation causes the multiplication factor fluctuations.
+Protactinium-233 continuously removing into the tank for protactinium decay.
+$^{233}$Pa has a half-life of 27 days and beta decays into $^{233}$U which as fresh fuel goes back to the reactor core.
+The infinite multiplication factor decreases first 400 days of depletion due to strong absorbers (e.g.
+$^{233}$Th, $^{234}$U) accumulation which causes relatively high fuel ($^{233}$U) refill inflow to keep reactor critical.
+During reactor operation producing fissile materials other than $^{233}$U in the core (e.g.
+$^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel refill rate after ~1 year of operation.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.8em}
+  \includegraphics[width=1.03\linewidth]{fuel_composition.png}
+  \caption{Normalized number density of major isotopes during 4 years depletion.}
+  \label{fig:compos}
+  \vspace{-0.8em}
+\end{figure}
+
+The analysis of the fuel salt composition variation gives clearer information about equilibrium core state.
+Figure~\ref{fig:compos} shows the normalized number density of important isotopes that have strong influence on the core neutronics at the beginning of each depletion time interval.
+The number density of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount of it produced during 3-days reprocessing step.
+It can be seen that the the multiplication factor reaches the equilibrium state at about 950  days.
+Figure~\ref{fig:rates} represents the rates of materials in online reprocessing flows during 4 years of depletion calculations.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\captionsetup[table]{
-  labelsep = newline,
-  name = TABLE, 
-  justification=justified,
-  singlelinecheck=false,%%%%%%% a single line is centered by default
-  labelsep=colon,%%%%%%
-  skip = \medskipamount}
-\begin{table}[h!]
+%\captionsetup[table]{
+%  labelsep = newline,
+%  name = TABLE, 
+%  justification=justified,
+%  singlelinecheck=false,%%%%%%% a single line is centered by default
+%  labelsep=colon,%%%%%%
+%  skip = \medskipamount}
+%\begin{table}[h!]
 %\centering
-\begin{tabular}{p{0.22\linewidth} p{0.22\linewidth} p{0.21\linewidth} p{0.15\linewidth}} \toprule
-   Reactivity coefficient [pcm/K]  & Serpent2      & MCNP6 \cite{park_whole_2015}   & Reference \cite{robertson_conceptual_1971}      
-\\ \midrule
-Fuel salt        & $-3.93\pm0.005$ & $-3.20\pm0.05$ & $-3.22$ 
-\\ \midrule
-Moderator        & $+2.44\pm0.013$ & $-0.11\pm0.05$ & $+2.35$ 
-\\ \midrule
-Total            & $-1.74\pm0.030$ & $-3.21\pm0.04$ & $-0.87$ 
-\\
-\bottomrule
-\end{tabular}
-  \caption{Temperature coefficients of reactivity.}
-  \label{tab:tcoef}
-\end{table}
+%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
+%      Isotope & First 400 days     & After 400 days          
+%\\ \midrule
+%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
+%\\ \midrule
+%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
+%\\ \midrule
+%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
+%\\
+%\bottomrule
+%\end{tabular}
+%  \caption{Materials flows rates during \gls{MSBR} online reprocessing [1/s*cm$^3$].}
+%  \label{tab:rates}
+%\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-On the one hand, changes in fuel temperature cause only density variation, geometry keeps the same because fuel is in the form of liquid.
-On the other hand, when moderator heats up both the density and the geometry changes due to thermal expansion of the graphite blocks and the reflector.
-New graphite density was calculated using linear temperature expansion coefficient of reactor graphite which is $1.3\times10^{-6}1/K$ \cite{robertson_conceptual_1971}.
-Based on this information new geometry input, which takes into account graphite expansion, was created.
+\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.8em}
+  \includegraphics[width=1.03\linewidth]{rates_fuel.png}
+  \caption{Materials flows rates during online reprocessing.}
+  \label{fig:rates}
+  \vspace{-0.8em}
+\end{figure}
+From the graph below we can see that to keep reactor critical higher $^{233}$U flow rate required for first 400 days of operation and after that much smaller uranium-233 flow rate from the protactinium decay tank needed.
+The $^{232}$Th rate slightly decreases over 4 years of operation due to other than $^{233}$U fissile materials accumulation.
 
-The fuel temperature coefficient (FTC) is positive due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with early research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient is negative due to changing density, and would increases during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
-Finally, the total temperature coefficient of reactivity is relatively large and negative, despite graphite components, and affords excellent reactor stability and controllability.
+\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.8em}
+  \includegraphics[width=1.03\linewidth]{rates_outflow.png}
+  \caption{Materials flows rates for the protactinium decay tank during \gls{MSBR} online reprocessing.}
+  \vspace{-0.6em}
+  \label{fig:outflow}
+  \vspace{-0.8em}
+\end{figure}
+As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay accumulates $^{233}$Pa approximately 200 days and fresh fuel ($^{233}$U) flow established also after 200 days.
+Uranium produced in the tank by protactinium decay is separated by circulation of the salt through a flourinator.
+The fully processed molten salt, on its way back to the primary loop, has uranium added at the rate required to maintain or adjust the fissile material concentration and, hence, the reactivity, in the reactor core as desired.
+
+\subsection{Neutron spectrum}
+
+Figure~\ref{fig:spectrum} represents the normalized neutron flux distribution of the initial and the equilibrium core compositions.
+The spectrum for the equilibrium state is harder than the initial state due to heavy fission products.
+\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.85em}
+  \includegraphics[width=1.04\linewidth]{spectrum.png}
+  \vspace{-0.6em}
+  \caption{Normalized neutron energy spectrum for initial and equilibrium composition.}
+  \label{fig:spectrum}
+  \vspace{-0.10em}
+\end{figure}
+
+In this work only Zone I unit cell with 0.132 volume fraction of fuel considered, neutron spectrum for Zone II cell where salt fraction is 37\% should be harder and the peak in thermal energy region predicted to be much lower.
+To obtain high fidelity neutron energy spectrum whole \gls{MSBR} core analysis is required.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
-The MSBR full-core analysis was performed using the Serpent 2 Monte Carlo code.
-The complex geometry of the reactor is reconstructed in three-dimensional space without any major approximations.
-Accurate material data was employed to calculate reactor key design parameters.
-The effective multiplication factor for initial fuel composition is slightly higher than 1 (1.05) which allows reactor operation from startup to first online reprocessing cycle.
-The neutron flux energy spectrum was calculated for the whole core and represents the epithermal spectrum of the MSBR.
-The total temperature coefficient is negative, consequently, the MSBR has negative temperature feedback, but MTC is negative which has a negligible effect on safety because it is outweighed by the strong, negative FTC.
+The depletion calculation of the \gls{MSBR} init cell model for finding the equilibrium states was performed using the Serepent 2 Monte Carlo code to simulate simplified case of the online reprocessing and refueling to find equilibrium material composition.
+When running depletion calculation, the fission products are removed and fertile/fissile materials are added to fuel salt every 3 days.
+The important MSR feature, online reprocessing I\& refueling is implemented in the Serpent 2 material burnup routine.
+The results of this study indicate that from the depletion calculation the multiplication factor slowly decreases and reaches to the equilibrium state.
+The most obvious finding to emerge from the analysis of initial and equilibrium materials composition is that neutron energy spectrum is harder for equilibrium state because significant amount of heavy fission products were accumulated in the \gls{MSBR} core.
 
-This high-fidelity full-core model will be employed for a number of future efforts.
-First, depletion simulation will be performed using built-in Serpent 2 depletion capabilities to find the equilibrium state of the MSBR, its optimal fuel salt composition, reprocessing characteristics (i.e.
-rates of removing fission products, the rate of adding thorium), and fuel utilization.
-Secondly, the model will be used to generate problem-oriented nuclear data libraries for multi-physics models of MSRs developed in the MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
-Finally, transient accident simulations for safety investigation of the reactor core will be performed to study the dynamic behavior of Molten Salt Breeder Reactor.
+These results are contrary with those of Jeong and Park (2016) who suggested two different unit cell models and uses \gls{MCNP} with Python-script to simulate \gls{MSBR} online reprocessing to find equilibrium composition.
+This inconsistency may be due to different fuel fraction in the unit cell (Jeong and Park selected 20.6\% salt fraction).
+To obtain better results in online reprocessing simualtion number of future efforts expected.
+First, depletion simulation will be performed using full-core tree-dimensional high-fidelity model of \gls{MSBR} developed in Serpent 2.
+In this case, different fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, reflectors would be taken into account to find accurate multiplication factor, neutron spectrum and, hence, depleted composition.
+Secondly, additional Serpent 2 flow control system subroutine should be developed to simulate adjusting material flows (e.g.
+rate of removing $^{233}$Pa from the salt and adding fissile $^{233}$U from the tank for protactinium decay) depending upon current reactivity value which is more promising reactivity control method than moving control and safety rods.
+Finally, temperature effect of reactivity for both fuel salt and graphite should be calculated to find optimal effective multiplication factor range.
 

### 2017-07-07 msbr_reproc.tex
consist->consisting

@@
 \section{Introduction}
-The thermal spectrum \gls{MSR} is an advanced type of reactor consist of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator.
+The thermal spectrum \gls{MSR} is an advanced type of reactor consisting of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator.
 This fuel form leads to immediate advantages over traditional, solid-fueled, reactors.

### 2017-07-07 msbr_reproc.tex
hard wrapped all lines for better diffing

--- 2017-07-06 msbr_reproc.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Online reprocessing simulation for thorium-fueled molten salt breeder reactor}
+\title{Online reprocessing simulation for thorium-fueled molten salt breeder 
+reactor}
 
@@
 \institute{
-Department of Nuclear, Plasma, and Radiological Engineering, University of Illinois at Urbana-Champaign \break
+        Department of Nuclear, Plasma, and Radiological Engineering, University 
+        of Illinois at Urbana-Champaign \break
         Urbana, IL
@@
 \section{Introduction}
-The thermal spectrum \gls{MSR} is an advanced type of reactor consist of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator.
-This fuel form leads to immediate advantages over traditional, solid-fueled, reactors.
-The molten-salt carrier salt with dissolved in it fissile and/or fertile material allows to use online refuelling and reprocessing, which means \gls{MSR}s can operate years without shutdown, achieve maximum fuel utilization, and outstanding neutron economy \cite{leblanc_molten_2010}.
-Moreover, this type of fuel does not need fabrication and could be transported from enrichment plant to \gls{NPP} in form of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with regards to economics.
-Additionally, it has high level of inherent safety due to strong negative temeperature coefficient of reactivity, near-atmospheric pressure in the primary loop, stable coolant, passive decay heat cooling, and small excess reactivity \cite{elsheikh_safety_2013}.
+The thermal spectrum \gls{MSR} is an advanced type of reactor consisting of 
+constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
+$LiF-BeF_2-ZrF_4-UF_4$) which also works as a coolant, and the reactor graphite 
+as moderator. This fuel form leads to immediate advantages over traditional, 
+solid-fueled, reactors. The molten-salt carrier salt with dissolved in it 
+fissile and/or fertile material allows to use online refuelling and 
+reprocessing, which means \gls{MSR}s can operate years without shutdown, 
+achieve maximum fuel utilization, and outstanding neutron economy 
+\cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
+fabrication and could be transported from enrichment plant to \gls{NPP} in form 
+of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with 
+regards to economics. Additionally, it has high level of inherent safety due to 
+strong negative temeperature coefficient of reactivity, near-atmospheric 
+pressure in the primary loop, stable coolant, passive decay heat cooling, and 
+small excess reactivity \cite{elsheikh_safety_2013}.
 
-The thorium fueled \gls{MSBR} was developed in early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
-Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment \cite{robertson_conceptual_1971}.
-In the matter of nuclear fuel cycle, the thorium cycle produces much less amount of plutonium and minor actinides (MAs) comparing to the traditional uranium fuel cycle, consequently, it might significantly increase prolifiration resistance when \gls{MSR} operates in the breeder regime.
-The \gls{MSR}s also could be employed as converter reactor for transmutation spent fuel from \gls{LWR} or others.
+The thorium fueled \gls{MSBR} was developed in early 1970s by \gls{ORNL} 
+specifically to realize the promise of the thorium fuel cycle which allows the 
+use of natural thorium instead of enriched uranium as the fertile element. 
+Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment 
+\cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
+thorium cycle produces much less amount of plutonium and minor actinides (MAs) 
+comparing to the traditional uranium fuel cycle, consequently, it might 
+significantly increase prolifiration resistance when \gls{MSR} operates in the 
+breeder regime. The \gls{MSR}s also could be employed as converter reactor for 
+transmutation spent fuel from \gls{LWR} or others.
 
-Nowadays, interest to \gls{MSR} coming back after long-term break because of its unique characteristics and features of this type of reactor, such as online reprocessing and refueling.
-For the development of \gls{MSR} conception special computational analysis methods and codes needed due to completely different physics of liquid-fueled nuclear reactor comparing with traditional, solid-fueled, reactors.
-Most of the contemporary nuclear reactor physics codes do not able to perform depletion calculations in the online reprocessing regime.
-J.J.
-Powers (\gls{ORNL}) has suggested a novel method to conducting depletion simulation for \gls{MSR} with taking into account the online reprocessing and refueling based on the deterministic computer code NEWT in SCALE \cite{powers_new_2013}.
-This approach was later used by Jeong et al.
-to find equilibrium state for \gls{MSBR} and validate it with \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.
-For the development of \gls{MSBR} research, this paper presents the single-cell model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code that was employed to find equilibrium core state, and several calculation results including the depletion calculation of the single-cell unit.
+Nowadays, interest to \gls{MSR} coming back after long-term break because of 
+its unique characteristics and features of this type of reactor, such as online 
+reprocessing and refueling. For the development of \gls{MSR} conception special 
+computational analysis methods and codes needed due to completely different 
+physics of liquid-fueled nuclear reactor comparing with traditional, 
+solid-fueled, reactors. Most of the contemporary nuclear reactor physics codes 
+do not able to perform depletion calculations in the online reprocessing 
+regime. J.J. Powers (\gls{ORNL}) has suggested a novel method to conducting 
+depletion simulation for \gls{MSR} with taking into account the online 
+reprocessing and refueling based on the deterministic computer code NEWT in 
+SCALE \cite{powers_new_2013}. This approach was later used by Jeong et al. to 
+find equilibrium state for \gls{MSBR} and validate it with \gls{MCNP}/CINDER90 
+model \cite{jeong_equilibrium_2016}. For the development of \gls{MSBR} 
+research, this paper presents the single-cell model developed using a 
+continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code 
+that was employed to find equilibrium core state, and several calculation 
+results including the depletion calculation of the single-cell unit.
 
-All calculations presented in this paper were performed using the Serpent 2 code version 2.1.29 with ENDF/B-VII.0
-nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}.
-Compared to Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
-This paper use build-in Serpent 2 depletion capabilities with online reprocessing subroutine.
-Another feature of \gls{MSBR}, circulating
+All calculations presented in this paper were performed using the Serpent 2 
+code version 2.1.29 with ENDF/B-VII.0
+nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}. Compared 
+to Serpent 1, Serpent 2 has many more useful features and contains a complete 
+redesign of memory management using hybrid OpenMP + MPI parallelization, which 
+is important in depletion calculations using computer clusters with multiple 
+cores \cite{leppanen_serpent_2015}. This paper use build-in Serpent 2 depletion 
+capabilities with online reprocessing subroutine. Another feature of 
+\gls{MSBR}, circulating
 liquid fuel, which causes delayed neutron precursor drift is not treated here.
@@
 \section{Description of the actual work}
-The \gls{MSBR} is thermal spectrum reactor.
-The reactor vessel has diameter of 680 cm and a height of 610 cm and contains molten fluoride fuel-salt mixture which performs two functions: to generate heat in the moderated region and to transport heat energy from the core to primary heat exchanger using the primary salt pump.
-The vessel also contains graphite blocks for neutron moderation and reflection.
-The lithium in the fuel-salt solution is enriched to 99.995\% $^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon neutron bombardment.
-In this study, the 0.005\% atomic fraction of $^6$Li has been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on neutron flux energy distribution and, consequently, on depletion calculation results.
-Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters \cite{robertson_conceptual_1971}.
+The \gls{MSBR} is thermal spectrum reactor. The reactor vessel has diameter of 
+680 cm and a height of 610 cm and contains molten fluoride fuel-salt mixture 
+which performs two functions: to generate heat in the moderated region and to 
+transport heat energy from the core to primary heat exchanger using the primary 
+salt pump. The vessel also contains graphite blocks for neutron moderation and 
+reflection. The lithium in the fuel-salt solution is enriched to 99.995\% 
+$^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon 
+neutron bombardment. In this study, the 0.005\% atomic fraction of $^6$Li has 
+been taken into account because even such a small amount of isotope with very 
+high absorption cross section might significantly affect on neutron flux energy 
+distribution and, consequently, on depletion calculation results. 
+Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters 
+\cite{robertson_conceptual_1971}.
 
@@
         labelsep = newline,
-  name = TABLE, 
-  justification=justified,
+        name = TABLE, justification=justified,
         singlelinecheck=false,%%%%%%% a single line is centered by default
@@
                 \\ \midrule
-%Net electrical output                 & 1000 MW(e) 
-%\\ \midrule
+                %Net electrical output                 & 1000 MW(e) \\ \midrule
                 %Net thermal efficiency        & 44.4\%
@@
                 \\ \midrule
-Fuel salt components                  & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	
-\\ \midrule
-Fuel salt composition                 & 71.767-16-12-0.232-0.0006 mole\%
+                Fuel salt components                  & 
+                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	\\ 
+                \midrule
+                Fuel salt composition                 & 
+                71.767-16-12-0.232-0.0006 mole\%
                 \\
@@
 
-The \gls{MSBR} core consist of two different zones with one flow.
-The central zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite.
-The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 2 safety rods consisting of boron carbide clad.
-The undermoderated zone, Zone II, with 37\% fuel salt, and radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
-In this work, only Zone I element with the hole diameter of 3.42138 cm, and the molten-salt fuel volume fraction is 0.132 was considered.
-Figure~\ref{fig:zoneI} shows the geometry of unit cell model.
-The boundary condition of the unit cell is periodic.
-The density of fuel salt is 3.3304 g/cm$^3$ and graphite one is 1.843 g/cm$^3$.
-The temperature of fuel and graphite is fixed for the whole reprocessing cycle at 908K \cite{robertson_conceptual_1971}.
+The \gls{MSBR} core consist of two different zones with one flow. The central 
+zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
+The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
+2 safety rods consisting of boron carbide clad. The undermoderated zone, Zone 
+II, with 37\% fuel salt, and radial reflector, surrounding the more active 
+portion serves to diminish neutron leakage from the reactor core. In this work, 
+only Zone I element with the hole diameter of 3.42138 cm, and the molten-salt 
+fuel volume fraction is 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
+geometry of unit cell model. The boundary condition of the unit cell is 
+periodic. The density of fuel salt is 3.3304 g/cm$^3$ and graphite one is 1.843 
+g/cm$^3$. The temperature of fuel and graphite is fixed for the whole 
+reprocessing cycle at 908K \cite{robertson_conceptual_1971}.
 
@@
 
-Currently, researchers usually using supporting tools and scripts to simulate online reprocessing and refueling.
-Most researchers investigating the \gls{MSR}s have utilised for reprocessing calculations stochastic (i.e.
-\gls{MCNP}) or deterministic (i.e.
-SCALE) code with originally-developed scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}.
-The Serpent 2 is the first code supporting continuous material reprocessing, and allows create needed number of material flows into the fuel and/or out from the fuel.
+Currently, researchers usually using supporting tools and scripts to simulate 
+online reprocessing and refueling. Most researchers investigating the 
+\gls{MSR}s have utilised for reprocessing calculations stochastic (i.e. 
+\gls{MCNP}) or deterministic (i.e. SCALE) code with originally-developed 
+scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}. The 
+Serpent 2 is the first code supporting continuous material reprocessing, and 
+allows create needed number of material flows into the fuel and/or out from the 
+fuel.
 
 The \gls{MSBR} has the capability to remove every 20 seconds all poisons (e.g. 
-$^{135}$Xe), noble metals and gases (e.g.
-$^{75}$Se, $^{85}$Kr) which also have relatively high absorption cross section.
-The thorium-232 absorbs thermal neutrons and produce $^{233}$Pa which then decay into the fissile $^{233}$U.
-The problem of protactinium is a large absorption cross section in the thermal energy spectrum, therefore $^{233}$Pa continuously removing from fuel salt into protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without reactor poisoning.
-The reactor reprocessing system designed to separate $^{233}$Pa from the molten-salt fuel over 3 days, held it to produce $^{233}$U and return it back to the primary loop.
-This feature allows to keep the neutrons losses to protactinium and fission products to a very low level, and increses the efficency of $^{233}$U breeding \cite{robertson_conceptual_1971}.
+$^{135}$Xe), noble metals and gases (e.g. $^{75}$Se, $^{85}$Kr) which also have 
+relatively high absorption cross section. The thorium-232 absorbs thermal 
+neutrons and produce $^{233}$Pa which then decay into the fissile $^{233}$U. 
+The problem of protactinium is a large absorption cross section in the thermal 
+energy spectrum, therefore $^{233}$Pa continuously removing from fuel salt into 
+protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
+reactor poisoning. The reactor reprocessing system designed to separate 
+$^{233}$Pa from the molten-salt fuel over 3 days, held it to produce $^{233}$U 
+and return it back to the primary loop. This feature allows to keep the 
+neutrons losses to protactinium and fission products to a very low level, and 
+increses the efficency of $^{233}$U breeding \cite{robertson_conceptual_1971}.
 
-A major problem with the reprocessing method is that different nuclides have specific removal rates.
-On the one hand, if the depletion time intervals are very short it means specific isotope beign instantly removed, and it is hard to obtain equilibrium composition because enormous large number of depletion steps.
-On the other hand, if the depletion calculation time interval is too long the results would not truly represents \gls{MSBR} conceptual design.
-Following this idea, the time interval for depletion calculations was selected 3 days that correlate with the removal interval of $^{233}$Pa which is the major isotope for producing $^{233}$U.
-Thorium is continuously adding to maintain the initial mass fraction of $^{232}$ThF$_4$.
+A major problem with the reprocessing method is that different nuclides have 
+specific removal rates. On the one hand, if the depletion time intervals are 
+very short it means specific isotope beign instantly removed, and it is hard to 
+obtain equilibrium composition because enormous large number of depletion 
+steps. On the other hand, if the depletion calculation time interval is too 
+long the results would not truly represents \gls{MSBR} conceptual design. 
+Following this idea, the time interval for depletion calculations was selected 
+3 days that correlate with the removal interval of $^{233}$Pa which is the 
+major isotope for producing $^{233}$U. Thorium is continuously adding to 
+maintain the initial mass fraction of $^{232}$ThF$_4$.
 
@@
 
-Using the methodology described previously, the \gls{MSBR} unit cell depletion analysis was performed to find equilibrium core conditions.
-In this section, the calculation results including multiplication factor, neutron flux energy spectrum, atomic density of major isotopes are summarised.
+Using the methodology described previously, the \gls{MSBR} unit cell depletion 
+analysis was performed to find equilibrium core conditions. In this section, 
+the calculation results including multiplication factor, neutron flux energy 
+spectrum, atomic density of major isotopes are summarised.
 
@@
 
-The method approximate a single representative unit cell for the whole \gls{MSBR} core, consequently, it does not take into consideration different fuel-moderator volume ratio for Zone I, Zone II, annulus, and reflector.
-The initial multiplication factor during depletion calculation is selected for state with fully withdrawn control and poison rods position which gaves high excess reactivity in the beginning of the cycle (approximately 5000 pcm).
+The method approximate a single representative unit cell for the whole 
+\gls{MSBR} core, consequently, it does not take into consideration different 
+fuel-moderator volume ratio for Zone I, Zone II, annulus, and reflector. The 
+initial multiplication factor during depletion calculation is selected for 
+state with fully withdrawn control and poison rods position which gaves high 
+excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
 Standart deviation is about 100 pcm.
@@
         \includegraphics[width=1.03\linewidth]{keff.png}
-  \caption{Infinite multiplication factor during 4 years depletion simulation.}
+        \caption{Infinite multiplication factor during 4 years depletion 
+        simulation.}
         \vspace{-0.8em}
@@
 
-Figure~\ref{fig:keff} shows the infinite muliplication factor for 4-year reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data.
-The high standard deviation causes the multiplication factor fluctuations.
+Figure~\ref{fig:keff} shows the infinite muliplication factor for 4-year 
+reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. The 
+high standard deviation causes the multiplication factor fluctuations. 
 Protactinium-233 continuously removing into the tank for protactinium decay. 
-$^{233}$Pa has a half-life of 27 days and beta decays into $^{233}$U which as fresh fuel goes back to the reactor core.
-The infinite multiplication factor decreases first 400 days of depletion due to strong absorbers (e.g.
-$^{233}$Th, $^{234}$U) accumulation which causes relatively high fuel ($^{233}$U) refill inflow to keep reactor critical.
-During reactor operation producing fissile materials other than $^{233}$U in the core (e.g.
-$^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel refill rate after ~1 year of operation.
+$^{233}$Pa has a half-life of 27 days and beta decays into $^{233}$U which as 
+fresh fuel goes back to the reactor core. The infinite multiplication factor 
+decreases first 400 days of depletion due to strong absorbers (e.g. $^{233}$Th, 
+$^{234}$U) accumulation which causes relatively high fuel ($^{233}$U) refill 
+inflow to keep reactor critical. During reactor operation producing fissile 
+materials other than $^{233}$U in the core (e.g. $^{235}$U, $^{239}$Pu) which 
+makes it possible to decrease fresh fuel refill rate after ~1 year of 
+operation.
 
@@
         \includegraphics[width=1.03\linewidth]{fuel_composition.png}
-  \caption{Normalized number density of major isotopes during 4 years depletion.}
+        \caption{Normalized number density of major isotopes during 4 years 
+        depletion.}
         \label{fig:compos}
@@
 
-The analysis of the fuel salt composition variation gives clearer information about equilibrium core state.
-Figure~\ref{fig:compos} shows the normalized number density of important isotopes that have strong influence on the core neutronics at the beginning of each depletion time interval.
-The number density of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount of it produced during 3-days reprocessing step.
-It can be seen that the the multiplication factor reaches the equilibrium state at about 950  days.
-Figure~\ref{fig:rates} represents the rates of materials in online reprocessing flows during 4 years of depletion calculations.
+The analysis of the fuel salt composition variation gives clearer information 
+about equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
+number density of important isotopes that have strong influence on the core 
+neutronics at the beginning of each depletion time interval. The number density 
+of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
+of it produced during 3-days reprocessing step. It can be seen that the the 
+multiplication factor reaches the equilibrium state at about 950  days. 
+Figure~\ref{fig:rates} represents the rates of materials in online reprocessing 
+flows during 4 years of depletion calculations. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %  labelsep = newline,
-%  name = TABLE, 
-%  justification=justified,
+%  name = TABLE, justification=justified,
 %  singlelinecheck=false,%%%%%%% a single line is centered by default
@@
 %\end{tabular}
-%  \caption{Materials flows rates during \gls{MSBR} online reprocessing [1/s*cm$^3$].}
+%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
+%  [1/s*cm$^3$].}
 %  \label{tab:rates}
@@
 \end{figure}
-From the graph below we can see that to keep reactor critical higher $^{233}$U flow rate required for first 400 days of operation and after that much smaller uranium-233 flow rate from the protactinium decay tank needed.
-The $^{232}$Th rate slightly decreases over 4 years of operation due to other than $^{233}$U fissile materials accumulation.
+From the graph below we can see that to keep reactor critical higher $^{233}$U 
+flow rate required for first 400 days of operation and after that much smaller 
+uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th 
+rate slightly decreases over 4 years of operation due to other than $^{233}$U 
+fissile materials accumulation.
 
@@
         \includegraphics[width=1.03\linewidth]{rates_outflow.png}
-  \caption{Materials flows rates for the protactinium decay tank during \gls{MSBR} online reprocessing.}
+        \caption{Materials flows rates for the protactinium decay tank during 
+        \gls{MSBR} online reprocessing.}
         \vspace{-0.6em}
@@
 \end{figure}
-As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay accumulates $^{233}$Pa approximately 200 days and fresh fuel ($^{233}$U) flow established also after 200 days.
-Uranium produced in the tank by protactinium decay is separated by circulation of the salt through a flourinator.
-The fully processed molten salt, on its way back to the primary loop, has uranium added at the rate required to maintain or adjust the fissile material concentration and, hence, the reactivity, in the reactor core as desired.
+As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay 
+accumulates $^{233}$Pa approximately 200 days and fresh fuel ($^{233}$U) flow 
+established also after 200 days. Uranium produced in the tank by protactinium 
+decay is separated by circulation of the salt through a flourinator. The fully 
+processed molten salt, on its way back to the primary loop, has uranium added 
+at the rate required to maintain or adjust the fissile material concentration 
+and, hence, the reactivity, in the reactor core as desired.
 
@@
 
-Figure~\ref{fig:spectrum} represents the normalized neutron flux distribution of the initial and the equilibrium core compositions.
-The spectrum for the equilibrium state is harder than the initial state due to heavy fission products.
-\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+Figure~\ref{fig:spectrum} represents the normalized neutron flux distribution 
+of the initial and the equilibrium core compositions. The spectrum for the 
+equilibrium state is harder than the initial state due to heavy fission 
+products.  \begin{figure}[hb] % replace 't' with 'b' to force it to be on the 
+        bottom
         \centering
@@
         \vspace{-0.6em}
-  \caption{Normalized neutron energy spectrum for initial and equilibrium composition.}
+        \caption{Normalized neutron energy spectrum for initial and equilibrium 
+        composition.}
         \label{fig:spectrum}
@@
 
-In this work only Zone I unit cell with 0.132 volume fraction of fuel considered, neutron spectrum for Zone II cell where salt fraction is 37\% should be harder and the peak in thermal energy region predicted to be much lower.
-To obtain high fidelity neutron energy spectrum whole \gls{MSBR} core analysis is required.
+In this work only Zone I unit cell with 0.132 volume fraction of fuel 
+considered, neutron spectrum for Zone II cell where salt fraction is 37\% 
+should be harder and the peak in thermal energy region predicted to be much 
+lower. To obtain high fidelity neutron energy spectrum whole \gls{MSBR} core 
+analysis is required.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
-The depletion calculation of the \gls{MSBR} init cell model for finding the equilibrium states was performed using the Serepent 2 Monte Carlo code to simulate simplified case of the online reprocessing and refueling to find equilibrium material composition.
-When running depletion calculation, the fission products are removed and fertile/fissile materials are added to fuel salt every 3 days.
-The important MSR feature, online reprocessing I\& refueling is implemented in the Serpent 2 material burnup routine.
-The results of this study indicate that from the depletion calculation the multiplication factor slowly decreases and reaches to the equilibrium state.
-The most obvious finding to emerge from the analysis of initial and equilibrium materials composition is that neutron energy spectrum is harder for equilibrium state because significant amount of heavy fission products were accumulated in the \gls{MSBR} core.
+The depletion calculation of the \gls{MSBR} init cell model for finding the 
+equilibrium states was performed using the Serepent 2 Monte Carlo code to 
+simulate simplified case of the online reprocessing and refueling to find 
+equilibrium material composition. When running depletion calculation, the 
+fission products are removed and fertile/fissile materials are added to fuel 
+salt every 3 days. The important MSR feature, online reprocessing I\& refueling 
+is implemented in the Serpent 2 material burnup routine. The results of this 
+study indicate that from the depletion calculation the multiplication factor 
+slowly decreases and reaches to the equilibrium state. The most obvious finding 
+to emerge from the analysis of initial and equilibrium materials composition is 
+that neutron energy spectrum is harder for equilibrium state because 
+significant amount of heavy fission products were accumulated in the \gls{MSBR} 
+core.
 
-These results are contrary with those of Jeong and Park (2016) who suggested two different unit cell models and uses \gls{MCNP} with Python-script to simulate \gls{MSBR} online reprocessing to find equilibrium composition.
-This inconsistency may be due to different fuel fraction in the unit cell (Jeong and Park selected 20.6\% salt fraction).
-To obtain better results in online reprocessing simualtion number of future efforts expected.
-First, depletion simulation will be performed using full-core tree-dimensional high-fidelity model of \gls{MSBR} developed in Serpent 2.
-In this case, different fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, reflectors would be taken into account to find accurate multiplication factor, neutron spectrum and, hence, depleted composition.
-Secondly, additional Serpent 2 flow control system subroutine should be developed to simulate adjusting material flows (e.g.
-rate of removing $^{233}$Pa from the salt and adding fissile $^{233}$U from the tank for protactinium decay) depending upon current reactivity value which is more promising reactivity control method than moving control and safety rods.
-Finally, temperature effect of reactivity for both fuel salt and graphite should be calculated to find optimal effective multiplication factor range.
+These results are contrary with those of Jeong and Park (2016) who suggested 
+two different unit cell models and uses \gls{MCNP} with Python-script to 
+simulate \gls{MSBR} online reprocessing to find equilibrium composition. This 
+inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
+Park selected 20.6\% salt fraction). To obtain better results in online 
+reprocessing simualtion number of future efforts expected. First, depletion 
+simulation will be performed using full-core tree-dimensional high-fidelity 
+model of \gls{MSBR} developed in Serpent 2. In this case, different 
+fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 
+reflectors would be taken into account to find accurate multiplication factor, 
+neutron spectrum and, hence, depleted composition. Secondly, additional Serpent 
+2 flow control system subroutine should be developed to simulate adjusting 
+material flows (e.g. rate of removing $^{233}$Pa from the salt and adding 
+fissile $^{233}$U from the tank for protactinium decay) depending upon current 
+reactivity value which is more promising reactivity control method than moving 
+control and safety rods. Finally, temperature effect of reactivity for both 
+fuel salt and graphite should be calculated to find optimal effective 
+multiplication factor range.
 

### 2017-07-07 msbr_reproc.tex
spellcheck with vim's spellchecker

@@
 \section{Introduction}
-The thermal spectrum \gls{MSR} is an advanced type of reactor consisting of 
+The thermal spectrum \gls{MSR} is an advanced type of reactor that consists of 
 constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
-$LiF-BeF_2-ZrF_4-UF_4$) which also works as a coolant, and the reactor graphite 
-as moderator. This fuel form leads to immediate advantages over traditional, 
-solid-fueled, reactors. The molten-salt carrier salt with dissolved in it 
-fissile and/or fertile material allows to use online refuelling and 
-reprocessing, which means \gls{MSR}s can operate years without shutdown, 
-achieve maximum fuel utilization, and outstanding neutron economy 
+$LiF-BeF_2-ZrF_4-UF_4$) and solid graphite moderator structures. This liquid 
+fuel form leads to immediate advantages over traditional, 
+solid-fueled, reactors. The molten-salt carrier with dissolved 
+fissile and/or fertile material allows for online refuelling and 
+reprocessing. Thus, \gls{MSR}s can potentially operate years without shutdown, 
+achieving maximum fuel utilization and outstanding neutron economy 
 \cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
@@
 regards to economics. Additionally, it has high level of inherent safety due to 
-strong negative temeperature coefficient of reactivity, near-atmospheric 
+strong negative temperature coefficient of reactivity, near-atmospheric 
 pressure in the primary loop, stable coolant, passive decay heat cooling, and 
@@
 comparing to the traditional uranium fuel cycle, consequently, it might 
-significantly increase prolifiration resistance when \gls{MSR} operates in the 
+significantly increase proliferation resistance when \gls{MSR} operates in the 
 breeder regime. The \gls{MSR}s also could be employed as converter reactor for 
@@
 The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
-2 safety rods consisting of boron carbide clad. The undermoderated zone, Zone 
+2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
 II, with 37\% fuel salt, and radial reflector, surrounding the more active 
@@
 neutrons losses to protactinium and fission products to a very low level, and 
-increses the efficency of $^{233}$U breeding \cite{robertson_conceptual_1971}.
+increases the efficiency of $^{233}$U breeding \cite{robertson_conceptual_1971}.
 
@@
 specific removal rates. On the one hand, if the depletion time intervals are 
-very short it means specific isotope beign instantly removed, and it is hard to 
+very short it means specific isotope being instantly removed, and it is hard to 
 obtain equilibrium composition because enormous large number of depletion 
@@
 initial multiplication factor during depletion calculation is selected for 
-state with fully withdrawn control and poison rods position which gaves high 
+state with fully withdrawn control and poison rods position which gives high 
 excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
-Standart deviation is about 100 pcm.
+Standard deviation is about 100 pcm.
 
@@
 
-Figure~\ref{fig:keff} shows the infinite muliplication factor for 4-year 
+Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
 reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. The 
@@
 of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
-of it produced during 3-days reprocessing step. It can be seen that the the 
+of it produced during 3-days reprocessing step. It can be seen that the 
 multiplication factor reaches the equilibrium state at about 950  days. 
@@
 \section{Conclusions}
-The depletion calculation of the \gls{MSBR} init cell model for finding the 
-equilibrium states was performed using the Serepent 2 Monte Carlo code to 
+The depletion calculation of the \gls{MSBR} unit cell model for finding the 
+equilibrium states was performed using the Serpent 2 Monte Carlo code to 
 simulate simplified case of the online reprocessing and refueling to find 
@@
 Park selected 20.6\% salt fraction). To obtain better results in online 
-reprocessing simualtion number of future efforts expected. First, depletion 
+reprocessing simulation number of future efforts expected. First, depletion 
 simulation will be performed using full-core tree-dimensional high-fidelity 

### 2017-07-07 msbr_reproc.tex
I wasn't sure what 'one flow' meant
some grammar, also reducing the strength of some sentences

@@
 \cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
-fabrication and could be transported from enrichment plant to \gls{NPP} in form 
-of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with 
-regards to economics. Additionally, it has high level of inherent safety due to 
+complex fabrication since the fissile material could be transported from any 
+enrichment plant to the \gls{NPP} in the form 
+of uranium hexafluoride ($UF_6$).  Additionally, \glspl{MSR} have a high level 
+of inherent safety due to their characteristically 
 strong negative temperature coefficient of reactivity, near-atmospheric 
@@
 
-The \gls{MSBR} core consist of two different zones with one flow. The central 
+The \gls{MSBR} core consists of two different zones. The central 
 zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 

### 2017-07-07 msbr_reproc.tex
some acronym edits, uses glspl to get plural acronyms.

@@
 fissile and/or fertile material allows for online refuelling and 
-reprocessing. Thus, \gls{MSR}s can potentially operate years without shutdown, 
+reprocessing. Thus, \glspl{MSR} can potentially operate years without shutdown, 
 achieving maximum fuel utilization and outstanding neutron economy 
@@
 
-The thorium fueled \gls{MSBR} was developed in early 1970s by \gls{ORNL} 
+The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} 
 specifically to realize the promise of the thorium fuel cycle which allows the 
@@
 \cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
-thorium cycle produces much less amount of plutonium and minor actinides (MAs) 
-comparing to the traditional uranium fuel cycle, consequently, it might 
-significantly increase proliferation resistance when \gls{MSR} operates in the 
-breeder regime. The \gls{MSR}s also could be employed as converter reactor for 
+thorium cycle produces a reduced quantity of plutonium and \glspl{MA} 
+compared to the traditional uranium fuel cycle. Consequently, it may 
+significantly increase proliferation resistance when the \gls{MSR} operates in the 
+breeder regime. The \glspl{MSR} also could be employed as converter reactor for 
 transmutation spent fuel from \gls{LWR} or others.
@@
 online reprocessing and refueling. Most researchers investigating the 
-\gls{MSR}s have utilised for reprocessing calculations stochastic (i.e. 
+\glspl{MSR} have utilised for reprocessing calculations stochastic (i.e. 
 \gls{MCNP}) or deterministic (i.e. SCALE) code with originally-developed 

### 2017-07-07 msbr_reproc.tex
figure spacing too tight

@@
 significantly increase proliferation resistance when the \gls{MSR} operates in the 
-breeder regime. The \glspl{MSR} also could be employed as converter reactor for 
-transmutation spent fuel from \gls{LWR} or others.
+breeder regime. The \glspl{MSR} also could be employed as a converter reactor for 
+transmutation or spent fuel from current \glspl{LWR}.
 
-Nowadays, interest to \gls{MSR} coming back after long-term break because of 
-its unique characteristics and features of this type of reactor, such as online 
-reprocessing and refueling. For the development of \gls{MSR} conception special 
-computational analysis methods and codes needed due to completely different 
+Recently, interest in \glspl{MSR} is resurgent, with multiple new companies 
+pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 
+        liquid-fueled molten salt designs
+        from Transatomic, Terrapower, Terrestrial, and Thorcon.}
+To further develop these \gls{MSR} concepts, strategies for online reprocessing 
+and refueling special 
+computational analysis methods and codes are needed due to the unique completely different 
 physics of liquid-fueled nuclear reactor comparing with traditional, 
-solid-fueled, reactors. Most of the contemporary nuclear reactor physics codes 
+solid-fueled, reactors. 
+Most of the contemporary nuclear reactor physics codes 
 do not able to perform depletion calculations in the online reprocessing 
@@
         \centering
-        \vspace{-0.6em}
         \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
@@
 
-\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
         \centering
-        \vspace{-0.8em}
         \includegraphics[width=1.03\linewidth]{keff.png}
@@
         simulation.}
-        \vspace{-0.8em}
         \label{fig:keff}
 \end{figure}
+
+\FloatBarrier
 
@@
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
         \centering
-        \vspace{-0.8em}
         \includegraphics[width=1.03\linewidth]{fuel_composition.png}
@@
         \label{fig:compos}
-        \vspace{-0.8em}
 \end{figure}
+
+\FloatBarrier
 
@@
         \centering
-        \vspace{-0.8em}
         \includegraphics[width=1.03\linewidth]{rates_fuel.png}
@@
         \label{fig:rates}
-        \vspace{-0.8em}
 \end{figure}
@@
         \centering
-        \vspace{-0.8em}
         \includegraphics[width=1.03\linewidth]{rates_outflow.png}
@@
         \gls{MSBR} online reprocessing.}
-        \vspace{-0.6em}
         \label{fig:outflow}
-        \vspace{-0.8em}
 \end{figure}
@@
 equilibrium state is harder than the initial state due to heavy fission 
-products.  \begin{figure}[hb] % replace 't' with 'b' to force it to be on the 
-        bottom
+products.  
+\begin{figure}[hb!] % replace 't' with 'b' to force it to be on the bottom
         \centering
-        \vspace{-0.85em}
         \includegraphics[width=1.04\linewidth]{spectrum.png}
-        \vspace{-0.6em}
         \caption{Normalized neutron energy spectrum for initial and equilibrium 
@@
         \label{fig:spectrum}
-        \vspace{-0.10em}
 \end{figure}

### 2017-07-07 msbr_reproc.tex
mostly grammar

@@
 pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 
-        liquid-fueled molten salt designs
-        from Transatomic, Terrapower, Terrestrial, and Thorcon.}
-To further develop these \gls{MSR} concepts, strategies for online reprocessing 
-and refueling special 
-computational analysis methods and codes are needed due to the unique completely different 
-physics of liquid-fueled nuclear reactor comparing with traditional, 
-solid-fueled, reactors. 
-Most of the contemporary nuclear reactor physics codes 
-do not able to perform depletion calculations in the online reprocessing 
-regime. J.J. Powers (\gls{ORNL}) has suggested a novel method to conducting 
+liquid-fueled molten salt designs from Transatomic, Terrapower, Terrestrial, 
+and Thorcon.}.
+To further develop these \gls{MSR} concepts, particularly with respect to their  
+strategies for online reprocessing and refueling, advanced
+computational analysis methods capturing
+their unique reactor physics and process chemistry are needed.
+Most contemporary nuclear reactor physics software is unable
+to perform depletion calculations in an online reprocessing 
+regime. Powers \emph{et al.} suggested a novel method to conducting 
 depletion simulation for \gls{MSR} with taking into account the online 
 reprocessing and refueling based on the deterministic computer code NEWT in 
-SCALE \cite{powers_new_2013}. This approach was later used by Jeong et al. to 
-find equilibrium state for \gls{MSBR} and validate it with \gls{MCNP}/CINDER90 
-model \cite{jeong_equilibrium_2016}. For the development of \gls{MSBR} 
-research, this paper presents the single-cell model developed using a 
-continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code 
-that was employed to find equilibrium core state, and several calculation 
-results including the depletion calculation of the single-cell unit.
+SCALE \cite{powers_new_2013}. This approach was later used by Jeong \emph{et 
+al.} to find an equilibrium fuel composition for \gls{MSBR} and to validate it 
+with an \gls{MCNP}/CINDER90 
+model \cite{jeong_equilibrium_2016}.
 
+The current paper presents the single-cell model developed using the
+continuous-energy Serpent 2 Monte Carlo reactor physics software. It was 
+employed to find an equilibrium core composition and core depletion of the 
+single-cell unit. 
 All calculations presented in this paper were performed using the Serpent 2 
 code version 2.1.29 with ENDF/B-VII.0
-nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}. Compared 
-to Serpent 1, Serpent 2 has many more useful features and contains a complete 
-redesign of memory management using hybrid OpenMP + MPI parallelization, which 
-is important in depletion calculations using computer clusters with multiple 
-cores \cite{leppanen_serpent_2015}. This paper use build-in Serpent 2 depletion 
-capabilities with online reprocessing subroutine. Another feature of 
-\gls{MSBR}, circulating
-liquid fuel, which causes delayed neutron precursor drift is not treated here.
+nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}. Serpent 
+2 is an improvement upon Serpent 1, and contains a complete 
+redesign of memory management using hybrid OpenMP + MPI parallelization.  This 
+hybrid parallelization is important in depletion calculations using computer 
+clusters with multiple cores \cite{leppanen_serpent_2015}. This work used the 
+built-in Serpent 2 depletion capabilities and its built-in online reprocessing 
+subroutine. Another feature of the \gls{MSBR}, its circulating liquid fuel and 
+corresponding delayed neutron precursor drift, is not treated here.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
         \centering
@@
 
-\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
         \centering
@@
 products.  
-\begin{figure}[hb!] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
         \centering
@@
 \end{figure}
+
+\FloatBarrier
 

### 2017-07-09 msbr_reproc.tex
active voice

@@
 
-Recently, interest in \glspl{MSR} is resurgent, with multiple new companies 
+Recently, interest in \glspl{MSR} has resurged, with multiple new companies 
 pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 

### 2017-07-09 msbr_reproc.tex
minor grammar fix

@@
 To further develop these \gls{MSR} concepts, particularly with respect to their  
-strategies for online reprocessing and refueling, advanced
-computational analysis methods capturing
+strategies for online reprocessing and refueling, computational analysis methods capturing
 their unique reactor physics and process chemistry are needed.
-Most contemporary nuclear reactor physics software is unable
-to perform depletion calculations in an online reprocessing 
-regime. Powers \emph{et al.} suggested a novel method to conducting 
-depletion simulation for \gls{MSR} with taking into account the online 
+However, most contemporary nuclear reactor physics software is unable to 
+perform depletion calculations in an online reprocessing 
+regime. Powers \emph{et al.} suggested a novel method for conducting 
+depletion simulations for \gls{MSR}. This suggested method takes into account 
+fuel salt composition changes due to online 
 reprocessing and refueling based on the deterministic computer code NEWT in 
 SCALE \cite{powers_new_2013}. This approach was later used by Jeong \emph{et 
-al.} to find an equilibrium fuel composition for \gls{MSBR} and to validate it 
-with an \gls{MCNP}/CINDER90 
-model \cite{jeong_equilibrium_2016}.
+al.} to find an equilibrium fuel composition for the \gls{MSBR} and was 
+validated with an \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.
 

### 2017-07-09 msbr_reproc.tex
minor grammar fix

@@
 
-The current paper presents the single-cell model developed using the
+The current paper presents a single-cell model developed using the
 continuous-energy Serpent 2 Monte Carlo reactor physics software. It was 
-employed to find an equilibrium core composition and core depletion of the 
-single-cell unit. 
+employed to establish a Serpent-based method for finding the equilibrium core composition and 
+core depletion of the \gls{MSBR}.
 All calculations presented in this paper were performed using the Serpent 2 

### 2017-07-09 msbr_reproc.tex
adding articles, a

@@
 \section{Description of the actual work}
-The \gls{MSBR} is thermal spectrum reactor. The reactor vessel has diameter of 
+The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
 680 cm and a height of 610 cm and contains molten fluoride fuel-salt mixture 

### 2017-07-09 msbr_reproc.tex
minor formatting and grammar

@@
 The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
-680 cm and a height of 610 cm and contains molten fluoride fuel-salt mixture 
+$680 cm$ and a height of $610 cm$. It contains a molten fluoride fuel-salt mixture 
 which performs two functions: to generate heat in the moderated region and to 

### 2017-07-09 msbr_reproc.tex
reordering of wording and capturing more math in math mode.

@@
 been taken into account because even such a small amount of isotope with very 
-high absorption cross section might significantly affect on neutron flux energy 
-distribution and, consequently, on depletion calculation results. 
-Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters 
-\cite{robertson_conceptual_1971}.
+high absorption cross section can significantly impact the neutron flux energy 
+distribution and, consequently, depletion calculation results. 
+Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters used by 
+this model \cite{robertson_conceptual_1971}.
 
@@
 portion serves to diminish neutron leakage from the reactor core. In this work, 
-only Zone I element with the hole diameter of 3.42138 cm, and the molten-salt 
-fuel volume fraction is 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
-geometry of unit cell model. The boundary condition of the unit cell is 
-periodic. The density of fuel salt is 3.3304 g/cm$^3$ and graphite one is 1.843 
-g/cm$^3$. The temperature of fuel and graphite is fixed for the whole 
-reprocessing cycle at 908K \cite{robertson_conceptual_1971}.
+only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
+fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
+geometry of the unit cell model. The boundary condition of the unit cell is 
+periodic. The density of the fuel salt is $3.3304 \frac{g}{cm^3}$ and the graphite density is 
+$1.843 \frac{g}{cm^3}$. The temperature of fuel and graphite is fixed at 908K for the whole 
+reprocessing cycle\cite{robertson_conceptual_1971}.
 

### 2017-07-09 msbr_reproc.tex
rephrasing in online reprocessing method section

@@
 \include{acros}
+
+\usepackage{tabularx} % for nice wrapping of table text
 
@@
         %\centering
-        \begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
+        %\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
+        \begin{tabularx}{\linewidth}{l X} \toprule 
                 Thermal capacity of reactor           & 2250 MW(t)
@@
                 %\\ \midrule
-                Volume fraction of salt in central core zone     & 0.132
+                Salt volume fraction in central core zone     & 0.132
                 \\ \midrule
-                Volume fraction of salt in outer core zone       & 0.37
+                Salt volume fraction in outer core zone       & 0.37
                 \\ \midrule
@@
                 \bottomrule
-        \end{tabular}
+        \end{tabularx}
         \caption{Summary of principal data for MSBR.}
@@
 geometry of the unit cell model. The boundary condition of the unit cell is 
-periodic. The density of the fuel salt is $3.3304 \frac{g}{cm^3}$ and the graphite density is 
-$1.843 \frac{g}{cm^3}$. The temperature of fuel and graphite is fixed at 908K for the whole 
+periodic. The density of the fuel salt is $3.3304 g/cm^3$ and the graphite density is 
+$1.843 g/cm^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
 reprocessing cycle\cite{robertson_conceptual_1971}.
 
-\begin{figure}[h] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
         \centering
@@
 
+\FloatBarrier
 \subsection{Online reprocessing method}
 
-Currently, researchers usually using supporting tools and scripts to simulate 
-online reprocessing and refueling. Most researchers investigating the 
-\glspl{MSR} have utilised for reprocessing calculations stochastic (i.e. 
-\gls{MCNP}) or deterministic (i.e. SCALE) code with originally-developed 
-scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}. The 
-Serpent 2 is the first code supporting continuous material reprocessing, and 
-allows create needed number of material flows into the fuel and/or out from the 
-fuel.
+Currently, researchers 
+investigating the \glspl{MSR} 
+typically develop custom supporting tools and scripts to simulate 
+online reprocessing and refueling. Most utilize stochastic (i.e. 
+\gls{MCNP}) or deterministic (i.e. SCALE) methods for depletion and supplement 
+these with custom Python scripts to capture the impacts of reprocessing 
+\cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
+first commonly used monte carlo software to support continuous material 
+reprocessing. It does so by allowing the user to 
+create multiple material flows into and out of the fuel.
 

### 2017-07-09 msbr_reproc.tex
minor grammatical stuff

@@
 
-The \gls{MSBR} has the capability to remove every 20 seconds all poisons (e.g. 
-$^{135}$Xe), noble metals and gases (e.g. $^{75}$Se, $^{85}$Kr) which also have 
-relatively high absorption cross section. The thorium-232 absorbs thermal 
-neutrons and produce $^{233}$Pa which then decay into the fissile $^{233}$U. 
-The problem of protactinium is a large absorption cross section in the thermal 
-energy spectrum, therefore $^{233}$Pa continuously removing from fuel salt into 
-protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
+The \gls{MSBR} has the capability to remove all poisons
+(e.g. 
+$^{135}$Xe), noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) 
+every 20 seconds. The $^{232}$Th in the fuel absorbs thermal 
+neutrons and produces $^{233}$Pa which then decay into the fissile $^{233}$U. 
+Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
+energy spectrum. Accordingly, $^{233}$Pa is continuously removed from fuel salt 
+into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
 reactor poisoning. The reactor reprocessing system designed to separate 

### 2017-07-09 msbr_reproc.tex
rephrasing.

@@
 into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
-reactor poisoning. The reactor reprocessing system designed to separate 
-$^{233}$Pa from the molten-salt fuel over 3 days, held it to produce $^{233}$U 
-and return it back to the primary loop. This feature allows to keep the 
-neutrons losses to protactinium and fission products to a very low level, and 
+poisoning the reactor. The reactor reprocessing system is designed to separate 
+$^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa 
+decays into $^{233}$U 
+and return it back to the primary loop. This feature allows the reactor to 
+avoid neutron losses to protactinium, keeps fission products to a very low level, and 
 increases the efficiency of $^{233}$U breeding \cite{robertson_conceptual_1971}.

### 2017-07-10 msbr_reproc.tex

@@
 steps. On the other hand, if the depletion calculation time interval is too 
-long the results would not truly represents \gls{MSBR} conceptual design. 
+long the results would not truly represent the \gls{MSBR} conceptual design. 
 Following this idea, the time interval for depletion calculations was selected 
-3 days that correlate with the removal interval of $^{233}$Pa which is the 
-major isotope for producing $^{233}$U. Thorium is continuously adding to 
+as 3 days to correlate with the removal interval of $^{233}$Pa. Thorium is 
+continuously added to 
 maintain the initial mass fraction of $^{232}$ThF$_4$.

### 2017-07-20 msbr_reproc.tex
zone 1 rather than the first zone
minor rephrasing, adding data to table...

@@
                 %\\ \midrule
-                Salt volume fraction in central core zone     & 0.132
+                Vessel diameter                 & $680 [cm]$
                 \\ \midrule
-                Salt volume fraction in outer core zone       & 0.37
+                Vessel height                 & $610 [cm]$
                 \\ \midrule
-                Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
+                fuel-salt enrichment                 & $<++> [<++>]$
                 \\ \midrule
-                Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
+                <++>                 & $<++> [<++>]$
+                \\ \midrule
+                Central fuel channel (Zone I)                 & $3.42138 [cm]$
+                \\ \midrule
+                Salt volume fraction in central core zone     & $0.132$
+                \\ \midrule
+                Salt volume fraction in outer core zone       & $0.37$
+                \\ \midrule
+                Fuel-salt inventory (Zone I)                  & $8.2 [m^3]$	
+                \\ \midrule
+                Fuel-salt inventory (Zone II)                 & $10.8 [m^3]$	
                 \\ \midrule
@@
 zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
-The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
+Zone I is composed of 1320 graphite cells, 2 graphite control rods, and 
 2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
@@
 portion serves to diminish neutron leakage from the reactor core. In this work, 
-only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
-fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
+a Zone I element was considered. This element has a $3.42138 cm$ diameter 
+central fuel channel and a molten-salt 
+fuel volume fraction of 0.132. Figure~\ref{fig:zoneI} shows the 
 geometry of the unit cell model. The boundary condition of the unit cell is 
@@
 as 3 days to correlate with the removal interval of $^{233}$Pa. Thorium is 
-continuously added to 
-maintain the initial mass fraction of $^{232}$ThF$_4$.
+continuously added to maintain the initial mass fraction of $^{232}$ThF$_4$.
 

### 2017-07-25 discussion.tex
ANS revisions

@@
 reprocessing and \gls{MOX} fabrication capacities,
-France can transition into a fully \gls{SFR} fleet
+France, by receiving \gls{UNF} from other \gls{EU} nations,
+can transition into a full \gls{SFR} fleet
 with installed capacity of 60,000 MWe by 2076.
 The initial fuel demand is filled by \gls{MOX} from
-reprocessed \gls{SNF}, which later on
-is met by \gls{MOX} created from recycled \gls{MOX}.
+reprocessed \gls{UNF}, which later on
+will be met by \gls{MOX} created from recycled \gls{MOX}.
 
-Since most \gls{EU} nations do not have an operating \gls{SNF}
+Since most \gls{EU} nations do not have an operating \gls{UNF}
 repository or a management plan, they have a strong incentive
-to send all their \gls{SNF} to France. France has a financial
-incentive (compensation from other nations) to take this fuel,
-and since reuse of spent fuel from
+to send all their \gls{UNF} to France. Especially, the nations
+with aggressive nuclear reduction can phase out nuclear
+without constructing a High Level Waste repository. France has a financial
+incentive to take this fuel, since reuse of used fuel from
 other nations will allow France to meet their MOX demand

### 2017-07-25 introduction.tex
ANS revisions

--- 2017-06-24 introduction.tex
@@
 The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
-\cite{cne2_noauthor_2015} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
-This paper uses \Cyclus to explore the feasibility of using \gls{SNF}from other EU nations
+\cite{noauthor_cne2_nodate} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
+This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
 for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
-A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{SNF} mass
+A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{UNF} mass
 and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
 the transition into \glspl{SFR}. The study concludes that France can avoid deployment
-of additional \glspl{LWR} by accepting \gls{SNF} from other EU nations.
+of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.
 
@@
 This paper uses \Cyclus, the agent-based simulator \cite{huff_fundamental_2016} to analyze
-the future nuclear inventory in the European Union. This paper focuses on the spent fuel
-inventory in \gls{EU} member states in 2050, and analyzes various potential strategies of spent fuel
+the future nuclear inventory in the European Union. This paper focuses on the used fuel
+inventory in \gls{EU} member states in 2050, and analyzes a potential strategy of used fuel
 management.
 A major focus of this paper is to determine the extent to which France has an incentive
-to receive all the \gls{SNF} from \gls{EU} nations to create \gls{MOX}.
+to receive all the \gls{UNF} from \gls{EU} nations to create \gls{MOX}.
 The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
@@
 
-Past research, which focuses mostly on France, has made the assumptions that additional \glspl{LWR},
-namely \glspl{EPR} are constructed in order to supply \gls{SNF} required
-for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2007, freynet_multiobjective_2016}.
-There has been little attention in reprocessing legacy \gls{SNF} from other
+Past research, which focuses solely on France, has made the assumptions that additional \glspl{LWR},
+namely \glspl{EPR} are constructed in order to supply \gls{UNF} required
+for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
+There has been studies on implementation of partitioning and transmutation
+in a regional (European) context, with \glspl{ADS} and Gen-IV reactors \cite{fazio_study_2013}.
+There has been little attention in reprocessing legacy \gls{UNF} from other
 EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
@@
 need to construct additional \glspl{LWR} in France.
-
-A \Cyclus simulation is run to calculate
-how much spent fuel is created from \gls{EU} nations from 1970 to 2050, as well as the amount
-of \gls{MOX} that can be created with the \gls{SNF} inventory.
-The paper assumes a once-through cycle for all 
-\gls{EU} nations with the exception of France. France can reprocess spent \gls{UOX} and \gls{MOX} to
-produce \gls{MOX} from reprocessed plutonium and depleted uranium (tails).
-The simulation assumes \gls{MOX} is reprocessed infinitely. 
-After obtaining the \gls{SNF} inventory of all \gls{EU} in 2050, a separate
-simulation is run where the \gls{SNF} inventory is reprocessed and
-used as fuel for the newly deployed \gls{SFR} reactors.
-\gls{SFR} reactors in this paper models after the ASTRID reactor,
-and use \gls{MOX} fuel created from 9\% reprocessed plutonium
-and 91\% tailings to a burnup
-of approximately 100 GWdth/t. The high burnup allows enough production of plutonium
-for an equivalent mass of \gls{MOX}, if mixed with tailings.  Eventually,
-the used \gls{UOX} inventory will be exhausted, and the \glspl{SFR} must be
-fueled by \gls{MOX} created from recycled \gls{MOX}.
-It is assumed that \glspl{SFR} are available for deployment
-from 2040.
 
@@
 which lists the individual reactor units as agents. After running the \Cyclus input file,
-the output file is analyzed by another python script.
+the output file is analyzed by another python script. All the scrips and data used
+in this paper are available in \url{https://github.com/jbae11/transition-scenarios}.
 
-First, a simulation is run from 1970 to 2050 to calculate the mass of 
-\gls{SNF} and depleted uranium (tails) \gls{EU} accumulates before 2050. 
-The second simulation only looks at France, where France
-uses the entire \gls{SNF} inventory from the previous
-simulation to fuel
-the newly deployed \glspl{SFR}. French \gls{SFR}s are deployed
-to make up for the decommissioned capacity of \gls{LWR}s, to
-remain a constant installed capacity of 60,000 MWe.
+Two \Cyclus simulations are run for this paper. 
+The first simulation calculates
+how much used fuel and tailings \gls{EU} nations accumulate from 1970 to 2050,
+as well as the amount of \gls{MOX} that can be created with the \gls{UNF} inventory.
+The paper models a once-through cycle for all 
+\gls{EU} nations with the exception of France. France can reprocess used \gls{UOX} and \gls{MOX} to
+produce \gls{MOX} from reprocessed plutonium and depleted uranium (tailings).
+The simulation assumes \gls{MOX} is reprocessed infinitely.
+
+After obtaining the \gls{UNF} inventory of all \gls{EU} in 2050, the second
+simulation is run where the \gls{UNF} inventory is reprocessed and
+used as fuel for the newly deployed \gls{SFR} reactors.
+The \glspl{SFR} are deployed to make up for the decommissioned capacity
+of \glspl{LWR} in France, to remain a constant installed capacity of $60,000$ MWe up to 2160.
+\gls{SFR} reactors in this paper models after the ASTRID reactor,
+and use \gls{MOX} fuel created from 11\% reprocessed plutonium
+and 89\% tailings to a burnup
+of approximately 100 GWdth/t. The high burnup allows breeding of plutonium.
+Eventually, the entire fleet
+of \glspl{SFR} are fueled by \gls{MOX} created from recycled \gls{MOX}.
 
@@
 \begin{itemize}
-        \item \gls{SFR} technology available in 2040
+	\item \gls{SFR} technology available for deployment in 2040
 	\item Decay has no effect on reprocessing viability
 	\item Reactor construction is always completed on time 
-        \item Unused separated uranium is stockpiled
-        \item Nuclear power plants have a lifetime of 60 years, unless stated otherwise (early shutdown)
+	\item Separated uranium is stockpiled
+	\item \glspl{LWR} have a lifetime of 60 years, unless stated otherwise (early shutdown)
+	\item Newly deployed \glspl{SFR} have a lifetime of 80 years.
+	\item (Only for SFR Case) Reprocessing and \gls{MOX} fabrication begins in 2020.
 	\item (Only for SFR Case) French nuclear capacity remains constant at 60,000 MWe
@@
 assessed based on analysis from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
-and the World Nuclear Association and two other papers for future plans in EU nations
+the World Nuclear Association and two other papers for future plans in EU nations
 \cite{world_nuclear_association_nuclear_2017, joskow_future_2012, hatch_politics_2015}.
@@
 currently operating have a lifetime of 60 years, unless their government plans
-early shutdown. This will approximate when and how much \glspl{SFR} need to be built
+early shutdown. This will approximate when and how many \glspl{SFR} need to be built
 to make up for the shutdown of \glspl{LWR}.
@@
 600-MWe \gls{SFR}s are deployed to make up for the 
-decommissioned \gls{LWR} capacities.
+decommissioned \gls{LWR} capacities. Note that a second
+separate simulation is run to emphasize France apart from
+all other EU nations.
 
@@
 	\begin{center}
-                \includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
-        \end{center}
-        \caption{Timeseries of installed capacity of \gls{SFR}s}
-        \label{fig:sfr_cap}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[htbp!]
-        \begin{center}
 		\includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
 	\end{center}
-        \caption{Timeseries of number of \gls{SFR}s}
+	\caption{French Transition into an SFR Fleet}
 	\label{fig:sfr_num}
@@
 
-\Cref{fig:sfr_cap} and \cref{fig:sfr_num} display
-the \gls{SFR} number and capacity over time.
-The sharp increase from 2035 to 2060 is due mainly to
-French aggressive growth from 1975 to 2000.
+\Cref{fig:sfr_num} displays
+the French transition into \glspl{SFR} over time.
+The steep transition from 2035 to 2060 is due mainly to
+French aggressive growth from 1975 to 2000. Note the jump in
+2040 is due to an attempt to make up for the gap between the
+mass decommission of old \glspl{LWR} and the availability
+of \glspl{SFR}.
 
@@
 Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
-and spent fuel recipe is used for each reactor type. To capture varying reactor 
-capacity, a linear burnup model was assumed and extrapolated from the 
-appropriate recipe. For example, a PWR of
-1,000 MWe capacity has 193 assemblies of 3.2\% enriched
-uranium fuel, with each assembly with a mass of 523.4 kg.
-The core has a 18 month cycle, where one-third of the 
-core (64 assemblies) are discharged per refueling. The refueling
-is assumed to take 2 months to complete, during which the reactor
-is shut down. For the \gls{SFR}, a model design is adopted from
-Marsault–Marie-Sophie et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}.
-
+and used fuel recipe is used for each reactor type.
 For the compositions of the fuel, a reference depletion calculation
-from ORIGEN is used (see appendix). The recipe has also been used for
+from ORIGEN is used (see \cref{tab:comp}). The recipe has also been used for
 \cite{wilson_adoption_2009}.
@@
 provides natural uranium, which is enriched by an 'enrichment'
-facility to \gls{UOX}, while disposing enrichment waste (tailings)
+facility to produce \gls{UOX}, while disposing enrichment waste (tailings)
 to the 'sink' facility. The enriched \gls{UOX} is used
-in the \gls{LWR}s and \gls{UOX} waste is produced. The spent fuel
+in the \gls{LWR}s and \gls{UOX} waste is produced. The used fuel
 is then reprocessed to separate plutonium and uranium.
-The plutonium is mixed with depleted uranium (tails) to \gls{MOX}.
-The reprocessed uranium is stockpiled. \gls{SNF} decay is assumed
-to have no effect on reprocessing viability.
+The plutonium is mixed with depleted uranium (tailings) to \gls{MOX}.
+The reprocessed uranium is stockpiled. The cycle is illustrated in
+\cref{diag:fc}.
 
-The second scenario estimates the \gls{SNF} inventory in \gls{EU} at 2050,
-and reprocesses the \gls{SNF} to separate plutonium. The separated
-plutonium is mixed with the depleted uranium inventory from 2050
+The second scenario separates plutonium from the \gls{UNF}
+inventory from the previous simulation. The separated
+plutonium is mixed with the depleted uranium inventory from the previous simulation
 to create \gls{MOX}, which is used in the \gls{SFR}s. The used
-\gls{MOX} is also reprocessed to extract plutonium, which also
-is mixed with depleted uranium to produce \gls{MOX}.
+\gls{MOX} is also reprocessed to extract plutonium, which is also
+mixed with depleted uranium to produce \gls{MOX}.

### 2017-07-25 results.tex
ANS revisions

@@
 	\centering
-	\scalebox{0.86}{
-		\begin{tabular}{|c|c|c|}
+	\scalebox{0.7}{
+		\begin{tabular}{|c|c|c|c|}
 			\hline
-			Category  & Value [t] & Specifics \\ \hline
-			Total Natural U & 1,314,003 & \\ \hline
-			Total UOX Usage  & 188,196  &  \\ \hline
-			Total MOX Usage  & 118 & \\ \hline
-			Total Spent UOX  & 183,992 & \\ \hline
-			Total Spent MOX  & 0 & All is Reprocessed. \\ \hline
-			Total Tailings  & 1,125,798 & \\ \hline
+			Category & Unit & Value & Specifics\\ \hline
+			Total UOX Usage & MTHM & 178,865 &  \\ \hline
+			Total MOX Usage & MTHM & 8,909 & \\ \hline
+			Total Used UOX Stored & MTHM & 157,472 & \gls{UNF} that are not reprocessed\\ \hline
+			Total Used  MOX Stored & MTHM & 679 & \gls{UNF} that are not reprocessed \\ \hline
+			Total Tailings & MTHM & 1,063,909 & \\ \hline
+			Total Natural U Used & MTHM & 1,251,658 & \\ \hline
 		\end{tabular}}
-		\caption{Simulation Results}
+		\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
 		\label{tab:sim_result}
@@
 		values are the \gls{EU} inventory and history at year 2050.
+
+		Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
+		timeseries of number of reactors and installed capacity in \gls{EU} nations.
 
@@
 		\end{figure}
-
-Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
-timeseries of number of reactors and installed capacity in \gls{EU}.
+		\FloatBarrier
 
 		Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
-timeseries of mass of tailings and spent fuel accumulation in \gls{EU}.
+		timeseries of mass of tailings and used fuel accumulation in \gls{EU}.
+
+		Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.
 
@@
 			\end{center}
-	\caption{Timeseries of Tailings in the \gls{EU}.}
+			\caption{Timeseries of Tailings Mass in the \gls{EU}.}
 			\label{fig:eu_tail}
+		\end{figure}
+
+		\begin{figure}[htbp!]
+			\begin{center}
+				\includegraphics[width=\columnwidth]{./images/eu_future/total_fuel.png}
+			\end{center}
+			\caption{Timeseries of Total Fuel Usage in \gls{EU}.}
+			\label{fig:eu_fuel}
 		\end{figure}
@@
 			\end{center}
-	\caption{Timeseries of Spent Nuclear Fuel in Sink.}
+			\caption{Timeseries of Used Nuclear Fuel in \gls{EU}.}
 			\label{fig:eu_snf}
 		\end{figure}
+		\FloatBarrier
 
@@
 				\hline
-		Isotope & Mass Fraction in Spent Fuel [\%] & Quantity [t] \\ \hline
-		Total & .9358 & 1,721.79 \\ \hline
-		Pu238 & .0111 & 20.42 \\ \hline
-		Pu239 & .518 & 953.07 \\ \hline
-		Pu240 & .232 & 426.86 \\ \hline
-		Pu241 & .126 & 231.82 \\ \hline
-		Pu242 & .0487 & 89.6 \\ \hline
+				Isotope & Mass Fraction in Used Fuel [\%] & Quantity [t] \\ \hline
+				Total & .9358 & 1,473 \\ \hline
+				Pu238 & .0111 & 17.47 \\ \hline
+				Pu239 & .518 & 815.7 \\ \hline
+				Pu240 & .232 & 365.33 \\ \hline
+				Pu241 & .126 & 198.41 \\ \hline
+				Pu242 & .0487 & 76.68 \\ \hline
 			\end{tabular}
-	\caption{Plutonium From Spent Fuel}
+			\caption{Plutonium From Used Fuel}
 			\label{tab:pu}
@@
 
-To create \gls{MOX}, ~9\% Pu and ~91\% depleted uranium is used.
-Thus $1,721$ tons of plutonium yields $19,122$ tons of
+		To create \gls{MOX} for an ASTRID, 11\% Pu and 89\% depleted uranium is used.
+		Thus $1,473$ tons of plutonium yields $13,390$ tons of
 		\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
-and quantity of plutonium that can be obtained from the 2050 \gls{SNF} inventory.
+		and quantity of plutonium that can be obtained from the 2050 \gls{UNF} inventory.
 
@@
 
-From Varaine et al., a French
-ASTRID-type \gls{SFR} of capacity $600 MWe$ needs $1.225$ tons of
-plutonium a year, with an initial plutonium loading of $4.9$ tons
-\cite{marsaultmarie-sophie_pre-conceptual_2012}.
-Thus, it can be assumed that the ASTRID reactor takes in $49$ tons of 
-\gls{MOX}, and refuels a quarter of its fuel every year. Simply,
-an ASTRID reactor needs $12.25$ tons of \gls{MOX} per year.
+		From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
+		ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
+		plutonium a year, with an initial plutonium loading of $4.9$ tons. 
+		Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
+		plutonium from \gls{UNF} can be estimated to $\frac{1,473}{4.9} \approx 300$ \glspl{SFR},
+		assuming infinite reprocessing and fabrication capacity as well as
+		abundant depleted uranium supply.
 
-The number of SFR-years worth of fuel that can be created with
-the \gls{SNF} from 2050 is $\frac{19,122t}{12.25} = 1,560 $,
-assuming infinite reprocessing and \gls{MOX} fabrication capacity.
+		Also, assuming that \gls{MOX} can be recycled indefinitely,
+		used \gls{MOX} from an ASTRID reactor
+		contains enough plutonium to produce a \gls{MOX} fuel with
+		the same mass, if mixed with depleted uranium. For example,
+		used \gls{MOX} from an ASTRID reactor is assumed to be 12.6\% plutonium
+		in this simulation (see \cref{tab:comp}), whereas a fresh \gls{MOX} is 11\% plutonium.
+		Separating plutonium from used \gls{MOX} from
+		an ASTRID reactor can create \gls{MOX} of the mass of used \gls{MOX}.
+		The plutonium breeding ratio in this simulation is thus assumed to be
+		$\approx 1.145$.
 
-However, assuming that \gls{MOX} can be recycled indefinitely,
-spent \gls{MOX} from an ASTRID reactor
-contains enough plutonium to produce a \gls{MOX} fuel with
-the same mass, if mixed with depleted uranium. 
-Separating plutonium from spent \gls{MOX} from
-an ASTRID reactor can create \gls{MOX} 
-the mass of spent \gls{MOX}, given sufficient tailings supply.
-
-The second scenario, with the tails and spent \gls{UOX}
+		The second scenario, with the tailings and used \gls{UOX}
 		inventory, evaluates if the French can transition into \gls{SFR}
@@
 
-\Cref{fig:fuel} shows the mass of \gls{MOX} used in the 
-\gls{SFR}s separated by how they are made, over time.
-Note that the mass of \gls{MOX} from the spent \gls{UOX}
-stops increasing around 2050, which means that the spent
-\gls{MOX} is enough to create the \gls{MOX} for the
-\gls{SFR} fleet.
+		\Cref{fig:fuel} shows the timeseries mass of \gls{MOX} used in the 
+		\gls{SFR}s separated by their origin.
+		Note that the plot shows \gls{MOX}
+		accumulation prior to \gls{SFR} deployment from 2020.
 
@@
 
-\Cref{fig:pu_demand} shows the separated plutonium demand
-for \gls{MOX} production to fuel the ASTRID reactors given the deployment schedule.
+		\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
+		(minor actinides, fission products) over time. Note that 
+		reprocessing waste from \gls{UOX} reprocessing is substantially
+		greater than waste from \gls{MOX} reprocessing due to its lower
+		plutonium and uranium content.
+
+		\Cref{fig:pu_isotopics} shows the isotopics of the plutonium that are
+		reprocessed from the used fuel inventory.
 
@@
 			\begin{center}
-		\includegraphics[width=\columnwidth]{./images/french-transition/pu_total_demand.png}
+				\includegraphics[width=\columnwidth]{./images/french-transition/rep_pu.png}
 			\end{center}
-	\caption{Separated Plutonium demand for \gls{MOX} production}
-	\label{fig:pu_demand}
+			\caption{Plutonium timeseries separated by isotope}
+			\label{fig:pu_isotopics}
+		\end{figure}
+
+		\begin{figure}[htbp!]
+			\begin{center}
+				\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
+			\end{center}
+			\caption{Reprocessing Waste for French Transition Scenario.}
+			\label{fig:reprocess_waste}
 		\end{figure}
@@
 			\centering
-	\scalebox{0.86}{
+			\scalebox{0.7}{
 				\begin{tabular}{|c|c|c|}
 					\hline
-			Category [unit] & Value & Specifics \\ \hline
-			Total MOX used [t] & 164,141 & \\ \hline
-			Total MOX from UOX Waste [t] & 19,136.2  &   \\ \hline
-			Total MOX from MOX Waste [t] & 145,004.8 & \\ \hline
-			Total Tailings used [t] & 149,368.3 & \\ \hline
-			Total legacy SNF reprocessed [t] & 183,992 & \\ \hline
+					Category & Unit & Value  \\ \hline
+					Total MOX used & MTHM & 116,115  \\ \hline
+					Total \glspl{SFR} Deployed & & 200 \\ \hline
+					Total Plutonium Reprocessed & MTHM & 14,414 \\ \hline
+					Total MOX from UOX Waste & MTHM & 9,729  \\ \hline
+					Total MOX from MOX Waste & MTHM  & 150,426  \\ \hline
+					Total Tailings used & MTHM & 105,664 \\ \hline
+					Total legacy UNF reprocessed & MTHM & 97,298 \\ \hline
+					Total Reprocessed Uranium Stockpile & MTHM & 251,100 \\ \hline
+					Total Reprocess Waste & MTHM & 14,414 \\ \hline
 				\end{tabular}}

### 2017-07-27 Moltres.tex
Introduce comparison with MSRE, 3d results, scaling study.

--- 2017-05-11 Moltres.tex
@@
 \usepackage{minted}
+\usepackage{ifthen}
+%% \usepackage{listings}  % Allows code printing
+%% \definecolor{codegreen}{rgb}{0,0.6,0}
+%% \definecolor{codegray}{rgb}{0.5,0.5,0.5}
+%% \definecolor{codepurple}{rgb}{0.58,0,0.82}
+%% \definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+%% \lstdefinestyle{mystyle}{
+%%     backgroundcolor=\color{backcolour},
+%%     commentstyle=\color{codegreen},
+%%     keywordstyle=\color{magenta},
+%%     numberstyle=\tiny\color{codegray},
+%%     stringstyle=\color{codepurple},
+%%     basicstyle=\footnotesize,
+%%     breakatwhitespace=false,
+%%     breaklines=true,
+%%     captionpos=b,
+%%     keepspaces=true,
+%%     numbers=left,
+%%     numbersep=5pt,
+%%     showspaces=false,
+%%     showstringspaces=false,
+%%     showtabs=false,
+%%     tabsize=2
+%% }
+%% \lstset{style=mystyle}
 
@@
 \newcommand{\code}[1]{\texttt{#1}}
+\makeatletter
+\def\maxwidth#1{\ifdim\Gin@nat@width>#1 #1\else\Gin@nat@width\fi}
+\makeatother
 
@@
 Group constants are generated by the modeler with either Serpent
-\cite{leppanen_serpent_2015} or Scale \cite{dehart_reactor_2011}. Group constant
+\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Group constant
 temperature dependence is implemented via interpolation tables, which must be
-constructed separately for fuel and moderator regions.
+constructed separately for fuel and moderator regions. For this report,
+SCALE-generated group constants were used. To generate the group constants, an
+infinite square pitch lattice of cylindrical fuel channels surrounded by
+graphite was used, maintaining a fuel fraction of .225 to be consistent with the
+\gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
+input files used for generating the group constants can be found in the
+\code{io/msre\_conc\_cuboid\_lattice} directory of the
+\url{github.com/arfc/scale_io} repository.
 
@@
 
-\begin{figure}
+\begin{figure}[htpb]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[htpb]
   \centering
-  \includegraphics{auto_diff_rho_group1.eps}
+  \includegraphics{2d_gamma_heating_group1.eps}
         \caption{The group 1 flux in this 2-D cylindrical axisymmetric model
@@
 
-\begin{figure}
+\begin{figure}[htpb]
   \centering
-  \includegraphics{auto_diff_rho_group2.eps}
+  \includegraphics{2d_gamma_heating_group2.eps}
         \caption{The group 2 flux in this 2-D cylindrical axisymmetric model
@@
 
-\begin{figure}
+\begin{figure}[htpb]
   \centering
-  \includegraphics{auto_diff_rho_temp.eps}
+  \includegraphics{2d_gamma_heating_temp.eps}
         \caption{The reactor core temperature peaks near the reactor outlet in
           this 2-D axisymmetric model because of fuel advection ($r=0$ is center
-          of core).}
+          of core). Because of heating by gammas and other radiation the
+          moderator regions are hotter than the fuel, consistent with
+          observations of the \gls{MSRE}}
   \label{fig:temp}
@@
 % Fix me! Precursor concentrations have goofy scaling
-\begin{figure}
+\begin{figure}[htpb]
   \centering
-  \includegraphics{auto_diff_rho_pre1.eps}
+  \includegraphics{2d_gamma_heating_pre1.eps}
         \caption{The concentration of the group of longest lived precursors
@@
 % Fix me! Precursor concentrations have goofy scaling
-\begin{figure}
+\begin{figure}[htpb]
   \centering
-  \includegraphics{auto_diff_rho_pre6.eps}
+  \includegraphics{2d_gamma_heating_pre6.eps}
         \caption{The concentration of the group of shortest lived precursors
@@
   \label{fig:pre6}
+\end{figure}
+
+\subsection{3D}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{3d_gamma_heating_group1.eps}
+        \caption{Fast flux for 3D \gls{MSRE}-like model. Magnitude and shape in
+          good agreement with 2D axisymmetric model (see \cref{fig:group1})}
+  \label{fig:3d_group1}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{3d_gamma_heating_temp.eps}
+        \caption{Temperature for 3D \gls{MSRE}-like model. Magnitude and shape in
+          good agreement with 2D axisymmetric model (see \cref{fig:temp})}
+  \label{fig:3d_temp}
+\end{figure}
+
+\subsection{Comparison with \gls{MSRE}}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{fuel_vs_moderator_axial_sweep.eps}
+        \caption{Moltres predicted axial temperature profiles near r = 0}
+  \label{fig:moltres_axial_temps}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{msre_axial_temps.png}
+        \caption{\gls{MSRE} design axial temperature profiles near r = 0}
+  \label{fig:msre_axial_temps}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=\maxwidth{\textwidth}]{fast_vs_thermal_nt_flux_msre.png}
+  \caption{\gls{MSRE} design radial temperature profiles at reactor mid-plane}
+  \label{fig:msre_radial_temps}
+\end{figure}
+
+\subsection{Scaling study}
+
+As described earlier, Moltres runs naturally in parallel. To test its
+performance, a scaling study was conducted using a typical 2D axisymmetric input
+file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
+time follows very closely to the ideal; slight deviations are expected due to
+the expense of communication and the nature of iterative solvers. More
+parallelism means more ``older'' information is used in the solution process,
+which leads to slower convergence in terms of iterations \cite{satish_balay_petsc_2015}.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{scaling_study.eps}
+  \caption{Moltres performance on a typical 2D axisymmetric problem for
+    different numbers of processors}
+  \label{fig:scaling_study}
 \end{figure}

### 2017-07-27 Moltres.tex
Correct precursor scaling.
Begin MSRE comparison.

@@
 \usepackage{ifthen}
+\usepackage{subcaption}
 %% \usepackage{listings}  % Allows code printing
@@
 to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some
-three-dimensional simulations (results not discussed here), the number of
+three-dimensional simulations, the number of
 elements in the mesh and total number of degrees of freedom exceed one million
@@
 
-As a proof of concept and to ease resolution of strong transient gradients in
-temperature between fuel and moderator, the physical three dimensional problem
-is reduced to a two dimensional axisymmetric model. The model molten salt
-reactor is based on the \gls{MSRE}. To approximately simulate the lattice
-structure of the \gls{MSRE}, a geometry is constructed with 14 repeating
+The model molten salt
+reactor is based on the \gls{MSRE}. When developing new physics or investigating
+different types of transients, the model problem can be reduced to a two
+dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
+structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
 fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
@@
 larger fast flux magnitude is attributable to using \gls{BOL} fuel
-composition. As the fuel salt reaches an equilibrium composition, the thermal
-flux is expected to exceed that of the fast group.
+composition. As the fuel salt reaches an equilibrium composition, the fast to
+thermal flux ratio is expected to decrease.
 
@@
 
-% Fix me! Precursor concentrations have goofy scaling
 \begin{figure}[htpb]
   \centering
-  \includegraphics{2d_gamma_heating_pre1.eps}
+  \includegraphics{2d_gamma_heating_pre1_scaled.eps}
         \caption{The concentration of the group of longest lived precursors
@@
 
-% Fix me! Precursor concentrations have goofy scaling
 \begin{figure}[htpb]
   \centering
-  \includegraphics{2d_gamma_heating_pre6.eps}
+  \includegraphics{2d_gamma_heating_pre6_scaled.eps}
         \caption{The concentration of the group of shortest lived precursors
@@
 
-\subsection{3D}
+\subsection{Three dimensional simulation capability}
+
+\Cref{fig:3d_group1,fig:3d_temp} show Moltres physics applied to a three
+dimensional geometry. The fast group flux (\cref{fig:3d_group1}) is in good
+qualitative agreement with the two dimensional axisymmetric case shown in
+\cref{fig:group1}. \Cref{fig:3d_temp} is in similarly good agreement with
+\cref{fig:temp}. \Cref{fig:3d_temp_fuel_outlet} shows the temperature profile at
+the outlet of the reactor (z = H). This three dimensional case contained
+1,155,045 degrees of freedom and took only 2.5 hours to solve on 160 Blue Waters
+cores.
 
@@
 
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{3d_gamma_heating_z_slice_temp.eps}
+        \caption{Temperature at the reactor outlet for 3D \gls{MSRE}-like
+          model.}
+  \label{fig:3d_temp_fuel_outlet}
+\end{figure}
+
 \subsection{Comparison with \gls{MSRE}}
+
+\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
+profiles with cosinusoidal gamma heating and \gls{MSRE} design models
+\cite{briggs_molten-salt_1964} along the reactor center-line (r = 0).
 
@@
     \centering
-  \includegraphics{fuel_vs_moderator_axial_sweep.eps}
+    \begin{subfigure}[b]{.5\textwidth}
+      \includegraphics[width=\maxwidth{\textwidth}]{fuel_vs_moderator_axial_sweep.eps}
       \caption{Moltres predicted axial temperature profiles near r = 0}
       \label{fig:moltres_axial_temps}
+    \end{subfigure}
+    %\quad
+    \begin{subfigure}[b]{.5\textwidth}
+      \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_temps.png}
+      \caption{\gls{MSRE} design axial temperature profiles near r = 0
+        \cite{briggs_molten-salt_1964}}
+      \label{fig:msre_axial_temps}
+    \end{subfigure}
+    \caption{Comparison of \gls{MSRE} design and Moltres predicted axial
+      temperature profiles}
+    \label{fig:temp_compare}
 \end{figure}
@@
   \centering
-  \includegraphics{msre_axial_temps.png}
-        \caption{\gls{MSRE} design axial temperature profiles near r = 0}
-  \label{fig:msre_axial_temps}
+  \includegraphics[width=\maxwidth{\textwidth}]{msre_radial_fluxes.png}
+  \caption{\gls{MSRE} design radial flux profiles at reactor mid-plane
+    \cite{briggs_molten-salt_1964}}
+  \label{fig:msre_radial_fluxes}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\maxwidth{\textwidth}]{fast_vs_thermal_nt_flux_msre.png}
-  \caption{\gls{MSRE} design radial temperature profiles at reactor mid-plane}
-  \label{fig:msre_radial_temps}
+  \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_fluxes.png}
+  \caption{\gls{MSRE} design axial flux profiles at r = 0
+    \cite{briggs_molten-salt_1964}}
+  \label{fig:msre_axial_fluxes}
 \end{figure}

### 2017-07-28 Moltres.tex
Complete MSRE comparison.

@@
 \title{Introduction to Moltres: an Application for Simulation of Molten Salt Reactors}
-\author{Alexander Lindsay, Kathryn Huff}
+\author{Alexander Lindsay, Gavin Ridley, Kathryn Huff}
 
@@
 
-\Cref{fig:flux_comparison} compares the fast and thermal neutron fluxes at the
-reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
-moderator regions and visa versa in fuel regions are even more apparent. The
-larger fast flux magnitude is attributable to using \gls{BOL} fuel
-composition. As the fuel salt reaches an equilibrium composition, the fast to
-thermal flux ratio is expected to decrease.
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics{radial_group_comparison.eps}
-  \caption{The thermal and fast flux profiles are compared at the core mid-plane
-    ($z=H/2$) in this 2-D cylindrical axisymmetric model ($r=0$ is radial center
-    of core). }
-  \label{fig:flux_comparison}
-\end{figure}
-
 The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
@@
 profiles with cosinusoidal gamma heating and \gls{MSRE} design models
-\cite{briggs_molten-salt_1964} along the reactor center-line (r = 0).
+\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
+profiles are in good agreement. In the \gls{MSRE} design, the moderator
+temperature at the reactor inlet is about 20 degrees Faerenheit larger than the
+fuel temperature, whereas the temperatures are about the same in the Moltres
+model. This difference can perhaps be attributed to the neglection of axial
+conduction in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.
 
@@
       \includegraphics[width=\maxwidth{\textwidth}]{fuel_vs_moderator_axial_sweep.eps}
-      \caption{Moltres predicted axial temperature profiles near r = 0}
+      \caption{Moltres predicted axial temperature profiles in hottest channel
+        and adjacent graphite}
       \label{fig:moltres_axial_temps}
@@
       \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_temps.png}
-      \caption{\gls{MSRE} design axial temperature profiles near r = 0
-        \cite{briggs_molten-salt_1964}}
+      \caption{\gls{MSRE} design axial temperature profiles in hottest channel
+        and adjacent graphite stringer \cite[p. 99]{briggs_molten-salt_1964}}
       \label{fig:msre_axial_temps}
@@
 
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=\maxwidth{\textwidth}]{msre_radial_fluxes.png}
-  \caption{\gls{MSRE} design radial flux profiles at reactor mid-plane
-    \cite{briggs_molten-salt_1964}}
-  \label{fig:msre_radial_fluxes}
-\end{figure}
+\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
+reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
+moderator regions and visa versa in fuel regions are apparent. The flux
+magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
+calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
+\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
+approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
+3 for the Moltres calculation. The depression in the thermal flux in
+\cref{fig:msre_radial_fluxes} is caused by control rod thimbles and an extra
+volume of surrounding fuel that is not included in the Moltres calculations.
 
@@
     \centering
+    \begin{subfigure}[b]{.5\textwidth}
+      \includegraphics[width=\maxwidth{\textwidth}]{moltres_radial_fluxes.eps}
+      \caption{The thermal and fast flux profiles at the core mid-plane
+        ($z=H/2$) for Moltres 2-D cylindrical axisymmetric model ($r=0$ is radial center
+        of core)}
+      \label{fig:moltres_radial_fluxes}
+    \end{subfigure}
+    %\quad
+    \begin{subfigure}[b]{.5\textwidth}
+      \includegraphics[width=\maxwidth{\textwidth}]{msre_radial_fluxes.png}
+      \caption{The thermal and fast flux profiles at the core mid-plane
+        ($z=H/2$) for \gls{MSRE} design model \cite{briggs_molten-salt_1964}
+        ($r=0$ is radial center of core)}
+      \label{fig:msre_radial_fluxes}
+    \end{subfigure}
+    \caption{Comparison of \gls{MSRE} design and Moltres predicted radial
+      flux profiles}
+    \label{fig:radial_fluxes_compare}
+\end{figure}
+
+\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
+Moltres and the \gls{ORNL} \gls{MSRE} design model. Note that the radius for the
+plots are chosen to correspond to the peak of the thermal flux in both cases;
+for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
+because of the effect of the control rod thimbles and extra fuel along the
+center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
+calculations include the lower and upper plena which are not included in this
+report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
+extends to lower and higher z-values than
+\cref{fig:moltres_axial_fluxes}. Additionally, the deviation of the thermal flux
+from a sinusoidal shape in \cref{fig:msre_axial_fluxes} is due to absorption in
+the plena.
+
+\begin{figure}[htpb]
+    \centering
+    \begin{subfigure}[b]{.5\textwidth}
+      \includegraphics[width=\maxwidth{\textwidth}]{moltres_axial_fluxes.eps}
+      \caption{Moltres axial flux profiles along core center line}
+      \label{fig:moltres_axial_fluxes}
+    \end{subfigure}
+    %\quad
+    \begin{subfigure}[b]{.5\textwidth}
       \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_fluxes.png}
-  \caption{\gls{MSRE} design axial flux profiles at r = 0
-    \cite{briggs_molten-salt_1964}}
+      \caption{\gls{MSRE} design axial flux profiles 8.4 inches from the core
+        center line \cite{briggs_molten-salt_1964}}
       \label{fig:msre_axial_fluxes}
+    \end{subfigure}
+    \caption{Comparison of \gls{MSRE} design and Moltres predicted axial
+      flux profiles}
+    \label{fig:axial_fluxes_compare}
 \end{figure}
@@
 equations in anywhere from one to three dimensions and can be deployed on an
-arbitrary number of processing units. The model problem presented here has a
-2D-axisymmetric geometry with heterogeneous group constants for fuel and
-moderator regions. Fuel volume fraction and fuel salt composition are based on
-the \gls{MSRE}. Neutron fluxes show expected cosinusoidal shapes in radial and
-axial directions with visible striations between fuel and moderator regions. The
-fast group flux is enhanced in fuel regions while the thermal group flux in
-enhanced in moderator regions. Due to advection the temperature profile
-increases monotonically in the direction of salt flow. The role of advection is
-also seen in precursor concentrations. Long lived precursors exhibit maximum
-concentrations at the core outlet. As the decay constant increases across
-precursor groups the maximum concentrations moves towards the reactor center
-where the precursor production rate is maximum. Future Moltres work includes
-generating a high-fidelity 3D model as well as investigating various transient
-accident scenarios.
+arbitrary number of processing units. The 2D-axisymmetric and 3D models
+presented here employ heterogeneous group constants for fuel and moderator
+regions generated with SCALE. Fuel volume fraction and fuel salt composition are
+based on the \gls{MSRE}. Neutron fluxes show expected cosinusoidal shapes in
+radial and axial directions with visible striations between fuel and moderator
+regions. The fast group flux is enhanced in fuel regions while the thermal group
+flux in enhanced in moderator regions. Due to advection the temperature profile
+in the fuel increases monotonically in the direction of salt flow, while the
+moderator temperature exhibits a maximum between the mid-plane and outlet. The
+role of advection is also seen in precursor concentrations. Long lived
+precursors exhibit maximum concentrations at the core outlet. As the decay
+constant increases across precursor groups the maximum concentrations moves
+towards the reactor center where the precursor production rate is
+maximum. Results from 2D-axisymmetric and 3D models show good qualitative
+agreement. Moreover, Moltres results compare favorably with the actual design
+calculations of the \gls{MSRE}. Strong parallel scaling was demonstrated on a
+typical Moltres model problem. Future Moltres publications will highlight
+transient simulation cases investigating control rod ejection, single channel
+blockage, loss of flow, and loss of secondary cooling.
 

### 2017-07-31 msbr_reproc.tex
brevity and clarity

--- 2017-07-10 msbr_reproc.tex
@@
 zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
-The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
+Zone I composed of 1320 graphite cells, 2 graphite control rods, and 
 2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
-II, with 37\% fuel salt, and radial reflector, surrounding the more active 
-portion serves to diminish neutron leakage from the reactor core. In this work, 
+II, with 37\% fuel salt, and radial reflector, surrounds the Zone I core region 
+and serves to diminish neutron leakage. In this work, 
 only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 

### 2017-07-31 msbr_reproc.tex
space before citation
oxford commas now have legal precedent

@@
 $1.843 g/cm^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
-reprocessing cycle\cite{robertson_conceptual_1971}.
+reprocessing cycle \cite{robertson_conceptual_1971}.
 
@@
 Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
-energy spectrum. Accordingly, $^{233}$Pa is continuously removed from fuel salt 
+energy spectrum. Accordingly, $^{233}$Pa is continuously removed from the fuel salt 
 into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
@@
 $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa 
-decays into $^{233}$U 
-and return it back to the primary loop. This feature allows the reactor to 
+decays into $^{233}$U, and return it back to the primary loop. This feature allows the reactor to 
 avoid neutron losses to protactinium, keeps fission products to a very low level, and 

### 2017-07-31 msbr_reproc.tex
rephrasing for clarity

@@
 
-A major problem with the reprocessing method is that different nuclides have 
-specific removal rates. On the one hand, if the depletion time intervals are 
-very short it means specific isotope being instantly removed, and it is hard to 
-obtain equilibrium composition because enormous large number of depletion 
-steps. On the other hand, if the depletion calculation time interval is too 
-long the results would not truly represent the \gls{MSBR} conceptual design. 
-Following this idea, the time interval for depletion calculations was selected 
-as 3 days to correlate with the removal interval of $^{233}$Pa. Thorium is 
-continuously added to 
-maintain the initial mass fraction of $^{232}$ThF$_4$.
+Since removal rates vary among nuclides in this reactor concept, the Serpent 2 
+reprocessing method is unable to capture the desired reprocessing strategy. 
+The removal rates also dictate the necessary resolution of depletion 
+calculations. If the depletion time intervals are 
+very short an enormous number of depletion steps are required to
+obtain the equilibrium composition. On the other hand, if the depletion 
+calculation time interval is too long, serious impacts of short lived fission 
+products are not captured in a manner that is faithful \gls{MSBR} conceptual design. 
+To compromise, the time interval for depletion calculations in this model was selected 
+as 3 days to correlate with the removal interval of $^{233}$Pa and Thorium was 
+continuously added to maintain the initial mass fraction of $^{232}$ThF$_4$.
 

### 2017-07-31 msbr_reproc.tex
rephrasing for active voice
approximately rather than about

@@
 Using the methodology described previously, the \gls{MSBR} unit cell depletion 
-analysis was performed to find equilibrium core conditions. In this section, 
-the calculation results including multiplication factor, neutron flux energy 
-spectrum, atomic density of major isotopes are summarised.
+analysis was performed to find equilibrium core conditions. Calculation results reported 
+in this section include multiplication factor, neutron flux energy 
+spectrum, and atomic density of major isotopes.
 
@@
 excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
-Standard deviation is about 100 pcm.
+Standard deviation for these calculations is approximately 100 pcm.
 

### 2017-07-31 msbr_reproc.tex
grammar"

@@
 
-The method approximate a single representative unit cell for the whole 
-\gls{MSBR} core, consequently, it does not take into consideration different 
-fuel-moderator volume ratio for Zone I, Zone II, annulus, and reflector. The 
+This analysis models a single representative unit cell rather than the whole 
+\gls{MSBR} core. Consequently, it does not take into consideration different 
+fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
 initial multiplication factor during depletion calculation is selected for 
@@
         \includegraphics[width=1.03\linewidth]{keff.png}
-        \caption{Infinite multiplication factor during 4 years depletion 
+        \caption{Infinite multiplication factor during a 4-years depletion 
         simulation.}
@@
         \includegraphics[width=1.03\linewidth]{fuel_composition.png}
-        \caption{Normalized number density of major isotopes during 4 years 
+        \caption{Normalized number density of major isotopes during 4 years of 
         depletion.}

### 2017-07-31 msbr_reproc.tex
grammar

@@
 reprocessing. It does so by allowing the user to 
-create multiple material flows into and out of the fuel.
+define multiple material flows into and out of the fuel. This work applies this 
+Serpent 2 feature to the \gls{MSBR}.
 
@@
 initial multiplication factor during depletion calculation is selected for 
-state with fully withdrawn control and poison rods position which gives high 
-excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
+state with fully withdrawn control and poison rods position which gives 
+considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
 Standard deviation for these calculations is approximately 100 pcm.
@@
 Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
-reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. The 
-high standard deviation causes the multiplication factor fluctuations. 
-Protactinium-233 continuously removing into the tank for protactinium decay. 
-$^{233}$Pa has a half-life of 27 days and beta decays into $^{233}$U which as 
-fresh fuel goes back to the reactor core. The infinite multiplication factor 
-decreases first 400 days of depletion due to strong absorbers (e.g. $^{233}$Th, 
-$^{234}$U) accumulation which causes relatively high fuel ($^{233}$U) refill 
-inflow to keep reactor critical. During reactor operation producing fissile 
-materials other than $^{233}$U in the core (e.g. $^{235}$U, $^{239}$Pu) which 
-makes it possible to decrease fresh fuel refill rate after ~1 year of 
-operation.
+reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. A 
+significant standard deviation (100 pcm) causes the multiplication factor 
+fluctuations visible in this plot.  Protactinium-233 continuously removing into 
+the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
+beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
+The infinite multiplication factor decreases first 400 days of depletion due to 
+strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
+relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
+reactor operation producing fissile materials other than $^{233}$U in the core 
+(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
+refill rate after ~1 year of operation.
 
@@
 The analysis of the fuel salt composition variation gives clearer information 
-about equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
-number density of important isotopes that have strong influence on the core 
+about the equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
+number density of isotopes influential to core 
 neutronics at the beginning of each depletion time interval. The number density 
 of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
-of it produced during 3-days reprocessing step. It can be seen that the 
-multiplication factor reaches the equilibrium state at about 950  days. 
-Figure~\ref{fig:rates} represents the rates of materials in online reprocessing 
-flows during 4 years of depletion calculations. 
+of it is produced during the 3-day reprocessing period. In this assessment, the multiplication 
+factor stabilizes after approximately 950 days. 
+Figure~\ref{fig:rates} represents the rates of online reprocessing material flows
+flows over the 4-year depletion calculation. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-07-31 msbr_reproc.tex
grammar

@@
 \end{figure}
-From the graph below we can see that to keep reactor critical higher $^{233}$U 
-flow rate required for first 400 days of operation and after that much smaller 
-uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th 
+In Figure~\ref{fig:rates} we can see that, to keep the reactor critical, a higher $^{233}$U 
+flow rate from the protactinium decay tank was required for first 400 days of 
+operation. After that, the $^{233}$U flow rate can be reduced. The $^{232}$Th 
 rate slightly decreases over 4 years of operation due to other than $^{233}$U 
@@
 As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay 
-accumulates $^{233}$Pa approximately 200 days and fresh fuel ($^{233}$U) flow 
-established also after 200 days. Uranium produced in the tank by protactinium 
+accumulates $^{233}$Pa for approximately 200 days. Fresh $^{233}$U fuel flow is 
+also established after 200 days. Uranium produced in the tank by protactinium 
 decay is separated by circulation of the salt through a flourinator. The fully 

### 2017-07-31 msbr_reproc.tex
grammar

@@
 
-In this work only Zone I unit cell with 0.132 volume fraction of fuel 
-considered, neutron spectrum for Zone II cell where salt fraction is 37\% 
-should be harder and the peak in thermal energy region predicted to be much 
-lower. To obtain high fidelity neutron energy spectrum whole \gls{MSBR} core 
+In this work, only the Zone I unit cell, where the fuel salt volume fraction is 
+13.2\%, was considered. The neutron spectrum for Zone II cell, where the fuel 
+salt volume fraction is 37\% is expected to be harder and the peak in thermal 
+energy region is predicted to be much 
+lower. To obtain a high-fidelity neutron energy spectrum, a full-core \gls{MSBR}
 analysis is required.

### 2017-07-31 msbr_reproc.tex
grammar
spelling and stuff

@@
 fission products are removed and fertile/fissile materials are added to fuel 
-salt every 3 days. The important MSR feature, online reprocessing I\& refueling 
+salt every 3 days. The important MSR feature, online reprocessing \& refueling 
 is implemented in the Serpent 2 material burnup routine. The results of this 
@@
 inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
-Park selected 20.6\% salt fraction). To obtain better results in online 
-reprocessing simulation number of future efforts expected. First, depletion 
-simulation will be performed using full-core tree-dimensional high-fidelity 
+Park selected 20.6\% salt fraction). To obtain better results for this online 
+reprocessing simulation, many future efforts are planned. First, a depletion 
+simulation will be performed using a  full-core, three-dimensional, high-fidelity 
 model of \gls{MSBR} developed in Serpent 2. In this case, different 

### 2017-07-31 msbr_reproc.tex
minor grammar

@@
 simulation will be performed using a  full-core, three-dimensional, high-fidelity 
-model of \gls{MSBR} developed in Serpent 2. In this case, different 
+model of \gls{MSBR} that has been developed in Serpent 2. In this case, different 
 fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 

### 2017-08-01 acros.tex

--- 2017-02-27 acros.tex
@@
 \newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
+\newacronym{BOL}{BOL}{Beginning-of-Life}
+\newacronym{BSD}{BSD}{Berkeley Software Distribution}
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
@@
 \newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
-\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
+\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies
+Alternatives}
+\newacronym{CG}{CG}{Continuous Galerkin}
 \newacronym{CI}{CI}{continuous integration}
@@
 \newacronym{DBE}{DBE}{Design Basis Event}
+\newacronym{DG}{DG}{Discontinuous Galerkin}
 \newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
@@
 \newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
+\newacronym{gpm}{gpm}{gallons per minute}
 \newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
@@
 \newacronym{LP}{LP}{linear program}
+\newacronym{LWR}{LWR}{Light Water Reactor}
 \newacronym{MARKAL}{MARKAL}{MARKet and ALlocation}
@@
 \newacronym{SWU}{SWU}{Separative Work Unit}
+\newacronym{ThOX}{ThOX}{thorium oxide}
 \newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 
-This work introduces Moltres, a new physics application for multiphysics
-modeling of fluid-fuelled molten salt reactors. The neutronics model, thermal
+This work introduces Moltres, a new physics application for modeling coupled 
+physics in fluid-fuelled, molten salt reactors. The neutronics model, thermal
 hydraulics model, and their coupling in the MOOSE framework are
@@
 input card. Results for many-channel configurations in 2D-axisymmetric and 3D
-coordinates are presented. These are compared against other coupled models as
+coordinates are presented and compared against other coupled models as
 well as the Molten Salt Reactor Experiment.

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 
-\gls{MSR} modeling efforts are focused on description of steady-state and
+\gls{MSR} modeling efforts describe steady-state and
 transient behavior. Krepel et. al. extended the in-house \gls{LWR}
@@
 et. al. used iterative coupling between in-house three-dimensional neutronic and
-one-dimensional heat conduction models DALTON and THERM to analyze the normal
-operational state of the \gls{MSRE} as well as channel-blocking-incident
+one-dimensional heat conduction models DALTON and THERM to analyze normal 
+\gls{MSRE} operation as well as channel-blocking-incident
 transients \cite{kophazi_development_2009}. Additions in the Kophazi model

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 \gls{MSRE} operation as well as channel-blocking-incident
-transients \cite{kophazi_development_2009}. Additions in the Kophazi model
-included entrance effects of heat transfer coefficients as well as thermal
+transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
+effects of heat transfer coefficients as well as thermal
 coupling between fuel channels through moderator heat conduction. More recently,

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 \gls{MSBR} using the commercial finite element package COMSOL
-Multiphysics \cite{cammi_multi-physics_2011}. Advances in that work included
-solution of the fuel salt velocity field, use of heterogeneous group constants
-in fuel and moderator regions, and employment of a software package (COMSOL)
+Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
+fuel salt velocity field, used heterogeneous group constants
+in fuel and moderator regions, and employed a software package (COMSOL)
 intrinsically designed for coupled multi-physics simulation.

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 The present work introduces the open source simulation tool, Moltres
-\cite{lindsay_arfc/moltres_nodate}, for \gls{MSR} simulation.  By implementing
+\cite{lindsay_arfc/moltres_nodate}, for simulating \glspl{MSR}.  By implementing
 deterministic neutronics and thermal hydraulics in the context of the
@@
 \mintinline{latex}{git} for version control, integration testing to protect
-developed physics capabilities, and a C++ object-oriented design to allow easy
-class extensibility and minimal code duplication. Moreover, Moltres is built on
+developed physics capabilities, and a C++ object-oriented design to
+enable extension and code reuse. Moreover, Moltres is built on
 top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 \gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
-\gls{BSD}-licensed toolkit for solving nonlinear equations stemming from
-discretization of PDEs. \gls{MOOSE} and LibMesh handle translation of
-application (Moltres) defined weak PDE forms into residual and Jacobian
+\gls{BSD}-licensed toolkit for solving nonlinear equations yielded by 
+discretizing PDEs. \gls{MOOSE} and LibMesh translate weak PDE forms defined by
+applications (e.g. Moltres) into residual and Jacobian
 functions that are the inputs into PetSc Newton-Raphson solution routines. All

### 2017-08-01 Moltres.tex
nouns to verbs
no need for very

@@
 applications (e.g. Moltres) into residual and Jacobian
-functions that are the inputs into PetSc Newton-Raphson solution routines. All
+functions. These functions are the inputs into PetSc Newton-Raphson solution routines. All
 codes use MPI for parallel communication and are easily deployed on
@@
 Jacobian contributions corresponding to individual piecies of governing
-equations. Developing the code-base in this way allows very modular construction
+equations. Developing the code-base in this way allows modular construction
 of equation systems; e.g. the same kernel that is used to represent heat

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 conduction can also be used to represent generic chemical diffusion. Moltres
-also features neutron and precursor ``actions.'' These actions enable automatic
-construction of the systems of equations for an arbitrary number of neutron and
+also features neutron and precursor ``actions.'' These actions automatically 
+construct the systems of equations for an arbitrary number of neutron and
 precursor groups. This means that as long as group constants are provided in an appropriate

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 two and using a structured mesh that can be much more coarse in the axial
-direction allows problem solution to be carried out on a single core in under
+direction allows the problem to be solved on a single core in under
 five minutes.

### 2017-08-01 Moltres.tex
nouns to verbs

@@
 boundary conditions is shown clearly in the cosinusoidal shapes in radial and
-axial directions. Striations are observed in both fast and thermal fluxes, with
+axial directions. Both the fast and thermal fluxes are striated, with
 the fast group preferring the fuel and the thermal group preferring the moderator.
@@
 fuel temperature, whereas the temperatures are about the same in the Moltres
-model. This difference can perhaps be attributed to the neglection of axial
-conduction in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.
+model. This difference is likely because axial
+conduction was neglected in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.
 

### 2017-08-01 Moltres.tex
passive to active

@@
 fuel temperature, whereas the temperatures are about the same in the Moltres
-model. This difference is likely because axial
-conduction was neglected in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.
+model. This difference is likely because axial the \gls{MSRE} design model 
+neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.
 
@@
 extends to lower and higher z-values than
-\cref{fig:moltres_axial_fluxes}. Additionally, the deviation of the thermal flux
-from a sinusoidal shape in \cref{fig:msre_axial_fluxes} is due to absorption in
-the plena.
+\cref{fig:moltres_axial_fluxes}. Additionally, absorption in the plena caused 
+deviation of the thermal flux from a sinusoidal shape in 
+\cref{fig:msre_axial_fluxes}.
 

### 2017-08-01 Moltres.tex
getting rid of extraneous adverbs

@@
 
-This work introduces Moltres, a new physics application for modeling coupled 
-physics in fluid-fuelled, molten salt reactors. The neutronics model, thermal
-hydraulics model, and their coupling in the MOOSE framework are
-described. Neutron and precursor equations are implemented using an Action
-system that allows use of an arbitrary number of groups with no change in the
-input card. Results for many-channel configurations in 2D-axisymmetric and 3D
-coordinates are presented and compared against other coupled models as
-well as the Molten Salt Reactor Experiment.
+Moltres is a new physics application for modeling coupled physics in 
+fluid-fuelled, molten salt reactors. This paper describes its neutronics model, 
+thermal hydraulics model, and their coupling in the MOOSE framework. Neutron 
+and precursor equations are implemented using an Action system that allows use 
+of an arbitrary number of groups with no change in the input card. Results for 
+many-channel configurations in 2D-axisymmetric and 3D coordinates are presented 
+and compared against other coupled models as well as the Molten Salt Reactor 
+Experiment.
 
@@
 in this work. However, it should be noted that Moltres can also use explicit
-time-stepping routines as well as segregated solution methods, making it very
+time-stepping routines as well as segregated solution methods, making it 
 extensible to myriad future modeling challenges.
@@
 file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
-time follows very closely to the ideal; slight deviations are expected due to
+time follows closely to the ideal; slight deviations are expected due to
 the expense of communication and the nature of iterative solvers. More

### 2017-08-01 Moltres.tex
getting rid of extraneous adverbs
z is height

@@
 Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
-boundary conditions is shown clearly in the cosinusoidal shapes in radial and
+boundary conditions is shown by the cosinusoidal shapes in radial and
 axial directions. Both the fast and thermal fluxes are striated, with
@@
 The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
-rises steadily with increasing z-coordinate. As is expected, the temperature
+rises along the reactor height. As is expected, the temperature
 gradient is negative in the radial direction.

### 2017-08-01 Moltres.tex
adverbs
Unneccessary : It should be noted that.

@@
 
-Other simulation inputs are outlined in \Cref{table:params}. It should be noted
-that the reactor simulation height of 151.75 cm was chosen to produce an
+Other simulation inputs are outlined in \Cref{table:params}.
+The reactor simulation height of 151.75 cm was chosen to produce an
 approximately critical reactor configuration corresponding to \gls{BOL}
@@
 reactor. Not surprisingly, the channel concentrations are higher in fuel channels
-with higher neutron fluxes and consequently a higher number of fission
+with higher neutron fluxes and corresponding fission
 events. Because of the small decay constant of the precursor, the maximum

### 2017-08-01 Moltres.tex
unneccessary that is
rephrase

@@
 Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
-to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some
+to run on super-computing platforms like the Blue Waters supercomputer at the \gls{NCSA}. For some
 three-dimensional simulations, the number of
@@
 \cref{fig:msre_radial_fluxes} is caused by control rod thimbles and an extra
-volume of surrounding fuel that is not included in the Moltres calculations.
+volume of surrounding fuel not included in the Moltres calculations.
 

### 2017-08-01 Moltres.tex
passive to active

@@
 
-Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a
-tool that can be freely used, studied, interrogated, and improved by the
-\gls{MSR} community.  Its openness is a defining characteristic and promotes
+Moltres is an open source code licensed under \gls{LGPL} terms so that the 
+\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
+is a defining characteristic and promotes
 quality through transparency and ease of peer review. In the era of
@@
 Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
-to run on super-computing platforms like the Blue Waters supercomputer at the \gls{NCSA}. For some
+to run on super-computing platforms like the Blue Waters supercomputer at the 
+\gls{NCSA}. For some
 three-dimensional simulations, the number of

### 2017-08-01 Moltres.tex
brevity and clarity

@@
 default use monolithic and implicit methods that are ideal for closely-coupled
-and multi-scale physics. These methods are ideal for the model problem described
-in this work. However, it should be noted that Moltres can also use explicit
+and multi-scale physics, such as the model problem described
+in this work. However, Moltres can also use explicit
 time-stepping routines as well as segregated solution methods, making it 
@@
 equations. Developing the code-base in this way allows modular construction
-of equation systems; e.g. the same kernel that is used to represent heat
+of equation systems; e.g. the kernel used to represent heat
 conduction can also be used to represent generic chemical diffusion. Moltres

### 2017-08-01 Moltres.tex
brevity and clarity
passive to active

@@
 developed physics capabilities, and a C++ object-oriented design to
-enable extension and code reuse. Moreover, Moltres is built on
-top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another
-\gls{LGPL} code that itself leans on LibMesh \cite{kirk_libmesh:_2006}, a
+enable extension and code reuse. Moreover, Moltres depends on the \gls{MOOSE} 
+framework, \cite{gaston_physics-based_2015} another \gls{LGPL} code that itself 
+leans on LibMesh \cite{kirk_libmesh:_2006}, a
 \gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
@@
 of equation systems; e.g. the kernel used to represent heat
-conduction can also be used to represent generic chemical diffusion. Moltres
+conduction can also represent generic chemical diffusion. Moltres
 also features neutron and precursor ``actions.'' These actions automatically 

### 2017-08-01 Moltres.tex
brevity and clarity
avoids passive voice... rewrites interpolation table sentence a bit.

@@
 
-In this work $Q_g$ is set equal to $\gamma Q_f$, where $\gamma$ is a factor
+In this work, $Q_g = \gamma Q_f$, where $\gamma$ is a factor
 representing heat dissipation by gamma and neutron irradiation in the moderator.
@@
 Group constants are generated by the modeler with either Serpent
-\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Group constant
-temperature dependence is implemented via interpolation tables, which must be
+\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Moltres 
+interpolates group constant temperature dependence from prepared tables, which must be
 constructed separately for fuel and moderator regions. For this report,

### 2017-08-01 Moltres.tex
passive to active

@@
 
-The model molten salt
-reactor is based on the \gls{MSRE}. When developing new physics or investigating
+The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
 different types of transients, the model problem can be reduced to a two
@@
 
-The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
-and is given in \Cref{table:comp} \cite{robertson_msre_1965}.
+The model fuel composition is the \gls{BOL} enriched uranium composition in the 
+\gls{MSRE} and is given in \Cref{table:comp} \cite{robertson_msre_1965}.
 
@@
   \end{center}
-        \caption{Fuel salt composition is based on the \gls{BOL} enriched
+        \caption{Fuel salt composition is the \gls{BOL} enriched
         uranium composition in the \gls{MSRE} design
@@
 
-Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
-boundary conditions is shown by the cosinusoidal shapes in radial and
-axial directions. Both the fast and thermal fluxes are striated, with
+Group fluxes are shown in \Cref{fig:group1,fig:group2}. The cosinusoidal shapes in radial and
+axial directions are caused by the vacuum boundary conditions. Both the fast and thermal fluxes are striated, with
 the fast group preferring the fuel and the thermal group preferring the moderator.

### 2017-08-01 Moltres.tex
passive to active

@@
 
-Group fluxes are shown in \Cref{fig:group1,fig:group2}. The cosinusoidal shapes in radial and
+Group fluxes are shown in \Cref{fig:group1,fig:group2}. The cosinusoidal shapes 
+in radial and
 axial directions are caused by the vacuum boundary conditions. Both the fast and thermal fluxes are striated, with
@@
 
-The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
-rises along the reactor height. As is expected, the temperature
-gradient is negative in the radial direction.
+In \Cref{fig:temp} the temperature rises along the reactor height because of 
+fuel advection. The temperature gradient is negative in the 
+radial direction, as expected.
 

### 2017-08-01 Moltres.tex
passive to active

@@
 approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
-3 for the Moltres calculation. The depression in the thermal flux in
-\cref{fig:msre_radial_fluxes} is caused by control rod thimbles and an extra
-volume of surrounding fuel not included in the Moltres calculations.
+3 for the Moltres calculation. Meanwhile, control rod thimbles and
+an extra volume of surrounding fuel not included in the Moltres calculations
+cause the depression in the thermal flux in \crep{fig:msre_radial_fluxes}.
 

### 2017-08-01 Moltres.tex
passive to active

@@
 performance, a scaling study was conducted using a typical 2D axisymmetric input
-file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
-time follows closely to the ideal; slight deviations are expected due to
+file. \Cref{fig:scaling_study} shows Moltres's performance. The solution
+time follows the ideal closely; slight deviations are expected due to
 the expense of communication and the nature of iterative solvers. More
-parallelism means more ``older'' information is used in the solution process,
-which leads to slower convergence in terms of iterations \cite{satish_balay_petsc_2015}.
+parallelism means the solution process uses more ``older'' information, 
+which leads to slower convergence in terms of iterations 
+\cite{satish_balay_petsc_2015}.
 

### 2017-08-01 msbr_reproc.tex

@@
 initial multiplication factor during depletion calculation is selected for 
-state with fully withdrawn control and poison rods position which gives 
+a state with fully withdrawn control rods, which gives 
 considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
@@
 fuel-moderator volume ratios for the reactor Zone I, Zone II, annulus, 
-reflectors would be taken into account to find accurate multiplication factor, 
-neutron spectrum and, hence, depleted composition. Secondly, additional Serpent 
+and reflectors will be taken into account to find accurate multiplication factor, 
+neutron spectrum and, hence, depleted composition. Secondly, an additional Serpent 
 2 flow control system subroutine should be developed to simulate adjusting 
 material flows (e.g. rate of removing $^{233}$Pa from the salt and adding 
-fissile $^{233}$U from the tank for protactinium decay) depending upon current 
-reactivity value which is more promising reactivity control method than moving 
-control and safety rods. Finally, temperature effect of reactivity for both 
+fissile $^{233}$U from the tank for protactinium decay) depending upon the 
+instantaneous reactivity value, which is a more promising reactivity control method than moving 
+control rods. Finally, the temperature effect of reactivity for both 
 fuel salt and graphite should be calculated to find optimal effective 

### 2017-08-01 msbr_reproc.tex
Pictures position changed

--- 2017-07-31 msbr_reproc.tex
@@
 solid-fueled, reactors. The molten-salt carrier with dissolved 
-fissile and/or fertile material allows for online refuelling and 
+fissile and/or fertile material allows for online refueling and 
 reprocessing. Thus, \glspl{MSR} can potentially operate years without shutdown, 
@@
 of inherent safety due to their characteristically 
-strong negative temperature coefficient of reactivity, near-atmospheric 
+the strong negative temperature coefficient of reactivity, near-atmospheric 
 pressure in the primary loop, stable coolant, passive decay heat cooling, and 
@@
 al.} to find an equilibrium fuel composition for the \gls{MSBR} and was 
-validated with an \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.
+validated with a \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.
 
@@
 zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
-Zone I composed of 1320 graphite cells, 2 graphite control rods, and 
+The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
 2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
-II, with 37\% fuel salt, and radial reflector, surrounds the Zone I core region 
-and serves to diminish neutron leakage. In this work, 
+II, with 37\% fuel salt, and radial reflector, surrounding the more active 
+portion serves to diminish neutron leakage from the reactor core. In this work, 
 only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
@@
 $1.843 g/cm^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
-reprocessing cycle \cite{robertson_conceptual_1971}.
+reprocessing cycle\cite{robertson_conceptual_1971}.
 
@@
 \cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
-first commonly used monte carlo software to support continuous material 
+first commonly used Monte Carlo software to support continuous material 
 reprocessing. It does so by allowing the user to 
-define multiple material flows into and out of the fuel. This work applies this 
-Serpent 2 feature to the \gls{MSBR}.
+create multiple material flows into and out of the fuel.
 
@@
 every 20 seconds. The $^{232}$Th in the fuel absorbs thermal 
-neutrons and produces $^{233}$Pa which then decay into the fissile $^{233}$U. 
+neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U. 
 Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
-energy spectrum. Accordingly, $^{233}$Pa is continuously removed from the fuel salt 
+energy spectrum. Accordingly, $^{233}$Pa is continuously removed from fuel salt 
 into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
@@
 $^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa 
-decays into $^{233}$U, and return it back to the primary loop. This feature allows the reactor to 
+decays into $^{233}$U 
+and return it back to the primary loop. This feature allows the reactor to 
 avoid neutron losses to protactinium, keeps fission products to a very low level, and 
@@
 
-Since removal rates vary among nuclides in this reactor concept, the Serpent 2 
-reprocessing method is unable to capture the desired reprocessing strategy. 
-The removal rates also dictate the necessary resolution of depletion 
-calculations. If the depletion time intervals are 
-very short an enormous number of depletion steps are required to
-obtain the equilibrium composition. On the other hand, if the depletion 
-calculation time interval is too long, serious impacts of short lived fission 
-products are not captured in a manner that is faithful \gls{MSBR} conceptual design. 
-To compromise, the time interval for depletion calculations in this model was selected 
-as 3 days to correlate with the removal interval of $^{233}$Pa and Thorium was 
-continuously added to maintain the initial mass fraction of $^{232}$ThF$_4$.
+A major problem with the reprocessing method is that different nuclides have 
+specific removal rates. On the one hand, if the depletion time intervals are 
+very short it means specific isotope being instantly removed, and it is hard to 
+obtain equilibrium composition because of an enormously large number of depletion 
+steps. On the other hand, if the depletion calculation time interval is too 
+long the results would not truly represent the \gls{MSBR} conceptual design. 
+Following this idea, the time interval for depletion calculations was selected 
+as 3 days to correlate with the removal interval of $^{233}$Pa. Thorium is 
+continuously added to 
+maintain the initial mass fraction of $^{232}$ThF$_4$.
 
@@
 Using the methodology described previously, the \gls{MSBR} unit cell depletion 
-analysis was performed to find equilibrium core conditions. Calculation results reported 
-in this section include multiplication factor, neutron flux energy 
-spectrum, and atomic density of major isotopes.
+analysis was performed to find equilibrium core conditions. In this section, 
+the calculation results including multiplication factor, neutron flux energy 
+spectrum, atomic density of major isotopes are summarized.
 
@@
 
-This analysis models a single representative unit cell rather than the whole 
-\gls{MSBR} core. Consequently, it does not take into consideration different 
-fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
+The method approximate a single representative unit cell for the whole 
+\gls{MSBR} core, consequently, it does not take into consideration different 
+fuel-moderator volume ratio for Zone I, Zone II, annulus, and reflector. The 
 initial multiplication factor during depletion calculation is selected for 
-state with fully withdrawn control and poison rods position which gives 
-considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
-Standard deviation for these calculations is approximately 100 pcm.
+state with fully withdrawn control and poison rods position which gives high 
+excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
+Standard deviation is about 100 pcm.
 
@@
         \includegraphics[width=1.03\linewidth]{keff.png}
-        \caption{Infinite multiplication factor during a 4-years depletion 
+        \caption{Infinite multiplication factor during 4 years depletion 
         simulation.}
@@
 
-Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
-reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. A 
-significant standard deviation (100 pcm) causes the multiplication factor 
-fluctuations visible in this plot.  Protactinium-233 continuously removing into 
-the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
-beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
-The infinite multiplication factor decreases first 400 days of depletion due to 
-strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
-relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
-reactor operation producing fissile materials other than $^{233}$U in the core 
-(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
-refill rate after ~1 year of operation.
+Figure~\ref{fig:keff} shows the infinite multiplication factor for 1200-days
+reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. The 
+high standard deviation causes the multiplication factor fluctuations. 
+Protactinium-233 continuously removing into the tank for protactinium decay. 
+$^{233}$Pa has a half-life of 27 days and beta decays into $^{233}$U which as 
+fresh fuel goes back to the reactor core. The infinite multiplication factor 
+decreases first 400 days of depletion due to strong absorbers (e.g. $^{233}$Th, 
+$^{234}$U) accumulation which causes relatively high fuel ($^{233}$U) refill 
+inflow to keep reactor critical. During reactor operation producing fissile 
+materials other than $^{233}$U in the core (e.g. $^{235}$U, $^{239}$Pu) which 
+makes it possible to decrease fresh fuel refill rate after ~1 year of 
+operation.
 
@@
         \includegraphics[width=1.03\linewidth]{fuel_composition.png}
-        \caption{Normalized number density of major isotopes during 4 years of 
+        \caption{Normalized number density of major isotopes during 1200 days 
         depletion.}
@@
 The analysis of the fuel salt composition variation gives clearer information 
-about the equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
-number density of isotopes influential to core 
+about equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
+number density of important isotopes that have strong influence on the core 
 neutronics at the beginning of each depletion time interval. The number density 
 of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
-of it is produced during the 3-day reprocessing period. In this assessment, the multiplication 
-factor stabilizes after approximately 950 days. 
-Figure~\ref{fig:rates} represents the rates of online reprocessing material flows
-flows over the 4-year depletion calculation. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\captionsetup[table]{
-%  labelsep = newline,
-%  name = TABLE, justification=justified,
-%  singlelinecheck=false,%%%%%%% a single line is centered by default
-%  labelsep=colon,%%%%%%
-%  skip = \medskipamount}
-%\begin{table}[h!]
-%\centering
-%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
-%      Isotope & First 400 days     & After 400 days          
-%\\ \midrule
-%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
-%\\ \midrule
-%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
-%\\ \midrule
-%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
-%\\
-%\bottomrule
-%\end{tabular}
-%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
-%  [1/s*cm$^3$].}
-%  \label{tab:rates}
-%\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+of it produced during 3-days reprocessing step. It can be seen that the 
+multiplication factor reaches the equilibrium state at about 950  days.
+
 \begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
@@
 \end{figure}
-In Figure~\ref{fig:rates} we can see that, to keep the reactor critical, a higher $^{233}$U 
-flow rate from the protactinium decay tank was required for first 400 days of 
-operation. After that, the $^{233}$U flow rate can be reduced. The $^{232}$Th 
+
+Figure~\ref{fig:rates} represents the rates of materials in online reprocessing 
+flows during 1200 days of depletion calculations. From the graph below we can 
+see that to keep reactor critical higher $^{233}$U 
+flow rate required for first 400 days of operation and after that much smaller 
+uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th 
 rate slightly decreases over 4 years of operation due to other than $^{233}$U 
@@
 As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay 
-accumulates $^{233}$Pa for approximately 200 days. Fresh $^{233}$U fuel flow is 
-also established after 200 days. Uranium produced in the tank by protactinium 
+accumulates $^{233}$Pa approximately 200 days and fresh fuel ($^{233}$U) flow 
+established also after 200 days. Uranium produced in the tank by protactinium 
 decay is separated by circulation of the salt through a flourinator. The fully 
@@
 
-In this work, only the Zone I unit cell, where the fuel salt volume fraction is 
-13.2\%, was considered. The neutron spectrum for Zone II cell, where the fuel 
-salt volume fraction is 37\% is expected to be harder and the peak in thermal 
-energy region is predicted to be much 
-lower. To obtain a high-fidelity neutron energy spectrum, a full-core \gls{MSBR}
+In this work only Zone I unit cell with 0.132 volume fraction of fuel 
+considered, neutron spectrum for Zone II cell where salt fraction is 37\% 
+should be harder and the peak in thermal energy region predicted to be much 
+lower. To obtain high fidelity neutron energy spectrum whole \gls{MSBR} core 
 analysis is required.
@@
 fission products are removed and fertile/fissile materials are added to fuel 
-salt every 3 days. The important MSR feature, online reprocessing \& refueling 
+salt every 3 days. The important MSR feature, online reprocessing I\& refueling 
 is implemented in the Serpent 2 material burnup routine. The results of this 
@@
 inconsistency may be due to different fuel fraction in the unit cell (Jeong and 
-Park selected 20.6\% salt fraction). To obtain better results for this online 
-reprocessing simulation, many future efforts are planned. First, a depletion 
-simulation will be performed using a  full-core, three-dimensional, high-fidelity 
+Park selected 20.6\% salt fraction). To obtain better results in online 
+reprocessing simulation number of future efforts expected. First, depletion 
+simulation will be performed using full-core tree-dimensional high-fidelity 
 model of \gls{MSBR} developed in Serpent 2. In this case, different 

### 2017-08-01 msbr_reproc.tex
Spectrum graph corrected (normalize to 1 using trapz)

--- 2017-08-01 msbr_reproc.tex
@@
 The thermal spectrum \gls{MSR} is an advanced type of reactor that consists of 
-constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
-$LiF-BeF_2-ZrF_4-UF_4$) and solid graphite moderator structures. This liquid 
+constantly circulating liquid fuel (i.e., mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ or 
+LiF-BeF$_2$-ZrF$_4$-UF$_4$) and solid graphite moderator structures. This liquid 
 fuel form leads to immediate advantages over traditional, 
 solid-fueled, reactors. The molten-salt carrier with dissolved 
-fissile and/or fertile material allows for online refuelling and 
+fissile and/or fertile material allows for online refueling and 
 reprocessing. Thus, \glspl{MSR} can potentially operate years without shutdown, 
@@
 enrichment plant to the \gls{NPP} in the form 
-of uranium hexafluoride ($UF_6$).  Additionally, \glspl{MSR} have a high level 
+of uranium hexafluoride (UF$_6$).  Additionally, \glspl{MSR} have a high level 
 of inherent safety due to their characteristically 
-strong negative temperature coefficient of reactivity, near-atmospheric 
+the strong negative temperature coefficient of reactivity, near-atmospheric 
 pressure in the primary loop, stable coolant, passive decay heat cooling, and 
@@
 use of natural thorium instead of enriched uranium as the fertile element. 
-Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment 
+Thorium breeds the fissile $^{233}$U and avoids uranium enrichment 
 \cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
@@
 The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
-$680 cm$ and a height of $610 cm$. It contains a molten fluoride fuel-salt mixture 
+680 cm and a height of 610 cm. It contains a molten fluoride fuel-salt mixture 
 which performs two functions: to generate heat in the moderated region and to 
@@
         %\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
+        \caption{Summary of principal data for MSBR.}
         \begin{tabularx}{\linewidth}{l X} \toprule 
@@
         \end{tabularx}
-        \caption{Summary of principal data for MSBR.}
         \label{tab:data}
@@
 and serves to diminish neutron leakage. In this work, 
-only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
+only a Zone I element with a 3.42138 cm diameter central fuel channel and molten-salt 
 fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
 geometry of the unit cell model. The boundary condition of the unit cell is 
-periodic. The density of the fuel salt is $3.3304 g/cm^3$ and the graphite density is 
-$1.843 g/cm^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
+periodic. The density of the fuel salt is 3.3304 g/cm$^3$ and the graphite density is 
+1.843 g/cm$^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
 reprocessing cycle \cite{robertson_conceptual_1971}.
@@
         \centering
-        \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
+        \includegraphics[width=0.95\linewidth]{zone_I_mesh.png}
         \caption{MSBR unit cell of Zone I geometry.}
@@
 \cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
-first commonly used monte carlo software to support continuous material 
+first commonly used Monte Carlo software to support continuous material 
 reprocessing. It does so by allowing the user to 
@@
 every 20 seconds. The $^{232}$Th in the fuel absorbs thermal 
-neutrons and produces $^{233}$Pa which then decay into the fissile $^{233}$U. 
+neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U. 
 Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
@@
 considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
-Standard deviation for these calculations is approximately 100 pcm.
+Standard deviation for these calculations is approximately 100 pcm.Figure~\ref{fig:keff} 
+shows the infinite multiplication factor for 1200-days reprocessing cycle calculated by 
+Serpent 2 with ENDF/B-VII.0 nuclear data. A 
+significant standard deviation (100 pcm) causes the multiplication factor 
+fluctuations visible in this plot.
 
@@
         \includegraphics[width=1.03\linewidth]{keff.png}
-        \caption{Infinite multiplication factor during a 4-years depletion 
+        \caption{Infinite multiplication factor during a 1200 days depletion
         simulation.}
@@
 
-Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
-reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. A 
-significant standard deviation (100 pcm) causes the multiplication factor 
-fluctuations visible in this plot.  Protactinium-233 continuously removing into 
-the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
+Protactinium-233 continuously removing into the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
 beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
@@
         \includegraphics[width=1.03\linewidth]{fuel_composition.png}
-        \caption{Normalized number density of major isotopes during 4 years of 
+        \caption{Normalized number density of major isotopes during 1200 days of 
         depletion.}
@@
 neutronics at the beginning of each depletion time interval. The number density 
-of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
+of protactinium is very low (less than 10$^{16}$ 1/cm$^3$) but some small amount 
 of it is produced during the 3-day reprocessing period. In this assessment, the multiplication 
@@
         \centering
-        \includegraphics[width=1.03\linewidth]{rates_fuel.png}
+        \includegraphics[width=1.04\linewidth]{rates_fuel.png}
         \caption{Materials flows rates during online reprocessing.}
@@
         \centering
-        \includegraphics[width=1.03\linewidth]{rates_outflow.png}
+        \includegraphics[width=1.04\linewidth]{rates_outflow.png}
         \caption{Materials flows rates for the protactinium decay tank during 

### 2017-08-01 Moltres.tex
ref typo

@@
 an extra volume of surrounding fuel not included in the Moltres calculations
-cause the depression in the thermal flux in \crep{fig:msre_radial_fluxes}.
+cause the depression in the thermal flux in \cref{fig:msre_radial_fluxes}.
 

### 2017-08-01 Moltres.tex
passive to active

@@
 the reactor temperature profile, re-casting the extended code as
-DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
-experimental \gls{MSRE} data and was then used to simulate local fuel channel
+DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
+experimental \gls{MSRE} data and then used it to simulate local fuel channel
 blockages as well as local temperature perturbations. In a similar vein, Kophazi

### 2017-08-01 Moltres.tex
passive to active

@@
 constructed separately for fuel and moderator regions. For this report,
-SCALE-generated group constants were used. To generate the group constants, an
-infinite square pitch lattice of cylindrical fuel channels surrounded by
-graphite was used, maintaining a fuel fraction of .225 to be consistent with the
+we generated group constants with SCALE with
+an infinite square pitch lattice of cylindrical fuel channels surrounded by
+graphite. This model maintained a fuel fraction of 0.225 to be consistent with the
 \gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
@@
 Other simulation inputs are outlined in \Cref{table:params}.
-The reactor simulation height of 151.75 cm was chosen to produce an
+We chose a reactor simulation height of 151.75 cm to produce an
 approximately critical reactor configuration corresponding to \gls{BOL}
-\gls{MSRE} composition. It is about 10 cm shorter than the actual \gls{MSRE}
-height of 162.56 cm.
+\gls{MSRE} composition. This differs from the actual \gls{MSRE} height, which 
+was 162.56 cm.
 
@@
 As described earlier, Moltres runs naturally in parallel. To test its
-performance, a scaling study was conducted using a typical 2D axisymmetric input
-file. \Cref{fig:scaling_study} shows Moltres's performance. The solution
+performance, we conducted a scaling study with a typical 2D axisymmetric input
+file. \Cref{fig:scaling_study} shows Moltres' performance. The solution
 time follows the ideal closely; slight deviations are expected due to

### 2017-08-01 Moltres.tex
passive to active

@@
 \gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
-input files used for generating the group constants can be found in the
+input files used for generating the group constants appear in the
 \code{io/msre\_conc\_cuboid\_lattice} directory of the
@@
 The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
-different types of transients, the model problem can be reduced to a two
+different types of transients, one can reduce the model problem to a two
 dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
@@
 agreement. Moreover, Moltres results compare favorably with the actual design
-calculations of the \gls{MSRE}. Strong parallel scaling was demonstrated on a
-typical Moltres model problem. Future Moltres publications will highlight
+calculations of the \gls{MSRE}. Moltres demonstrated strong parallel scaling on a
+typical model problem. Future Moltres publications will highlight
 transient simulation cases investigating control rod ejection, single channel

### 2017-08-01 Moltres.tex
commas for clarity

@@
 elements in the mesh and total number of degrees of freedom exceed one million
-and ten million respectively. To handle problems of this size, Moltres has been
-run on up to 608 cores. However, reducing the problem dimension from three to
-two and using a structured mesh that can be much more coarse in the axial
-direction allows the problem to be solved on a single core in under
+and ten million respectively. To handle problems of this size, we ran Moltres
+on up to 608 cores. However, reducing the problem dimension from three to
+two and using a structured mesh, which can be much more coarse in the axial
+direction, allows the problem to be solved on a single core in under
 five minutes.

### 2017-08-01 Moltres.tex
spelling

@@
 interest in the past decade, with many new nuclear companies proposing both
-fluid-fuelled and solid-fuelled commerical \gls{MSR} designs
+fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
 \cite{hyde_liquid_2015,leblanc_integral_2015,noauthor_-able_2017,scarlat_design_2014,noauthor_neutronics_2016}. Two
@@
 inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  These
-characteristics give the \gls{MSR} a potentially unique capability for actinide
-burning and extension of fuel resources.
+Due to these characteristics give the \gls{MSR} potentially unique 
+capabilities burning actinides and extending fuel resources.
 
@@
 jargon, kernels are C++ classes that contain methods for computing residual and
-Jacobian contributions corresponding to individual piecies of governing
+Jacobian contributions corresponding to individual pieces of governing
 equations. Developing the code-base in this way allows modular construction
@@
 tabular form, a user only has to modify a couple of lines in a Moltres input
-file to change from say two to fourty-four neutron groups.
+file to change from say two to forty-four neutron groups.
 
@@
 profiles are in good agreement. In the \gls{MSRE} design, the moderator
-temperature at the reactor inlet is about 20 degrees Faerenheit larger than the
+temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
 fuel temperature, whereas the temperatures are about the same in the Moltres

### 2017-08-01 Moltres.tex
extraneous 'that'

@@
 
-Moltres is an open source code licensed under \gls{LGPL} terms so that the 
+Moltres is an open source code licensed under \gls{LGPL} terms so the 
 \gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
@@
 massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
-default use monolithic and implicit methods that are ideal for closely-coupled
+default use monolithic and implicit methods ideal for closely-coupled
 and multi-scale physics, such as the model problem described
@@
 construct the systems of equations for an arbitrary number of neutron and
-precursor groups. This means that as long as group constants are provided in an appropriate
+precursor groups. Therefore, as long as group constants are provided in an appropriate
 tabular form, a user only has to modify a couple of lines in a Moltres input
@@
 fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
-radii are chosen such that the resulting area/volume fraction of fuel is .225 as
+radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
 for the \gls{MSRE}.
@@
 \Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
-Moltres and the \gls{ORNL} \gls{MSRE} design model. Note that the radius for the
+Moltres and the \gls{ORNL} \gls{MSRE} design model. The radius for the
 plots are chosen to correspond to the peak of the thermal flux in both cases;

### 2017-08-01 Moltres.tex
get rid of random These
fixes weird hybrid sentence
removes cruft from editing, "axial"

@@
 burn-up. Together, these attributes result in significantly reduced core fissile
-inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  These
-Due to these characteristics give the \gls{MSR} potentially unique 
-capabilities burning actinides and extending fuel resources.
+inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  
+Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
+burning actinides and extending fuel resources.
 
@@
 fuel temperature, whereas the temperatures are about the same in the Moltres
-model. This difference is likely because axial the \gls{MSRE} design model 
+model. This difference is likely because the \gls{MSRE} design model 
 neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

### 2017-08-01 Moltres.tex
removes meanwhile

@@
 approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
-3 for the Moltres calculation. Meanwhile, control rod thimbles and
+3 for the Moltres calculation. Control rod thimbles and
 an extra volume of surrounding fuel not included in the Moltres calculations

### 2017-08-01 Moltres.tex
radius -> radii

@@
 \Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
-Moltres and the \gls{ORNL} \gls{MSRE} design model. The radius for the
+Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the
 plots are chosen to correspond to the peak of the thermal flux in both cases;

### 2017-08-02 Moltres.tex
Combine moltres and msre lines in one plot.

@@
 \cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
-profiles are in good agreement. In the \gls{MSRE} design, the moderator
+profile shapes are in decent qualitative agreement with both Moltres and
+\gls{MSRE} calculations showing a peak in graphite temperature before the
+reactor outlet. Fuel temperature increases monotonically in both Moltres and
+\gls{MSRE} models. In the \gls{MSRE} design, the moderator
 temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
@@
     \centering
-    \begin{subfigure}[b]{.5\textwidth}
-      \includegraphics[width=\maxwidth{\textwidth}]{fuel_vs_moderator_axial_sweep.eps}
-      \caption{Moltres predicted axial temperature profiles in hottest channel
+    \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial_temps.eps}
+    \caption{Moltres and \gls{MSRE} design
+      \cite[p. 99]{briggs_molten-salt_1964} predicted axial temperature profiles in hottest channel
       and adjacent graphite}
-      \label{fig:moltres_axial_temps}
-    \end{subfigure}
-    %\quad
-    \begin{subfigure}[b]{.5\textwidth}
-      \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_temps.png}
-      \caption{\gls{MSRE} design axial temperature profiles in hottest channel
-        and adjacent graphite stringer \cite[p. 99]{briggs_molten-salt_1964}}
-      \label{fig:msre_axial_temps}
-    \end{subfigure}
-    \caption{Comparison of \gls{MSRE} design and Moltres predicted axial
-      temperature profiles}
     \label{fig:temp_compare}
@@
 
-\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
-reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
-moderator regions and visa versa in fuel regions are apparent. The flux
+\Cref{fig:radial_fluxes_compare} compares the fast and thermal neutron fluxes at
+the reactor mid-plane ($z=H/2$) for Moltres and \gls{MSRE} design models. Local
+thermal flux growth and fast flux decay in moderator regions and visa versa in
+fuel regions are apparent in the Moltres calculation. The Moltres flux
 magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
-calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
-\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
-approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
-3 for the Moltres calculation. Control rod thimbles and
-an extra volume of surrounding fuel not included in the Moltres calculations
-cause the depression in the thermal flux in \cref{fig:msre_radial_fluxes}.
+calculations \cite[p. 92]{briggs_molten-salt_1964}. The peak fast to thermal
+flux ratio is approximately 3.5 in the \gls{MSRE} design calculation as opposed
+to a ratio of 3 for the Moltres calculation. Control rod thimbles and an extra
+volume of surrounding fuel not included in the Moltres calculations cause the
+depression in the thermal flux in the \gls{MSRE} profile.
 
@@
     \centering
-    \begin{subfigure}[b]{.5\textwidth}
-      \includegraphics[width=\maxwidth{\textwidth}]{moltres_radial_fluxes.eps}
+      \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_radial.eps}
       \caption{The thermal and fast flux profiles at the core mid-plane
-        ($z=H/2$) for Moltres 2-D cylindrical axisymmetric model ($r=0$ is radial center
-        of core)}
-      \label{fig:moltres_radial_fluxes}
-    \end{subfigure}
-    %\quad
-    \begin{subfigure}[b]{.5\textwidth}
-      \includegraphics[width=\maxwidth{\textwidth}]{msre_radial_fluxes.png}
-      \caption{The thermal and fast flux profiles at the core mid-plane
-        ($z=H/2$) for \gls{MSRE} design model \cite{briggs_molten-salt_1964}
-        ($r=0$ is radial center of core)}
-      \label{fig:msre_radial_fluxes}
-    \end{subfigure}
-    \caption{Comparison of \gls{MSRE} design and Moltres predicted radial
-      flux profiles}
+        ($z=H/2$) for the Moltres 2-D cylindrical axisymmetric model and the
+        \gls{MSRE} design model \cite[p. 92]{briggs_molten-salt_1964} ($r=0$ is
+        radial center of core).}
     \label{fig:radial_fluxes_compare}
@@
 \Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
-Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the
-plots are chosen to correspond to the peak of the thermal flux in both cases;
-for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
-because of the effect of the control rod thimbles and extra fuel along the
+Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the plots are
+chosen to correspond to the peak of the thermal flux in both cases; for the
+\gls{ORNL} calculations this is 8.4 inches from the core center-line because of
+the effect of the control rod thimbles and extra fuel along the
 center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
 calculations include the lower and upper plena which are not included in this
-report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
-extends to lower and higher z-values than
-\cref{fig:moltres_axial_fluxes}. Additionally, absorption in the plena caused 
-deviation of the thermal flux from a sinusoidal shape in 
-\cref{fig:msre_axial_fluxes}.
+report's Moltres model. Consequently, the \gls{MSRE} lines extend to lower and
+higher z-values than the Moltres lines. Additionally, absorption
+in the plena cause deviation of the thermal flux from a sinusoidal shape in the
+\gls{MSRE} design case.
 
@@
     \centering
-    \begin{subfigure}[b]{.5\textwidth}
-      \includegraphics[width=\maxwidth{\textwidth}]{moltres_axial_fluxes.eps}
-      \caption{Moltres axial flux profiles along core center line}
-      \label{fig:moltres_axial_fluxes}
-    \end{subfigure}
-    %\quad
-    \begin{subfigure}[b]{.5\textwidth}
-      \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_fluxes.png}
-      \caption{\gls{MSRE} design axial flux profiles 8.4 inches from the core
-        center line \cite{briggs_molten-salt_1964}}
-      \label{fig:msre_axial_fluxes}
-    \end{subfigure}
-    \caption{Comparison of \gls{MSRE} design and Moltres predicted axial
-      flux profiles}
+    \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial.eps}
+    \caption{Moltres axial flux profiles along core center line and \gls{MSRE}
+      design axial flux profiles 8.4 inches from core center line \cite[p. 91]{briggs_molten-salt_1964}.}
     \label{fig:axial_fluxes_compare}

### 2017-08-04 rodRemovalPlot.py
Made python script for rod removal plot :snake:

@@ -1,0 +1,42 @@
+#!/usr/bin/env python3
+# makes a plot for the control rod removal transient
+# note: you need to comment out the header on the csv file
+import matplotlib.pyplot as pl
+from matplotlib import rc
+import numpy as np
+
+# directory with output data:
+outdir = ('/home/gavin/projects/moltres/problems/'
+          'publication_level_cases/twod_control_rod_yank/')
+
+data = np.loadtxt(outdir+'out.csv', delimiter=',')
+
+# get colnames:
+with open(outdir+'out.csv') as fh:
+    line1 = fh.readline().rstrip()
+colnames = line1[1:].split(sep=',')
+print("Found these data columns:")
+print(colnames)
+
+# maps colnames to column index
+colname2col = dict(zip(colnames, range(len(colnames))))
+
+# latex
+rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica'], 'size': 20})
+rc('text', usetex=True)
+pl.style.use('ggplot')  # mwahaha, now people think i know R
+
+# make da plot
+fig, ax = pl.subplots(figsize=(6, 4))
+ax.set_title('Rod position and power level over time')
+ax.set_ylabel('Average nuclear power (W/cm$^3$)', color='r')
+ax.set_xlabel('Time (s)')
+ax.plot(data[:, colname2col['time']],
+        data[:, colname2col['average_fission_heat']], 'r-*')
+ax.set_xlim([0.0, 30.0])
+ax2 = ax.twinx()  # separate y scales
+ax2.set_ylabel('Rod position (cm)', color='b')
+ax2.plot(data[:, colname2col['time']],
+         data[:, colname2col['rodPosition']], 'b-*')
+ax2.set_xlim([0.0, 30.0])
+fig.savefig('rodJerk.png')

### 2017-08-04 flowLossPlot.py
Started loss of flow plot

@@ -1,0 +1,27 @@
+#!/usr/bin/env python3
+# makes a plot for the flow loss plot
+# note: you need to comment out the header on the csv file
+import matplotlib.pyplot as pl
+from matplotlib import rc
+import numpy as np
+
+# directory with output data:
+outdir = ('/home/gavin/projects/moltres/problems/'
+          'publication_level_cases/twod_control_rod_yank/')
+
+data = np.loadtxt(outdir+'out.csv', delimiter=',')
+
+# get colnames:
+with open(outdir+'out.csv') as fh:
+    line1 = fh.readline().rstrip()
+colnames = line1[1:].split(sep=',')
+print("Found these data columns:")
+print(colnames)
+
+# maps colnames to column index
+colname2col = dict(zip(colnames, range(len(colnames))))
+
+# latex
+rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica'], 'size': 20})
+rc('text', usetex=True)
+pl.style.use('ggplot')  # mwahaha, now people think i know R

### 2017-08-04 flowLossPlot.py
Added script that plots power over the flow loss case

@@ -1,13 +1,13 @@
 #!/usr/bin/env python3
-# makes a plot for the flow loss plot
+# makes a plot for the flow loss case
 # note: you need to comment out the header on the csv file
 import matplotlib.pyplot as pl
 from matplotlib import rc
 import numpy as np
 
 # directory with output data:
-outdir = ('/home/gavin/projects/moltres/problems/'
-          'publication_level_cases/twod_control_rod_yank/')
+outdir = ('/home/gav/projects/moltres/problems/'
+          'LOFA/')
 
 data = np.loadtxt(outdir+'out.csv', delimiter=',')
 
@@ -25,3 +25,20 @@ colname2col = dict(zip(colnames, range(len(colnames))))
 rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica'], 'size': 20})
 rc('text', usetex=True)
 pl.style.use('ggplot')  # mwahaha, now people think i know R
+
+fig, ax = pl.subplots( figsize=(6,4))
+ax.set_title('Power vs. salt flow velocity in core')
+ax.set_xlabel('Time (s)')
+ax2 = ax.twinx()
+ax.set_ylabel('Salt flow velocity (cm/s)', color='b')
+ax2.set_ylabel('Average nuclear power (W/cm$^3$)', color='r')
+def flowRate(t):
+    """ gives fixed flow rate as a function of time
+    notice that it depends on pump coastdown time constant, so
+    be sure to change that if needed. right now, it's set to 5s """
+    tau = 5.0
+    return 21.7 * np.exp(-t/tau)
+ax.plot(data[:,0], data[:,1], 'r-*')
+ax2.plot(data[:,0], flowRate(data[:,0]), 'b-*')
+
+fig.savefig('pumpFail.png')

### 2017-08-04 flowLossPlot.py
fixed title

@@ -27,7 +27,7 @@ rc('text', usetex=True)
 pl.style.use('ggplot')  # mwahaha, now people think i know R
 
 fig, ax = pl.subplots( figsize=(6,4))
-ax.set_title('Power vs. salt flow velocity in core')
+ax.set_title('Power and salt flow velocity in core versus time')
 ax.set_xlabel('Time (s)')
 ax2 = ax.twinx()
 ax.set_ylabel('Salt flow velocity (cm/s)', color='b')

### 2017-08-04 coolingLossPlot.py
finished loss of cooling plot script

@@ -1,0 +1,42 @@
+#!/usr/bin/env python3
+# makes a plot for the cooling loss case
+# note: you need to comment out the header on the csv file
+import matplotlib.pyplot as pl
+from matplotlib import rc
+import numpy as np
+
+# directory with output data:
+outdir = ('/home/gav/projects/moltres/problems/'
+          'publication_level_cases/LOSCA/HXFail/')
+
+data = np.loadtxt(outdir+'out.csv', delimiter=',')
+
+# get colnames:
+with open(outdir+'out.csv') as fh:
+    line1 = fh.readline().rstrip()
+colnames = line1[1:].split(sep=',')
+print("Found these data columns:")
+print(colnames)
+
+# maps colnames to column index
+colname2col = dict(zip(colnames, range(len(colnames))))
+
+# latex
+rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica'], 'size': 20})
+rc('text', usetex=True)
+pl.style.use('ggplot')  # mwahaha, now people think i know R
+
+tmax = 200.0
+fig, ax = pl.subplots( figsize=(6,4))
+ax.set_title('Power and temperatures in core')
+ax.set_xlabel('Time (s)')
+ax2 = ax.twinx()
+ax.set_ylabel('Temperature (K)', color='b')
+ax2.set_ylabel('Average nuclear power (W/cm$^3$)', color='r')
+for a in [ax, ax2]:
+    a.set_xlim([0,tmax])
+ax.plot(data[:,0], data[:,1], 'r-*')
+ax2.plot(data[:,0], data[:,2], 'b-*', data[:,0], data[:,3], 'g-*')
+ax2.legend(['Inlet Mean Temp.', 'Fuel Average Temp.'])
+
+fig.savefig('coolingLoss.png')

### 2017-08-07 msbr_reproc.tex
Neutron spectrum normalized by lethargy, STD for K-eff added

@@
         \includegraphics[width=0.95\linewidth]{zone_I_mesh.png}
-        \caption{MSBR unit cell of Zone I geometry.}
+        \caption{MoltenSalt Breeder Reactor (MSBR) unit cell of Zone I geometry.}
         \label{fig:zoneI}
@@
 considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
-Standard deviation for these calculations is approximately 100 pcm.Figure~\ref{fig:keff} 
+Standard deviation for these calculations is approximately 100 pcm. Figure~\ref{fig:keff} 
 shows the infinite multiplication factor for 1200-days reprocessing cycle calculated by 
-Serpent 2 with ENDF/B-VII.0 nuclear data. A 
-significant standard deviation (100 pcm) causes the multiplication factor 
-fluctuations visible in this plot.
+Serpent 2 with ENDF/B-VII.0 nuclear data. A significant standard deviation causes the 
+multiplication factor fluctuations visible in this plot.
 
@@
         \centering
-        \includegraphics[width=1.03\linewidth]{keff.png}
+        \includegraphics[width=1.05\linewidth]{keff.png}
         \caption{Infinite multiplication factor during a 1200 days depletion
-        simulation.}
+        simulation.The confidence interval $\pm\sigma$ is shaded.}
         \label{fig:keff}
@@
 
-Protactinium-233 continuously removing into the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
+Protactinium-233 is continuously removing into the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
 beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
@@
         \centering
-        \includegraphics[width=1.03\linewidth]{fuel_composition.png}
+        \includegraphics[width=1.04\linewidth]{fuel_composition.png}
         \caption{Normalized number density of major isotopes during 1200 days of 
@@
 
-Figure~\ref{fig:spectrum} represents the normalized neutron flux distribution 
+Figure~\ref{fig:spectrum} represents the neutron flux per lethargy energy distribution 
 of the initial and the equilibrium core compositions. The spectrum for the 
@@
         \centering
-        \includegraphics[width=1.04\linewidth]{spectrum.png}
-        \caption{Normalized neutron energy spectrum for initial and equilibrium 
-        composition.}
+        \includegraphics[width=1.05\linewidth]{spectrum.png}
+        \caption{Neutron spectrum for initial and equilibrium 
+        composition (normalized per lethargy).}
         \label{fig:spectrum}

### 2017-08-07 Moltres.tex
bib is broken because its not clear which zotero directory was used to create the original.

@@
 the inclusion of the \gls{MSR} among the Generation-IV reactor designs
-\cite{noauthor_gif_2015}, this reactor concept has gained renewed research
+\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
 interest in the past decade, with many new nuclear companies proposing both
 fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
-\cite{hyde_liquid_2015,leblanc_integral_2015,noauthor_-able_2017,scarlat_design_2014,noauthor_neutronics_2016}. Two
+\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_neutronics_2016}. Two
 key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
@@
 burn-up. Together, these attributes result in significantly reduced core fissile
-inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  
+inventories and spent nuclear fuel mass 
+\cite{gif_generation_2008,gif_generation_2015}.  
 Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
@@
 \gls{MSR} modeling efforts describe steady-state and
-transient behavior. Krepel et. al. extended the in-house \gls{LWR}
+transient behavior. Krepel et al. extended the in-house \gls{LWR}
 diffusion code DYN3D to consider drift of delayed neutron precursors alongside
@@
 intrinsically designed for coupled multi-physics simulation.
+Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
+approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
+Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.
 
@@
 quality through transparency and ease of peer review. In the era of
-GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
+GitHub\cite{github_build_2017} and international scientific collaboration,
 open and modern software practices must be employed in order for nuclear
@@
 \FloatBarrier
+
+\section{Acknowledgments}
+
+All figures in this paper were generated using the python package yt
+\cite{turk_yt:_2011}. The package engauge-digitizer
+\cite{mark_mitchell_markummitchell/engauge-digitizer:_2017} was used to convert
+rasterized \gls{MSRE} line plots into point data for plotting alongside Moltres
+data.
+
 \clearpage

### 2017-08-07 Moltres.tex
re-export of bib"

@@
 fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
-\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_neutronics_2016}. Two
-key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
+\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
+Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
 utilization and no radiation damage constraint on attainable fuel
@@
 The present work introduces the open source simulation tool, Moltres
-\cite{lindsay_arfc/moltres_nodate}, for simulating \glspl{MSR}.  By implementing
+\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
 deterministic neutronics and thermal hydraulics in the context of the
@@
 
-Moltres \cite{lindsay_arfc/moltres_nodate} is implemented as an application for
+Moltres \cite{lindsay_moltres_2017} is implemented as an application for
 use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework.

### 2017-08-07 Moltres.tex
acknowledgements

@@
 
+This work was supported by the University of Illinois Department of Nuclear, 
+Plasma, and Radiological Engineering, the National Center for Supercomputing 
+Applications, and the University of Illinois Blue Waters Professors program. 
+Undergraduate researcher Gavin Ridley was supported through NSF REU Site award 
+1659702, ``INCLUSION - Incubating a New Community of Leaders Using Software, 
+Inclusion, Innovation, Interdisciplinary and OpeN-Science.''
+
+Finally, the authors would like to thank Matthew Turk and the Data Explortation 
+Lab for co-supporting Dr. Lindsay during his postdoctoral appointment.
+
 \clearpage

### 2017-08-07 moltres_cover_letter.tex

% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%       PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
%\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
%\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
%\usepackage{wallpaper}
%\ULCornerWallPaper{0.97}{bk_logo.eps}

\begin{document}

%----------------------------------------------------------------------------------------
%       ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Lynn Weaver, Mostafa Ghiaasiaan, Imre Pazsit\\
Editors\\
Annals of Nuclear Energy}

%----------------------------------------------------------------------------------------
%       YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\address{Department of Nuclear, Plasma, and Radiological Engineering\\
Talbot Hall, Room 226\\
104 S Wright St\\
University of Illinois, Urbana-Champaign\\
Urbana, IL 61801}

\name{\vspace{5mm}
Alexander Lindsay\\
Postdoctoral Scholar}

%----------------------------------------------------------------------------------------
%       LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Professors Weaver, Ghiaasiann, Pazsit:}

Please find enclosed a manuscript entitled: ``Introduction to Moltres: an
Application for Simulation of Molten Salt Reactors'' which I am submitting for
exclusive consideration of publication as a research article in Annals of
Nuclear Energy.

This manuscript describes the new molten salt simulation package Moltres, built
on top of the Multiphysics Object-Oriented Simulation Environment (MOOSE). In
its current version, Moltres combines neutron diffusion, heat transport, and
precursor drift for simulation of thermal molten-salt reactors in two and three
dimensions. Through its MOOSE infrastructure, Moltres is inherently parallel; to
date simulations have been run on as many as 640 cpu cores. The enclosed
manuscript details application of Moltres for reproducing the predicted and
observed steady-state physics of the Molten Salt Reactor Experiment (MSRE)
conducted at Oak Ridge during the 1960s. Good qualitative agreement between
Moltres calculations and the MSRE design is demonstrated. Additionally, we show
nearly perfect parallel scaling of Moltres with increasing processor
count. Though this publication focuses on thermal molten salt reactors (MSRs), the code
in Moltres is general, and simulations of fast MSRs and liquid metal reactors
are planned in the upcoming months.

Thank you for your consideration of our work.  I expect it will be of interest
to a broad readership concerned with multi-physics simulation of next generation
reactors.  Please address all correspondence concerning this manuscript to me
at alexlindsay239@gmail.com.

\closing{Sincere regards,}
%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2017-08-09 msbr_reproc.tex
Revision comments have applied #25

@@
                 \\ \midrule
-                %Net electrical output                 & 1000 MW(e) \\ \midrule
-                %Net thermal efficiency        & 44.4\%
-                %\\ \midrule
+                Net electrical output                 & 1000 MW(e) 
+                \\ \midrule
+                Net thermal efficiency        & 44.4\%
+                \\ \midrule
                 Salt volume fraction in central core zone     & 0.132
@@
                 Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
+                \\ \midrule
+                Fuel-salt inventory (annulus)                 & 3.8 m$^3$	
                 \\ \midrule
@@
         \centering
-        \includegraphics[width=0.95\linewidth]{zone_I_mesh.png}
-        \caption{MoltenSalt Breeder Reactor (MSBR) unit cell of Zone I geometry.}
+        \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
+        \caption{\glsfirst{MSBR} unit cell of Zone I geometry.}
         \label{fig:zoneI}
@@
 considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
-Standard deviation for these calculations is approximately 100 pcm. Figure~\ref{fig:keff} 
+The standard deviation for these calculations is approximately 100 pcm. Figure~\ref{fig:keff} 
 shows the infinite multiplication factor for 1200-days reprocessing cycle calculated by 

### 2017-08-10 full-core_msbr_model.tex
Makefile added
Spectrum and K-eff recalculated with fuel share 13%, reviewers comments accepted

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Full-core analysis of thorium-fueled molten salt breeder reactor using the SERPENT 2 Monte Carlo code}
+\title{Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code}
 
@@
 \usepackage[section]{placeins}
+\usepackage[acronym,toc]{glossaries}  % acronyms inclusion
+\include{acros}
 \graphicspath{{figures/}}
-
+\captionsetup{justification   = raggedright,
+              singlelinecheck = false}
 \newcommand{\SN}{S$_N$}
@@
 \newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
+\makeglossaries
 
@@
 \section{Introduction}
-The molten salt reactor (MSR) is an advanced type of reactor which was developed at Oak Ridge National Laboratory (ORNL) in the 1950s and was operated in the 1960s.
+The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s.
 In the MSR, fluorides of fissile and/or fertile materials (i.e.
-$UF_4$, $PuF_3$ and/or $ThF_4$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
+UF$_4$, PuF$_3$ and/or ThF$_4$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
 This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
@@
 
-The thermal spectrum Molten Salt Breeder Reactor (MSBR) was designed specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
-Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment.
-The mixture of $LiF-BeF_2-ThF_4-UF_4-PuF_3$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
-The MSBR geometry is difficult to describe in computer code input and usually require major approximations to proceed \cite{park_whole_2015}.
+The thermal spectrum \gls{MSBR} was designed specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
+Thorium breeds the fissile $^{233}$U and avoids uranium enrichment.
+The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$-PuF$_3$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
+The \gls{MSBR} geometry is difficult to describe in computer code input and usually require major approximations to proceed \cite{park_whole_2015}.
 
 For the development of MSBR research, this paper demonstrates an advanced whole-core three-dimensional model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code and cross-verification with existing MCNP6 results \cite{park_whole_2015,leppanen_serpent_2012}.
-This neutronics model is of sufficient fidelity to inform optimization of fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation, and for depletion calculations using built-in Serpent burnup module.
-Moreover, this model in the future will be employed to generate problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}, and for routine applications.
+This neutronics model is of sufficient fidelity to inform optimization of fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation.
+Moreover, this model in the future will be employed for depeletion calculations, generation problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}, and for routine applications.
 
 All calculations presented in this paper were performed using the Serpent 2 code version 2.1.28.
-Compared with Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
-Before burnup calculations could be undertaken, MSBR model was verified.
+Compared to Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
 In Section 2, a brief description of the MSBR geometry model is given.
@@
 The reactor core has a central zone, Zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
-The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 2 safety rods consisting of boron carbide clad.
+The first zone is composed of 1320 graphite cells and 4 holes for control rods.
+Two holes are for graphite control rods which have both regulating and shimming functions for normal operation regimes, and two holes are for safety rods which are primarily for backup to assure sufficient negative reactivity for emergency situations.
 The undermoderated zone, Zone II, with 37\% fuel salt, and radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
 This zone is formed of two kinds of elements: elements like those in Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
-At the outer of the core there are graphite reflector and vessel wall.
-Between the core and the reflector blocks located annulus which is 100\% salt needed to provide possibility removing and inserting a graphite assembly.
+At the outer of the core, there are graphite reflector and vessel wall.
+Zones I and II are surrounded radially and axially by fuel salt.
+This space for fuel is necessarily for injection and flow of molten salt.
 
-Figure~\ref{fig:plan} shows the plan view of the whole-core configuration at the expected reactor operational level when all control rods are fully withdrawn from the core.
-Figure~\ref{fig:elevation} shows the longitudinal section of the reactor.
+Fig.~\ref{fig:plan} shows the plan view of the whole-core configuration at the expected reactor operational level when both graphite control rods are fully inserted, and the safety rods are fully withdrawn.
+The safety rods only get inserted during an accident.
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \vspace{-0.3em}
+  \includegraphics[width=0.95\linewidth]{figure_2_1.png}
+  \caption{Plan view of \gls{MSBR} core.}
+  \vspace{-0.6em}
+  \label{fig:plan}
+\end{figure}
+\FloatBarrier
+Fig.~\ref{fig:elevation} shows the longitudinal section of the reactor.
 The violet color represents bare graphite, and the yellow represents fuel salt.
 The blue color shows Hastelloy-N, a material used for the plenum and vessel wall, and the black color is a void space.
-All figures of the core in this work generated using built-in Serpent plotter.
-\begin{figure}[!htb] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \vspace{-0.6em}
-  \includegraphics[width=0.93\linewidth]{figure_2_1.png}
-  \caption{Plan view of MSBR core.}
-  \label{fig:plan}
-\end{figure}
+In this work, all figures of the core were generated using the built-in Serpent plotter.
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
   \centering
   \includegraphics[width=\linewidth]{figure_2_2.png}
-  \caption{Elevation view of MSBR core.}
+  \caption{Elevation view of \gls{MSBR} core.}
   \label{fig:elevation}
@@
 \subsection{Core Zone I and II-A}
-The central portion, called Zone I, is made up of $10.16cm\times10.16cm\times396.24cm$-long graphite elements.
-The fuel salt to graphite volume ratio of Zone I is 13.2\%, and the central hole has a diameter of $3.42cm$.
-Zone II has 37\% salt and central hole diameter of $6.604cm$.
+The central portion, called Zone I, is made up of 10.16cm$\times$10.16cm$\times$396.24cm-long graphite elements.
+The fuel salt to graphite volume ratio of Zone I is 13\%, and the central hole has a diameter of 3.42cm.
+Zone II has 37\% salt and the central hole diameter of 6.604cm.
 Both types of elements mostly have a rectangular shape with a part of cylinder sticking out at each corner to form salt flow between the graphite channels.
 Different sizes of elements are necessary to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
-Figure~\ref{fig:zone12A} demonstrates the reconstructed graphite element utilized for this Monte Carlo model.
-
-\begin{figure}[h] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.96\linewidth]{figure_2_4.png}
-  \caption{Zone I (left) and Zone II-A (right) elements.}
-  \label{fig:zone12A}
-\end{figure}
+Figure~\ref{fig:zone12A} demonstrates the elevation and sectional views of graphite elements utilized for this Monte Carlo model.
 
@@
 The graphite elements for Zone II-A are prismatic and form the first reflecting layer surrounding the core zone I.
-The elements for zone II-B made up in the form of rectangular slats spaced far enough apart to achieve 0.37 fuel salt volume fraction.
-Figure~\ref{fig:zone2B} shows the outer Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
+Zone II-B elements are in the form of rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
+Fig.~\ref{fig:zone2B} shows the outer Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
 The annulus contains 100\% fuel salt and serves to reduce the damage flux at the internal surface of the graphite reflector blocks.
-The reactor Zone II-B graphite $5.08cm$-thick slats and various length in width (average width is about $26.67cm$) are reconstructed as is in the model without any approximation.
-From the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 graphite elements every $45^\circ$ with irregular shape as well as holes for the flow of salt and were simplified into a right circular hollow cylinder sector shape with the central hole.
-This is only simplification for this Monte Carlo model.
-
+The reactor Zone II-B graphite 5.08cm-thick slats and various length in width (average width is about 26.67cm) are reconstructed as is in the model without any approximation.
+From the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 graphite elements every 45$^\circ$ with irregular shape as well as holes for the flow of salt and were simplified into a right circular hollow cylinder sector shape with the central hole.
+This is the only simplification for this model.
+\FloatBarrier
+\begin{figure}[htp!] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=\linewidth]{figure_2_4.png}
+  \caption{Zone I (left) and Zone II-A (right) elements.}
+  \label{fig:zone12A}
+\end{figure}
 \subsection{Material composition}
-The fuel salt, the reactor graphite, and the modified Hastelloy N are exclusive MSBR materials which were created at ORNL.
-The isotope composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to Serpent model without any modification.
-
-\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
+The fuel salt, the reactor graphite, and the modified HastelloyN are materials unique of the MSBR and were created at \gls{ORNL}.
+The initial fuel salt loading composition is LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.8-16-12-0.2 mole \%).
+The lithium in the molten salt fuel is a fully enriched $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
+For cross section data generation ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
+The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when Serpent generate problem-oriented nuclear data library.
+%The isotope composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to Serpent model without any modification.
+%
+\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
   \centering
-  \includegraphics[width=0.93\linewidth]{figure_2_5.png}
+  \includegraphics[width=0.96\linewidth]{figure_2_5.png}
   \caption{Plan view of Zone II-B.}
@@
 \end{figure}
-
-The initial fuel salt loading composition is $LiF-BeF_2-ThF_4-^{233}UF_4-^{239}PuF_3$ (72-16-12-0.232-0.0006 mole \%).
-The lithium is enriched to 99.995\% $^{7}Li$ because $^{6}Li$ is a very strong neutron poison and becomes tritium upon neutron bombardment.
-In this study, the 0.005\% atomic fraction of $^{6}Li$ has been taken into account because even such a small amount of isotope with very high absorption cross section might significantly affect on effective multiplication factor.
-For cross section data generation ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
-%Specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when Serpent generate problem-oriented nuclear data library.
-
+\FloatBarrier
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The MSBR criticality simulations were performed on one Intel Xeon E3-1225 3.3GHz processor wich has four physical cores.
-Each simulation took 23 minutes or 92 minutes per one core.
-A similar whole-core MSBR simulation using MCNP6 required approximately 890 minutes per core \cite{park_whole_2015}, consequently, Serpent 2 can provide tremendous computer costs savings for compute-heavy depletion calculations.
-
 \subsection{Neutron spectrum}
-Figure~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for the whole core in the energy range from $10^{-10}$ to $100 MeV$.
+Fig.~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for the whole core in the energy range from $10^{-9}$ to $10$ MeV.
 The results show close fit with the MCNP simulation \cite{park_whole_2015}, especially in thermal energy range.
@@
   \centering
-  \includegraphics[width=\linewidth]{figure_3_1.png} 
+  \includegraphics[width=1.05\linewidth]{figure_3_1.png} 
   \caption{Neutron flux spectrum of MSBR for MCNP6 and Serpent 2 model.}
@@
 \end{figure}
-It is important to obtain the epithermal and thermal spectrum to produce $^{233}U$ from $^{232}Th$ because radiative capture cross section of thorium monotonically decreasing from $10^{-10} MeV$ to $10^{-5} MeV$.
-Hardening the spectrim tends to significantly increasing resonance absorbtion in thorium and decreasing the absorptions in fissile and construction materials thus large amount of fissile material will be needed to make the reactor critical.
+It is important to obtain the epithermal and thermal spectrum to produce $^{233}$U from $^{232}$Th because radiative capture cross section of thorium monotonically decreasing from $10^{-10}$ MeV to $10^{-5}$ MeV.
+Hardening the spectrum tends to significantly increase resonance absorption in thorium and decreasing the absorptions in fissile and construction materials thus large amount of fissile material will be needed to make the reactor critical.
 
@@
 Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 and Serpent 2 whole core models.
-The coefficient obtained using Serpent 2 is about 4.37\% higher than MCNP6 one.
-The discrepancy was ocurred most likely because the model used in Park et al.
-didn't take into account $^{239}PuF_3$, contained in the fuel salt solution.
-Plutonium-239 has very high fission cross section in thermal energy range and produce more neutrons per fission than $^{233}U$, consequently, multiplication factor for this case is higher.
+The factor obtained using Serpent 2 is about 300 pcm lower than MCNP6 one, while standard deviations are 5 and 9 pcm, respectively.
+The discrepancy might occurred because the model used in Park \emph{et al.} has few simplification in Zone II geometry.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\centering
+\caption{Effective multiplication factor of whole core model.}
 \begin{tabular}{p{0.15\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
@@
 \\ \midrule
-$K_{eff}$  & $1.05134\pm0.00116$ & $1.00736$
+K$_{eff}$  & 1.00389$\pm$0.00005 & 1.00736$\pm$0.00009
 \\
@@
 \end{tabular}
-  \caption{Effective multiplication factor of whole core model.}
   \label{tab:keff}
@@
 Uncertainty for each temperature coefficient also was calculated and shown in Table~\ref{tab:tcoef}.
-The main physical principle underlying the reactor temperature feedback is expandsion of matter when it is heated.
+The main physical principle underlying the reactor temperature feedback is an expansion of matter when it is heated.
 When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is defined by the space for fuel bounded by the graphite.
 When the reactor graphite temperature grows, the density of graphite declines which also frees up space for fuel salt.
-To determine temperature coefficients, three cases were considered:
+To determine temperature coefficients the cross-section temperatures for fuel and moderator were changed from 900K to 1200K.
+Three different cases were considered:
 \begin{enumerate}  
@@
 %\centering
+  \caption{Temperature coefficients of reactivity.}
 \begin{tabular}{p{0.22\linewidth} p{0.22\linewidth} p{0.21\linewidth} p{0.15\linewidth}} \toprule
@@
 \\ \midrule
-Fuel salt        & $-3.93\pm0.005$ & $-3.20\pm0.05$ & $-3.22$ 
+Fuel salt        & $-3.70\pm0.016$ & $-3.20\pm0.05$ & $-3.22$ 
 \\ \midrule
-Moderator        & $+2.44\pm0.013$ & $-0.11\pm0.05$ & $+2.35$ 
+Moderator        & $+2.33\pm0.027$ & $-0.11\pm0.05$ & $+2.35$ 
 \\ \midrule
-Total            & $-1.74\pm0.030$ & $-3.21\pm0.04$ & $-0.87$ 
+Total            & $-1.57\pm0.033$ & $-3.21\pm0.04$ & $-0.87$ 
 \\
@@
 \end{tabular}
-  \caption{Temperature coefficients of reactivity.}
   \label{tab:tcoef}
@@
 On the other hand, when moderator heats up both the density and the geometry changes due to thermal expansion of the graphite blocks and the reflector.
-New graphite density was calculated using linear temperature expansion coefficient of reactor graphite which is $1.3\times10^{-6}1/K$ \cite{robertson_conceptual_1971}.
+New graphite density was calculated using linear temperature expansion coefficient of reactor graphite which is 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
 Based on this information new geometry input, which takes into account graphite expansion, was created.
@@
 The fuel temperature coefficient (FTC) is positive due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with early research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient is negative due to changing density, and would increases during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
+The moderator temperature coefficient is negative due to changing density and would increases during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
 Finally, the total temperature coefficient of reactivity is relatively large and negative, despite graphite components, and affords excellent reactor stability and controllability.
@@
 Accurate material data was employed to calculate reactor key design parameters.
-The effective multiplication factor for initial fuel composition is slightly higher than 1 (1.05) which allows reactor operation from startup to first online reprocessing cycle.
+The effective multiplication factor for initial fuel composition is slightly higher than 1 (1.00389) which allows reactor operation from startup to first online reprocessing cycle.
 The neutron flux energy spectrum was calculated for the whole core and represents the epithermal spectrum of the MSBR.
@@
 rates of removing fission products, the rate of adding thorium), and fuel utilization.
-Secondly, the model will be used to generate problem-oriented nuclear data libraries for multi-physics models of MSRs developed in the MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
+Secondly, the model will be used to generate problem-oriented nuclear data libraries for multi-physics models of \glspl{MSR} developed in the MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
 Finally, transient accident simulations for safety investigation of the reactor core will be performed to study the dynamic behavior of Molten Salt Breeder Reactor.

### 2017-08-13 full-core_msbr_model.tex
english

@@
 
-The thermal spectrum \gls{MSBR} was designed specifically to realize the promise of the thorium fuel cycle which allows the use of natural thorium instead of enriched uranium as the fertile element.
-Thorium breeds the fissile $^{233}$U and avoids uranium enrichment.
-The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$-PuF$_3$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}.
-The \gls{MSBR} geometry is difficult to describe in computer code input and usually require major approximations to proceed \cite{park_whole_2015}.
+The thermal spectrum \gls{MSBR} was designed to realize the promise of the 
+thorium fuel cycle, which uses of natural thorium instead of enriched uranium. 
+Thorium breeds fissile $^{233}$U and avoids uranium enrichment. The mixture of 
+LiF-BeF$_2$-ThF$_4$-UF$_4$-PuF$_3$ has a melting point of $499^\circ$C, a low 
+vapor pressure at operating temperatures, and good flow and heat transfer 
+properties \cite{robertson_conceptual_1971}. The \gls{MSBR} complex geometry is 
+challenging to describe in software input and usually require major 
+geometric approximations\cite{park_whole_2015}.
 
-For the development of MSBR research, this paper demonstrates an advanced whole-core three-dimensional model developed using a continuous-energy the Serpent 2 Monte Carlo reactor physics calculation code and cross-verification with existing MCNP6 results \cite{park_whole_2015,leppanen_serpent_2012}.
-This neutronics model is of sufficient fidelity to inform optimization of fuel salt composition and fuel utilization, neutron fluxes and spectrum evaluation.
-Moreover, this model in the future will be employed for depeletion calculations, generation problem-oriented homogenized nuclear data (multi-group cross sections and diffusion constants) for deterministic reactor codes, multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}, and for routine applications.
+We used the continuous-energy Serpent 2 Monte Carlo particle transport code to 
+calulate whole-core depletion in the \gls{MSBR}. We then compare these results 
+with existing MCNP6 results with a more simplified geometric model 
+\cite{park_whole_2015,leppanen_serpent_2012}. This neutronics model is of 
+sufficient fidelity to inform optimization of fuel salt composition, fuel 
+utilization, neutron fluxes, and spectrum evaluation. Moreover, this model  
+will be employed for depeletion calculations, generation of problem-oriented 
+homogenized nuclear data (multi-group cross sections and diffusion constants) 
+for deterministic reactor codes, and multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}.
 
-All calculations presented in this paper were performed using the Serpent 2 code version 2.1.28.
-Compared to Serpent 1, Serpent 2 has many more useful features and contains a complete redesign of memory management using hybrid OpenMP + MPI parallelization, which is important in depletion calculations using computer clusters with multiple cores \cite{leppanen_serpent_2015}.
-In Section 2, a brief description of the MSBR geometry model is given.
-In Section 3 the results are presented and discussed.
-Section 4 reflected conclusions and plans for the future research.
+All calculations presented in this paper were performed using Serpent 2 version 
+2.1.28. Serpent 2 levereges hybrid OpenMP + MPI parallelized memory management, 
+which enabled us to conduct depletion calculations on computer clusters with multiple cores \cite{leppanen_serpent_2015}.
+
+In Section 2, a brief description of the \gls{MSBR} geometry model is given. In 
+Section 3 the results are presented and discussed. Section 4 reflects 
+conclusions and plans for future research.
 
@@
 \section{MSBR design description}
-The MSBR vessel has diameter of 680 cm and a height of 610 cm.
-It contains molten fluoride fuel-salt mixture which performs two functions: to generate heat in the moderated region and to transport heat energy from the core to primary heat exchanger using the primary salt pump.
-The vessel also contains graphite blocks for neutron moderation and reflection.
-The reactor core has a central zone, Zone I, in which 13\% of the volume is fuel salt and 87\% graphite.
-The first zone is composed of 1320 graphite cells and 4 holes for control rods.
-Two holes are for graphite control rods which have both regulating and shimming functions for normal operation regimes, and two holes are for safety rods which are primarily for backup to assure sufficient negative reactivity for emergency situations.
-The undermoderated zone, Zone II, with 37\% fuel salt, and radial reflector, surrounding the more active portion serves to diminish neutron leakage from the reactor core.
-This zone is formed of two kinds of elements: elements like those in Zone I except for a larger hole size (Zone II-A), and radially spread graphite slats (Zone II-B).
-At the outer of the core, there are graphite reflector and vessel wall.
-Zones I and II are surrounded radially and axially by fuel salt.
-This space for fuel is necessarily for injection and flow of molten salt.
+The \gls{MSBR} vessel has diameter of 680 cm and a height of 610 cm. It 
+contains a molten fluoride fuel-salt mixture that generates heat in the active 
+core region and transports that heat to the primary heat exchanger by way of 
+the primary salt pump.
+In the active core region, the salt flows through channels in moderating 
+and reflecting graphite blocks.
 
-Fig.~\ref{fig:plan} shows the plan view of the whole-core configuration at the expected reactor operational level when both graphite control rods are fully inserted, and the safety rods are fully withdrawn.
-The safety rods only get inserted during an accident.
+The core has two radial zones bounded by a solid cylindrical graphite reflector 
+and the vessel wall.  Zones I and II are surrounded radially and axially by 
+fuel salt. This space for fuel is necessary for injection and flow of molten salt.
+
+Fig.~\ref{fig:plan} shows the plan view of the whole-core configuration at the 
+expected reactor operational level when both graphite control rods are fully 
+inserted, and the safety rods are fully withdrawn. The safety rods only get 
+inserted during an accident. 
 \begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
@@
 \FloatBarrier
-Fig.~\ref{fig:elevation} shows the longitudinal section of the reactor.
-The violet color represents bare graphite, and the yellow represents fuel salt.
-The blue color shows Hastelloy-N, a material used for the plenum and vessel wall, and the black color is a void space.
-In this work, all figures of the core were generated using the built-in Serpent plotter.
+Fig.~\ref{fig:elevation} shows the longitudinal section of the reactor. The 
+violet color represents bare graphite, and the yellow represents fuel salt. The 
+blue color shows Hastelloy-N, a material used for the plenum and vessel wall, 
+and the black color is a void space. In this work, all figures of the core were 
+generated using the built-in Serpent plotter.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{figure_2_2.png}
+  \includegraphics[width=\linewidth]{figure_2_2.}
   \caption{Elevation view of \gls{MSBR} core.}
@@
 
-\subsection{Core Zone I and II-A}
-The central portion, called Zone I, is made up of 10.16cm$\times$10.16cm$\times$396.24cm-long graphite elements.
-The fuel salt to graphite volume ratio of Zone I is 13\%, and the central hole has a diameter of 3.42cm.
-Zone II has 37\% salt and the central hole diameter of 6.604cm.
-Both types of elements mostly have a rectangular shape with a part of cylinder sticking out at each corner to form salt flow between the graphite channels.
-Different sizes of elements are necessary to reduce the peak damage flux and power density in the center of the core to prevent local graphite damage.
-Figure~\ref{fig:zone12A} demonstrates the elevation and sectional views of graphite elements utilized for this Monte Carlo model.
+\subsection{Core Zone I}
+
+The central portion, called Zone I, is made up of 1320 graphite elements, each 
+$10.16$cm$\times10.16$cm$\times396.24$cm.
+In Zone I, 13\% of the volume is fuel salt and 87\% is 
+graphite. Zone I is composed of 1320 graphite cells and 4 channels for control 
+rods : two for graphite rods which both regulate and shim during normal operation, and two
+for backup safety rods to assure sufficient negative reactivity for emergency situations.
+
+These graphite elements have a mostly rectangular shape with lengthwise ridges 
+at each corner that leave space for salt flow elements. Various element sizes 
+reduce the peak damage flux and power density in the center of the core prevent 
+local graphite damage. Figure~\ref{fig:zone12A} 
+demonstrates the elevation and sectional views of graphite elements exactly as 
+they are represented in this Monte Carlo model.
 
 \subsection{Core Zone II-B}
-The second core zone is divided into two different zones: Zone II-A and Zone II-B.
-The graphite elements for Zone II-A are prismatic and form the first reflecting layer surrounding the core zone I.
-Zone II-B elements are in the form of rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume fraction.
-Fig.~\ref{fig:zone2B} shows the outer Zone II, 5.08cm-wide annular space between the core graphite and the radial reflector graphite.
-The annulus contains 100\% fuel salt and serves to reduce the damage flux at the internal surface of the graphite reflector blocks.
-The reactor Zone II-B graphite 5.08cm-thick slats and various length in width (average width is about 26.67cm) are reconstructed as is in the model without any approximation.
-From the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 graphite elements every 45$^\circ$ with irregular shape as well as holes for the flow of salt and were simplified into a right circular hollow cylinder sector shape with the central hole.
-This is the only simplification for this model.
+
+The undermoderated zone, Zone II, surrounds Zone I.
+Combined with the bounding radial reflector, Zone II serves to diminish neutron leakage. This zone is formed of two kinds of elements: elements like those 
+in Zone I with a larger channel diameter (Zone II-A), and radial
+graphite slats (Zone II-B).
+
+Zone II is Zone II 37\% salt by volume and each element has a fuel channel diameter of 
+6.604cm. It is divided into two different zones: Zone II-A and Zone II-B. The 
+graphite elements for Zone II-A are prismatic. Zone II-B elements are in the 
+form of rectangular slats spaced far enough apart to provide the 0.37 fuel salt 
+volume fraction. Fig.~\ref{fig:zone2B} additionally shows the 5.08cm-wide 
+annular space between the core graphite and the radial reflector graphite. The 
+annulus contains 100\% fuel salt and serves to reduce the damage flux at the 
+internal surface of the graphite reflector blocks. The reactor Zone II-B 
+graphite 5.08cm-thick slats and various length in width (average width is about 
+26.67cm) are reconstructed as is in the model without any approximation. From 
+the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone 
+II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as 
+salt channels. These graphite elements were simplified into right-circular 
+cylindrical shapes with central channels. This is the only simplification made 
+to the \gls{MSBR} conceptual geometry in this work.
 \FloatBarrier
@@
 \subsection{Material composition}
-The fuel salt, the reactor graphite, and the modified HastelloyN are materials unique of the MSBR and were created at \gls{ORNL}.
+The fuel salt, the reactor graphite, and the modified HastelloyN are materials 
+unique of the \gls{MSBR} and were created at \gls{ORNL}.
 The initial fuel salt loading composition is LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.8-16-12-0.2 mole \%).
@@
   \includegraphics[width=1.05\linewidth]{figure_3_1.png} 
-  \caption{Neutron flux spectrum of MSBR for MCNP6 and Serpent 2 model.}
+  \caption{Neutron flux spectrum of \gls{MSBR} for MCNP6 and Serpent 2 model.}
   \label{fig:spectrum}
@@
 \section{Conclusions}
-The MSBR full-core analysis was performed using the Serpent 2 Monte Carlo code.
+We performed \gls{MSBR} full-core analysis using the Serpent 2 Monte Carlo code.
 The complex geometry of the reactor is reconstructed in three-dimensional space without any major approximations.
@@
 
-This high-fidelity full-core model will be employed for a number of future efforts.
-First, depletion simulation will be performed using built-in Serpent 2 depletion capabilities to find the equilibrium state of the MSBR, its optimal fuel salt composition, reprocessing characteristics (i.e.
+This high-fidelity full-core model will be employed for a number of future 
+efforts.
+First, depletion simulation will be performed using Serpent 2 depletion capabilities to find the equilibrium state of the MSBR, its optimal fuel salt composition, reprocessing characteristics (i.e.
 rates of removing fission products, the rate of adding thorium), and fuel utilization.

### 2017-08-13 full-core_msbr_model.tex
grammar

@@
 6.604cm. It is divided into two different zones: Zone II-A and Zone II-B. The 
-graphite elements for Zone II-A are prismatic. Zone II-B elements are in the 
-form of rectangular slats spaced far enough apart to provide the 0.37 fuel salt 
+graphite elements for Zone II-A are prismatic. Zone II-B elements are 
+rectangular slats spaced far enough apart to provide the 0.37 fuel salt 
 volume fraction. Fig.~\ref{fig:zone2B} additionally shows the 5.08cm-wide 
@@
 internal surface of the graphite reflector blocks. The reactor Zone II-B 
-graphite 5.08cm-thick slats and various length in width (average width is about 
-26.67cm) are reconstructed as is in the model without any approximation. From 
+graphite 5.08cm-thick slats vary in the radial dimension (average width is 
+26.67cm) but are reconstructed without any approximation. From 
 the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone 
@@
 The fuel salt, the reactor graphite, and the modified HastelloyN are materials 
-unique of the \gls{MSBR} and were created at \gls{ORNL}.
-The initial fuel salt loading composition is LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.8-16-12-0.2 mole \%).
-The lithium in the molten salt fuel is a fully enriched $^{7}$Li because $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron capture.
-For cross section data generation ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
+unique of the \gls{MSBR} and were created at \gls{ORNL}. The initial fuel salt 
+loading composition is LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ (71.8-16-12-0.2 mole 
+\%). The lithium in the molten salt fuel is a fully enriched $^{7}$Li because 
+$^{6}$Li is a very strong neutron poison and becomes tritium upon neutron 
+capture.
+For cross section generation, ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
 The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when Serpent generate problem-oriented nuclear data library.
@@
   \includegraphics[width=0.96\linewidth]{figure_2_5.png}
-  \caption{Plan view of Zone II-B.}
+  \caption{Plan view that includes Zone I, II-A, and II-B elements.}
   \label{fig:zone2B}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and Analysis}
-The reactor physics calculation was carried out using the methods described earlier.
-This section presents calculation results, such as the effective multiplication factor for whole core, neutron flux spectrum, and temperature reactivity coefficients.
-The normalized neutron flux distribution is calculated for the whole core using continuous-energy nuclear data which allows to obtaining very smooth distribution.
+\section{R}
+This section presents calculation results, such as the effective multiplication 
+factor for whole core, neutron flux spectrum, and temperature reactivity 
+coefficients. The normalized neutron flux distribution is calculated for the 
+whole core using continuous-energy nuclear data.
 The temperature coefficients for both fuel salt solution and reactor graphite are computed by comparing effective multiplication factors for two temperatures in the working range.
@@
 \end{figure}
-It is important to obtain the epithermal and thermal spectrum to produce $^{233}$U from $^{232}$Th because radiative capture cross section of thorium monotonically decreasing from $10^{-10}$ MeV to $10^{-5}$ MeV.
-Hardening the spectrum tends to significantly increase resonance absorption in thorium and decreasing the absorptions in fissile and construction materials thus large amount of fissile material will be needed to make the reactor critical.
+It is important to obtain the epithermal and thermal spectrum to produce 
+$^{233}$U from $^{232}$Th because radiative capture cross section of thorium 
+monotonically decreases from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the 
+spectrum tends to significantly increase resonance absorption in thorium and 
+decrease the absorptions in fissile and construction materials. Thus, 
+a signficant amount fissile material will be needed to make the reactor critical.
 
 \subsection{Effective multiplication factor}
-Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 and Serpent 2 whole core models.
-The factor obtained using Serpent 2 is about 300 pcm lower than MCNP6 one, while standard deviations are 5 and 9 pcm, respectively.
-The discrepancy might occurred because the model used in Park \emph{et al.} has few simplification in Zone II geometry.
+Table~\ref{tab:keff} shows the effective multiplication factor for both MCNP6 
+and Serpent 2 whole core models. The factor obtained using Serpent 2 is 300 pcm 
+lower than that obtained by Park \emph{et al.} using MCNP6 \cite{park_whole_2015}. Standard 
+deviations are 5 and 9 pcm, respectively. The discrepancy is likely due to 
+simplificiations to the Zone II geometry model used in Park \emph{et al.}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Temperature effect of reactivity}
-Table~\ref{tab:tcoef} represents the quantitive analysis of temperature effects on reactivity.
-Uncertainty for each temperature coefficient also was calculated and shown in Table~\ref{tab:tcoef}.
-The main physical principle underlying the reactor temperature feedback is an expansion of matter when it is heated.
-When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is defined by the space for fuel bounded by the graphite.
-When the reactor graphite temperature grows, the density of graphite declines which also frees up space for fuel salt.
-To determine temperature coefficients the cross-section temperatures for fuel and moderator were changed from 900K to 1200K.
-Three different cases were considered:
+Table~\ref{tab:tcoef} shows temperature effects on reactivity calculated in 
+this work as compared to both \cite{park_whole_2015} and 
+\cite{robertson_conceptual_1971}. Uncertainty for each temperature coefficient 
+also appears in Table~\ref{tab:tcoef}. The main physical principle underlying 
+the reactor temperature feedback is an expansion of matter when it is heated. 
+When the fuel salt temperature increases, the density of the salt decreases, 
+but at the same time, the total volume of fuel salt in the core remains 
+constant because it is bounded by the graphite. When the reactor graphite 
+temperature grows, the density of graphite declines creating additional space 
+for fuel salt. To determine temperature coefficients, the cross-section temperatures for fuel and moderator were changed from 900K to 1200K. Three different cases were considered:
 \begin{enumerate}  
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-On the one hand, changes in fuel temperature cause only density variation, geometry keeps the same because fuel is in the form of liquid.
-On the other hand, when moderator heats up both the density and the geometry changes due to thermal expansion of the graphite blocks and the reflector.
-New graphite density was calculated using linear temperature expansion coefficient of reactor graphite which is 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}.
-Based on this information new geometry input, which takes into account graphite expansion, was created.
+In the first case, changes in the fuel temperature only impact fuel density. In 
+this case, the geometry is unchanged because fuel is a liquid. However, when 
+the moderator heats up, both the density and the geometry change due to thermal 
+expansion of the solid graphite blocks and reflector. Accordingly, the new 
+graphite density was calculated using a linear temperature expansion 
+coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new 
+geometry input was created based on this information.
 

### 2017-08-13 full-core_msbr_model.tex
sign of fuel and moderator temperature coefficients were reversed from results and table. Please double check this is the correct correction @andrewryh .

@@
 
-The fuel temperature coefficient (FTC) is positive due to thermal Doppler broadening of the resonance capture cross sections in the thorium and is in a good agreement with early research \cite{robertson_conceptual_1971,park_whole_2015}.
-The moderator temperature coefficient is negative due to changing density and would increases during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
+The fuel temperature coefficient (FTC) is negative due to thermal Doppler 
+broadening of the resonance capture cross sections in the thorium and is in a 
+good agreement with early research 
+\cite{robertson_conceptual_1971,park_whole_2015}. The moderator temperature 
+coefficient is positive due to changing density and would increase during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
 Finally, the total temperature coefficient of reactivity is relatively large and negative, despite graphite components, and affords excellent reactor stability and controllability.

### 2017-08-14 full-core_msbr_model.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code}
+\title{Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using 
+the SERPENT 2 Monte Carlo code}
 
@@
 \institute{
-Department of Nuclear, Plasma, and Radiological Engineering, University of Illinois at Urbana-Champaign \break
+Department of Nuclear, Plasma, and Radiological Engineering, University of 
+Illinois at Urbana-Champaign \break
 Urbana, IL
@@
 \section{Introduction}
-The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} in the 1950s and was operated in the 1960s.
-In the MSR, fluorides of fissile and/or fertile materials (i.e.
-UF$_4$, PuF$_3$ and/or ThF$_4$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}.
-This innovation leads to immediate advantages over traditional, solid-fueled, reactors.
-These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
+The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} 
+in the 1950s and was operated in the 1960s. In the MSR, fluorides of fissile 
+and/or fertile materials (i.e. UF$_4$, PuF$_3$ and/or ThF$_4$) are mixed with 
+carrier salts to form a liquid fuel which is circulated in a loop-type primary 
+circuit \cite{haubenreich_experience_1970}. This innovation leads to immediate 
+advantages over traditional, solid-fueled, reactors. These include 
+near-atmospheric pressure in the primary loop, relatively high coolant 
+temperature, outstanding neutron economy, a high level of inherent safety, 
+reduced fuel preprocessing, and the ability to continuously remove fission 
+products and add fissile and/or fertile elements \cite{leblanc_molten_2010}.
 
@@
 properties \cite{robertson_conceptual_1971}. The \gls{MSBR} complex geometry is 
-challenging to describe in software input and usually require major 
-geometric approximations\cite{park_whole_2015}.
+challenging to describe in software input and usually require major geometric 
+approximations\cite{park_whole_2015}.
 
@@
 homogenized nuclear data (multi-group cross sections and diffusion constants) 
-for deterministic reactor codes, and multi-physics simulations \cite{fridman_use_2011,valtavirta_coupled_2017}.
+for deterministic reactor codes, and multi-physics simulations 
+\cite{fridman_use_2011,valtavirta_coupled_2017}.
 
@@
 2.1.28. Serpent 2 levereges hybrid OpenMP + MPI parallelized memory management, 
-which enabled us to conduct depletion calculations on computer clusters with multiple cores \cite{leppanen_serpent_2015}.
+which enabled us to conduct depletion calculations on computer clusters with 
+multiple cores \cite{leppanen_serpent_2015}.
 
@@
 the primary salt pump.
-In the active core region, the salt flows through channels in moderating 
-and reflecting graphite blocks.
+In the active core region, the salt flows through channels in moderating and 
+reflecting graphite blocks.
 
@@
 and the vessel wall.  Zones I and II are surrounded radially and axially by 
-fuel salt. This space for fuel is necessary for injection and flow of molten salt.
+fuel salt. This space for fuel is necessary for injection and flow of molten 
+salt.
 
@@
 inserted, and the safety rods are fully withdrawn. The safety rods only get 
-inserted during an accident. 
-\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
+inserted during an accident.  \begin{figure}[htbp!] % replace 't' with 'b' to 
+        force it to be on the bottom
   \centering
@@
 $10.16$cm$\times10.16$cm$\times396.24$cm.
-In Zone I, 13\% of the volume is fuel salt and 87\% is 
-graphite. Zone I is composed of 1320 graphite cells and 4 channels for control 
-rods : two for graphite rods which both regulate and shim during normal operation, and two
-for backup safety rods to assure sufficient negative reactivity for emergency situations.
+In Zone I, 13\% of the volume is fuel salt and 87\% is graphite. Zone I is 
+composed of 1320 graphite cells and 4 channels for control rods : two for 
+graphite rods which both regulate and shim during normal operation, and two
+for backup safety rods to assure sufficient negative reactivity for emergency 
+situations.
 
@@
 reduce the peak damage flux and power density in the center of the core prevent 
-local graphite damage. Figure~\ref{fig:zone12A} 
-demonstrates the elevation and sectional views of graphite elements exactly as 
-they are represented in this Monte Carlo model.
+local graphite damage. Figure~\ref{fig:zone12A} demonstrates the elevation and 
+sectional views of graphite elements exactly as they are represented in this 
+Monte Carlo model.
 
@@
 The undermoderated zone, Zone II, surrounds Zone I.
-Combined with the bounding radial reflector, Zone II serves to diminish neutron leakage. This zone is formed of two kinds of elements: elements like those 
-in Zone I with a larger channel diameter (Zone II-A), and radial
+Combined with the bounding radial reflector, Zone II serves to diminish neutron 
+leakage. This zone is formed of two kinds of elements: elements like those in 
+Zone I with a larger channel diameter (Zone II-A), and radial
 graphite slats (Zone II-B).
 
-Zone II is Zone II 37\% salt by volume and each element has a fuel channel diameter of 
-6.604cm. It is divided into two different zones: Zone II-A and Zone II-B. The 
-graphite elements for Zone II-A are prismatic. Zone II-B elements are 
-rectangular slats spaced far enough apart to provide the 0.37 fuel salt 
-volume fraction. Fig.~\ref{fig:zone2B} additionally shows the 5.08cm-wide 
-annular space between the core graphite and the radial reflector graphite. The 
-annulus contains 100\% fuel salt and serves to reduce the damage flux at the 
-internal surface of the graphite reflector blocks. The reactor Zone II-B 
-graphite 5.08cm-thick slats vary in the radial dimension (average width is 
-26.67cm) but are reconstructed without any approximation. From 
-the ORNL report \cite{robertson_conceptual_1971}, the suggested design of Zone 
-II-B has 8 irregularly-shaped graphite elements every 45$^\circ$ as well as 
-salt channels. These graphite elements were simplified into right-circular 
-cylindrical shapes with central channels. This is the only simplification made 
-to the \gls{MSBR} conceptual geometry in this work.
+Zone II is Zone II 37\% salt by volume and each element has a fuel channel 
+diameter of 6.604cm. It is divided into two different zones: Zone II-A and Zone 
+II-B. The graphite elements for Zone II-A are prismatic. Zone II-B elements are 
+rectangular slats spaced far enough apart to provide the 0.37 fuel salt volume 
+fraction. Fig.~\ref{fig:zone2B} additionally shows the 5.08cm-wide annular 
+space between the core graphite and the radial reflector graphite. The annulus 
+contains 100\% fuel salt and serves to reduce the damage flux at the internal 
+surface of the graphite reflector blocks. The reactor Zone II-B graphite 
+5.08cm-thick slats vary in the radial dimension (average width is 26.67cm) but 
+are reconstructed without any approximation. From the ORNL report 
+\cite{robertson_conceptual_1971}, the suggested design of Zone II-B has 8 
+irregularly-shaped graphite elements every 45$^\circ$ as well as salt channels. 
+These graphite elements were simplified into right-circular cylindrical shapes 
+with central channels. This is the only simplification made to the \gls{MSBR} 
+conceptual geometry in this work.
 \FloatBarrier
@@
 $^{6}$Li is a very strong neutron poison and becomes tritium upon neutron 
-capture.
-For cross section generation, ENDF/B-VII was employed \cite{chadwick_endf/b-vii.0:_2006}.
-The specific temperature was fixed for each material to correctly model the Doppler-broadening of resonance peaks when Serpent generate problem-oriented nuclear data library.
-%The isotope composition of each material at the initial state was described in detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} and has been applied to Serpent model without any modification.
-%
+capture. For cross section generation, ENDF/B-VII was employed 
+\cite{chadwick_endf/b-vii.0:_2006}. The specific temperature was fixed for each 
+material to correctly model the Doppler-broadening of resonance peaks when 
+Serpent generate problem-oriented nuclear data library.
+%The isotope composition of each material at the initial state was described in 
+%detail in the MSBR conceptual design study \cite{robertson_conceptual_1971} 
+%and has been applied to Serpent model without any modification. %
 \begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
@@
 whole core using continuous-energy nuclear data.
-The temperature coefficients for both fuel salt solution and reactor graphite are computed by comparing effective multiplication factors for two temperatures in the working range.
+The temperature coefficients for both fuel salt solution and reactor graphite 
+are computed by comparing effective multiplication factors for two temperatures 
+in the working range.
 
 \subsection{Neutron spectrum}
-Fig.~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for the whole core in the energy range from $10^{-9}$ to $10$ MeV.
-The results show close fit with the MCNP simulation \cite{park_whole_2015}, especially in thermal energy range.
-\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
+Fig.~\ref{fig:spectrum} demonstrates the normalized neutron flux spectrum for 
+the whole core in the energy range from $10^{-9}$ to $10$ MeV. The results show 
+close fit with the MCNP simulation \cite{park_whole_2015}, especially in 
+thermal energy range.  \begin{figure}[h!] % replace 't' with 'b' to force it to 
+        be on the bottom
   \centering
-  \includegraphics[width=1.05\linewidth]{figure_3_1.png} 
-  \caption{Neutron flux spectrum of \gls{MSBR} for MCNP6 and Serpent 2 model.}
+  \includegraphics[width=1.05\linewidth]{figure_3_1.png} \caption{Neutron flux 
+  spectrum of \gls{MSBR} for MCNP6 and Serpent 2 model.}
   \label{fig:spectrum}
@@
 spectrum tends to significantly increase resonance absorption in thorium and 
-decrease the absorptions in fissile and construction materials. Thus, 
-a signficant amount fissile material will be needed to make the reactor critical.
+decrease the absorptions in fissile and construction materials. Thus, a 
+signficant amount fissile material will be needed to make the reactor critical.
 
@@
 and Serpent 2 whole core models. The factor obtained using Serpent 2 is 300 pcm 
-lower than that obtained by Park \emph{et al.} using MCNP6 \cite{park_whole_2015}. Standard 
-deviations are 5 and 9 pcm, respectively. The discrepancy is likely due to 
-simplificiations to the Zone II geometry model used in Park \emph{et al.}.
+lower than that obtained by Park \emph{et al.} using MCNP6 
+\cite{park_whole_2015}. Standard deviations are 5 and 9 pcm, respectively. The 
+discrepancy is likely due to simplificiations to the Zone II geometry model 
+used in Park \emph{et al.}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   labelsep = newline,
-  name = TABLE, 
-  justification=justified,
+  name = TABLE, justification=justified,
   singlelinecheck=false,%%%%%%% a single line is centered by default
@@
 \begin{tabular}{p{0.15\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
-      & Serpent2      & MCNP6 \cite{park_whole_2015}          
-\\ \midrule
+      & Serpent2      & MCNP6 \cite{park_whole_2015}          \\ \midrule
 K$_{eff}$  & 1.00389$\pm$0.00005 & 1.00736$\pm$0.00009
@@
 temperature grows, the density of graphite declines creating additional space 
-for fuel salt. To determine temperature coefficients, the cross-section temperatures for fuel and moderator were changed from 900K to 1200K. Three different cases were considered:
-\begin{enumerate}  
-\item Temperature of fuel salt rising from 900K to 1200K.
-\item Temperature of graphite rising from 900K to 1200K. 
-\item Whole reactor temperature rising from 900K to 1200K.
+for fuel salt. To determine temperature coefficients, the cross-section 
+temperatures for fuel and moderator were changed from 900K to 1200K. Three 
+different cases were considered:
+\begin{enumerate}  \item Temperature of fuel salt rising from 900K to 1200K.
+\item Temperature of graphite rising from 900K to 1200K.  \item Whole reactor 
+        temperature rising from 900K to 1200K.
 \end{enumerate}
@@
   \caption{Temperature coefficients of reactivity.}
-\begin{tabular}{p{0.22\linewidth} p{0.22\linewidth} p{0.21\linewidth} p{0.15\linewidth}} \toprule
-   Reactivity coefficient [pcm/K]  & Serpent2      & MCNP6 \cite{park_whole_2015}   & Reference \cite{robertson_conceptual_1971}      
+\begin{tabular}{p{0.22\linewidth} p{0.22\linewidth} p{0.21\linewidth} 
+        p{0.15\linewidth}} \toprule
+   Reactivity coefficient [pcm/K]  & Serpent2      & MCNP6 
+        \cite{park_whole_2015}   & Reference \cite{robertson_conceptual_1971}      
         \\ \midrule
-Fuel salt        & $-3.70\pm0.016$ & $-3.20\pm0.05$ & $-3.22$ 
-\\ \midrule
-Moderator        & $+2.33\pm0.027$ & $-0.11\pm0.05$ & $+2.35$ 
-\\ \midrule
-Total            & $-1.57\pm0.033$ & $-3.21\pm0.04$ & $-0.87$ 
-\\
+Fuel salt        & $-3.70\pm0.016$ & $-3.20\pm0.05$ & $-3.22$ \\ \midrule
+Moderator        & $+2.33\pm0.027$ & $-0.11\pm0.05$ & $+2.35$ \\ \midrule
+Total            & $-1.57\pm0.033$ & $-3.21\pm0.04$ & $-0.87$ \\
 \bottomrule
@@
 \cite{robertson_conceptual_1971,park_whole_2015}. The moderator temperature 
-coefficient is positive due to changing density and would increase during reactor operation because of spectrum hardening along with fuel depletion \cite{park_whole_2015}.
-Finally, the total temperature coefficient of reactivity is relatively large and negative, despite graphite components, and affords excellent reactor stability and controllability.
+coefficient is positive due to changing density and would increase during 
+reactor operation because of spectrum hardening along with fuel depletion 
+\cite{park_whole_2015}. Finally, the total temperature coefficient of 
+reactivity is relatively large and negative, despite graphite components, and 
+affords excellent reactor stability and controllability.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
-We performed \gls{MSBR} full-core analysis using the Serpent 2 Monte Carlo code.
-The complex geometry of the reactor is reconstructed in three-dimensional space without any major approximations.
-Accurate material data was employed to calculate reactor key design parameters.
-The effective multiplication factor for initial fuel composition is slightly higher than 1 (1.00389) which allows reactor operation from startup to first online reprocessing cycle.
-The neutron flux energy spectrum was calculated for the whole core and represents the epithermal spectrum of the MSBR.
-The total temperature coefficient is negative, consequently, the MSBR has negative temperature feedback, but MTC is negative which has a negligible effect on safety because it is outweighed by the strong, negative FTC.
+We performed \gls{MSBR} full-core analysis using the Serpent 2 Monte Carlo 
+code. The complex geometry of the reactor is reconstructed in three-dimensional 
+space without any major approximations. Accurate material data was employed to 
+calculate reactor key design parameters. The effective multiplication factor 
+for initial fuel composition is slightly higher than 1 (1.00389) which allows 
+reactor operation from startup to the first online reprocessing cycle. The 
+neutron flux energy spectrum was calculated for the whole core and represents 
+the epithermal spectrum of the MSBR. The total temperature coefficient is 
+negative, consequently, the MSBR has negative temperature feedback, but MTC is 
+negative which has a negligible effect on safety because it is outweighed by 
+the strong, negative FTC.
 
 This high-fidelity full-core model will be employed for a number of future 
-efforts.
-First, depletion simulation will be performed using Serpent 2 depletion capabilities to find the equilibrium state of the MSBR, its optimal fuel salt composition, reprocessing characteristics (i.e.
-rates of removing fission products, the rate of adding thorium), and fuel utilization.
-Secondly, the model will be used to generate problem-oriented nuclear data libraries for multi-physics models of \glspl{MSR} developed in the MOOSE-based coupled neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.
-Finally, transient accident simulations for safety investigation of the reactor core will be performed to study the dynamic behavior of Molten Salt Breeder Reactor.
+efforts. First, depletion simulation will be performed using Serpent 2 
+depletion capabilities to find the equilibrium state of the MSBR, its optimal 
+fuel salt composition, reprocessing characteristics (i.e. rates of removing 
+fission products, the rate of adding thorium), and fuel utilization. Secondly, 
+the model will be used to generate problem-oriented nuclear data libraries for 
+multi-physics models of \glspl{MSR} developed in the MOOSE-based coupled 
+neutronics/thermal-hydraulics code Moltres \cite{lindsay_arfc/moltres:_2017}.  
+Finally, transient accident simulations for safety investigation of the reactor 
+core will be performed to study the dynamic behavior of Molten Salt Breeder 
+Reactor.
 

### 2017-08-14 full-core_msbr_model.tex

@@
 challenging to describe in software input and usually require major geometric 
-approximations\cite{park_whole_2015}.
+approximations \cite{park_whole_2015}.
 
@@
 inserted, and the safety rods are fully withdrawn. The safety rods only get 
-inserted during an accident.  \begin{figure}[htbp!] % replace 't' with 'b' to 
-        force it to be on the bottom
+inserted during an accident.
+
+Fig.~\ref{fig:elevation} shows the longitudinal section of the reactor. The 
+violet color represents bare graphite, and the yellow represents fuel salt. The 
+blue color shows Hastelloy-N, a material used for the plenum and vessel wall, 
+and the black color is a void space. In this work, all figures of the core were 
+generated using the built-in Serpent plotter.
+
+\begin{figure}[hbp!] % replace 't' with 'b' to 
   \centering
@@
 \FloatBarrier
-Fig.~\ref{fig:elevation} shows the longitudinal section of the reactor. The 
-violet color represents bare graphite, and the yellow represents fuel salt. The 
-blue color shows Hastelloy-N, a material used for the plenum and vessel wall, 
-and the black color is a void space. In this work, all figures of the core were 
-generated using the built-in Serpent plotter.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{figure_2_2.}
+  \includegraphics[width=\linewidth]{figure_2_2.png}
   \caption{Elevation view of \gls{MSBR} core.}
@@
 The central portion, called Zone I, is made up of 1320 graphite elements, each 
-$10.16$cm$\times10.16$cm$\times396.24$cm.
+$10.16$cm$\times$10.16cm$\times$396.24cm.
 In Zone I, 13\% of the volume is fuel salt and 87\% is graphite. Zone I is 
-composed of 1320 graphite cells and 4 channels for control rods : two for 
+composed of 1320 graphite cells and 4 channels for control rods: two for 
 graphite rods which both regulate and shim during normal operation, and two
@@
 
-\subsection{Core Zone II-B}
-
+\subsection{Core Zone II}
 The undermoderated zone, Zone II, surrounds Zone I.
@@
 \FloatBarrier
-\begin{figure}[htp!] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
   \centering
@@
 \end{figure}
+\FloatBarrier
 \subsection{Material composition}
@@
   \centering
-  \includegraphics[width=0.96\linewidth]{figure_2_5.png}
+  \includegraphics[width=0.89\linewidth]{figure_2_5.png}
   \caption{Plan view that includes Zone I, II-A, and II-B elements.}
+    \vspace{-0.6em}
   \label{fig:zone2B}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{R}
+\section{Results}
 This section presents calculation results, such as the effective multiplication 
@@
 close fit with the MCNP simulation \cite{park_whole_2015}, especially in 
-thermal energy range.  \begin{figure}[h!] % replace 't' with 'b' to force it to 
-        be on the bottom
+thermal energy range.  
+\begin{figure}[b!] % replace 't' with 'b' to force it to 
   \centering
@@
 discrepancy is likely due to simplificiations to the Zone II geometry model 
-used in Park \emph{et al.}.
+used in Park \emph{et al.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-08-31 discussion.tex
update ans paper to recent publications

@@
 \section{Discussion}
-This work demonstrated that, given infinite
-reprocessing and \gls{MOX} fabrication capacities,
+This work demonstrated that, with reprocessing capacity of 250 MTHM per month,
+and a fabrication capacity of 300 MTHM per month,
 France, by receiving \gls{UNF} from other \gls{EU} nations,
-can transition into a full \gls{SFR} fleet
-with installed capacity of 60,000 MWe by 2076.
-The initial fuel demand is filled by \gls{MOX} from
-reprocessed \gls{UNF}, which later on
-will be met by \gls{MOX} created from recycled \gls{MOX}.
+can transition into, for unchanging nuclear electricity demand,
+a fully \gls{SFR} fleet
+with installed capacity of 66,000 MWe by 2076.
+\gls{MOX} from reprocessed \gls{UNF} meets the initial fuel demand,
+which later on is supplied by \gls{MOX} created from recycled \gls{MOX}.
 
@@
 repository or a management plan, they have a strong incentive
-to send all their \gls{UNF} to France. Especially, the nations
-with aggressive nuclear reduction can phase out nuclear
-without constructing a High Level Waste repository. France has a financial
+to send all their \gls{UNF} to France. The nations
+with aggressive nuclear reduction will be able phase out nuclear
+without constructing a High Level Waste repository. France has an
 incentive to take this fuel, since reuse of used fuel from
@@
 
-Though complex political and economic factors have not been
-addressed, and various assumptions were made for this scenario,
+Though complex political and economic factors are not
+addressed, and various assumptions present for this scenario,
 this option may hold value for the \gls{EU} as a nuclear community,

### 2017-08-31 introduction.tex
update ans paper to recent publications

@@
 \section{Abstract}
-The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
-\cite{noauthor_cne2_nodate} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
+The French 2012-2015 Commission Nationale d'Evaluation reports
+\cite{noauthor_cne2_nodate} emphasize preparation for a transition from \glspl{LWR} to \glspl{SFR}.
 This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
 for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
-A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{UNF} mass
-and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
-the transition into \glspl{SFR}. The study concludes that France can avoid deployment
+A \Cyclus simulation ran from 1950 to 2160 for EU to track the \gls{UNF} mass
+and tails inventory to support
+the transition into \glspl{SFR} (66GWe - 110 \glspl{SFR}). The study concludes that France can avoid deployment
 of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.
@@
 \section{Introduction}
-This paper uses \Cyclus, the agent-based simulator \cite{huff_fundamental_2016} to analyze
-the future nuclear inventory in the European Union. This paper focuses on the used fuel
-inventory in \gls{EU} member states in 2050, and analyzes a potential strategy of used fuel
+We used \Cyclus to analyze
+the future nuclear inventory in the European Union. \Cyclus is an agent-based extensible
+framework for modeling the flow of material through future nuclear cycles \cite{huff_fundamental_2016}.
+This paper focuses on the used fuel
+inventory in \gls{EU} member states in 2050, and focuses on a potential strategy of used fuel
 management.
@@
 The \gls{MOX} created will fuel French transition to a \gls{SFR} fleet
-and may allow France to avoid building additional \glspl{LWR}.
+and allows France to avoid building additional \glspl{LWR}.
 
-Past research, which focuses solely on France, has made the assumptions that additional \glspl{LWR},
-namely \glspl{EPR} are constructed in order to supply \gls{UNF} required
-for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
-There has been studies on implementation of partitioning and transmutation
+Past research focused solely on France typically assumes that additional \glspl{LWR},
+namely \glspl{EPR} supply \gls{UNF} to produce \gls{MOX} \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
+Studies exist on implementation of partitioning and transmutation
 in a regional (European) context, with \glspl{ADS} and Gen-IV reactors \cite{fazio_study_2013}.
-There has been little attention in reprocessing legacy \gls{UNF} from other
+There is little attention paid to reprocessing legacy \gls{UNF} from other
 EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
@@
 \section{Methodology}
-The work relies on \Cyclus, an agent-based simulator, to simulate the nuclear fuel cycle
-and track material flows in \gls{EU} nations. The \gls{PRIS} open-source 
-database from \gls{IAEA} was used to populate the simulation with deployment 
-information. That database is imported as a csv file, listing the country, reactor unit, type, net capacity (MWe), status,
+
+The nuclear history of EU nations are modeled, using the \gls{PRIS} open-source 
+database from \gls{IAEA}. That database is imported as a csv file, to populate the simulation
+with deployment information, listing the country, reactor unit, type, net capacity (MWe), status,
 operator, construction date, first criticality date, first grid date, commercial date, shutdown
@@
 which lists the individual reactor units as agents. After running the \Cyclus input file,
-the output file is analyzed by another python script. All the scrips and data used
-in this paper are available in \url{https://github.com/jbae11/transition-scenarios}.
+another python script analyzes the output file. All the scripts and data used
+in this paper are available in \cite{jin_whan_bae_2017_854820}.
+%% Probably a separate repository is needed..?
 
@@
 The first simulation calculates
-how much used fuel and tailings \gls{EU} nations accumulate from 1970 to 2050,
-as well as the amount of \gls{MOX} that can be created with the \gls{UNF} inventory.
-The paper models a once-through cycle for all 
-\gls{EU} nations with the exception of France. France can reprocess used \gls{UOX} and \gls{MOX} to
-produce \gls{MOX} from reprocessed plutonium and depleted uranium (tailings).
-The simulation assumes \gls{MOX} is reprocessed infinitely.
+the mass and composition of used fuel and tails \gls{EU} nations accumulate from 1970 to 2050,
+as well as the amount of \gls{MOX} that the \gls{UNF} inventory creates.
+All EU nations with the exception of France adopts a once-through fuel cycle.
+France can reprocess used \gls{UOX} and \gls{MOX} to
+produce \gls{MOX} from reprocessed plutonium and depleted uranium (tails).
+The simulation assumes infinite \gls{MOX} reprocessing.
 
+%%% PASSIVE PHRASE WHAT TO DO
 After obtaining the \gls{UNF} inventory of all \gls{EU} in 2050, the second
-simulation is run where the \gls{UNF} inventory is reprocessed and
-used as fuel for the newly deployed \gls{SFR} reactors.
-The \glspl{SFR} are deployed to make up for the decommissioned capacity
-of \glspl{LWR} in France, to remain a constant installed capacity of $60,000$ MWe up to 2160.
-\gls{SFR} reactors in this paper models after the ASTRID reactor,
-and use \gls{MOX} fuel created from 11\% reprocessed plutonium
-and 89\% tailings to a burnup
-of approximately 100 GWdth/t. The high burnup allows breeding of plutonium.
-Eventually, the entire fleet
-of \glspl{SFR} are fueled by \gls{MOX} created from recycled \gls{MOX}.
+simulation runs where the \gls{UNF} inventory is reprocessed and used
+as fuel for the newly deployed \gls{SFR} reactors.
+\gls{SFR} reactors in this paper model after the ASTRID reactor.
+ASTRID-type \glspl{SFR} make up for the decommissioned capacity
+of \glspl{LWR} in France, to remain a constant installed capacity of $66,000$ MWe up to 2160.
+It is assumed that ASTRID-type reactors use \gls{MOX} fuel created from 11\% reprocessed plutonium
+and 89\% tails and burns the \gls{MOX} fuel to approximately 100 GWdth/t.
+The high burnup allows breeding of plutonium.
+Eventually, the  \gls{MOX} created from recycled \gls{MOX}
+fuels the entire fleet of 110 \glspl{SFR}.
 
 \subsection{Assumptions}
-This paper makes the following assumptions:
+The simulation ran for this paper had the following assumptions:
 \begin{itemize}
-	\item \gls{SFR} technology available for deployment in 2040
-	\item Decay has no effect on reprocessing viability
-	\item Reactor construction is always completed on time 
-	\item Separated uranium is stockpiled
-	\item \glspl{LWR} have a lifetime of 60 years, unless stated otherwise (early shutdown)
+	\item \gls{SFR} technology is available for deployment in 2040.
+	\item Decay is not taken into account.
+	\item Reactor construction is always completed on time.
+	\item Separated uranium is unused and stockpiled.
+	\item \glspl{LWR} have an assumed lifetime of 60 years, unless shut down prematurely.
 	\item Newly deployed \glspl{SFR} have a lifetime of 80 years.
-	\item (Only for SFR Case) Reprocessing and \gls{MOX} fabrication begins in 2020.
-	\item (Only for SFR Case) French nuclear capacity remains constant at 60,000 MWe
-	\item (Only for SFR Case) Infinite reprocessing and fabrication capacity
+	\item Additional assumptions in the \gls{SFR} case include:
+	\begin{itemize}
+		\item Reprocessing and \gls{MOX} fabrication begins in 2020.
+		\item French nuclear capacity remains constant at 66,000 MWe.
+		\item Reprocessing and fabrication capacity is unlimited.
+	\end{itemize}
 \end{itemize}
@@
 \subsection{Deployment Timeline}
-Projections of future reactor deployment in this simulation were
-assessed based on analysis from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
+Projections of future reactor deployment in this simulation is based on assessment of analyses
+from references such as \gls{PRIS} for reactors planned for construction \cite{iaea_pris_nodate},
 the World Nuclear Association and two other papers for future plans in EU nations
@@
 The projections extend to 2050 at the latest. This allows the simulation to take place from
-1970 to 2050, the latest foreseeable future. The specific plans for each \gls{EU} nation are explained
-in detail in later sections.
+1970 to 2050, the latest foreseeable future. Later sections explain, in detail, the specific plans for each \gls{EU} nation.
 
-It is also assumed that all reactors that are 
-currently operating have a lifetime of 60 years, unless their government plans
-early shutdown. This will approximate when and how many \glspl{SFR} need to be built
-to make up for the shutdown of \glspl{LWR}.
+Figure \ref{fig:eu_pow} displays the
+timeseries of installed capacity in \gls{EU} nations.
+
+\begin{figure}[htbp!]
+	\begin{center}
+		\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
+	\end{center}
+	\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
+	\label{fig:eu_pow}
+\end{figure}
+\FloatBarrier
 
@@
 
-From 2040, when \gls{SFR}s become available,
-600-MWe \gls{SFR}s are deployed to make up for the 
-decommissioned \gls{LWR} capacities. Note that a second
-separate simulation is run to emphasize France apart from
-all other EU nations.
-
-Initially in 2040, 22 \gls{SFR}s
-are deployed for the previously decommissioned
-\gls{LWR}s. From then, \glspl{SFR} are deployed to
-make up for the decommissioned \gls{LWR} capacity.
-This results in an installed capacity of 60,000 MWe
-of \gls{SFR} by 2076.
+Once \glspl{SFR} become available, in 2040,
+600-MWe \glspl{SFR} are deployed to make up for the 
+decommissioned \gls{LWR} capacities. 
+This results in an installed capacity of 66,000 MWe
+of \gls{SFR} by 2076, when the last \gls{LWR} decommissions.
 
@@
 	\begin{center}
-		\includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
+		\includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
 	\end{center}
@@
 \end{figure}
+\begin{figure}[htbp!]
+	\begin{center}
+		\includegraphics[width=\columnwidth]{./images/french-transition/sfr_deploy.png}
+	\end{center}
+	\caption{Deployment of French \glspl{SFR} and total installed capacity}
+	\label{fig:dep}
+\end{figure}
 \FloatBarrier
 
-\Cref{fig:sfr_num} displays
-the French transition into \glspl{SFR} over time.
-The steep transition from 2035 to 2060 is due mainly to
-French aggressive growth from 1975 to 2000. Note the jump in
-2040 is due to an attempt to make up for the gap between the
-mass decommission of old \glspl{LWR} and the availability
-of \glspl{SFR}.
+\Cref{fig:sfr_num} and \cref{fig:dep} display
+the French transition to \glspl{SFR} over time.
+The steep transition from 2040 to 2060 reflects the scheduled
+decommissioning of reactors built in the 1975-2000
+era of aggressive nuclear growth in France.
 
-\subsection{Depletion Calculations}
+\subsection{Material Definitions}
 Depletion calculations of the nuclear fuel are recipe-based, such that a fresh 
@@
 For the compositions of the fuel, a reference depletion calculation
-from ORIGEN is used (see \cref{tab:comp}). The recipe has also been used for
+from ORIGEN is used. The recipe has also been used for
 \cite{wilson_adoption_2009}.
@@
 \subsection{Scenario Descriptions}
-The simulation follows the model fuel cycle, where a `source'
-provides natural uranium, which is enriched by an 'enrichment'
-facility to produce \gls{UOX}, while disposing enrichment waste (tailings)
-to the 'sink' facility. The enriched \gls{UOX} is used
-in the \gls{LWR}s and \gls{UOX} waste is produced. The used fuel
-is then reprocessed to separate plutonium and uranium.
-The plutonium is mixed with depleted uranium (tailings) to \gls{MOX}.
-The reprocessed uranium is stockpiled. The cycle is illustrated in
-\cref{diag:fc}.
-
-The second scenario separates plutonium from the \gls{UNF}
-inventory from the previous simulation. The separated
-plutonium is mixed with the depleted uranium inventory from the previous simulation
-to create \gls{MOX}, which is used in the \gls{SFR}s. The used
-\gls{MOX} is also reprocessed to extract plutonium, which is also
-mixed with depleted uranium to produce \gls{MOX}.
+The simulation follows the model fuel cycle
+where a `source' provides natural uranium, which is enriched by an 'enrichment'
+facility to produce \gls{UOX}, while disposing enrichment waste (tails)
+to the 'sink' facility. The enriched \gls{UOX} fuels
+the \gls{LWR}s and \gls{UOX} waste is produced. The used fuel
+is sent to a pool to cool for 3 years \cite{carre_overview_2009}.
+The cooled fuel is then reprocessed to separate plutonium and uranium,
+or sent to a repository.
+The plutonium mixed with depleted uranium (tails) makes \gls{MOX}.
+The reprocessed uranium is unused and stockpiled. Uranium is reprocessed
+in order to separate the raffinate (Minor actinides and fission products)
+from 'usable' material. Though not utilized in this paper, reprocessed
+uranium may substitute depleted uranium for \gls{MOX} production. In this
+paper, there was sufficient depleted uranium inventory that using reprocessed
+uranium was not considered. However, further in the future where the depleted
+uranium inventory drains, reprocessed uranium (or, natural uranium) will need to be utilized.

### 2017-08-31 results.tex
update ans paper to recent publications

@@
 
+\Cref{tab:sim_result} lists the important metrics
+obtained from the first simulation. The following
+values are the \gls{EU} inventory and history at year 2050,
+and will be reprocessed in the second simulation.
+
 \begin{table}[h]
 	\centering
-	\scalebox{0.7}{
+		\scalebox{0.77}{
 	\begin{tabular}{|c|c|c|c|}
@@
 		Category & Unit & Value & Specifics\\ \hline
-			Total UOX Usage & MTHM & 178,865 &  \\ \hline
-			Total MOX Usage & MTHM & 8,909 & \\ \hline
-			Total Used UOX Stored & MTHM & 157,472 & \gls{UNF} that are not reprocessed\\ \hline
-			Total Used  MOX Stored & MTHM & 679 & \gls{UNF} that are not reprocessed \\ \hline
-			Total Tailings & MTHM & 1,063,909 & \\ \hline
-			Total Natural U Used & MTHM & 1,251,658 & \\ \hline
-		\end{tabular}}
+		Total UOX Usage & MTHM & 181,471 &  \\ \hline
+		Total MOX Usage & MTHM & 6,302 & \\ \hline
+		Total Used UOX Stored & MTHM & 141,659 & \gls{UNF} that is not reprocessed\\ \hline
+		Total Used  MOX Stored & MTHM & 3,611 & \gls{UNF} that is not reprocessed \\ \hline
+		Total Tailings & MTHM & 1,081,826 & \\ \hline
+		Total Natural U Used & MTHM & 1,269,897 & \\ \hline
+	\end{tabular}
+}
 	\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
@@
 	\end {table}
-
-		\Cref{tab:sim_result} lists the important metrics
-		obtained from the first simulation. The following
-		values are the \gls{EU} inventory and history at year 2050.
-
-		Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
-		timeseries of number of reactors and installed capacity in \gls{EU} nations.
-
-		\begin{figure}[htbp!]
-			\begin{center}
-				\includegraphics[width=\columnwidth]{./images/eu_future/number_plot.png}
-			\end{center}
-			\caption{Timeseries of number of reactors in \gls{EU}.}
-			\label{fig:eu_num}
-		\end{figure}
-
-		\begin{figure}[htbp!]
-			\begin{center}
-				\includegraphics[width=\columnwidth]{./images/eu_future/power_plot.png}
-			\end{center}
-			\caption{Timeseries of installed nuclear capacity in \gls{EU}.}
-			\label{fig:eu_pow}
-		\end{figure}
 	\FloatBarrier
@@
 	timeseries of mass of tailings and used fuel accumulation in \gls{EU}.
-
 	Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.
@@
 		\begin{center}
-				\includegraphics[width=\columnwidth]{./images/eu_future/tailings.png}
+			\includegraphics[width=\columnwidth]{./images/eu_future/tails.png}
 		\end{center}
-			\caption{Timeseries of Tailings Mass in the \gls{EU}.}
+		\caption{Timeseries of Tails Mass in the \gls{EU}.}
 		\label{fig:eu_tail}
@@
 		\begin{center}
-				\includegraphics[width=\columnwidth]{./images/eu_future/snf.png}
+			\includegraphics[width=\columnwidth]{./images/eu_future/snf_discharge.png}
 		\end{center}
@@
 
-		\begin{table}[h]
-			\centering
-			\begin{tabular}{|c|c|c|}
-				\hline
-				Isotope & Mass Fraction in Used Fuel [\%] & Quantity [t] \\ \hline
-				Total & .9358 & 1,473 \\ \hline
-				Pu238 & .0111 & 17.47 \\ \hline
-				Pu239 & .518 & 815.7 \\ \hline
-				Pu240 & .232 & 365.33 \\ \hline
-				Pu241 & .126 & 198.41 \\ \hline
-				Pu242 & .0487 & 76.68 \\ \hline
-			\end{tabular}
-			\caption{Plutonium From Used Fuel}
-			\label{tab:pu}
-		\end{table}
+	\subsection{French \gls{SFR} Transition Scenario}
 
-		To create \gls{MOX} for an ASTRID, 11\% Pu and 89\% depleted uranium is used.
-		Thus $1,473$ tons of plutonium yields $13,390$ tons of
-		\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
-		and quantity of plutonium that can be obtained from the 2050 \gls{UNF} inventory.
-
-		\subsection{French \gls{SFR} Transition Scenario}
+	Reprocessing \gls{UNF} collected from all EU nations can start approximately
+	270 \glspl{SFR}, which is more than enough for two generations of 66GWe \gls{SFR}
+	fleet. With the \gls{SFR} breeding ratio of over one, France can transition into
+	a fully \gls{SFR} fleet without extra construction of \glspl{LWR}.
 
@@
 	Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
-		plutonium from \gls{UNF} can be estimated to $\frac{1,473}{4.9} \approx 300$ \glspl{SFR},
+	plutonium from \gls{UNF} can be estimated to $\frac{Pu \ from \ legacy \ \gls{UNF}}{4.9} \approx 270$ \glspl{SFR},
 	assuming infinite reprocessing and fabrication capacity as well as
@@
 	Also, assuming that \gls{MOX} can be recycled indefinitely,
-		used \gls{MOX} from an ASTRID reactor
-		contains enough plutonium to produce a \gls{MOX} fuel with
+	used \gls{MOX} from an ASTRID reactor contains enough plutonium to produce a \gls{MOX} fuel with
 	the same mass, if mixed with depleted uranium. For example,
 	used \gls{MOX} from an ASTRID reactor is assumed to be 12.6\% plutonium
-		in this simulation (see \cref{tab:comp}), whereas a fresh \gls{MOX} is 11\% plutonium.
+	in this simulation, whereas a fresh \gls{MOX} is 11\% plutonium.
 	Separating plutonium from used \gls{MOX} from
@@
 
-		The second scenario, with the tailings and used \gls{UOX}
-		inventory, evaluates if the French can transition into \gls{SFR}
-		without constructing additional \gls{LWR}s. This simulation
-		assumed infinite reprocessing and fabrication capacity.
-
-		\Cref{fig:fuel} shows the timeseries mass of \gls{MOX} used in the 
-		\gls{SFR}s separated by their origin.
-		Note that the plot shows \gls{MOX}
-		accumulation prior to \gls{SFR} deployment from 2020.
+	\Cref{fig:fuel} shows \gls{MOX} loaded in the \glspl{SFR} per month.
+	The spikes are due to initial fuel demand for new deployment of \glspl{SFR}.
+	The initial loading of new \glspl{SFR} are done with the \gls{MOX} created
+	from legacy \gls{UNF}. Once there are enough amounts of extra plutonium creation
+	by deployed \glspl{SFR}, the legacy \gls{UNF} is no longer used.
 
@@
 		\end{center}
-			\caption{Timeseries of fuel used in the \gls{SFR}s [tons]}
+		\caption{Timeseries of fuel loaded into \glspl{SFR}}
 		\label{fig:fuel}
@@
 	\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
-		(minor actinides, fission products) over time. Note that 
-		reprocessing waste from \gls{UOX} reprocessing is substantially
-		greater than waste from \gls{MOX} reprocessing due to its lower
-		plutonium and uranium content.
-
-		\Cref{fig:pu_isotopics} shows the isotopics of the plutonium that are
-		reprocessed from the used fuel inventory.
+	(minor actinides, fission products) over time. The spikes in the 
+	waste discharge is due to large influx of spent fuel from
+	decommissioned \glspl{SFR}.\Cref{fig:pu_no_cum} shows the separated plutonium discharge
+	per month from the reprocessing plant. The plutonium outflux
+	does not precisely follow the fuel demand because \Cyclus agents have
+	material buffers that store commodity fuel for later usage. 
+	\Cref{tab:sfr_sim_result} lists metrics obtained from the second simulation.
 
@@
 		\begin{center}
-				\includegraphics[width=\columnwidth]{./images/french-transition/rep_pu.png}
+			\includegraphics[width=\columnwidth]{./images/french-transition/pu.png}
 		\end{center}
-			\caption{Plutonium timeseries separated by isotope}
-			\label{fig:pu_isotopics}
+		\caption{Separated plutonium discharge from Reprocessing Plant}
+		\label{fig:pu_no_cum}
 	\end{figure}
@@
 		\end{center}
-			\caption{Reprocessing Waste for French Transition Scenario.}
+		\caption{Reprocessing waste discharge from Reprocessing Plant}
 		\label{fig:reprocess_waste}
@@
 		\centering
-			\scalebox{0.7}{
+		\scalebox{0.86}{
 			\begin{tabular}{|c|c|c|}
@@
 				Category & Unit & Value  \\ \hline
-					Total MOX used & MTHM & 116,115  \\ \hline
-					Total \glspl{SFR} Deployed & & 200 \\ \hline
-					Total Plutonium Reprocessed & MTHM & 14,414 \\ \hline
-					Total MOX from UOX Waste & MTHM & 9,729  \\ \hline
-					Total MOX from MOX Waste & MTHM  & 150,426  \\ \hline
-					Total Tailings used & MTHM & 105,664 \\ \hline
-					Total legacy UNF reprocessed & MTHM & 97,298 \\ \hline
-					Total Reprocessed Uranium Stockpile & MTHM & 251,100 \\ \hline
-					Total Reprocess Waste & MTHM & 14,414 \\ \hline
+				Total MOX used & MTHM & 127,640  \\ \hline
+				Total \glspl{SFR} Deployed & & 220 \\ \hline
+				Total Plutonium Reprocessed & MTHM & 16,352 \\ \hline
+				Total MOX from UOX Waste & MTHM & 6,570  \\ \hline
+				Total MOX from MOX Waste & MTHM  & 121,070 \\ \hline
+				Total Tails used & MTHM & 116,153 \\ \hline
+				Total legacy UNF reprocessed & MTHM & 77,082 \\ \hline
+				Total Reprocessed Uranium Stockpile & MTHM & 184,172 \\ \hline
+				Total Reprocess Waste & MTHM & 16,352 \\ \hline
 			\end{tabular}}

### 2017-08-31 introduction.tex
shortened page to 4

@@
 The French 2012-2015 Commission Nationale d'Evaluation reports
-\cite{noauthor_cne2_nodate} emphasize preparation for a transition from \glspl{LWR} to \glspl{SFR}.
+\cite{noauthor_reports_2015} emphasize preparation for a transition from \glspl{LWR} to \glspl{SFR}.
 This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
@@
 another python script analyzes the output file. All the scripts and data used
-in this paper are available in \cite{jin_whan_bae_2017_854820}.
+in this paper are available in \cite{bae_arfc/transition-scenarios:_2017}.
 %% Probably a separate repository is needed..?

### 2017-08-31 results.tex
shortened page to 4

@@
 \subsection{Historical Operation of \gls{EU} Reactors}
-
-\Cref{tab:sim_result} lists the important metrics
-obtained from the first simulation. The following
-values are the \gls{EU} inventory and history at year 2050,
-and will be reprocessed in the second simulation.
 
@@
 		\end{tabular}
+
+\Cref{tab:sim_result} lists the important metrics
+obtained from the first simulation. The following
+values are the \gls{EU} inventory and history at year 2050,
+and will be reprocessed in the second simulation.
+
 }
@@
 	\end {table}
-	\FloatBarrier
-
 	Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
@@
 
-	From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
+	From Varaine et al. \cite{varaine_pre-conceptual_2012}, a French
 	ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
@@
 	Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
-	plutonium from \gls{UNF} can be estimated to $\frac{Pu \ from \ legacy \ \gls{UNF}}{4.9} \approx 270$ \glspl{SFR},
+	plutonium from \gls{UNF} can be estimated to 270 \glspl{SFR},
 	assuming infinite reprocessing and fabrication capacity as well as
@@
 
-	\Cref{fig:fuel} shows \gls{MOX} loaded in the \glspl{SFR} per month.
-	The spikes are due to initial fuel demand for new deployment of \glspl{SFR}.
-	The initial loading of new \glspl{SFR} are done with the \gls{MOX} created
-	from legacy \gls{UNF}. Once there are enough amounts of extra plutonium creation
-	by deployed \glspl{SFR}, the legacy \gls{UNF} is no longer used.
-
 	\begin{figure}[htbp!]
@@
 	\end{figure}
-
-	\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
-	(minor actinides, fission products) over time. The spikes in the 
-	waste discharge is due to large influx of spent fuel from
-	decommissioned \glspl{SFR}.\Cref{fig:pu_no_cum} shows the separated plutonium discharge
-	per month from the reprocessing plant. The plutonium outflux
-	does not precisely follow the fuel demand because \Cyclus agents have
-	material buffers that store commodity fuel for later usage. 
-	\Cref{tab:sfr_sim_result} lists metrics obtained from the second simulation.
 
@@
 
-	\begin{figure}[htbp!]
-		\begin{center}
-			\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
-		\end{center}
-		\caption{Reprocessing waste discharge from Reprocessing Plant}
-		\label{fig:reprocess_waste}
-	\end{figure}
-
+	\Cref{fig:fuel} shows \gls{MOX} loaded in the \glspl{SFR} per month.
+	The spikes are due to initial fuel demand for new deployment of \glspl{SFR}.
+	The initial loading of new \glspl{SFR} are done with the \gls{MOX} created
+	from legacy \gls{UNF}. Once there are enough amounts of extra plutonium creation
+	by deployed \glspl{SFR}, the legacy \gls{UNF} is no longer used. 
 	\begin{table}[h]
@@
 			\end {table}
+
+	\Cref{fig:pu_no_cum} shows the separated plutonium discharge
+	per month from the reprocessing plant. The plutonium outflux
+	does not precisely follow the fuel demand because \Cyclus agents have
+	material buffers that store commodity fuel for later usage. 
+	\Cref{tab:sfr_sim_result} lists metrics obtained from the second simulation.

### 2017-10-03 revise/revise.tex
adds revision response doc -- uses the exam class

%        File: revise.tex
%     Created: Wed Oct 09 02:00 PM 2013 P
% Last Change: Wed Oct 09 02:00 PM 2013 P
%

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,12pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}
\usepackage[hyphens]{url}

%\journal{Advances in Engineering Software}

\begin{document}

%\begin{frontmatter}

   % Title, authors and addresses

   % use the tnoteref command within \title for footnotes;
   % use the tnotetext command for the associated footnote;
   % use the fnref command within \author or \address for footnotes;
   % use the fntext command for the associated footnote;
   % use the corref command within \author for corresponding author footnotes;
   % use the cortext command for the associated footnote;
   % use the ead command for the email address,
   % and the form \ead[url] for the home page:
   %
   % \title{Title\tnoteref{label1}}
   % \tnotetext[label1]{}
   % \author{Name\corref{cor1}\fnref{label2}}
   % \ead{email address}
   % \ead[url]{home page}
   % \fntext[label2]{}
   % \cortext[cor1]{}
   % \address{Address\fnref{label3}}
   % \fntext[label3]{}

        \title{<++>}

   % use optional labels to link authors explicitly to addresses:
   % \author[label1,label2]{<author name>}
   % \address[label1]{<address>}
   % \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}

\section*{General Response}
I would like to thank the reviewers for their detailed assessment of this 
paper.

\section*{Reviewer 1}
\begin{questions}
\question The paper presents an interesting and original work on a new solver for MSRs based on the MOOSE platform.  It is clearly written but it lacks depth both in the description of the work and in the positioning of it in the available scientific literature.  In addition, the paper fails in properly supporting the main claim of an " unmatched fidelity in coupled neutronics and thermal hydraulics MSR simulation", since the proposed results are limited and compared only with an old MSRE model. The paper would represent an interesting contribution to the scientific community but it requires revision. In  particular the authors should deepen their bibliographical research, and include a comparison either with experimental results or with other state-of-the-art tools.
\begin{solution}
<++>
\end{solution}

\question
 In the introduction, the authors mention that:
"Two key advantages offered by the fluid-fuelled MSR are improved fuel utilization and no radiation damage constraint on attainable fuel burn-up. Together, these attributes result in significantly reduced core fissile inventories and spent nuclear fuel mass"
However, the fissile inventory is not necessarily related to fuel burnup and fuel utilization. It can actually be  very high in chloride-based fast-spectrum MSRs.
\begin{solution}
<++>
\end{solution}

\question 
The introduction includes a review of previous work done on the subject. However, few important (and recent) works have not been mentioned. In particular, significant efforts have been spent in the frame of the Euratom Evol project, and the results have been published in several papers, including e.g.,:

Manuele Aufiero, Antonio Cammi, Olivier Geoffroy, Mario Losa, Lelio Luzzi, Marco E. Ricotti, Hervé Rouch, Development of an OpenFOAM model for the Molten Salt Fast Reactor transient analysis, Chemical Engineering Science, Volume 111, 2014, Pages 390-401, ISSN 0009-2509, http://dx.doi.org/10.1016/j.ces.2014.03.003.
(http://www.sciencedirect.com/science/article/pii/S0009250914001146)

Carlo Fiorina, Danny Lathouwers, Manuele Aufiero, Antonio Cammi, Claudia Guerrieri, Jan Leen Kloosterman, Lelio Luzzi, Marco Enrico Ricotti, Modelling and analysis of the MSFR transient behaviour, Annals of Nuclear Energy, Volume 64, 2014, Pages 485-498, ISSN 0306-4549, http://dx.doi.org/10.1016/j.anucene.2013.08.003.
(http://www.sciencedirect.com/science/article/pii/S0306454913004118)

Matteo Zanetti, Antonio Cammi, Carlo Fiorina, Lelio Luzzi, A Geometric Multiscale modelling approach to the analysis of MSR plant dynamics, Progress in Nuclear Energy, Volume 83, 2015, Pages 82-98, ISSN 0149-1970, http://dx.doi.org/10.1016/j.pnucene.2015.02.014.

A. Laureau, D. Heuer, E. Merle-Lucotte, P.R. Rubiolo, M. Allibert, M. Aufiero, Transient coupled calculations of the Molten Salt Fast Reactor using the Transient Fission Matrix approach, Nuclear Engineering and Design, Volume 316, 2017, Pages 112-124, ISSN 0029-5493, http://dx.doi.org/10.1016/j.nucengdes.2017.02.022.

Other important works have been prepared in China in the frame of the Chinese MSR program.

\begin{solution}
<++>
\end{solution}

\question 
 The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
\begin{solution}
<++>
\end{solution}

\question 
The authors write:
"Moltres is devoted to previously unmatched fidelity in coupled neutronics and thermal hydraulics MSR simulation."
This is an overstatement as codes with similar degree of fidelity have been written in the past. This is the case of the tools developed in the frame of the Evol project, as well as e.g. the work from Aufiero on the coupling between OpenFOAM and Serpent (that the authors mention earlier in the introduction). The authors are required to modify this sentence based on a better bibliographical research.
\begin{solution}
<++>
\end{solution}

\question 
Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country. The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.

\begin{solution}
<++>
\end{solution}

\question  It's somehow interesting that "For some three-dimensional simulations, the number of elements in the mesh and total number of degrees of freedom exceed one million and ten million respectively. To handle problems of this size, we ran Moltres on up to 608 cores." Normally problems of few million degrees of freedom can be handled with few tens of cores. The authors should discuss more extensively the performances of their code in order to give the reader the possibility to compare them with those of other tools. In particular, it is possible that slow performances may derive from trying to achieve a fully coupled solution (i.e., all the equations in the same matrix), which seems to be the case in this work. In this sense and to better support the claims of the paper, it would be important to compare the performances of a segregated and a fully coupled  solver, both in terms of accuracy and computational time. In addition to helping supporting the claims of the paper, this
would represent a significant contribution to the scientific community, since many of the currently available tools employ segregated solvers, and since the advantages and disadvantages of a fully coupled solver are often a subject of discussion.

\begin{solution}
<++>
\end{solution}

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.

\begin{solution}
<++>
\end{solution}

\question The heat generation in the graphite is calculated as a fraction of that in the fuel. How exactly is this achieved considering that the two sources are spatially separated?

\begin{solution}
<++>
\end{solution}

\question It is not clear how the domain is discretized. Is there a radial discretization in graphite and channels? Was the mesh convergence checked? Please discuss.

\begin{solution}
<++>
\end{solution}

\question  The MSRE had Reynolds numbers very close to the laminar-turbulent transition. Did you use a laminar model? In case, did you encounter convergence problems ?
Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?

\begin{solution}
<++>
\end{solution}

\question The authors are required to use the international system of units (meters, Kelvin, etc).

\begin{solution}
<++>
\end{solution}

\question The authors should briefly describe what "MSRE design models" are. Otherwise it is very difficult for the readers to assess the accuracy of the model.

\begin{solution}
<++>
\end{solution}

\question  Is the heat generation in the hottest channel the same for the Moltres and the MSRE model?

\begin{solution}
<++>
\end{solution}

\question  The authors claim an unprecedented accuracy of their model? How the results of their model compare with previous results from other authors? The presented results do not seem sufficient to support such claim.

\begin{solution}
<++>
\end{solution}

\question The differences between the MSRE and the Moltres model are significant and should be discussed in more details. In particular the difference between fast fluxes is suspicious.

\begin{solution}
<++>
\end{solution}

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.

\begin{solution}
<++>
\end{solution}
\end{questions}
\end{document}  
  %
  % End of file `elsarticle-template-num.tex'.

### 2017-10-23 full-core_msbr_model.tex

@@
 negative, consequently, the MSBR has negative temperature feedback, but MTC is 
-negative which has a negligible effect on safety because it is outweighed by 
+positive which has a negligible effect on safety because it is outweighed by 
 the strong, negative FTC.

### 2017-11-21 Moltres.tex
explortation->exploration, thanks @lindsayad
This removes the overstatement about unmatched fidelity

@@
 from one to three dimensions and can be deployed on an arbitrary number of
-processing units. Through its computing power, Moltres is devoted to previously
-unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
-simulation.
+processing units.
 
@@
 
-Finally, the authors would like to thank Matthew Turk and the Data Explortation 
+Finally, the authors would like to thank Matthew Turk and the Data Exploration 
 Lab for co-supporting Dr. Lindsay during his postdoctoral appointment.

### 2017-11-21 revise/revise.tex
better merge solution.

@@
 %\documentclass[preprint,12pt]{elsarticle}
-\documentclass[answers,12pt]{exam}
+\documentclass[answers,11pt]{exam}
 
@@
 
-%\journal{Advances in Engineering Software}
+%\journal{Annals of Nuclear Energy}
 
@@
 
-        \title{<++>}
+\title{Introduction to Moltres: an Application for Simulation of Molten Salt 
+        Reactors}
 
@@
 
-\section*{General Response}
-I would like to thank the reviewers for their detailed assessment of this 
-paper.
+\section*{Review General Response}
+We would like to again thank the reviewers for their detailed assessment of 
+this paper.
 
@@
 \begin{questions}
-\question The paper presents an interesting and original work on a new solver for MSRs based on the MOOSE platform.
-It is clearly written but it lacks depth both in the description of the work and in the positioning of it in the available scientific literature.
-In addition, the paper fails in properly supporting the main claim of an " unmatched fidelity in coupled neutronics and thermal hydraulics MSR simulation", since the proposed results are limited and compared only with an old MSRE model.
-The paper would represent an interesting contribution to the scientific community but it requires revision.
-In  particular the authors should deepen their bibliographical research, and include a comparison either with experimental results or with other state-of-the-art tools.
+
+\question The paper presents an interesting and original work on a new solver
+for MSRs based on the MOOSE platform.  It is clearly written but it lacks depth
+both in the description of the work and in the positioning of it in the
+available scientific literature.  In addition, the paper fails in properly
+supporting the main claim of an ``unmatched fidelity in coupled neutronics and
+thermal hydraulics MSR simulation'', since the proposed results are limited and
+compared only with an old MSRE model. The paper would represent an interesting
+contribution to the scientific community but it requires revision. In
+particular the authors should deepen their bibliographical research, and
+include a comparison either with experimental results or with other
+state-of-the-art tools.
 \begin{solution}
-<++>
+        The statement concerning `unmatched' fidelity has been removed 
+        entirely.
 \end{solution}
 
-\question
- In the introduction, the authors mention that:
-"Two key advantages offered by the fluid-fuelled MSR are improved fuel utilization and no radiation damage constraint on attainable fuel burn-up.
-Together, these attributes result in significantly reduced core fissile inventories and spent nuclear fuel mass"
+\question <++>
+
+\question In the introduction, the authors mention that:
+``Two key advantages offered by the fluid-fuelled MSR are improved fuel 
+        utilization and no radiation damage constraint on attainable fuel 
+        burn-up. Together, these attributes result in significantly reduced 
+        core fissile inventories and spent nuclear fuel mass''
 However, the fissile inventory is not necessarily related to fuel burnup and fuel utilization. It can actually be  very high in chloride-based fast-spectrum MSRs.
@@
 
-\question 
-The introduction includes a review of previous work done on the subject.
+\question The introduction includes a review of previous work done on the subject.
 However, few important (and recent) works have not been mentioned.
@@
 Other important works have been prepared in China in the frame of the Chinese MSR program.
-
 \begin{solution}
@@
 
-\question 
- The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
-\begin{solution}
-<++>
-\end{solution}
+\question The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
 
-\question 
-The authors write:
-"Moltres is devoted to previously unmatched fidelity in coupled neutronics and thermal hydraulics MSR simulation."
+\question The authors write:
+``Moltres is devoted to previously unmatched fidelity in coupled neutronics and 
+        thermal hydraulics MSR simulation.''
 This is an overstatement as codes with similar degree of fidelity have been written in the past.
@@
 
-\question 
-Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country.
+\question Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country.
 The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.
-
 \begin{solution}
@@
 
-\question  It's somehow interesting that "For some three-dimensional simulations, the number of elements in the mesh and total number of degrees of freedom exceed one million and ten million respectively.
-To handle problems of this size, we ran Moltres on up to 608 cores." Normally problems of few million degrees of freedom can be handled with few tens of cores.
+\question It's somehow interesting that ``For some three-dimensional 
+simulations, the number of elements in the mesh and total number of degrees of 
+freedom exceed one million and ten million respectively. To handle problems of 
+this size, we ran Moltres on up to 608 cores.'' Normally problems of few million degrees of freedom can be handled with few tens of cores.
 The authors should discuss more extensively the performances of their code in order to give the reader the possibility to compare them with those of other tools.
@@
 would represent a significant contribution to the scientific community, since many of the currently available tools employ segregated solvers, and since the advantages and disadvantages of a fully coupled solver are often a subject of discussion.
-
 \begin{solution}
@@
 \question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.
-
 \begin{solution}
@@
 \question The heat generation in the graphite is calculated as a fraction of that in the fuel. How exactly is this achieved considering that the two sources are spatially separated?
-
 \begin{solution}
@@
 \question It is not clear how the domain is discretized. Is there a radial discretization in graphite and channels? Was the mesh convergence checked? Please discuss.
-
 \begin{solution}
@@
 Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?
-
 \begin{solution}
@@
 \question The authors are required to use the international system of units (meters, Kelvin, etc).
-
 \begin{solution}
@@
 
-\question The authors should briefly describe what "MSRE design models" are. Otherwise it is very difficult for the readers to assess the accuracy of the model.
-
+\question The authors should briefly describe what ``MSRE design models'' are. Otherwise it is very difficult for the readers to assess the accuracy of the model.
 \begin{solution}
@@
 \question Is the heat generation in the hottest channel the same for the Moltres and the MSRE model?
-
 \begin{solution}
@@
 The presented results do not seem sufficient to support such claim.
-
 \begin{solution}
@@
 \question The differences between the MSRE and the Moltres model are significant and should be discussed in more details. In particular the difference between fast fluxes is suspicious.
-
 \begin{solution}
@@
 The authors should either extend significantly the section, or remove it completely.
-
 \begin{solution}
@@
 \end{solution}
+
 \end{questions}
   \end{document}
+
   %

### 2017-11-21 Moltres.tex
Strong ans weak scalability plots and text in section 4.3 added

@@
 from one to three dimensions and can be deployed on an arbitrary number of
-processing units.
+processing units. Through its computing power, Moltres is devoted to previously
+unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
+simulation.
 
@@
 
-\subsection{Scaling study}
+\subsection{Scaling performance}
 
-As described earlier, Moltres runs naturally in parallel. To test its
-performance, we conducted a scaling study with a typical 2D axisymmetric input
-file. \Cref{fig:scaling_study} shows Moltres' performance. The solution
-time follows the ideal closely; slight deviations are expected due to
-the expense of communication and the nature of iterative solvers. More
-parallelism means the solution process uses more ``older'' information, 
-which leads to slower convergence in terms of iterations 
-\cite{satish_balay_petsc_2015}.
+Parallelization in Moltres implemented via LibMesh, which includes a set of utilities
+ for massively parallel finite element based computations, including mesh input/output,
+ finite element library and interface for connections with solver packages. Employing 
+the interfaces in LibMesh provides Moltres a significant flexibility including the ability 
+to swap out solver libraries such as PetSc, which includes an expanding suite of parallel 
+linear and nonlinear solvers. Problem domain decomposition utilized using LibMesh mesh 
+adaptation capabilities for running on a specific number of processors and can either be 
+performed manually before the start of the simulation or automatically at the parameters of computation.
+
+In case of strong scaling, the problem size keeps fixed but the number of processors is increased. 
+The goal of strong scaling study is to find an optimal ratio between a number of processors and elements 
+that allows the computation to finish in a reasonable amount of time, and does not waste too much computational
+ power due to parallel overhead. We measured Moltres performance for the strong scaling of a simple 2D 
+axisymmetric case for various problem sizes separately for intra-node (2,820; 5,640; 11,280 and 28,200 elements) 
+and extra-node (86,655; 173,310; 317,735; 664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
+CPU, 16 integer scheduling units, 32 virtual cores, nominal clock speed 2.3 GHz).
+
+\Cref{fig:intra_strong_scaling} shows Moltres performance, i.e. seconds per element vs. number of cores on 1 node
+ (maximum 32 cores). As can be seen, up to 8 cores larger problem required considerably more time per element 
+ because of cache overhead, but beyond this scaling demonstrates asymptotic dependence of the number of processors 
+ due to increasing communication costs. The best parallel efficiency for intra-node study is approximately 89\% and 
+ has been achieved for the largest problem (28,200 elements).
 
@@
   \centering
-  \includegraphics{scaling_study.eps}
-  \caption{Moltres performance on a typical 2D axisymmetric problem for
-    different numbers of processors}
-  \label{fig:scaling_study}
+  \includegraphics[width=\maxwidth{\textwidth}]{intra-node_strong.png}
+  \caption{Moltres intra-node strong scaling efficiency for various problem size, for 1 \ldots 32 cores.}
+  \label{fig:intra_strong_scaling}
 \end{figure}
+
+\Cref{fig:extra_strong_scaling} shows Moltres strong scaling up to 768 processors which takes into account communication costs 
+between nodes. Similarly to intra-node study, up to 128 cores cache overhead causes performance slow down for a larger problem, 
+while beyond 256 cores time per element stays almost constant for small cases (86,655 and 173,310 elements) and slighly 
+decreasing for two larger problems. For extra-node scaling parallel efficiency also growth with the problem size and reach 
+optimal value about 73\% for 664,355 elements.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=\maxwidth{\textwidth}]{extra-node_strong.png}
+  \caption{Moltres extra-node strong scaling efficiency for various problem size, for 1 \ldots 24 nodes.}
+  \label{fig:extra_strong_scaling}
+\end{figure}
+
+For the weak scaling study, the part of the problem (workload) assigned to each processor stays constant and additional elements are 
+used to solve a bigger problem which would not fit in memory on a single node. Thus, the weak scaling measurement is justification
+ for memory-bound application such as multiphysics code. Linear weak scaling is achieved when the execution time stays constant 
+ while the workload increasing in direct proportion to the number of cores. We performed Moltres weak-scaling tests on Blue Waters, 
+ keeping the workload constant at 581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows Moltres weak scaling 
+performance measured for 1 \ldots 32 core within one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance for 
+32 \ldots 128 core. As expected, the largest drop in performance occurs when the number of cores increases from one to $\approx$ 8, which 
+corresponds to switching from no communication to a 2-D domain decomposition. The further reduction in performance of only about 50\% over 
+a range of 32 cores is likely caused by increased communication latency appearing from collective MPI calls. For extra-node case, performance
+ drops about three times most likely because of poor node selection by job scheduler and significantly increased latency and bandwidth costs.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.75\textwidth]{intra-node_weak.png}
+  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of particles
+per processor, for 1 \ldots 32 cores.}
+  \label{fig:intra_weak}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.75\textwidth]{extra-node_weak.png}
+  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of particles
+per processor, for 32 \ldots 128 cores.}
+  \label{fig:extra_weak}
+\end{figure}
+
+Moltres scalability study results clearly indicate that parallelization using LibMesh automatical domain decomposition is not perfectly efficient and
+ further parallel performance optimization needed. Thus, focus on communication patterns study necessarily to identify latency and bandwidth costs
+ and to optimize communications. Moreover, Moltres is memory-bound code and very sensitive to host memory and memory bandwidth, consequently, we will
+ consider a transition from CPUs computing to GPU-accelerated computing which much faster for this type of algorithms because operates on the fly with global 
+ memory instead of store in a CPU's cache before computations. Another way to improve parallel performance is to force the solver use more ``older'' 
+ information from previous iteration, which leads to slower convergence in terms of iterations and workload increasing \cite{satish_balay_petsc_2015}.
 

### 2017-11-21 Moltres.tex
Answer for reviewer question added

@@
 
-Parallelization in Moltres implemented via LibMesh, which includes a set of utilities
- for massively parallel finite element based computations, including mesh input/output,
- finite element library and interface for connections with solver packages. Employing 
-the interfaces in LibMesh provides Moltres a significant flexibility including the ability 
-to swap out solver libraries such as PetSc, which includes an expanding suite of parallel 
-linear and nonlinear solvers. Problem domain decomposition utilized using LibMesh mesh 
-adaptation capabilities for running on a specific number of processors and can either be 
-performed manually before the start of the simulation or automatically at the parameters of computation.
+Parallelization in Moltres implemented via LibMesh, which includes a set of
+utilities for massively parallel finite element based computations, including
+mesh input/output, finite element library and interface for connections with
+solver packages. Employing the interfaces in LibMesh provides Moltres a
+significant flexibility including the ability to swap out solver libraries
+such as PetSc, which includes an expanding suite of parallel linear and
+nonlinear solvers. Problem domain decomposition utilized using LibMesh mesh
+adaptation capabilities for running on a specific number of processors and
+can either be performed manually before the start of the simulation or
+automatically at the parameters of computation.
 
-In case of strong scaling, the problem size keeps fixed but the number of processors is increased. 
-The goal of strong scaling study is to find an optimal ratio between a number of processors and elements 
-that allows the computation to finish in a reasonable amount of time, and does not waste too much computational
- power due to parallel overhead. We measured Moltres performance for the strong scaling of a simple 2D 
-axisymmetric case for various problem sizes separately for intra-node (2,820; 5,640; 11,280 and 28,200 elements) 
-and extra-node (86,655; 173,310; 317,735; 664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
-CPU, 16 integer scheduling units, 32 virtual cores, nominal clock speed 2.3 GHz).
+In case of strong scaling, the problem size keeps fixed but the number of
+processors is increased. The goal of strong scaling study is to find an
+optimal ratio between a number of processors and elements that allows the
+computation to finish in a reasonable amount of time, and does not waste
+too much computational power due to parallel overhead. We measured
+Moltres performance for the strong scaling of a simple 2D axisymmetric
+case for various problem sizes separately for intra-node (2,820; 5,640;
+11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
+664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
+CPU, 16 integer scheduling units, 32 virtual units, nominal clock speed
+2.3 GHz).
 
-\Cref{fig:intra_strong_scaling} shows Moltres performance, i.e. seconds per element vs. number of cores on 1 node
- (maximum 32 cores). As can be seen, up to 8 cores larger problem required considerably more time per element 
- because of cache overhead, but beyond this scaling demonstrates asymptotic dependence of the number of processors 
- due to increasing communication costs. The best parallel efficiency for intra-node study is approximately 89\% and 
- has been achieved for the largest problem (28,200 elements).
+\Cref{fig:intra_strong_scaling} shows Moltres performance, i.e. seconds
+per element vs. number of cores on 1 node (maximum 32 cores). As can be
+seen, up to 8 cores larger problem required considerably more time per
+element because of cache overhead, but beyond this scaling demonstrates
+asymptotic dependence of the number of processors due to increasing
+communication costs. The best parallel efficiency for intra-node study
+is approximately 89\% and has been achieved for the largest problem
+(28,200 elements).
 
@@
 
-\Cref{fig:extra_strong_scaling} shows Moltres strong scaling up to 768 processors which takes into account communication costs 
-between nodes. Similarly to intra-node study, up to 128 cores cache overhead causes performance slow down for a larger problem, 
-while beyond 256 cores time per element stays almost constant for small cases (86,655 and 173,310 elements) and slighly 
-decreasing for two larger problems. For extra-node scaling parallel efficiency also growth with the problem size and reach 
-optimal value about 73\% for 664,355 elements.
+\Cref{fig:extra_strong_scaling} shows Moltres strong scaling up to 768
+processors which takes into account communication costs between nodes.
+Similarly to intra-node study, up to 128 cores cache overhead causes
+performance slow down for a larger problem, while beyond 256 cores
+time per element stays almost constant for small cases (86,655 and
+173,310 elements) and slighly decreasing for two larger problems.
+For extra-node scaling parallel efficiency also growth with the
+problem size and reach optimal value about 73\% for 664,355 elements.
 
@@
 
-For the weak scaling study, the part of the problem (workload) assigned to each processor stays constant and additional elements are 
-used to solve a bigger problem which would not fit in memory on a single node. Thus, the weak scaling measurement is justification
- for memory-bound application such as multiphysics code. Linear weak scaling is achieved when the execution time stays constant 
- while the workload increasing in direct proportion to the number of cores. We performed Moltres weak-scaling tests on Blue Waters, 
- keeping the workload constant at 581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows Moltres weak scaling 
-performance measured for 1 \ldots 32 core within one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance for 
-32 \ldots 128 core. As expected, the largest drop in performance occurs when the number of cores increases from one to $\approx$ 8, which 
-corresponds to switching from no communication to a 2-D domain decomposition. The further reduction in performance of only about 50\% over 
-a range of 32 cores is likely caused by increased communication latency appearing from collective MPI calls. For extra-node case, performance
- drops about three times most likely because of poor node selection by job scheduler and significantly increased latency and bandwidth costs.
+For the weak scaling study, the part of the problem (workload) assigned
+to each processor stays constant and additional elements are used to
+solve a bigger problem which would not fit in memory on a single node.
+Thus, the weak scaling measurement is justification for memory-bound
+application such as multiphysics code. Linear weak scaling is achieved
+when the execution time stays constant while the workload increasing
+in direct proportion to the number of cores. We performed Moltres
+weak-scaling tests on Blue Waters, keeping the workload constant at
+581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows
+Moltres weak scaling performance measured for 1 \ldots 32 core within
+one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance
+for 32 \ldots 128 core. As expected, the largest drop in performance
+occurs when the number of cores increases from one to $\approx$ 8, which 
+corresponds to switching from no communication to a 2-D domain
+decomposition. The further reduction in performance of only about 50\%
+over a range of 32 cores is likely caused by increased communication
+latency appearing from collective \gls{MPI} calls. For extra-node case,
+performance drops about three times most likely because of poor node
+selection by job scheduler and significantly increased latency and
+bandwidth costs.
 
@@
   \includegraphics[width=0.75\textwidth]{intra-node_weak.png}
-  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of particles
+  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
 per processor, for 1 \ldots 32 cores.}
@@
   \includegraphics[width=0.75\textwidth]{extra-node_weak.png}
-  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of particles
+  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
 per processor, for 32 \ldots 128 cores.}
@@
 
-Moltres scalability study results clearly indicate that parallelization using LibMesh automatical domain decomposition is not perfectly efficient and
- further parallel performance optimization needed. Thus, focus on communication patterns study necessarily to identify latency and bandwidth costs
- and to optimize communications. Moreover, Moltres is memory-bound code and very sensitive to host memory and memory bandwidth, consequently, we will
- consider a transition from CPUs computing to GPU-accelerated computing which much faster for this type of algorithms because operates on the fly with global 
- memory instead of store in a CPU's cache before computations. Another way to improve parallel performance is to force the solver use more ``older'' 
- information from previous iteration, which leads to slower convergence in terms of iterations and workload increasing \cite{satish_balay_petsc_2015}.
+Moltres scalability study results clearly indicate that parallelization
+using LibMesh automatical domain decomposition is not perfectly
+efficient and further parallel performance optimization needed. Thus,
+focus on communication patterns study necessarily to identify latency
+and bandwidth costs and to optimize communications. Moreover, Moltres
+is memory-bound code and very sensitive to host memory and memory
+bandwidth, consequently, we will consider a transition from CPUs
+computing to GPU-accelerated computing which much faster for this
+type of algorithms because operates on the fly with global memory
+instead of store in a CPU's cache before computations. Another way
+to improve parallel performance is to force the solver use more
+``older'' information from previous iteration, which leads to slower
+convergence in terms of iterations and workload
+increasing \cite{satish_balay_petsc_2015}.
 

### 2017-11-21 Moltres.tex
incorporates review of Aufiero, Laureau, and Fiorina.

--- 2017-11-21 Moltres.tex
@@
 experimental \gls{MSRE} data and then used it to simulate local fuel channel
-blockages as well as local temperature perturbations. In a similar vein, Kophazi
-et. al. used iterative coupling between in-house three-dimensional neutronic and
-one-dimensional heat conduction models DALTON and THERM to analyze normal 
-\gls{MSRE} operation as well as channel-blocking-incident
-transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
-effects of heat transfer coefficients as well as thermal
-coupling between fuel channels through moderator heat conduction. More recently,
-Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
-\gls{MSBR} using the commercial finite element package COMSOL
-Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
-fuel salt velocity field, used heterogeneous group constants
-in fuel and moderator regions, and employed a software package (COMSOL)
-intrinsically designed for coupled multi-physics simulation.
-Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
-approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
-Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.
+blockages as well as local temperature perturbations.
+
+In a similar vein, Kophazi et. al. used iterative coupling between in-house
+three-dimensional neutronic and one-dimensional heat conduction models DALTON
+and THERM to analyze normal \gls{MSRE} operation as well as
+channel-blocking-incident transients \cite{kophazi_development_2009}. The
+Kophazi model added entrance effects of heat transfer coefficients as well as
+thermal coupling between fuel channels through moderator heat conduction. More
+recently, Cammi et. al. performed a 2D-axisymmetric single-channel analysis of
+the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
+\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
+velocity field, used heterogeneous group constants in fuel and moderator
+regions, and employed the \gls{COMSOL} software package intrinsically designed
+for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
+colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
+which this Politecnico di Milano approach was expanded to a multi-channel model
+and compared to code from the University of Delft
+\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
+\cite{kophazi_development_2009}. These models showed good agreement for
+accident transients in the \gls{MSFR}.
+
+More recently, Aufiero et.  al \cite{aufiero_development_2014} have begun to
+approach transient simulations in the \gls{MSFR} within the finite volume
+OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
+benefits from pre-implemented turbulence models availble in the OpenFOAM
+library and captures the full-core three-dimensional geometry of the reactor
+primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
+al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
+neutronics within the \gls{MSFR}.
 

### 2017-11-21 Moltres.tex
only use myriad once

@@
 
-\gls{MSR} modeling efforts describe steady-state and
-transient behavior. Krepel et al. extended the in-house \gls{LWR}
+Simulation tools developed by many authors successfully describe steady-state and
+transient behavior of myriad \gls{MSR} concepts. Krepel et al. extended the in-house \gls{LWR}
 diffusion code DYN3D to consider drift of delayed neutron precursors alongside
@@
 which this Politecnico di Milano approach was expanded to a multi-channel model 
-and compared to code from the University of Delft
+of the \gls{MSFR} and compared to code from the University of Delft
 \cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
 \cite{kophazi_development_2009}. These models showed good agreement for
-accident transients in the \gls{MSFR}.
+multiple accident transients.
 
@@
 OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
-benefits from pre-implemented turbulence models availble in the OpenFOAM
+benefits from pre-implemented turbulence models available in the OpenFOAM
 library and captures the full-core three-dimensional geometry of the reactor

### 2017-11-21 acros.tex
MPI acronym added #42
updates acros.tex with recent acros.tex

@@
 \newacronym{BSD}{BSD}{Berkeley Software Distribution}
-\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
+\newacronym{CAFCA}{CAFCA}{Code for Advanced Fuel Cycles Assessment}
 \newacronym{CASL}{CASL}{Consortium for Advanced Simulation of Light Water Reactors}
 \newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
-\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies
-Alternatives}
+\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
 \newacronym{CG}{CG}{Continuous Galerkin}
@@
 \newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
+\newacronym{COMSOL}{COMSOL}{COMmon SOLution}
 \newacronym{COSI}{COSI}{Commelini-Sicard}
@@
 \newacronym{DBE}{DBE}{Design Basis Event}
+\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
 \newacronym{DG}{DG}{Discontinuous Galerkin}
-\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
 \newacronym{DHS}{DHS}{Department of Homeland Security}
@@
 \newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
-\newacronym{gpm}{gpm}{gallons per minute}
 \newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
@@
 \newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
+\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}
 \newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
@@
 \newacronym{PEI}{PEI}{Peak Environmental Impact}
-\newacronym{PetSc}{PetSc}{Portable, Extensible Toolkit for Scientific Computation}
 \newacronym{PH}{PRONGHORN}{PRONGHORN}
@@
 \newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
+\newacronym{PWR}{PWR}{Pressurized Water Reactor}
+\newacronym{PetSc}{PetSc}{Portable, Extensible Toolkit for Scientific Computation}
 \newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
@@
 \newacronym{SWU}{SWU}{Separative Work Unit}
-\newacronym{ThOX}{ThOX}{thorium oxide}
 \newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
@@
 \newacronym{YMR}{YMR}{Yucca Mountain Repository Site}
+\newacronym{gpm}{gpm}{gallons per minute}

### 2017-11-21 revise/revise.tex
adds new text to solution

@@
 \begin{solution}
-        <++>
+        Thank you for the excellent recommendations. The new text reads thus:
+
+        Simulation tools developed by many authors successfully describe 
+        steady-state and
+        transient behavior of myriad MSR concepts. Krepel et al. extended 
+        the in-house LWR
+        diffusion code DYN3D to consider drift of delayed neutron precursors 
+        alongside
+        the reactor temperature profile, re-casting the extended code as
+        DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR 
+        against
+        experimental MSRE data and then used it to simulate local fuel 
+        channel
+        blockages as well as local temperature perturbations.
+
+        In a similar vein, Kophazi et. al. used iterative coupling between 
+        in-house
+        three-dimensional neutronic and one-dimensional heat conduction models 
+        DALTON
+        and THERM to analyze normal MSRE operation as well as
+        channel-blocking-incident transients \cite{kophazi_development_2009}. 
+        The
+        Kophazi model added entrance effects of heat transfer coefficients as 
+        well as
+        thermal coupling between fuel channels through moderator heat 
+        conduction. More
+        recently, Cammi et. al. performed a 2D-axisymmetric single-channel 
+        analysis of
+        the MSBR using the commercial finite element package COMSOL 
+        Multiphysics
+        \cite{cammi_multi-physics_2011}. That work directly solved the fuel 
+        salt
+        velocity field, used heterogeneous group constants in fuel and 
+        moderator
+        regions, and employed the COMSOL software package intrinsically 
+        designed
+        for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
+        colleagues conducted a benchmarking exercise 
+        \cite{fiorina_modelling_2013} in
+        which this Politecnico di Milano approach was expanded to a 
+        multi-channel model 
+        of the MSFR and compared to code from the University of Delft
+        \cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach 
+        in
+        \cite{kophazi_development_2009}. These models showed good agreement for
+        multiple accident transients. Meanwhile, leveraging lessons learned 
+        from these 
+        efforts has resulted in a multiscale approach from Zanetti et al. 
+        \cite{zanetti_geometric_2015} successfully combines high and low 
+        geometric 
+        fidelity for graphite-moderated MSRs.
+
+        More recently, Aufiero et.  al \cite{aufiero_development_2014} have 
+        begun to
+        approach transient simulations in the MSFR within the finite 
+        volume
+        OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This 
+        approach
+        benefits from pre-implemented turbulence models available in the 
+        OpenFOAM
+        library and captures the full-core three-dimensional geometry of the 
+        reactor
+        primary circuit.  OpenFOAM CFD has additionally been shown by 
+        Laureau et
+        al. \cite{laureau_transient_2017} to couple well with Transient Fission 
+        Matrix
+        neutronics within the MSFR.
 \end{solution}
@@
 \end{questions}
+\bibliographystyle{unsrt}
+\bibliography{Moltres}
   \end{document}

### 2017-11-21 Moltres.tex
adds zanetti
Fixed "et al.": now it is the same everywhere
For multiple authors right way to cite is: **et al.**
http://davidson.libguides.com/c.php?g=349327&p=2357431

@@
 
-In a similar vein, Kophazi et. al. used iterative coupling between in-house
+In a similar vein, Kophazi et al. used iterative coupling between in-house
 three-dimensional neutronic and one-dimensional heat conduction models DALTON
@@
 thermal coupling between fuel channels through moderator heat conduction. More
-recently, Cammi et. al. performed a 2D-axisymmetric single-channel analysis of
+recently, Cammi et al. performed a 2D-axisymmetric single-channel analysis of
 the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
@@
 \cite{kophazi_development_2009}. These models showed good agreement for
-multiple accident transients.
+multiple accident transients. Meanwhile, leveraging lessons learned from these 
+efforts has resulted in a multiscale approach from Zanetti et al. 
+\cite{zanetti_geometric_2015} successfully combines high and low geometric 
+fidelity for graphite-moderated \glspl{MSR}.
 
-More recently, Aufiero et.  al \cite{aufiero_development_2014} have begun to
+More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
 approach transient simulations in the \gls{MSFR} within the finite volume

### 2017-11-21 revise/revise.tex
Fixed "et al." everywhere

@@
 
-        In a similar vein, Kophazi et. al. used iterative coupling between 
+        In a similar vein, Kophazi et al. used iterative coupling between 
         in-house
@@
         conduction. More
-        recently, Cammi et. al. performed a 2D-axisymmetric single-channel 
+        recently, Cammi et al. performed a 2D-axisymmetric single-channel 
         analysis of
@@
 
-        More recently, Aufiero et.  al \cite{aufiero_development_2014} have 
+        More recently, Aufiero et al. \cite{aufiero_development_2014} have 
         begun to

### 2017-11-21 Moltres.tex
english edits

--- 2017-11-21 Moltres.tex
@@
 experimental \gls{MSRE} data and then used it to simulate local fuel channel
-blockages as well as local temperature perturbations.
-
-In a similar vein, Kophazi et. al. used iterative coupling between in-house
-three-dimensional neutronic and one-dimensional heat conduction models DALTON
-and THERM to analyze normal \gls{MSRE} operation as well as
-channel-blocking-incident transients \cite{kophazi_development_2009}. The
-Kophazi model added entrance effects of heat transfer coefficients as well as
-thermal coupling between fuel channels through moderator heat conduction. More
-recently, Cammi et. al. performed a 2D-axisymmetric single-channel analysis of
-the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
-\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
-velocity field, used heterogeneous group constants in fuel and moderator
-regions, and employed the \gls{COMSOL} software package intrinsically designed
-for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
-colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
-which this Politecnico di Milano approach was expanded to a multi-channel model
-and compared to code from the University of Delft
-\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
-\cite{kophazi_development_2009}. These models showed good agreement for
-accident transients in the \gls{MSFR}.
-
-More recently, Aufiero et.  al \cite{aufiero_development_2014} have begun to
-approach transient simulations in the \gls{MSFR} within the finite volume
-OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
-benefits from pre-implemented turbulence models availble in the OpenFOAM
-library and captures the full-core three-dimensional geometry of the reactor
-primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
-al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
-neutronics within the \gls{MSFR}.
+blockages as well as local temperature perturbations. In a similar vein, Kophazi
+et. al. used iterative coupling between in-house three-dimensional neutronic and
+one-dimensional heat conduction models DALTON and THERM to analyze normal 
+\gls{MSRE} operation as well as channel-blocking-incident
+transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
+effects of heat transfer coefficients as well as thermal
+coupling between fuel channels through moderator heat conduction. More recently,
+Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
+\gls{MSBR} using the commercial finite element package COMSOL
+Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
+fuel salt velocity field, used heterogeneous group constants
+in fuel and moderator regions, and employed a software package (COMSOL)
+intrinsically designed for coupled multi-physics simulation.
+Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
+approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
+Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.
 
@@
 
-\subsection{Scaling study}
+\subsection{Scaling performance}
 
-As described earlier, Moltres runs naturally in parallel. To test its
-performance, we conducted a scaling study with a typical 2D axisymmetric input
-file. \Cref{fig:scaling_study} shows Moltres' performance. The solution
-time follows the ideal closely; slight deviations are expected due to
-the expense of communication and the nature of iterative solvers. More
-parallelism means the solution process uses more ``older'' information, 
-which leads to slower convergence in terms of iterations 
-\cite{satish_balay_petsc_2015}.
+Parallelization in Moltres is implemented via LibMesh, which includes a set of
+utilities for massively parallel finite element based computations, including
+mesh input/output, a finite element library, and an interface for connections with
+solver packages. Employing LibMesh provides Moltres
+significant flexibility including the ability to swap out solver libraries
+such as PetSc, which includes an expanding suite of parallel linear and
+nonlinear solvers. Problem domain decomposition relies on LibMesh mesh
+adaptation capabilities for running on a specific number of processors and
+can either be performed manually before the start of the simulation or
+automatically at the parameters of computation.
+
+We conducted strong and weak scaling studies to characterize parallel 
+performance in Moltres.
+In case of strong scaling, the problem size remains fixed but the number of
+processors is increased. Strong scaling studies seek to identify an
+optimal ratio between the number of processors and elements for the most
+rapid and power-efficient computation for a given problem. We measured
+Moltres strong scaling with a simple 2D axisymmetric
+case for various problem sizes separately for intra-node (2,820; 5,640;
+11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
+664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
+CPU, 16 integer scheduling units, 32 virtual units, nominal clock speed
+2.3 GHz).
+
+\Cref{fig:intra_strong_scaling} shows the simulation speed in seconds
+per element vs. the number of cores on 1 node (maximum 32 cores). Up to 8 
+cores, larger problems required considerably more time per
+element because of cache overhead. However, beyond 8 cores, scaling demonstrates
+asymptotic dependence on the number of processors due to increasing
+communication costs. The best parallel efficiency for the intra-node study
+is approximately 89\% and has been achieved for the largest problem
+(28,200 elements).
 
@@
   \centering
-  \includegraphics{scaling_study.eps}
-  \caption{Moltres performance on a typical 2D axisymmetric problem for
-    different numbers of processors}
-  \label{fig:scaling_study}
+  \includegraphics[width=\maxwidth{\textwidth}]{intra-node_strong.png}
+  \caption{Moltres intra-node strong scaling efficiency for various problem 
+        sizes, for $n_{cores} \in [1,32]$.}
+  \label{fig:intra_strong_scaling}
 \end{figure}
+
+\Cref{fig:extra_strong_scaling} shows Moltres strong scaling up to 768
+processors. This takes into account communication costs between nodes.
+Similar to the intra-node study, when fewer than 128 cores were used, 
+cache overhead causes performance slow down for larger problems. However, 
+beyond 256 cores, the simulation time per element remains almost constant for small cases (86,655 and
+173,310 elements) and slighly decreases for the two larger problems.
+For extra-node scaling, parallel efficiency also grows with the
+problem size and reaches an optimal value of 73\% for 664,355 elements.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=\maxwidth{\textwidth}]{extra-node_strong.png}
+  \caption{Moltres extra-node strong scaling efficiency for various problem size, for $n_{nodes} \in [1,24]$.}
+  \label{fig:extra_strong_scaling}
+\end{figure}
+
+For the weak scaling study, the part of the problem (workload) assigned
+to each processor stays constant and additional elements are used to
+solve a bigger problem which would not fit in memory on a single node.
+Thus, the weak scaling measurement is justification for memory-bound
+application such as multiphysics code. Linear weak scaling is achieved
+when the execution time stays constant while the workload increasing
+in direct proportion to the number of cores. We performed Moltres
+weak-scaling tests on Blue Waters, keeping the workload constant at
+581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows
+Moltres weak scaling performance measured for $n_{cores} \in [1,32]$ within
+one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance
+for $n_{cores} \in [32,128]$. As expected, the largest drop in performance 
+occurs when the number of cores increases from one to $\approx$ 8, which 
+corresponds to switching from no communication to a 2-D domain
+decomposition. The further reduction in performance of only about 50\%
+over a range of 32 cores is likely caused by increased communication
+latency appearing from collective \gls{MPI} calls. In the extra-node case,
+the performance drops by a factor of three, which is most likely due to poor node
+selection by the Blue Waters job scheduler and significantly increased latency and
+bandwidth costs.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.75\textwidth]{intra-node_weak.png}
+  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
+        per processor, and $n_{cores}\in[1,32]$.}
+  \label{fig:intra_weak}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=0.75\textwidth]{extra-node_weak.png}
+  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
+        per processor, for and $n_{cores}\in[32,128]$.}
+  \label{fig:extra_weak}
+\end{figure}
+
+Moltres scalability study results clearly indicate that parallelization
+using LibMesh's automatic domain decomposition is good, but not perfectly
+efficient. This scaling performance is satisfactory for \gls{MSR} simulations 
+approached thus far and improved parallel performance would require further optimization
+within LibMesh.  Moreover, Moltres is memory-bound and therefore very sensitive to host memory and memory
+bandwidth. Consequently, if improved performance is needed, one could consider a transition from CPUs
+computing to GPU-accelerated computing because GPUs operate on the fly with 
+global memory, avoiding CPU cache storage issues. Another way
+to improve parallel performance is to force the solver to use
+``older'' information from previous iterations. However, this has been shown to 
+slow convergence in terms of iterations and increased workload \cite{satish_balay_petsc_2015}.
 

### 2017-11-21 revise/revise.tex

--- 2017-11-21 revise/revise.tex
@@
 \begin{solution}
-        The statement concerning `unmatched' fidelity has been removed 
-        entirely.
+        <++>
 \end{solution}
@@
 \begin{solution}
-        <++>
+        We are performed strong and weak scaling up to 768 cores separately for intra-node and extra-node cases.
+Parallelization implemented using LibMesh library (for automatical domain decomposition) and PetSc library which contains set of parallel solvers.
+Detailed information added in Section 4.3 introduction.
 \end{solution}

### 2017-11-21 Moltres.tex

@@
 experimental \gls{MSRE} data and then used it to simulate local fuel channel
-blockages as well as local temperature perturbations. In a similar vein, Kophazi
-et. al. used iterative coupling between in-house three-dimensional neutronic and
-one-dimensional heat conduction models DALTON and THERM to analyze normal 
-\gls{MSRE} operation as well as channel-blocking-incident
-transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
-effects of heat transfer coefficients as well as thermal
-coupling between fuel channels through moderator heat conduction. More recently,
-Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
-\gls{MSBR} using the commercial finite element package COMSOL
-Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
-fuel salt velocity field, used heterogeneous group constants
-in fuel and moderator regions, and employed a software package (COMSOL)
-intrinsically designed for coupled multi-physics simulation.
-Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
-approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
-Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.
+blockages as well as local temperature perturbations.
+
+In a similar vein, Kophazi et al. used iterative coupling between in-house
+three-dimensional neutronic and one-dimensional heat conduction models DALTON
+and THERM to analyze normal \gls{MSRE} operation as well as
+channel-blocking-incident transients \cite{kophazi_development_2009}. The
+Kophazi model added entrance effects of heat transfer coefficients as well as
+thermal coupling between fuel channels through moderator heat conduction. More
+recently, Cammi et al. performed a 2D-axisymmetric single-channel analysis of
+the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
+\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
+velocity field, used heterogeneous group constants in fuel and moderator
+regions, and employed the \gls{COMSOL} software package intrinsically designed
+for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
+colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
+which this Politecnico di Milano approach was expanded to a multi-channel model 
+of the \gls{MSFR} and compared to code from the University of Delft
+\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
+\cite{kophazi_development_2009}. These models showed good agreement for
+multiple accident transients. Meanwhile, leveraging lessons learned from these 
+efforts has resulted in a multiscale approach from Zanetti et al. 
+\cite{zanetti_geometric_2015} successfully combines high and low geometric 
+fidelity for graphite-moderated \glspl{MSR}.
+
+More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
+approach transient simulations in the \gls{MSFR} within the finite volume
+OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
+benefits from pre-implemented turbulence models available in the OpenFOAM
+library and captures the full-core three-dimensional geometry of the reactor
+primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
+al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
+neutronics within the \gls{MSFR}.
 

### 2017-11-22 Moltres.tex
adds refs of other open source tools, including the continuous energy monte carlo code OpenMC, and fixes some bib entries. Adds a sentence about dual use and export control.

@@
 for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
-colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
+colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2014} in
 which this Politecnico di Milano approach was expanded to a multi-channel model 
 of the \gls{MSFR} and compared to code from the University of Delft
-\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
+\cite{de_zwaan_static_2007,van_der_linden_coupled_2012} based on the approach in
 \cite{kophazi_development_2009}. These models showed good agreement for
@@
 developed physics capabilities, and a C++ object-oriented design to
-enable extension and code reuse. Moreover, Moltres depends on the \gls{MOOSE} 
+enable extension and code reuse. While export control laws have the potential 
+to restrict openness of software that is dual use, Moltres requires that 
+cross sections be provided by the user, is tailored to molten salt reactor 
+physics, and joins a veritable parade of open academic nuclear engineering
+software such as OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
+PyNE\cite{bates_pyne_2014,biondo_quality_2014}.
+
+Moreover, Moltres depends on the \gls{MOOSE} 
 framework, \cite{gaston_physics-based_2015} another \gls{LGPL} code that itself 

### 2017-11-22 Moltres.tex
more details on export control

@@
 enable extension and code reuse. While export control laws have the potential 
-to restrict openness of software that is dual use, Moltres requires that 
-cross sections be provided by the user, is tailored to molten salt reactor 
-physics, and joins a veritable parade of open academic nuclear engineering
-software such as OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
+to restrict openness of neutron transport software that is dual use, there is 
+no reason to believe that Moltres could be used for weapons proliferation. 
+Moltres requires that cross sections be provided by the user, implements a 
+combination of algorithms that can be easily derived from open literature, is 
+tailored to molten salt reactor physics. Accordingly, Moltres joins a veritable 
+parade of open academic nuclear engineering software such as 
+OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
 PyNE\cite{bates_pyne_2014,biondo_quality_2014}.

### 2017-11-22 revise/revise.tex

@@
 \begin{solution}
-        <++>
+	Excellent point. We have added the following text: ``While export
+control laws have the potential to restrict openness of neutron transport
+software that is dual use, there is no reason to believe that Moltres could be
+used for weapons proliferation.  Moltres requires that cross sections be
+provided by the user, implements a combination of algorithms that can be easily
+derived from open literature, is tailored to molten salt reactor physics.
+Accordingly, Moltres joins a veritable parade of open academic nuclear
+engineering software such as OpenMC\cite{romano_openmc:_2015},
+OpenMOC\cite{boyd_openmoc_2014}, and
+PyNE\cite{bates_pyne_2014,biondo_quality_2014}.''
+
 \end{solution}

### 2017-11-22 Moltres.tex
spaces before citations

@@
 approach transient simulations in the \gls{MSFR} within the finite volume
-OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
+OpenFOAM multiphysics toolkit \cite{weller_tensorial_1998}.  This approach
 benefits from pre-implemented turbulence models available in the OpenFOAM
@@
 quality through transparency and ease of peer review. In the era of
-GitHub\cite{github_build_2017} and international scientific collaboration,
+GitHub \cite{github_build_2017} and international scientific collaboration,
 open and modern software practices must be employed in order for nuclear
@@
 parade of open academic nuclear engineering software such as 
-OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
-PyNE\cite{bates_pyne_2014,biondo_quality_2014}.
+OpenMC \cite{romano_openmc:_2015}, OpenMOC \cite{boyd_openmoc_2014}, and 
+PyNE \cite{bates_pyne_2014,biondo_quality_2014}.
 

### 2017-11-22 revise/revise.tex
spaces before citations

@@
         volume
-        OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This 
+        OpenFOAM multiphysics toolkit \cite{weller_tensorial_1998}.  This 
         approach
@@
 Accordingly, Moltres joins a veritable parade of open academic nuclear
-engineering software such as OpenMC\cite{romano_openmc:_2015},
-OpenMOC\cite{boyd_openmoc_2014}, and
-PyNE\cite{bates_pyne_2014,biondo_quality_2014}.''
+engineering software such as OpenMC \cite{romano_openmc:_2015},
+OpenMOC \cite{boyd_openmoc_2014}, and
+PyNE \cite{bates_pyne_2014,biondo_quality_2014}.''
 

### 2017-11-24 Moltres.tex
Updated information about BW XK7 node
Taken in from NCSA site: https://bluewaters.ncsa.illinois.edu/node_core_comparison

--- 2017-11-22 Moltres.tex
@@
 11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
-664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
-CPU, 16 integer scheduling units, 32 virtual units, nominal clock speed
-2.3 GHz).
+664,355 elements) setup on Blue Waters' XK7 nodes (two AMD 6276 Interlagos 
+CPU per node, 16 floating-point bulldozer core units per node or 32 "integer"
+cores per node, nominal clock speed is 2.3 GHz).
 
@@
 cache overhead causes performance slow down for larger problems. However, 
-beyond 256 cores, the simulation time per element remains almost constant for small cases (86,655 and
-173,310 elements) and slighly decreases for the two larger problems.
-For extra-node scaling, parallel efficiency also grows with the
-problem size and reaches an optimal value of 73\% for 664,355 elements.
+beyond 256 cores, the simulation time per element remains almost constant
+for small cases (86,655 and 173,310 elements) and slighly decreases for the 
+two larger problems. For extra-node scaling, parallel efficiency also grows 
+with the problem size and reaches an optimal value of 73\% for 664,355 elements.
 

### 2017-11-24 Moltres.tex
BW node clock speed fixed (2.45)

--- 2017-11-22 Moltres.tex
@@
 11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
-664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
-CPU, 16 integer scheduling units, 32 virtual units, nominal clock speed
-2.3 GHz).
+664,355 elements) setup on Blue Waters' XK7 nodes (two AMD 6276 Interlagos 
+CPU per node, 16 floating-point bulldozer core units per node or 32 "integer"
+cores per node, nominal clock speed is 2.45 GHz).
 

### 2017-11-26 Moltres.tex
inches to cm

--- 2017-11-22 Moltres.tex
@@
 \gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
-neutron diffusion, temperature, and precursor governing equations in anywhere
-from one to three dimensions and can be deployed on an arbitrary number of
-processing units.
+neutron diffusion, temperature, and precursor governing equations on a single 
+mesh in anywhere from one to three dimensions and can be deployed on an 
+arbitrary number of processing units.
 
@@
 chosen to correspond to the peak of the thermal flux in both cases; for the
-\gls{ORNL} calculations this is 8.4 inches from the core center-line because of
+\gls{ORNL} calculations this is 21.336 cm (8.4 inches) from the core center-line because of
 the effect of the control rod thimbles and extra fuel along the
@@
     \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial.eps}
-    \caption{Moltres axial flux profiles along core center line and \gls{MSRE}
-      design axial flux profiles 8.4 inches from core center line \cite[p. 91]{briggs_molten-salt_1964}.}
+    \caption{Moltres axial flux profiles along the core center line and \gls{MSRE}
+    design axial flux profiles 21.336 cm (8.4 inches) from the core center line \cite[p. 91]{briggs_molten-salt_1964}.}
     \label{fig:axial_fluxes_compare}

### 2017-11-26 revise/revise.tex
inches to cm

@@
 \begin{solution}
-        <++>
+        This has now been clarified in the introductory text. The equations are 
+        solved on a single mesh. This is enabled by the underlying MOOSE 
+        framework, which also enables 'loose' coupling instead.
 \end{solution}
@@
 \begin{solution}
-        <++>
+        These calculations were performed without including turbulence. However, a $k-\epsilon$ model is being implemented to support future simulations.
 \end{solution}

### 2017-11-26 Moltres.tex
@lindsayad I think that since he ran the scaling study, Andrei should be one of the authors. If you agree, pleae merge.

--- 2017-11-24 Moltres.tex
@@
 \title{Introduction to Moltres: an Application for Simulation of Molten Salt Reactors}
-\author{Alexander Lindsay, Gavin Ridley, Kathryn Huff}
+\author{Alexander Lindsay, Gavin Ridley, Andrei Rykhlevskii, Kathryn Huff}
 
@@
 
-Simulation tools developed by many authors successfully describe steady-state and
-transient behavior of myriad \gls{MSR} concepts. Krepel et al. extended the in-house \gls{LWR}
+\gls{MSR} modeling efforts describe steady-state and
+transient behavior. Krepel et al. extended the in-house \gls{LWR}
 diffusion code DYN3D to consider drift of delayed neutron precursors alongside
@@
 experimental \gls{MSRE} data and then used it to simulate local fuel channel
-blockages as well as local temperature perturbations.
-
-In a similar vein, Kophazi et al. used iterative coupling between in-house
-three-dimensional neutronic and one-dimensional heat conduction models DALTON
-and THERM to analyze normal \gls{MSRE} operation as well as
-channel-blocking-incident transients \cite{kophazi_development_2009}. The
-Kophazi model added entrance effects of heat transfer coefficients as well as
-thermal coupling between fuel channels through moderator heat conduction. More
-recently, Cammi et al. performed a 2D-axisymmetric single-channel analysis of
-the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
-\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
-velocity field, used heterogeneous group constants in fuel and moderator
-regions, and employed the \gls{COMSOL} software package intrinsically designed
-for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
-colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2014} in
-which this Politecnico di Milano approach was expanded to a multi-channel model 
-of the \gls{MSFR} and compared to code from the University of Delft
-\cite{de_zwaan_static_2007,van_der_linden_coupled_2012} based on the approach in
-\cite{kophazi_development_2009}. These models showed good agreement for
-multiple accident transients. Meanwhile, leveraging lessons learned from these 
-efforts has resulted in a multiscale approach from Zanetti et al. 
-\cite{zanetti_geometric_2015} successfully combines high and low geometric 
-fidelity for graphite-moderated \glspl{MSR}.
-
-More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
-approach transient simulations in the \gls{MSFR} within the finite volume
-OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
-benefits from pre-implemented turbulence models available in the OpenFOAM
-library and captures the full-core three-dimensional geometry of the reactor
-primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
-al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
-neutronics within the \gls{MSFR}.
+blockages as well as local temperature perturbations. In a similar vein, Kophazi
+et. al. used iterative coupling between in-house three-dimensional neutronic and
+one-dimensional heat conduction models DALTON and THERM to analyze normal 
+\gls{MSRE} operation as well as channel-blocking-incident
+transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
+effects of heat transfer coefficients as well as thermal
+coupling between fuel channels through moderator heat conduction. More recently,
+Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
+\gls{MSBR} using the commercial finite element package COMSOL
+Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
+fuel salt velocity field, used heterogeneous group constants
+in fuel and moderator regions, and employed a software package (COMSOL)
+intrinsically designed for coupled multi-physics simulation.
+Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
+approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
+Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.
 
@@
 developed physics capabilities, and a C++ object-oriented design to
-enable extension and code reuse. While export control laws have the potential 
-to restrict openness of neutron transport software that is dual use, there is 
-no reason to believe that Moltres could be used for weapons proliferation. 
-Moltres requires that cross sections be provided by the user, implements a 
-combination of algorithms that can be easily derived from open literature, is 
-tailored to molten salt reactor physics. Accordingly, Moltres joins a veritable 
-parade of open academic nuclear engineering software such as 
-OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
-PyNE\cite{bates_pyne_2014,biondo_quality_2014}.
-
-Moreover, Moltres depends on the \gls{MOOSE} 
+enable extension and code reuse. Moreover, Moltres depends on the \gls{MOOSE} 
 framework, \cite{gaston_physics-based_2015} another \gls{LGPL} code that itself 
@@
 
-\subsection{Scaling performance}
+\subsection{Scaling study}
 
-Parallelization in Moltres is implemented via LibMesh, which includes a set of
-utilities for massively parallel finite element based computations, including
-mesh input/output, a finite element library, and an interface for connections with
-solver packages. Employing LibMesh provides Moltres
-significant flexibility including the ability to swap out solver libraries
-such as PetSc, which includes an expanding suite of parallel linear and
-nonlinear solvers. Problem domain decomposition relies on LibMesh mesh
-adaptation capabilities for running on a specific number of processors and
-can either be performed manually before the start of the simulation or
-automatically at the parameters of computation.
-
-We conducted strong and weak scaling studies to characterize parallel 
-performance in Moltres.
-In case of strong scaling, the problem size remains fixed but the number of
-processors is increased. Strong scaling studies seek to identify an
-optimal ratio between the number of processors and elements for the most
-rapid and power-efficient computation for a given problem. We measured
-Moltres strong scaling with a simple 2D axisymmetric
-case for various problem sizes separately for intra-node (2,820; 5,640;
-11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
-664,355 elements) setup on Blue Waters' XK7 nodes (two AMD 6276 Interlagos 
-CPU per node, 16 floating-point bulldozer core units per node or 32 "integer"
-cores per node, nominal clock speed is 2.3 GHz).
-
-\Cref{fig:intra_strong_scaling} shows the simulation speed in seconds
-per element vs. the number of cores on 1 node (maximum 32 cores). Up to 8 
-cores, larger problems required considerably more time per
-element because of cache overhead. However, beyond 8 cores, scaling demonstrates
-asymptotic dependence on the number of processors due to increasing
-communication costs. The best parallel efficiency for the intra-node study
-is approximately 89\% and has been achieved for the largest problem
-(28,200 elements).
+As described earlier, Moltres runs naturally in parallel. To test its
+performance, we conducted a scaling study with a typical 2D axisymmetric input
+file. \Cref{fig:scaling_study} shows Moltres' performance. The solution
+time follows the ideal closely; slight deviations are expected due to
+the expense of communication and the nature of iterative solvers. More
+parallelism means the solution process uses more ``older'' information, 
+which leads to slower convergence in terms of iterations 
+\cite{satish_balay_petsc_2015}.
 
@@
   \centering
-  \includegraphics[width=\maxwidth{\textwidth}]{intra-node_strong.png}
-  \caption{Moltres intra-node strong scaling efficiency for various problem 
-        sizes, for $n_{cores} \in [1,32]$.}
-  \label{fig:intra_strong_scaling}
+  \includegraphics{scaling_study.eps}
+  \caption{Moltres performance on a typical 2D axisymmetric problem for
+    different numbers of processors}
+  \label{fig:scaling_study}
 \end{figure}
-
-\Cref{fig:extra_strong_scaling} shows Moltres strong scaling up to 768
-processors. This takes into account communication costs between nodes.
-Similar to the intra-node study, when fewer than 128 cores were used, 
-cache overhead causes performance slow down for larger problems. However, 
-beyond 256 cores, the simulation time per element remains almost constant
-for small cases (86,655 and 173,310 elements) and slighly decreases for the 
-two larger problems. For extra-node scaling, parallel efficiency also grows 
-with the problem size and reaches an optimal value of 73\% for 664,355 elements.
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=\maxwidth{\textwidth}]{extra-node_strong.png}
-  \caption{Moltres extra-node strong scaling efficiency for various problem size, for $n_{nodes} \in [1,24]$.}
-  \label{fig:extra_strong_scaling}
-\end{figure}
-
-For the weak scaling study, the part of the problem (workload) assigned
-to each processor stays constant and additional elements are used to
-solve a bigger problem which would not fit in memory on a single node.
-Thus, the weak scaling measurement is justification for memory-bound
-application such as multiphysics code. Linear weak scaling is achieved
-when the execution time stays constant while the workload increasing
-in direct proportion to the number of cores. We performed Moltres
-weak-scaling tests on Blue Waters, keeping the workload constant at
-581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows
-Moltres weak scaling performance measured for $n_{cores} \in [1,32]$ within
-one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance
-for $n_{cores} \in [32,128]$. As expected, the largest drop in performance 
-occurs when the number of cores increases from one to $\approx$ 8, which 
-corresponds to switching from no communication to a 2-D domain
-decomposition. The further reduction in performance of only about 50\%
-over a range of 32 cores is likely caused by increased communication
-latency appearing from collective \gls{MPI} calls. In the extra-node case,
-the performance drops by a factor of three, which is most likely due to poor node
-selection by the Blue Waters job scheduler and significantly increased latency and
-bandwidth costs.
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.75\textwidth]{intra-node_weak.png}
-  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
-        per processor, and $n_{cores}\in[1,32]$.}
-  \label{fig:intra_weak}
-\end{figure}
-
-\begin{figure}[htpb]
-  \centering
-  \includegraphics[width=0.75\textwidth]{extra-node_weak.png}
-  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
-        per processor, for and $n_{cores}\in[32,128]$.}
-  \label{fig:extra_weak}
-\end{figure}
-
-Moltres scalability study results clearly indicate that parallelization
-using LibMesh's automatic domain decomposition is good, but not perfectly
-efficient. This scaling performance is satisfactory for \gls{MSR} simulations 
-approached thus far and improved parallel performance would require further optimization
-within LibMesh.  Moreover, Moltres is memory-bound and therefore very sensitive to host memory and memory
-bandwidth. Consequently, if improved performance is needed, one could consider a transition from CPUs
-computing to GPU-accelerated computing because GPUs operate on the fly with 
-global memory, avoiding CPU cache storage issues. Another way
-to improve parallel performance is to force the solver to use
-``older'' information from previous iterations. However, this has been shown to 
-slow convergence in terms of iterations and increased workload \cite{satish_balay_petsc_2015}.
 

### 2017-11-26 revise/revise.tex
responding to reviewer comments in the doc

@@
 \begin{solution}
-        <++>
+        Thanks for catching this. The mention of inches has been converted to cm.
 \end{solution}
@@
 \begin{solution}
-        <++>
+        The paper has been clarified. That section is now careful to state that 
+        our comparison is made against the simple two-group calculation 
+        conducted to pinpoint the design of the MSRE. 
 \end{solution}
@@
 \begin{solution}
-        <++>
+        This claim has been removed entirely. Thank you.
 \end{solution}
@@
 \begin{solution}
-        We are performed strong and weak scaling up to 768 cores separately for intra-node and extra-node cases.
-Parallelization implemented using LibMesh library (for automatical domain decomposition) and PetSc library which contains set of parallel solvers.
-Detailed information added in Section 4.3 introduction.
+        We performed strong and weak scaling up to 768 cores separately for 
+        intra-node and extra-node cases. Parallelization was implemented using 
+        LibMesh library (for automatical domain decomposition) and PetSc 
+        library which contains set of parallel solvers. Detailed information, 
+        including results of the scalind studies, has now been added in the 
+        Section 4.3 introduction.
 \end{solution}

### 2017-11-27 Moltres.tex
handles description of the model from ORNL.

--- 2017-11-26 Moltres.tex
@@
 \Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
-profiles with cosinusoidal gamma heating and \gls{MSRE} design models
-\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
-profile shapes are in decent qualitative agreement with both Moltres and
-\gls{MSRE} calculations showing a peak in graphite temperature before the
+profiles with cosinusoidal gamma heating and \gls{MSRE} design calculations
+\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. 
+The \gls{MSRE} design calculation in \cref{fig:temp_compare} was conducted in 
+1963
+32-group calculations using legacy computing tools (GAM-I, MODRIC, and 
+EQUIPOSE, and THERMOS). That calculation was conducted in two-dimensional R-Z 
+geometry (a cylinder with angular symmetry), with 20 spatial regions. Notably, 
+one limitation of the \gls{ORNL} model was the control rod thimbles that, due to 
+angular symmetry, were effectively a cylindrical shell of metal.
+
+The profile shapes are in decent qualitative agreement with both Moltres and
+\gls{MSRE} calculations, showing a peak in graphite temperature before the
 reactor outlet. Fuel temperature increases monotonically in both Moltres and

### 2017-11-27 Moltres.tex
handles question about 'what are msre design models' .

@@
 \cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. 
-The \gls{MSRE} design calculation in \cref{fig:temp_compare} was conducted in 
-1963
-32-group calculations using legacy computing tools (GAM-I, MODRIC, and 
-EQUIPOSE, and THERMOS). That calculation was conducted in two-dimensional R-Z 
+The \gls{ORNL} \gls{MSRE} design calculations, conducted in 
+1963-1964,  were 32-group calculations using legacy computing tools (GAM-I, MODRIC, and 
+EQUIPOSE, and THERMOS). Those calculations were conducted in two-dimensional R-Z 
 geometry (a cylinder with angular symmetry), with 20 spatial regions. Notably, 

### 2017-11-27 revise/revise.tex
handles description of the model from ORNL.
handles question about 'what are msre design models' .

@@
         The paper has been clarified. That section is now careful to state that 
-        our comparison is made against the simple two-group calculation 
-        conducted to pinpoint the design of the MSRE. 
+        our comparison is made against a 1963-1964 calculation conducted by ORNL 
+        to pinpoint the MSRE design. The text has been updated to refer to 
+        ``MSRE design models'' as ``MSRE design calculations'' and explains 
+        that the MSRE design calculations conducted in 1963 were 32-group 
+        calculations using legacy computing tools (GAM-I, MODRIC, and EQUIPOSE, 
+        and THERMOS). These calculations were conducted in two-dimensional R-Z 
+        geometry (a cylinder with angular symmetry), with 20 spatial regions. 
+        Notably, one limitation of the ORNL model was the control rod thimbles 
+        that, due to angular symmetry, were effectively a cylindrical shell of 
+        metal.  
 \end{solution}

### 2017-11-27 revise/revise.tex
quick edits to responses in revise doc

@@
 \begin{solution}
+        Thank you for your kind review.
         The statement concerning `unmatched' fidelity has been removed 
-        entirely.
+        entirely and the bibliography has been expanded significantly. See the 
+        responses below for more detail..
 \end{solution}
-
-\question <++>
 

### 2017-11-27 revise/revise.tex
responses in revise doc to handle the concern about unmatched fidelity
moves complaint about bibliography to appropriate section

@@
 Other important works have been prepared in China in the frame of the Chinese MSR program.
+
+The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
 \begin{solution}
@@
 \end{solution}
-
-\question The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
 

### 2017-11-27 Moltres.tex

@@
 \usepackage{placeins}
+\usepackage{amsmath}
 \usepackage[T1]{fontenc}
@@
 \renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}
+
+% upright d's for differentials
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
 
@@
 
-In this work, $Q_g = \gamma Q_f$, where $\gamma$ is a factor
-representing heat dissipation by gamma and neutron irradiation in the moderator.
+In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f \diff V$, where $\gamma$ is a factor
+representing heat dissipation by gamma and neutron irradiation in the moderator,
+called the graphite to fuel power density ratio. \cite{robertson_conceptual_1971}'s
+original \gls{MSBR} analysis included a calculation of $\gamma$.
+\cite{krepel_dyn3d-msr_2007,zhang_development_2009,cammi_multi-physics_2011} all
+calculated gamma heating through such a factor. We follow \cite{cammi_multi-physics_2011}
+and set $\gamma=0.0144$. Notably, the Moltres physics kernel for radiation heating can be
+calculate the volume average fission heat in a variety of means: whole-core and local averages
+are possible. Whole-core averages are employed for simplicity and in accordance with prior literature.
+Knowledge of fision heat rates, however, require knowledge of neutron fluxes, implying a need for
+group constants.
 

### 2017-11-27 revise/revise.tex
again, more concerns about the overstatement of fidelity.
cleaning up responses
fixes sentence in revise doc about petsc

@@
 \begin{solution}
-        <++>
+        That statement has been removed and the bibliography has been enriched 
+        (as discussed above).
 \end{solution}
@@
         solved on a single mesh. This is enabled by the underlying MOOSE 
-        framework, which also enables 'loose' coupling instead.
+        framework, which also enables `loose' coupling instead.
 \end{solution}
@@
         intra-node and extra-node cases. Parallelization was implemented using 
-        LibMesh library (for automatical domain decomposition) and PetSc 
-        library which contains set of parallel solvers. Detailed information, 
-        including results of the scalind studies, has now been added in the 
-        Section 4.3 introduction.
+        LibMesh library for automatic domain decomposition and PetSc 
+        library for parallel solution of systems of non-linear equations. 
+        Detailed information, including results of the scalind studies, has now 
+        been added in the Section 4.3 introduction.
 \end{solution}

### 2017-11-27 Moltres.tex
removed comma

@@
 The profile shapes are in decent qualitative agreement with both Moltres and
-\gls{MSRE} calculations, showing a peak in graphite temperature before the
+\gls{MSRE} calculations showing a peak in graphite temperature before the
 reactor outlet. Fuel temperature increases monotonically in both Moltres and

### 2017-11-27 Moltres.tex
Address fuel utilization question (Closes #64

@@
 the inclusion of the \gls{MSR} among the Generation-IV reactor designs
-\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
-interest in the past decade, with many new nuclear companies proposing both
-fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
+\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained
+renewed research interest in the past decade, with many new nuclear companies
+proposing both fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
 \cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}.
@@
 utilization and no radiation damage constraint on attainable fuel
-burn-up. Together, these attributes result in significantly reduced core fissile
-inventories and spent nuclear fuel mass 
-\cite{gif_generation_2008,gif_generation_2015}.  
-Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
-burning actinides and extending fuel resources.
+burn-up. Together these attributes can result in significantly reduced spent
+fuel mass and, in the case of fluoride salt reactors in particular, reduced core
+fissile inventories \cite{gif_generation_2008,gif_generation_2015}.  Due to
+these characteristics, the \gls{MSR} is potentially uniquely capable of burning
+actinides and extending fuel resources.
 
@@
 mesh input/output, a finite element library, and an interface for connections with
-solver packages. Employing LibMesh provides Moltres
+solver packages. Employing LibMesh provides Moltres with
 significant flexibility including the ability to swap out solver libraries

### 2017-11-27 revise/revise.tex
Just reformat revise.tex to use shorter lines
Address fuel utilization question (Closes #64

@@
 
-\question In the introduction, the authors mention that:
-``Two key advantages offered by the fluid-fuelled MSR are improved fuel 
-        utilization and no radiation damage constraint on attainable fuel 
-        burn-up. Together, these attributes result in significantly reduced 
-        core fissile inventories and spent nuclear fuel mass''
-However, the fissile inventory is not necessarily related to fuel burnup and fuel utilization. It can actually be  very high in chloride-based fast-spectrum MSRs.
+\question In the introduction, the authors mention that: ``Two key advantages
+offered by the fluid-fuelled MSR are improved fuel utilization and no radiation
+damage constraint on attainable fuel burn-up. Together, these attributes result
+in significantly reduced core fissile inventories and spent nuclear fuel mass''
+However, the fissile inventory is not necessarily related to fuel burnup and
+fuel utilization. It can actually be very high in chloride-based fast-spectrum
+MSRs.
 \begin{solution}
-        <++>
+        We have edited this sentence to read ``Together these attributes can
+        result in significantly reduced spent fuel mass and, in the case of
+        fluoride salt reactors in particular, reduced core fissile
+        inventories'', recognizing that you're quite correct for the chloride salts.
 \end{solution}
 
-\question The introduction includes a review of previous work done on the subject.
-However, few important (and recent) works have not been mentioned.
-In particular, significant efforts have been spent in the frame of the Euratom Evol project, and the results have been published in several papers, including e.g.,:
+\question The introduction includes a review of previous work done on the
+subject. However, few important (and recent) works have not been mentioned. In
+particular, significant efforts have been spent in the frame of the Euratom Evol
+project, and the results have been published in several papers, including e.g.,:
 
-Manuele Aufiero, Antonio Cammi, Olivier Geoffroy, Mario Losa, Lelio Luzzi, Marco E.
-Ricotti, Hervé Rouch, Development of an OpenFOAM model for the Molten Salt Fast Reactor transient analysis, Chemical Engineering Science, Volume 111, 2014, Pages 390-401, ISSN 0009-2509, http://dx.doi.org/10.1016/j.ces.2014.03.003.
+Manuele Aufiero, Antonio Cammi, Olivier Geoffroy, Mario Losa, Lelio Luzzi, Marco
+E. Ricotti, Hervé Rouch, Development of an OpenFOAM model for the Molten Salt
+Fast Reactor transient analysis, Chemical Engineering Science, Volume 111, 2014,
+Pages 390-401, ISSN 0009-2509, http://dx.doi.org/10.1016/j.ces.2014.03.003.
 (http://www.sciencedirect.com/science/article/pii/S0009250914001146)
 
-Carlo Fiorina, Danny Lathouwers, Manuele Aufiero, Antonio Cammi, Claudia Guerrieri, Jan Leen Kloosterman, Lelio Luzzi, Marco Enrico Ricotti, Modelling and analysis of the MSFR transient behaviour, Annals of Nuclear Energy, Volume 64, 2014, Pages 485-498, ISSN 0306-4549, http://dx.doi.org/10.1016/j.anucene.2013.08.003.
+Carlo Fiorina, Danny Lathouwers, Manuele Aufiero, Antonio Cammi, Claudia
+Guerrieri, Jan Leen Kloosterman, Lelio Luzzi, Marco Enrico Ricotti, Modelling
+and analysis of the MSFR transient behaviour, Annals of Nuclear Energy, Volume
+64, 2014, Pages 485-498, ISSN 0306-4549,
+http://dx.doi.org/10.1016/j.anucene.2013.08.003.
 (http://www.sciencedirect.com/science/article/pii/S0306454913004118)
 
-Matteo Zanetti, Antonio Cammi, Carlo Fiorina, Lelio Luzzi, A Geometric Multiscale modelling approach to the analysis of MSR plant dynamics, Progress in Nuclear Energy, Volume 83, 2015, Pages 82-98, ISSN 0149-1970, http://dx.doi.org/10.1016/j.pnucene.2015.02.014.
+Matteo Zanetti, Antonio Cammi, Carlo Fiorina, Lelio Luzzi, A Geometric
+Multiscale modelling approach to the analysis of MSR plant dynamics, Progress in
+Nuclear Energy, Volume 83, 2015, Pages 82-98, ISSN 0149-1970,
+http://dx.doi.org/10.1016/j.pnucene.2015.02.014.
 
-A.
-Laureau, D.
-Heuer, E.
-Merle-Lucotte, P.R.
-Rubiolo, M.
-Allibert, M.
-Aufiero, Transient coupled calculations of the Molten Salt Fast Reactor using the Transient Fission Matrix approach, Nuclear Engineering and Design, Volume 316, 2017, Pages 112-124, ISSN 0029-5493, http://dx.doi.org/10.1016/j.nucengdes.2017.02.022.
+A. Laureau, D. Heuer, E. Merle-Lucotte, P.R. Rubiolo, M. Allibert, M. Aufiero,
+Transient coupled calculations of the Molten Salt Fast Reactor using the
+Transient Fission Matrix approach, Nuclear Engineering and Design, Volume 316,
+2017, Pages 112-124, ISSN 0029-5493,
+http://dx.doi.org/10.1016/j.nucengdes.2017.02.022.
 
@@
 
-The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
+The authors should deepen the discussion on the current state of the art,
+mentioning at least the several efforts spent in the Evol project, and
+re-balancing their claims accordingly.
 \begin{solution}
@@
 
-\question The authors write:
-``Moltres is devoted to previously unmatched fidelity in coupled neutronics and 
-        thermal hydraulics MSR simulation.''
-This is an overstatement as codes with similar degree of fidelity have been written in the past.
-This is the case of the tools developed in the frame of the Evol project, as well as e.g.
-the work from Aufiero on the coupling between OpenFOAM and Serpent (that the authors mention earlier in the introduction).
-The authors are required to modify this sentence based on a better bibliographical research.
+\question The authors write: ``Moltres is devoted to previously unmatched
+fidelity in coupled neutronics and thermal hydraulics MSR simulation.''  This is
+an overstatement as codes with similar degree of fidelity have been written in
+the past. This is the case of the tools developed in the frame of the Evol
+project, as well as e.g. the work from Aufiero on the coupling between OpenFOAM
+and Serpent (that the authors mention earlier in the introduction). The authors
+are required to modify this sentence based on a better bibliographical research.
 \begin{solution}
@@
 
-\question Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country.
-The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.
+\question Concerning the openness of the code and the possibility to contribute
+to it, it should be noted that codes solving for neutron transport can be
+subject to export restrictions (following their potential dual use), and in
+principle all contributors should get an export control authorization from their
+own country. The authors are not strictly required to change the manuscript, but
+they may consider mentioning the fact that the openness of a nuclear code can be
+somewhat thwarted by national and international laws.
 \begin{solution}
@@
 freedom exceed one million and ten million respectively. To handle problems of
-this size, we ran Moltres on up to 608 cores.'' Normally problems of few million degrees of freedom can be handled with few tens of cores.
-The authors should discuss more extensively the performances of their code in order to give the reader the possibility to compare them with those of other tools.
-In particular, it is possible that slow performances may derive from trying to achieve a fully coupled solution (i.e., all the equations in the same matrix), which seems to be the case in this work.
-In this sense and to better support the claims of the paper, it would be important to compare the performances of a segregated and a fully coupled  solver, both in terms of accuracy and computational time.
-In addition to helping supporting the claims of the paper, this
-would represent a significant contribution to the scientific community, since many of the currently available tools employ segregated solvers, and since the advantages and disadvantages of a fully coupled solver are often a subject of discussion.
+this size, we ran Moltres on up to 608 cores.'' Normally problems of few million
+degrees of freedom can be handled with few tens of cores. The authors should
+discuss more extensively the performances of their code in order to give the
+reader the possibility to compare them with those of other tools. In particular,
+it is possible that slow performances may derive from trying to achieve a fully
+coupled solution (i.e., all the equations in the same matrix), which seems to be
+the case in this work. In this sense and to better support the claims of the
+paper, it would be important to compare the performances of a segregated and a
+fully coupled solver, both in terms of accuracy and computational time. In
+addition to helping supporting the claims of the paper, this would represent a
+significant contribution to the scientific community, since many of the
+currently available tools employ segregated solvers, and since the advantages
+and disadvantages of a fully coupled solver are often a subject of discussion.
 \begin{solution}
@@
 
-\question The heat generation in the graphite is calculated as a fraction of that in the fuel. How exactly is this achieved considering that the two sources are spatially separated?
+\question The heat generation in the graphite is calculated as a fraction of
+that in the fuel. How exactly is this achieved considering that the two sources
+are spatially separated?
 \begin{solution}
@@
 
-\question It is not clear how the domain is discretized. Is there a radial discretization in graphite and channels? Was the mesh convergence checked? Please discuss.
+\question It is not clear how the domain is discretized. Is there a radial
+discretization in graphite and channels? Was the mesh convergence checked?
+Please discuss.
 \begin{solution}
@@
 
-\question The MSRE had Reynolds numbers very close to the laminar-turbulent transition. Did you use a laminar model? In case, did you encounter convergence problems ?
-Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?
+\question The MSRE had Reynolds numbers very close to the laminar-turbulent
+transition. Did you use a laminar model? In case, did you encounter convergence
+problems ?  Or did you include turbulence? More generally, is Moltres capable of
+turbulent simulations?
 \begin{solution}
-        These calculations were performed without including turbulence. However, a $k-\epsilon$ model is being implemented to support future simulations.
+        These calculations were performed without including turbulence. However,
+        a $k-\epsilon$ model is being implemented to support future simulations.
 \end{solution}
@@
 
-\question The authors should briefly describe what ``MSRE design models'' are. Otherwise it is very difficult for the readers to assess the accuracy of the model.
+\question The authors should briefly describe what ``MSRE design models''
+are. Otherwise it is very difficult for the readers to assess the accuracy of
+the model.
 \begin{solution}
@@
 
-\question The authors claim an unprecedented accuracy of their model?
-How the results of their model compare with previous results from other authors?
-The presented results do not seem sufficient to support such claim.
+\question The authors claim an unprecedented accuracy of their model? How the
+results of their model compare with previous results from other authors? The
+presented results do not seem sufficient to support such claim.
 \begin{solution}
@@
 
-\question The differences between the MSRE and the Moltres model are significant and should be discussed in more details. In particular the difference between fast fluxes is suspicious.
+\question The differences between the MSRE and the Moltres model are significant
+and should be discussed in more details. In particular the difference between
+fast fluxes is suspicious.
 \begin{solution}
@@
 
-\question The proposed scaling test is very limited.
-Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc.
-In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy.
-The authors should either extend significantly the section, or remove it completely.
+\question The proposed scaling test is very limited. Proper scaling tests would
+require weak and strong scaling tests, an assessment on the impact of the size
+of problem per core, a separate assessment of intra-node and extra-node scaling,
+etc. In addition, information should be provided on the employed numerical
+algorithms and on the parallelization strategy. The authors should either extend
+significantly the section, or remove it completely.
 \begin{solution}
@@
         library for parallel solution of systems of non-linear equations.
-        Detailed information, including results of the scalind studies, has now 
+        Detailed information, including results of the scaling studies, has now
         been added in the Section 4.3 introduction.

### 2017-11-27 Moltres.tex
Address monolithic vs segregated solution question.

@@
 ``older'' information from previous iterations. However, this has been shown to
-slow convergence in terms of iterations and increased workload \cite{satish_balay_petsc_2015}.
+slow convergence in terms of iterations and increased workload
+\cite{satish_balay_petsc_2015}.
+
+\subsection{Monolithic vs. Segregated Solution}
+
+Relative performance of monolithic vs. segregated solution methods for large
+systems of equations is an active area of research. Monolithic solvers are
+generally regarded to be more robust than their segregated counterparts but are
+often perceived as being too expensive for large-scale problems. Work conducted
+by Heil et. al. \cite{heil2008solvers} demonstrates that monolithic solvers are
+competitive with segregated techniques for weakly coupled physics; moreover, for
+strongly coupled problems the segregated methods struggle to achieve
+convergence. It is noted by the authors that use of monolithic solvers
+on large 3D problems requires efficient preconditioning to be effective.
+
+Monolithic and segregated solution techniques were compared in Moltres using the
+2D-axisymmetric problem but with delayed neutron precursors removed. In this
+case starting from arbitrary initial conditions the neutron multiplication
+exhibits damped oscillation around the critical state. Feedback between the
+power deposition by neutrons and temperature modification of neutron macroscopic
+group constants make this a very tightly coupled problem. Using adaptive time
+stepping based on the number of non-linear iterations at each time step,
+steady-state neutron fluxes and temperature profiles are achieved in 358 time
+steps and in 4 minutes of compute time on a single core using full-coupling
+(e.g. neutron fluxes and temperature in the same matrix). Alternatively,
+a solution was also attempted splitting neutron and temperature solves and
+performing Picard iterations until convergence. Ultimately, a steady-state
+solution could not be achieved using the segregated method. After 670
+time-steps, the Picard solve hits the maximum number of allowed iterations (100)
+after only halving the neutronics residual. Before reaching the fail-point, the
+segregated solution required numerous Picard iterations to converge (68, 37, 22
+for the previous three time-steps for example), resulting in a total compute
+time of 37 minutes before failure. These results suggest that for solving tight coupling
+between neutronics and temperature, a monololithic solve approach is more effective.
 

### 2017-11-27 revise/revise.tex
Address monolithic vs segregated solution question.

@@
 \begin{solution}
- <++>
+        It is definitely true that for many problems an operator-splitting or
+        segregated solution method will be faster and require less
+        computational resources. A fully-coupled Newton's method is
+        computationally expensive. We could in theory use fewer cores to solve
+        our million DOF problems and have the problem run longer. However,
+        particularly in our department and with our collaboration with Illinois's
+        National Center for Supercomputing Applications, we are encouraged to
+        use the computational resources at our disposal, so we elect to run our
+        large problems as quickly as possible on Blue Waters. Additionally, the
+        developers of PetSc recommend using approximately 20k degrees of freedom
+        per process, which is a rule of thumb we generally adhere to.
+
+        For coupling between neutrons and temperature, we performed a comparison
+        between monolothic and segregated solution techniques. The results are
+        outlined in a new results subsection placed immediately before the
+        Conclusion section. In brief, for this problem which exhibits such strong
+        feedback between physics, we were unable to achieve convergence using the
+        segregated method.
 \end{solution}

### 2017-11-27 revise/revise.tex
Add comment on 'slowness' (Closes #43)
Add fuel-moderator heating answer to revise.tex

@@
         developers of PetSc recommend using approximately 20k degrees of freedom
-        per process, which is a rule of thumb we generally adhere to.
+        per process, which is a rule of thumb we generally adhere to. For the 3D
+        problem for which we report results (1.16 million DOFs), we are fairly
+        pleased with the 2.5 hour solution on 160 cores and do not consider this
+        performance as slow, at least in the context of a fully coupled, fully
+        implicit solution method.
 
@@
 \begin{solution}
-        <++>
+        A good question. We have a variety of options available, but in this
+        work we take a whole-core average of the fuel heat generation and then
+        multiply by $\gamma$. For a constant $\gamma$ this results in uniform
+        heating with the moderator regions. We have added the following passage
+        to clarify this point:
+
+        In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f
+        \diff V$, where $\gamma$ is a factor representing heat dissipation by
+        gamma and neutron irradiation in the moderator, called the graphite to
+        fuel power density ratio. Robertson's \cite{robertson_conceptual_1971}
+        original \gls{MSBR} analysis included a calculation of $\gamma$.
+        \cite{krepel_dyn3d-msr_2007,zhang_development_2009,cammi_multi-physics_2011}
+        all calculated gamma heating through such a factor. We follow
+        \cite{cammi_multi-physics_2011} and set $\gamma=0.0144$. Notably, the
+        Moltres physics kernel for radiation heating can be calculate the volume
+        average fission heat in a variety of means: whole-core and local
+        averages are possible. Whole-core averages are employed for simplicity
+        and in accordance with prior literature.  Knowledge of fision heat
+        rates, however, require knowledge of neutron fluxes, implying a need for
+        group constants.
 \end{solution}

### 2017-11-27 Moltres.tex
Add reponse to question about model comparison.

@@
 representing heat dissipation by gamma and neutron irradiation in the moderator,
-called the graphite to fuel power density ratio. \cite{robertson_conceptual_1971}'s
+called the graphite to fuel power density ratio. Robertson's \cite{robertson_conceptual_1971}
 original \gls{MSBR} analysis included a calculation of $\gamma$.
@@
 \gls{MSRE} models. In the \gls{MSRE} design, the moderator
-temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
+temperature at the reactor inlet is about 11 K larger than the
 fuel temperature, whereas the temperatures are about the same in the Moltres
@@
 \end{figure}
+
+Although the qualitative agreement is decent, there are discrepancies between
+the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
+offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
+the hottest channel. The peak graphite temperature is around 14 K larger in the
+Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
+roughly 20\%. These are not insignificant differences. However, given the
+differing nature of the two models--no axial conduction in the \gls{MSRE} model,
+2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
+Moltres calculation--we believe this variation in quantitative behavior is
+acceptable for the purpose of this work, which is to introduce Moltres as a
+simulation tool. Trustworthy verification of Moltres results, such as spatial flux
+and temperature profiles, will require more detailed experimental measurements
+than those available in the \gls{ORNL} technical reports, which contain only
+macroscopic data such as steady-state power and heat-exchanger temperature
+drops. Additionally, detailed comparison with other modern modeling efforts such
+as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
+desirable. In that vein, a collaboration is under way with the primary author of
+\cite{aufiero_develoment_2014} to try and reproduce calculation results from
+OpenFOAM. We hope to publish the results of this comparison in a future work.
 

### 2017-11-27 revise/revise.tex
Add reponse to question about model comparison.

@@
 \begin{solution}
-        <++>
+        We have added the following passage at the end of the comparison section
+        to address this concern:
+
+        Although the qualitative agreement is decent, there are discrepancies between
+        the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
+        offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
+        the hottest channel. The peak graphite temperature is around 14 K larger in the
+        Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
+        roughly 20\%. These are not insignificant differences. However, given the
+        differing nature of the two models--no axial conduction in the \gls{MSRE} model,
+        2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
+        Moltres calculation--we believe this variation in quantitative behavior is
+        acceptable for the purpose of this work, which is to introduce Moltres as a
+        simulation tool. Trustworthy verification of Moltres results, such as spatial flux
+        and temperature profiles, will require more detailed experimental measurements
+        than those available in the \gls{ORNL} technical reports, which contain only
+        macroscopic data such as steady-state power and heat-exchanger temperature
+        drops. Additionally, detailed comparison with other modern modeling efforts such
+        as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
+        desirable. In that vein, a collaboration is under way with the primary author of
+        \cite{aufiero_develoment_2014} to try and reproduce calculation results from
+        OpenFOAM. We hope to publish the results of this comparison in a future work.
 \end{solution}

### 2017-11-27 Moltres.tex
backed up claims on MSRs being good on fuel

--- 2017-11-27 Moltres.tex
@@
 the inclusion of the \gls{MSR} among the Generation-IV reactor designs
-\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained
-renewed research interest in the past decade, with many new nuclear companies
-proposing both fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
+\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
+interest in the past decade, with many new nuclear companies proposing both
+fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
 \cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
-Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
-utilization and no radiation damage constraint on attainable fuel
-burn-up. Together these attributes can result in significantly reduced spent
-fuel mass and, in the case of fluoride salt reactors in particular, reduced core
-fissile inventories \cite{gif_generation_2008,gif_generation_2015}.  Due to
-these characteristics, the \gls{MSR} is potentially uniquely capable of burning
-actinides and extending fuel resources.
+The key advantages of \gls{MSR}s generally pertain to improved fuel utilization
+and reactor safety. In contrast to legacy reactors, only moderator fast neutron
+damage and fuel chemistry evolution limit burnup. A clever configuration of moderator
+as in \cite{engel_conceptual_1980} can enable reactor operation without opening the vessel
+for thirty or more years. Further, several fission products selectively precipitate onto
+nickel surfaces in fluoride salt, as documented in \cite{engel_conceptual_1980}, thus reducing
+unwanted neutron absorption. Lastly, the epithermal spectrum of graphite-moderated salt reactors
+incinerates plutonium more efficiently, thus reducing long-lived transuranic waste production \cite{engel_conceptual_1980}. 
+The sum of the aforementioned benefits imply spent nuclear fuel
+mass can be reduced in comparison to legacy reactors.
+Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
+extending fuel resources and ameliorating spent fuel burden.
 
@@
 mesh input/output, a finite element library, and an interface for connections with
-solver packages. Employing LibMesh provides Moltres with
+solver packages. Employing LibMesh provides Moltres
 significant flexibility including the ability to swap out solver libraries

### 2017-11-27 Moltres.tex
Describe peak power density.

@@
 incinerates plutonium more efficiently, thus reducing long-lived transuranic waste production \cite{engel_conceptual_1980}. 
-The sum of the aforementioned benefits imply spent nuclear fuel
-mass can be reduced in comparison to legacy reactors.
-Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
-extending fuel resources and ameliorating spent fuel burden.
+The sum of these characteristics implies the \gls{MSR} uniqely ameliorates spent fuel burden whilst
+extending nuclear fuel resources. To top all these benefits off, xenon transients become moot in
+\gls{MSR}s due to its insolubility in salt, thus narrowing transient analysis focus to thermalhydraulic
+concerns.
 

### 2017-11-27 Moltres.tex
Add additional sentence about precursor decay heat.

--- 2017-11-27 Moltres.tex
@@
 in the plena cause deviation of the thermal flux from a sinusoidal shape in the
-\gls{MSRE} design case.
+\gls{MSRE} design case. The peak power density from the \gls{MSRE} calculation
+is 31 kW/L; the corresponding value for Moltres is 29 kW/L.
 
@@
 acceptable for the purpose of this work, which is to introduce Moltres as a
-simulation tool. Trustworthy verification of Moltres results, such as spatial flux
-and temperature profiles, will require more detailed experimental measurements
-than those available in the \gls{ORNL} technical reports, which contain only
-macroscopic data such as steady-state power and heat-exchanger temperature
-drops. Additionally, detailed comparison with other modern modeling efforts such
-as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
-desirable. In that vein, a collaboration is under way with the primary author of
+simulation tool. One additional feature that could influence Moltres results is
+inclusion of precursor decay heat; this is under active development. Trustworthy
+verification of Moltres results, such as spatial flux and temperature profiles,
+will require more detailed experimental measurements than those available in the
+\gls{ORNL} technical reports, which contain only macroscopic data such as
+steady-state power and heat-exchanger temperature drops. Additionally, detailed
+comparison with other modern modeling efforts such as that conducted in
+\cite{aufiero_development_2014,laureau_transient_2017} is desirable. In that
+vein, a collaboration is under way with the primary author of
 \cite{aufiero_develoment_2014} to try and reproduce calculation results from

### 2017-11-27 revise/revise.tex
Describe peak power density.
Add additional sentence about precursor decay heat.

@@
 \begin{solution}
-        <++>
+        The peak power density for the MSRE model is 31 kW/L; for Moltres it is
+        29 kW/L. A corresponding line has been added to the manuscript.
 \end{solution}
@@
 
-        Although the qualitative agreement is decent, there are discrepancies between
-        the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
-        offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
-        the hottest channel. The peak graphite temperature is around 14 K larger in the
-        Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
-        roughly 20\%. These are not insignificant differences. However, given the
-        differing nature of the two models--no axial conduction in the \gls{MSRE} model,
-        2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
-        Moltres calculation--we believe this variation in quantitative behavior is
-        acceptable for the purpose of this work, which is to introduce Moltres as a
-        simulation tool. Trustworthy verification of Moltres results, such as spatial flux
-        and temperature profiles, will require more detailed experimental measurements
-        than those available in the \gls{ORNL} technical reports, which contain only
-        macroscopic data such as steady-state power and heat-exchanger temperature
-        drops. Additionally, detailed comparison with other modern modeling efforts such
-        as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
-        desirable. In that vein, a collaboration is under way with the primary author of
-        \cite{aufiero_develoment_2014} to try and reproduce calculation results from
-        OpenFOAM. We hope to publish the results of this comparison in a future work.
+        Although the qualitative agreement is decent, there are discrepancies
+        between the \gls{MSRE} and Moltres calculations. As outlined above there
+        is an 11 K offset between \gls{MSRE} and Moltres calculations for the
+        fuel temperature in the hottest channel. The peak graphite temperature
+        is around 14 K larger in the Moltres calculation. Fast fluxes are larger
+        in the \gls{MSRE} calculation by roughly 20\%. These are not
+        insignificant differences. However, given the differing nature of the
+        two models--no axial conduction in the \gls{MSRE} model, 2-group vs
+        32-group neutronics, exclusion of the control rod thimbles in the
+        Moltres calculation--we believe this variation in quantitative behavior
+        is acceptable for the purpose of this work, which is to introduce
+        Moltres as a simulation tool. One additional feature that could
+        influence Moltres results is inclusion of precursor decay heat; this is
+        under active development. Trustworthy verification of Moltres results,
+        such as spatial flux and temperature profiles, will require more
+        detailed experimental measurements than those available in the
+        \gls{ORNL} technical reports, which contain only macroscopic data such
+        as steady-state power and heat-exchanger temperature
+        drops. Additionally, detailed comparison with other modern modeling
+        efforts such as that conducted in
+        \cite{aufiero_development_2014,laureau_transient_2017} is desirable. In
+        that vein, a collaboration is under way with the primary author of
+        \cite{aufiero_develoment_2014} to try and reproduce calculation results
+        from OpenFOAM. We hope to publish the results of this comparison in a
+        future work.
 \end{solution}

### 2017-11-27 Moltres.tex
Add mesh convergence to Moltres.tex.

@@
 radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
-for the \gls{MSRE}.
+for the \gls{MSRE}. The 2D mesh has a characteristic size of 10 cm in the axial
+direction and .4 cm in the radial direction to capture the variation from moving
+between fuel and moderator subdomains. Solution time on the resulting 1960
+element, 8697 DOF problem is a couple minutes on a single core. Solving on a
+mesh uniformly refined three times yields the same qualitative behavior
+described in the results that follow for the coarse mesh. Additionally the 3x
+refinement yielded only a 1 K change in the average reactor temperature; thus,
+the coarse mesh results are regarded as sufficiently converged.
 

### 2017-11-27 Moltres.tex

@@
 the inclusion of the \gls{MSR} among the Generation-IV reactor designs
-\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained
-renewed research interest in the past decade, with many new nuclear companies
-proposing both fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
+\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
+interest in the past decade, with many new nuclear companies proposing both
+fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
 \cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}.
-Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
-utilization and no radiation damage constraint on attainable fuel
-burn-up. Together these attributes can result in significantly reduced spent
-fuel mass and, in the case of fluoride salt reactors in particular, reduced core
-fissile inventories \cite{gif_generation_2008,gif_generation_2015}.  Due to
-these characteristics, the \gls{MSR} is potentially uniquely capable of burning
-actinides and extending fuel resources.
+The key advantages of \gls{MSR}s generally pertain to improved fuel utilization
+and reactor safety. In contrast to legacy reactors, only moderator fast neutron
+damage and fuel chemistry evolution limit burnup. A clever configuration of moderator
+as in \cite{engel_conceptual_1980} can enable reactor operation without opening the vessel
+for thirty or more years. Further, several fission products selectively precipitate onto
+nickel surfaces in fluoride salt, as documented in \cite{engel_conceptual_1980}, thus reducing
+unwanted neutron absorption. Lastly, the epithermal spectrum of graphite-moderated salt reactors
+incinerates plutonium more efficiently, thus reducing long-lived transuranic waste production \cite{engel_conceptual_1980}.
+The sum of these characteristics implies the \gls{MSR} uniqely ameliorates spent fuel burden whilst
+extending nuclear fuel resources. To top all these benefits off, xenon transients become moot in
+\gls{MSR}s due to its insolubility in salt, thus narrowing transient analysis focus to thermalhydraulic
+concerns.
 

### 2017-11-27 revise/revise.tex
Add to revise.tex about mesh convergence. Closes #41

@@
 \begin{solution}
-       <++>
+       The following passage has been added:
+
+       The 2D mesh has a characteristic size of 10 cm in the axial
+       direction and .4 cm in the radial direction to capture the variation from moving
+       between fuel and moderator subdomains. Solution time on the resulting 1960
+       element, 8697 DOF problem is a couple minutes on a single core. Solving on a
+       mesh uniformly refined three times yields the same qualitative behavior
+       described in the results that follow for the coarse mesh. Additionally the 3x
+       refinement yielded only a 1 K change in the average reactor temperature; thus,
+       the coarse mesh results are regarded as sufficiently converged.
 \end{solution}

### 2017-11-27 Moltres.tex
Update Moltres.tex

@@
 \cite{aufiero_develoment_2014} to try and reproduce calculation results from
-OpenFOAM. We hope to publish the results of this comparison in a future work.
+OpenFOAM. Further, Dr. Collins from \cite{turner_virtual_2016} has expressed interest
+in comparing Moltres results against MSR-VERA in order to quantify errors resulting
+from usage of multigroup diffusion in comparison to 2D-1D method of characteristics fine group solutions.
+We hope to publish the results of these comparisons in a future work.
 

### 2017-11-27 Moltres.tex
Time steps without hyphen
Substitute new plots from twice refined grid.

--- 2017-11-27 Moltres.tex
@@
 radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
-for the \gls{MSRE}. The 2D mesh has a characteristic size of 10 cm in the axial
+for the \gls{MSRE}. The base 2D mesh has a characteristic size of 10 cm in the axial
 direction and .4 cm in the radial direction to capture the variation from moving
-between fuel and moderator subdomains. Solution time on the resulting 1960
-element, 8697 DOF problem is a couple minutes on a single core. Solving on a
-mesh uniformly refined three times yields the same qualitative behavior
-described in the results that follow for the coarse mesh. Additionally the 3x
-refinement yielded only a 1 K change in the average reactor temperature; thus,
-the coarse mesh results are regarded as sufficiently converged.
+between fuel and moderator subdomains. To determine whether results were
+converged, a mesh convergence study was conducted with up to three levels of isotropic
+refinement (e.g. each element was in half in both axial and radial directions,
+resulting in four new elements). The metric used to assess convergence was the integrated fast group
+flux. The result of the mesh convergence study is shown in
+\cref{fig:mesh_convergence}. From refinement level 2 to 3 the metric changes by
+only 1\%. We regard the results as sufficiently converged at level 2 for the
+purposes of our study; consequently, the results reported in the following
+section correspond to a radial element dimension of .1 cm and an axial element
+dimension of 2.5 cm.
 
@@
   \caption{A sketch of the \gls{MSR} model geometry}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{mesh_convergence.eps}
+  \label{fig:mesh_convergence}
+  \caption{Plot of the integrated fast group flux as the mesh in isotropically refined.}
 \end{figure}

### 2017-11-27 revise/revise.tex
Substitute new plots from twice refined grid.

--- 2017-11-27 revise/revise.tex
@@
 \begin{solution}
-       <++>
+       The following passage and a corresponding figure have been added:
+
+       The base 2D mesh has a characteristic size of 10 cm in the axial
+       direction and .4 cm in the radial direction to capture the variation from moving
+       between fuel and moderator subdomains. To determine whether results were
+       converged, a mesh convergence study was conducted with up to three levels of isotropic
+       refinement (e.g. each element was split in half in both axial and radial directions,
+       resulting in four new elements). The metric used to assess convergence was the integrated fast group
+       flux. The result of the mesh convergence study is shown in
+       \cref{fig:mesh_convergence}. From refinement level 2 to 3 the metric changes by
+       only 1\%. We regard the results as sufficiently converged at level 2 for the
+       purposes of our study; consequently, the results reported in the following
+       section correspond to a radial element dimension of .1 cm and an axial element
+       dimension of 2.5 cm.
 \end{solution}

### 2017-11-27 Moltres.tex

@@
 solution could not be achieved using the segregated method. After 670
-time-steps, the Picard solve hits the maximum number of allowed iterations (100)
+time steps, the Picard solve hits the maximum number of allowed iterations (100)
 after only halving the neutronics residual. Before reaching the fail-point, the

### 2017-11-27 Moltres.tex
Remove Dr. from Dr. Collins.

@@
 \cite{aufiero_develoment_2014} to try and reproduce calculation results from
-OpenFOAM. Further, Dr. Collins from \cite{turner_virtual_2016} has expressed interest
+OpenFOAM. Further, Collins from \cite{turner_virtual_2016} has expressed interest
 in comparing Moltres results against MSR-VERA in order to quantify errors resulting

### 2017-11-27 revise/revise.tex
Make revision compile.

@@
 \begin{solution}
-        We have edited this sentence to read ``Together these attributes can
-        result in significantly reduced spent fuel mass and, in the case of
-        fluoride salt reactors in particular, reduced core fissile
-        inventories'', recognizing that you're quite correct for the chloride salts.
+        This passage has been modified to read:
+
+        The key advantages of MSRs generally pertain to improved fuel
+        utilization and reactor safety. In contrast to legacy reactors, only
+        moderator fast neutron damage and fuel chemistry evolution limit
+        burnup. A clever configuration of moderator as in
+        \cite{engel_conceptual_1980} can enable reactor operation without
+        opening the vessel for thirty or more years. Further, several fission
+        products selectively precipitate onto nickel surfaces in fluoride salt,
+        as documented in \cite{engel_conceptual_1980}, thus reducing unwanted
+        neutron absorption. Lastly, the epithermal spectrum of
+        graphite-moderated salt reactors incinerates plutonium more efficiently,
+        thus reducing long-lived transuranic waste production
+        \cite{engel_conceptual_1980}.  The sum of these characteristics implies
+        the MSR uniqely ameliorates spent fuel burden whilst extending
+        nuclear fuel resources. To top all these benefits off, xenon transients
+        become moot in MSRs due to its insolubility in salt, thus
+        narrowing transient analysis focus to thermalhydraulic concerns.
+
 \end{solution}
@@
 Fast Reactor transient analysis, Chemical Engineering Science, Volume 111, 2014,
-Pages 390-401, ISSN 0009-2509, http://dx.doi.org/10.1016/j.ces.2014.03.003.
-(http://www.sciencedirect.com/science/article/pii/S0009250914001146)
+Pages 390-401, ISSN 0009-2509
 
@@
 and analysis of the MSFR transient behaviour, Annals of Nuclear Energy, Volume
-64, 2014, Pages 485-498, ISSN 0306-4549,
-http://dx.doi.org/10.1016/j.anucene.2013.08.003.
-(http://www.sciencedirect.com/science/article/pii/S0306454913004118)
+64, 2014, Pages 485-498, ISSN 0306-4549
 
@@
 Multiscale modelling approach to the analysis of MSR plant dynamics, Progress in
-Nuclear Energy, Volume 83, 2015, Pages 82-98, ISSN 0149-1970,
-http://dx.doi.org/10.1016/j.pnucene.2015.02.014.
+Nuclear Energy, Volume 83, 2015, Pages 82-98, ISSN 0149-1970
 
@@
 Transient Fission Matrix approach, Nuclear Engineering and Design, Volume 316,
-2017, Pages 112-124, ISSN 0029-5493,
-http://dx.doi.org/10.1016/j.nucengdes.2017.02.022.
+2017, Pages 112-124, ISSN 0029-5493
 
@@
         colleagues conducted a benchmarking exercise
-        \cite{fiorina_modelling_2013} in
+        \cite{fiorina_modelling_2014} in
         which this Politecnico di Milano approach was expanded to a
@@
         of the MSFR and compared to code from the University of Delft
-        \cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach
+        \cite{de_zwaan_static_2007,van_der_linden_coupled_2012} based on the approach
         in
@@
 
-        In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f
-        \diff V$, where $\gamma$ is a factor representing heat dissipation by
+        In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f dV$,
+        where $\gamma$ is a factor representing heat dissipation by
         gamma and neutron irradiation in the moderator, called the graphite to
         fuel power density ratio. Robertson's \cite{robertson_conceptual_1971}
-        original \gls{MSBR} analysis included a calculation of $\gamma$.
+        original MSBR analysis included a calculation of $\gamma$.
         \cite{krepel_dyn3d-msr_2007,zhang_development_2009,cammi_multi-physics_2011}
@@
        flux. The result of the mesh convergence study is shown in
-       \cref{fig:mesh_convergence}. From refinement level 2 to 3 the metric changes by
+       figure []. From refinement level 2 to 3 the metric changes by
        only 1\%. We regard the results as sufficiently converged at level 2 for the
@@
         Although the qualitative agreement is decent, there are discrepancies
-        between the \gls{MSRE} and Moltres calculations. As outlined above there
-        is an 11 K offset between \gls{MSRE} and Moltres calculations for the
+        between the MSRE and Moltres calculations. As outlined above there
+        is an 11 K offset between MSRE and Moltres calculations for the
         fuel temperature in the hottest channel. The peak graphite temperature
         is around 14 K larger in the Moltres calculation. Fast fluxes are larger
-        in the \gls{MSRE} calculation by roughly 20\%. These are not
+        in the MSRE calculation by roughly 20\%. These are not
         insignificant differences. However, given the differing nature of the
-        two models--no axial conduction in the \gls{MSRE} model, 2-group vs
+        two models--no axial conduction in the MSRE model, 2-group vs
         32-group neutronics, exclusion of the control rod thimbles in the
@@
         detailed experimental measurements than those available in the
-        \gls{ORNL} technical reports, which contain only macroscopic data such
+        ORNL technical reports, which contain only macroscopic data such
         as steady-state power and heat-exchanger temperature
@@
         that vein, a collaboration is under way with the primary author of
-        \cite{aufiero_develoment_2014} to try and reproduce calculation results
+        \cite{aufiero_development_2014} to try and reproduce calculation results
         from OpenFOAM. We hope to publish the results of this comparison in a
@@
 \bibliographystyle{unsrt}
-\bibliography{Moltres}
+\bibliography{revise}
   \end{document}

### 2018-04-06 bw-prop.tex
I misspelled waters.
final edits

@@
 %\rhead{}
-\lhead{\textcolor{gray}{Investigator: Prof. \authorname\\Presenter: Dr. Alexander Lindsay}}
+\lhead{\textcolor{gray}{Investigator: Prof. \authorname\\Presenter: Mr. Andrei Rykhlevskii}}
 \rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles\\}}
@@
 
+Additionally, we have developed 
+an online reprocessing model, SaltProc which includes fission product removal, fissile material 
+separations, and refuelling for time dependent analysis of fuel-salt evolution. 
+This tool relies on full-core high-fidelity Monte Carlo simulations perform depletion 
+computations.
+
 \paragraph{Role of Blue Waters}
@@
 temporal resolution are only possible with the aid of high performance
-computing resources.  To solve these large systems of partial differential
+computing resources.  
+To solve these large systems of partial differential
 equations on a finite element mesh in a fully-coupled, implicit way, the MOOSE
@@
 adaptive meshing.  These simulations are memory intensive, so the exceptional
-memory capability of the Blue Waters resource will be essential to performant
-simulation times. It is also important to note that rendering visualizations of
-the results can be computationally intensive was well.
+memory capability of the Blue Waters resource has been essential to performant
+simulation times.
 
@@
 
-Initial simulations of the MSRE have been conducted both locally on the desktop
-computer scale and on Blue Wates. These have been steady state simulations and
-have occupied up to many hundreds of nodes simultaneously. This talk will
+Initial simulations of the Molten Salt Reactor Experiment and the conceptual 
+Molten Salt Breeder Reactor have been conducted both locally on the desktop
+computer scale and on Blue Waters with deterministic multiphysics and monte 
+carlo methods respectively. Steady state, transient, and fuel cycle analysis 
+simulations have been run in 2D as well as 3D. These simulations
+have occupied up to many hundreds of nodes simultaneously and have resulted in 
+rich datasets for use in reactor design and analysis. This talk will
 describe how coupling between neutronics and thermal hydraulics have been
-established in the Moltres tool as well as the validation and verification
-efforts which are ongoing.
+established in the Moltres and SaltProc tools, as well as the validation 
+and verification efforts which have been completed.
 
-In the near term, these steady state calculations will provide the initial
-conditions for full core reactor transient simulations. Such simulations
-commonly occupy tens of thousands of CPU cores at a time and vary in completion
-time. The MOOSE framework is shown to scale very well up to 10,000 cores.
+The MOOSE framework is shown to scale very well up to 10,000 cores and Moltres 
+scaling studies on Blue Waters have followed suit.
 Transient and multi-scale simulations, which require greater capability per
-simulation, may occupy up to 100,000 CPU cores at a time. Such transient
-simulations will evaluate the safety performance of advanced reactors in severe
+simulation, can occupy thousands of CPU cores at a time. Such transient
+simulations evaluate the safety performance of advanced reactors in severe
 (beyond design basis) accidents.
 
+Fuel cycle dynamics and quasi-equilibrium compositions were obtained 
+from depletion and reprocessing simulations for a 10-year time frame. The 
+MSBR full-core safety analysis was performed at the initial and equilibrium 
+fuel salt compositions, for various reactor safety parameters such as effective 
+multiplication factor, neutron flux distributions, temperature coefficients, 
+rod worths, power and breeding distributions.
+
 \paragraph{Potential Impact}
-Detailed spatially and temporally resolved neutron flux and
-temperature distributions can improve designs, help characterize
-performance, inform reactor safety margins, and enable validation of numerical
-modeling techniques for unique physics.
-Future work may include similarly challenging materials and geometries such as
-those in sodium cooled, gas cooled, and very high temperature reactor designs
-which also boast improved safety and sustainability.
+Current interest in advanced nuclear energy systems and molten salt reactor 
+(MSR) concepts have reinforced interest in building tools to modeling these 
+systems.  Detailed spatially and temporally resolved neutron flux and 
+temperature distributions can improve designs, help characterize performance, 
+inform reactor safety margins, and enable validation of numerical modeling 
+techniques for unique physics.  Future work may include similarly challenging 
+materials and geometries such as those in sodium cooled, gas cooled, and very 
+high temperature reactor designs which also boast improved safety and 
+sustainability.
 
+\begin{figure}[ht]
+        \begin{center}
+                \includegraphics{breed_dens.png}
+        \end{center}
+        \caption{High fidelity monte carlo solutions of breeding density in the
+                Molten Salt Breeder Reactor is at the heart of fuel cycle 
+        analysis on Blue Waters.}
+        \label{fig:breed_dens}
+\end{figure}
 \end{document}

### 2018-04-10 bw-abstract.tex
Abstract for BW 2018 conference added

--- 2017-02-23 bw-prop.tex
@@
 %\rhead{}
-\lhead{\textcolor{gray}{Investigator: Prof. \authorname\\Presenter: Dr. Alexander Lindsay}}
-\rhead{\textcolor{gray}{Advanced Reactors and Fuel Cycles\\}}
+\lhead{\textcolor{gray}{Investigator: Prof. \authorname\\Presenter: Mr. Andrei Rykhlevskii}}
+\rhead{\textcolor{gray}{University of Illinois at Urbana-Champaign\\}}
 %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
@@
 \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}
+   \begin{center}
+      \Large\textbf{Computational tools for advanced Molten Salt Reactors simulation}\\
+   \end{center}
 
-\paragraph{Research Goal}
+The Advanced Reactors and Fuel Cycles (ARFC) group models and simulates the design, safety, and performance of advanced nuclear reactors.
+Such reactors  involve tight coupling between physics such as thermal-hydraulic phenomena, neutron transport, and fuel performance.
+Current work introduces an extension of the MOOSE framework, Moltres, to appropriately model coupled thermal-hydraulics and neutronics of promising molten-salt-fueled reactor designs.
+Additionally, we have developed an online reprocessing simulation tool, SaltProc which includes fission product removal, fissile material separations, and refuelling for time dependent analysis of fuel-salt evolution.
 
-The Advanced Reactors and Fuel Cycles (ARFC) group pursues improved safety and
-sustainability of nuclear power. To do so, we model and
-simulate the design, safety, and performance of advanced nuclear reactors.
-Such reactors  involve tight coupling between physics such as thermal-hydraulic
-phenomena, neutron transport, and fuel performance.
-
-The current state of the art in advanced nuclear reactor simulation (e.g. the
-CASL DOE innovation hub) is focused on traditional light water reactors.
-The ARFC group seeks to extend that state of the art by enabling similarly high fidelity simulation of more advanced reactor designs through development of models and tools for representing unique materials, geometries, and physical phenomena.
-Current work includes extension
-of the MOOSE framework to appropriately model coupled thermal-hydraulics and
-neutronics of promising molten salt fuelled reactor designs.
-ARFC develops physics kernel extensions and runs simulations using the highly
-scalable, fully implicit, Multiphysics Object-Oriented Simulation Environment
-(MOOSE) framework from Idaho National Laboratory.
-
-\paragraph{Role of Blue Waters}
-Simulations which faithfully capture this coupling at realistic spatial and
-temporal resolution are only possible with the aid of high performance
-computing resources.  To solve these large systems of partial differential
-equations on a finite element mesh in a fully-coupled, implicit way, the MOOSE
-framework was designed to take advantage of high performance computing
-capability.  The framework conducts fully implicit physics coupling with a
-Jacobian Free Newton Krylov (JFNK) solver method and sophisticated automatic
-adaptive meshing.  These simulations are memory intensive, so the exceptional
-memory capability of the Blue Waters resource will be essential to performant
-simulation times. It is also important to note that rendering visualizations of
-the results can be computationally intensive was well.
-
-\paragraph{Progress}
-
-Initial simulations of the MSRE have been conducted both locally on the desktop 
-computer scale and on Blue Wates. These have been steady state simulations and 
-have occupied up to many hundreds of nodes simultaneously. This talk will 
-describe how coupling between neutronics and thermal hydraulics ahve been 
-established in the Moltres tool as well as the validation and verification 
-efforts which are ongoing.
-
-In the near term, these steady state calculations will provide the initial 
-conditions for full core reactor transient simulations. Such simulations 
-commonly occupy tens of thousands of CPU cores at a time and vary in completion 
-time. The MOOSE framework is shown to scale very well up to 10,000 cores. 
-Transient and multi-scale simulations, which require greater capability per 
-simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those 
-larger simulations are likely to be run this year..
-
-\paragraph{Potential Impact}
-Detailed spatially and temporally resolved neutron flux and
-temperature distributions can improve designs, help characterize
-performance, inform reactor safety margins, and enable validation of numerical
-modeling techniques for unique physics.
-Future work may include similarly challenging materials and geometries such as
-those in sodium cooled, gas cooled, and very high temperature reactor designs
-which also boast improved safety and sustainability.
+Initial simulations of the Molten Salt Reactor Experiment and the conceptual 
+Molten Salt Breeder Reactor have been conducted on Blue Waters with deterministic multiphysics and Monte Carlo methods respectively.
+Steady state, transient, and fuel cycle analysis simulations have been run in 2D as well as 3D and compared against the Molten Salt Reactor Experiment.
+Fuel cycle dynamics and quasi-equilibrium compositions were obtained from depletion and reprocessing simulations for a 20-year time frame.
+The MSBR full-core safety analysis was performed at the startup and equilibrium fuel salt compositions, for important reactor safety parameters.
+In this work, conducted on Blue Waters, ARFC has demonstrated the capability to model complex physics in an advanced molten-salt-fueled nuclear reactor.
 

### 2018-08-26 siam-moltres-abstract.tex
Abstract ready

--- 2018-04-10 bw-abstract.tex
@@
    \begin{center}
-      \Large\textbf{Computational tools for advanced Molten Salt Reactors simulation}\\
+      \Large\textbf{Simulation of Molten Salt Reactors with Moltres}\\
    \end{center}
@@
 The Advanced Reactors and Fuel Cycles (ARFC) group models and simulates the design, safety, and performance of advanced nuclear reactors.
-Such reactors  involve tight coupling between physics such as thermal-hydraulic phenomena, neutron transport, and fuel performance.
-Current work introduces an extension of the MOOSE framework, Moltres, to appropriately model coupled thermal-hydraulics and neutronics of promising molten-salt-fueled reactor designs.
-Additionally, we have developed an online reprocessing simulation tool, SaltProc which includes fission product removal, fissile material separations, and refuelling for time dependent analysis of fuel-salt evolution.
+For these simulations coupling between physics such as neutron transport, thermal-hydraulics phenomena, and fuel performance must be taken into account.
+Our group performs high fidelity simulation of Gen IV reactor designs through development of models and tools for representing unique materials, complex geometries, and physical phenomena.
+Current work introduces an extension of the MOOSE framework, Moltres, to appropriately model coupled thermal-hydraulics and neutronics of promising liquid-fueled Molten Salt Reactor designs.
 
-Initial simulations of the Molten Salt Reactor Experiment and the conceptual 
-Molten Salt Breeder Reactor have been conducted on Blue Waters with deterministic multiphysics and Monte Carlo methods respectively.
+Initial simulations of the Molten Salt Reactor Experiment have been conducted on Blue Waters supercomputer with deterministic multiphysics.
 Steady state, transient, and fuel cycle analysis simulations have been run in 2D as well as 3D and compared against the Molten Salt Reactor Experiment.
-Fuel cycle dynamics and quasi-equilibrium compositions were obtained from depletion and reprocessing simulations for a 20-year time frame.
-The MSBR full-core safety analysis was performed at the startup and equilibrium fuel salt compositions, for important reactor safety parameters.
-In this work, conducted on Blue Waters, ARFC has demonstrated the capability to model complex physics in an advanced molten-salt-fueled nuclear reactor.
+These simulations
+have occupied up to many hundreds of nodes simultaneously and have resulted in rich datasets
+for use in reactor design and analysis.
+This talk will describe how coupling between neutronics and thermal hydraulics have been established in the Moltres as well as the validation and verification efforts which have been completed.
 
